### 2020-11-18 main.tex
AWR introduction submission

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}

% How to write a paper:
% https://mj.ucw.cz/papers/jakpsat.pdf
% Jones 2016: https://www.microsoft.com/en-us/research/academic-program/write-great-research-paper/
% AWR: https://jazyky.fel.cvut.cz/vyuka/RPP/BE9M04AKP/

% PAAR paper: https://github.com/filipbartek/learning-precedences-from-elementary-symbol-features/releases/download/paar2020%2Fceur-2/Learning_Precedences_from_Simple_Symbol_Features.pdf

% TODO: Compare to bag-of-words model.

\input{preamble}

\begin{document}

\maketitle

\begin{abstract}
\input{abstract}
\end{abstract}

\section{Introduction}

\input{introduction}

\section{Preliminaries}
% Terminology

\section{Architecture}
\label{sec:architecture}

\subsection{Layers}

\begin{enumerate}
\item Problem -> symbol embeddings
\item Symbol embedding -> symbol cost
\item Symbol costs -> precedence cost
\end{enumerate}

\subsection{Cost models}

%Let $\CostSym: \symbols \rightarrow \re$ be a differentiable symbol cost model.

We define precedence cost:
$$
\CostPrec(\pi) =
C \sum_{1 \leq i \leq n} \CostSym(\pi(i)) \cdot i =
C \sum_{1 \leq i \leq n} \CostSym(s_i) \cdot \inv{\pi}(s_i)
$$
Precedence cost is minimized by $\pi$ that orders the symbols by their costs in non-decreasing order.

Note that we can weight the symbols with an arbitrary non-decreasing function $f$ of symbol index:
$$
\CostPrec(\pi) =
C \sum_{1 \leq i \leq n} \CostSym(\pi(i)) \cdot f(i) =
C \sum_{1 \leq i \leq n} \CostSym(s_i) \cdot f(\inv{\pi}(s_i))
$$

We set $C = \frac{2}{n(n+1)}$ so that $\CostSym(s) = 1$ for all $s$ implies $\CostPrec(\pi) = 1$ for all $\pi$.

We define precedence pair cost:
$$
\CostPrecPair(\pi_0, \pi_1) =
\CostPrec(\pi_0) - \CostPrec(\pi_1) =
C \sum_{1 \leq i \leq n} \CostSym(s_i) \cdot [\inv{\pi_0}(s_i) - \inv{\pi_1}(s_i)]
$$
Clearly $\CostPrecPair(\pi_0, \pi_1) < 0$ iff $\CostPrec(\pi_0) < \CostPrec(\pi_1)$.
For a pair of precedences about which we know that $\pi_0$ is better than $\pi_1$,
we want $\CostPrecPair(\pi_0, \pi_1) < 0$.

We model the probability of misclassification of precedence pair $\pi_0, \pi_1$
such that $\pi_0$ is better than $\pi_1$
by the sigmoid of $\CostPrecPair(\pi_0, \pi_1)$:
$$
L(\pi_0, \pi_1) = \sigmoid(\CostPrecPair(\pi_0, \pi_1))
$$

\section{Evaluation}
\label{sec:evaluation}

\section{Related work}

\section{Conclusion}

\bibliography{main}

\end{document}

### 2020-12-11 awr_body.tex
AWR body submission

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}

% Academic Writing
% https://jazyky.fel.cvut.cz/vyuka/RPP/BE9M04AKP/

% How to export to DOCX: Export to PDF and then load the PDF in Word.

\usepackage[disable]{todonotes}

\input{preamble}

\begin{document}

\maketitle

\section{Example body paragraph}

Simplification ordering on terms
influences the proof search in \vampire{} on two levels.
First, the inferences on each clause are limited
to the selected literals.
In each clause,
either a negative literal or all the maximal literals are selected.
The maximality is evaluated
according to the simplification ordering.
% Note: The selection function Total does not use the simplification ordering.
Second, simplification ordering orients some of the equalities
to prevent superposition and equality factoring
from inferring redundant complex conclusions.
In each of these two roles,
the simplification ordering may impact the direction and,
in effect, the length of the proof search.

\end{document}

### 2020-12-11 introduction.tex
AWR body submission

% General motivation for FOL ATPing:
% Vampire is used as a sledgehammer in Isabelle/HOL:
% 1. https://people.mpi-inf.mpg.de/~jblanche/life.pdf
% 2. https://www.cl.cam.ac.uk/~lp15/papers/Automation/paar.pdf
% Formal methods for verification (survey): https://arxiv.org/pdf/1912.03028.pdf

\todo[author=Filip,inline]{Consider an alternative approach: Start with an example problem, rewrite in two ways, describe how do state-of-the-art provers differentiate between these two ways (by symbol precedence), ...}

% Jones 2016 guidelines:
% 1. Problem (explain by example)
% 2. Contributions (refutable, forward references to sections)

% AWR structure (Unit 7, page 1):
% 1. Attention-getter (lead-in) [1-2 sentences]
% 2. Set up for the thesis [minimum: 2-3 sentences]
% 3. Thesis statement (essay map) [1 sentence]

% AWR guidelines (Unit 7, page 5):
% Whet the reader's appetite
% Set the context
% State why the main idea is important
% State your thesis/claim

A \gls{fol} problem consists of \gls{fol} formulas divided into two categories:
one or more premises and one conjecture.
% We assume that \gls{fol} is expanded to FOL.
% For this reason the article is "an".
When presented with an \gls{fol} problem,
a \definiendum{saturation-based} \gls{atp} negates the conjecture (as a first step of proof by contradiction)
and converts all the formulas into an equisatisfiable set of clauses in \gls{cnf}.
\todo[author=Filip]{Are there any saturation-based ATPs that don't use CNF?}
The prover proceeds to iteratively infer new provable clauses
until a contradiction, represented by the empty clause, is inferred,
or until no new clauses can be inferred.
A proof of the fact that the premises and the negated conjecture entail a contradiction
constitutes a proof that the premises entail the conjecture.
\todo[author=Filip]{Cite some source that explains refutation-based automated theorem proving. Perhaps Harris?}
\todo[author=Martin]{prvni odstavec uvodu bych pro CADE publikum vynechal a zacal rovnou s druhym}

The state-of-the-art \gls{fol} \glspl{atp},
such as \vampire{} \cite{10.1007/978-3-642-39799-8_1} and E \cite{10.1007/978-3-030-29436-6_29},
are saturation-based and
infer new provable clauses by applying the rules of \definiendum{superposition calculus}.
\todo[author=Filip]{Cite some source that explains superposition calculus.}
The inferences under superposition calculus are constrained by a \definiendum{simplification ordering on the terms}.
\todo[author=Filip]{Do we mean terms in sensu stricto (applications of functions), or generalized terms (applications of functions and predicates)?}
The two classes of simplification orderings commonly used in practice are
\gls{lpo} \cite{Kamin1980} and \gls{kbo} \cite{Knuth1983}.
In both classes the ordering is specified by a \definiendum{symbol precedence},
\todo[author=Filip]{This may be an oversimplification: KBO is further parameterized by symbol weights.}
which is a permutation of predicate and function symbols of the input problem.

The typical approach to constructing a symbol precedence orders the symbols by a property
that is relatively cheap and straightforward to compute,
such as the frequency (the number of occurrences in the input problem) \cite{E-manual} or the arity.
\todo[author=Filip]{Cite the original source of the arity heuristic.}
The structure of the problem contains much information that is relevant for the choice of symbol precedence,
but is completely ignored by the symbol properties that inform the symbol precedences.
\todo[author=Filip]{Why do we believe this?}
\todo[author=Martin]{Klicovou vetu ... by asi chtelo rozvest treba do celeho odstavce. Takhle vyzni dost krypticky a neni moc jasne, co se snazi vyjadrit: "The structure of the problem" neni predem vysvetleno. "completely ignored" - "ignored" trosku zavani nejakym agentem, pritom je zde predmetem neziva vec / abstraktum}

This paper describes the architecture (\cref{sec:architecture}) and an empirical evaluation (\cref{sec:evaluation})
of a symbol precedence heuristic based on a \gls{gcn} \cite{kipf2017semisupervised}
and trained on proof attempts with random symbol precedences.
The experiments presented in \cref{sec:evaluation} demonstrate an improvement of success rate by 20 \%
compared to the state-of-the-art heuristic.
\todo[author=Martin]{Poslednimyu ostaveci by taky asi jeste mohlo neco predhazet, aby to mohl shrnout: "the architecture" ma urcity clen, ale predtim zadna "architecture" jeste neni. "graph convolution network" taky vlastne zminujes poprve}

% Filip: I decided not to follow the AWR structure in favor of Martin and CADE.

\iffalse % AWR draft

The performance of the state-of-the-art \acrfullpl{atp} is severely limited by some of the design decisions that constitute the provers' architecture.
For example, the \frequency{} symbol precedence heuristic of the \acrfull{fol} \acrshort{atp} \vampire{} is easily outperformed by the best of 10 random precedences.\cite{}
The gap in performance suggests that a more elaborate precedence heuristic with a superior performance exists.
% what is precedence heuristic?
% Thesis statement
Training a model from proof attempts with random precedences yields a heuristic that significantly outperforms the state-of-the-art heuristic.

\fi

### 2020-12-11 main.tex
AWR body submission

@@
 
+\usepackage[pdf]{graphviz}
+
 \begin{document}
@@
 
+\vampire{} \cite{10.1007/978-3-642-39799-8_1}
+is representative
+of the state-of-the-art \gls{fol} \gls{atp} design.
+\vampire{} was awarded the first place
+in the \gls{fol} category of \gls{casc} \cite{},
+an annual international competition of \glspl{atp},
+in eleven times in the years between 2010 and 2020 \cite{}.
+Moreover, 7 of 10 provers that have placed in the top 50 \% in 2020
+are saturation-based, refutation-based and resolution-based,
+similarly to \vampire{} \cite{}.
+
+%\vampire{} is a saturation-based prover.
+%Given a \gls{fol} problem,
+%\vampire{} converts the problem into \gls{cnf}.
+%and proceeds to saturate the set of clauses
+%by repeated application of inference rules.
+
+%\vampire{} searches for a proof by applying the rules
+%of the superposition inference system
+%\cite{10.1007/978-3-642-39799-8_1}.
+
+% AWR candidate
+Proof search in \vampire{} is crucially constrained
+by a simplification ordering on terms.
+Being refutation-based and saturation-based,
+\vampire{} searches for contradiction
+by iteratively inferring clauses provable from the input clauses.
+The inferences
+
+explores the space of clauses provable
+from the input formulas
+by applying rules of superposition inference system.
+This process continues until a contradiction is inferred,
+the processed clauses set is saturated
+or the execution hits a resource limit.
+
+During proof search,
+\vampire{} explores the space of provable clauses
+by applying inference rules to clauses
+that have already been proven.
+
+% AWR candidate
+Simplification ordering on terms
+influences the proof search in \vampire{} on two levels.
+First, the inferences on each clause are limited
+to the selected literals.
+In each clause,
+either a negative literal or all the maximal literals are selected.
+The maximality is evaluated
+according to the simplification ordering.
+% Note: The selection function Total does not use the simplification ordering.
+Second, simplification ordering orients some of the equalities
+to prevent superposition and equality factoring
+from inferring redundant complex conclusions.
+In each of these two roles,
+the simplification ordering may impact the direction and,
+in effect, the length of the proof search.
+
+The inference system used in the state-of-the-art \gls{fol} \gls{atp} \vampire{}
+is parameterized by a simplification ordering on terms.
+\vampire{} uses superposition inference system \cite{}.
+
+The \gls{atp} \vampire{} uses superposition inference system.
+
+Vampire supports two simplification term ordering classes:
+\gls{lpo} and \gls{kbo}.
+
+The superposition inference system \cite{} used in Vampire is parameterized
+by symbol precedence.
+
+% Example: It seems that a classical example for KBO an orienting equations is group theory axioms.
+
+The choice of symbol precedence may affect the length of a proof search to a great extent.
+
+Given a \gls{fol} problem,
+determining a symbol precedence that leads to a fast proof search is a non-trivial task.
+
 \section{Architecture}
@@
 
+This section describes the architecture of a precedence recommender system.
+When presented with a \gls{fol} problem $P$ with symbols $\symbols$,
+the system predicts a symbol precedence $\pi$ on $\symbols$
+that is expected to lead to a successful proof search.
+
+\subsection{Prediction pipeline}
+
+\subsection{Training pipeline}
+
+\begin{figure}[ht]
+\caption{Architecture overview}
+\centering
+\digraph[scale=0.4]{precedencepairclassifierdetailed}{
+	graph [splines=ortho];
+	node [shape=renctangle, fontsize=20];
+	edge [fontsize=20];
+	fol [label="FOL problem", shape=oval];
+	pi0 [shape=oval, label=<&pi;<SUB>0</SUB>>];
+	pi1 [shape=oval, label=<&pi;<SUB>1</SUB>>];
+	invpi0 [label=<&pi;<SUB>0</SUB><SUP>-1</SUP>>];
+	invpi1 [label=<&pi;<SUB>1</SUB><SUP>-1</SUP>>];
+	cnf [label="Clause normal form (CNF)"];
+	symbolembeddings [label="Symbol embeddings"];
+	symbolcosts [label="Symbol costs"];
+	pi1pi0 [label="Inverse precedence difference"];
+	normalized [label="Normalized inverse precedence difference"];
+	paircost [label="Precedence pair cost"];
+	fol -> cnf [xlabel=" Vampire "];
+	cnf -> symbolembeddings [xlabel=< <B>Graph Convolution Network</B> >];
+	symbolembeddings -> symbolcosts [xlabel=< <B>Feed-forward neural network</B> >, style=bold];
+	symbolcosts -> paircost [style=bold];
+	paircost -> loss [xlabel=" Binary cross-entropy ", style=bold];
+	loss [label="Loss", shape=oval];
+	pi0 -> invpi0 [xlabel=" Invert "];
+	pi1 -> invpi1 [xlabel=" Invert "];
+	invpi0 -> pi1pi0;
+	invpi1 -> pi1pi0;
+	pi1pi0 -> normalized [xlabel=" Normalize "];
+	normalized -> paircost;
+	symbolprecedence [label="Symbol precedence", style=dashed];
+	symbolcosts -> symbolprecedence [xlabel=" Order symbols by their costs ", style=dashed];
+}
+\end{figure}
+
 \subsection{Layers}
-
+'
 \begin{enumerate}
@@
 $$
-Precedence cost is minimized by $\pi$ that orders the symbols by their costs in non-decreasing order.
+Precedence cost is minimized by $\pi$ that orders the symbols by their costs in non-increasing order
+($\forall (1 \leq i < j \leq n) . (\CostSym(\pi(i)) \geq \CostSym(\pi(j)))$).
 
@@
 
-We define precedence pair cost:
+% Note that we use this orientation because the TensorFlow metric BinaryCrossentropy classifies 0 as negative and we use the value 0 for "failed to classify" logits.
+Given a pair of precedences $\pi_0, \pi_1$,
+we define the log-odds of the event "$\pi_0$ is better than $\pi_1$":
 $$
 \CostPrecPair(\pi_0, \pi_1) =
-\CostPrec(\pi_0) - \CostPrec(\pi_1) =
-C \sum_{1 \leq i \leq n} \CostSym(s_i) \cdot [\inv{\pi_0}(s_i) - \inv{\pi_1}(s_i)]
+\CostPrec(\pi_1) - \CostPrec(\pi_0) =
+C \sum_{1 \leq i \leq n} \CostSym(s_i) \cdot [\inv{\pi_1}(s_i) - \inv{\pi_0}(s_i)]
 $$
-Clearly $\CostPrecPair(\pi_0, \pi_1) < 0$ iff $\CostPrec(\pi_0) < \CostPrec(\pi_1)$.
+Clearly $\CostPrecPair(\pi_0, \pi_1) > 0$ iff $\CostPrec(\pi_0) < \CostPrec(\pi_1)$.
 For a pair of precedences about which we know that $\pi_0$ is better than $\pi_1$,
-we want $\CostPrecPair(\pi_0, \pi_1) < 0$.
+we want $\CostPrecPair(\pi_0, \pi_1) > 0$.
 
-We model the probability of misclassification of precedence pair $\pi_0, \pi_1$
-such that $\pi_0$ is better than $\pi_1$
-by the sigmoid of $\CostPrecPair(\pi_0, \pi_1)$:
+We model the probability of the event "$\pi_0$ is better than $\pi_1$"
+by the sigmoid of $\CostPrecPair(\pi_0, \pi_1)$:https://www.overleaf.com/project/5f75a50ba1a0930001ce1162
 $$
-L(\pi_0, \pi_1) = \sigmoid(\CostPrecPair(\pi_0, \pi_1))
+p(\pi_0, \pi_1) = \sigmoid(\CostPrecPair(\pi_0, \pi_1))
+$$
+
+We use the binary cross-entropy loss to train the model.
+Given a pair of precedences such that $\pi_0$ is better than $\pi_1$,
+the loss is as follows:
+$$
+Loss(\pi_0, \pi_1) = -\log(\sigmoid(\CostPrecPair(\pi_0, \pi_1)))
 $$

### 2021-02-11 abstract.tex
Write abstract and introduction for AWR
Overleaf: Version 695

https://www.overleaf.com/project/5f75a50ba1a0930001ce1162

% AWR: Guidelines (Unit 7, page 5):
% At most 300 words
% Content:
% Purpose of the study
% Research problems
% Basic design of the study
% Summary of interpretations and conclusions

% AWR: Parts of an abstract (checklist) (Unit 7, page 6):
% Motivation
% Problem statement
% Approach
% Results
% Conclusions

This paper describes and evaluates a symbol precedence heuristic based on a \acrlong{gcn}.
When trained on proof attempts with random symbol precedences,
the heuristic outperforms the state of the art by more than 20~\%.
For the purpose of the evaluation, the symbol precedences predicted by the heuristic
are used to instantiate Knuth-Bendix term simplification orderings.
These orderings in turn guide the proof search in the state-of-the-art \acrlong{atp} \vampire{}
by constraining the superposition calculus inferences.
The evaluation is performed on \acrlong{fol} problems from the TPTP problem library.

% Motivation and purpose of the study are excluded because the audience at CADE need not be reminded of the motivation for making the provers faster.

### 2021-02-11 introduction.tex
Write abstract and introduction for AWR
Overleaf: Version 695

https://www.overleaf.com/project/5f75a50ba1a0930001ce1162

@@
 
-A \gls{fol} problem consists of \gls{fol} formulas divided into two categories:
-one or more premises and one conjecture.
-% We assume that \gls{fol} is expanded to FOL.
-% For this reason the article is "an".
-When presented with an \gls{fol} problem,
+A \gls{fol} problem consists of \gls{fol} formulas of two categories:
+premises and a conjecture.
+When presented with a \gls{fol} problem,
 a \definiendum{saturation-based} \gls{atp} negates the conjecture (as a first step of proof by contradiction)
@@
 \todo[author=Filip]{Cite some source that explains refutation-based automated theorem proving. Perhaps Harris?}
-\todo[author=Martin]{prvni odstavec uvodu bych pro CADE publikum vynechal a zacal rovnou s druhym}
 
@@
 \todo[author=Filip]{This may be an oversimplification: KBO is further parameterized by symbol weights.}
-which is a permutation of predicate and function symbols of the input problem.
+that is a permutation of predicate and function symbols of the input problem.
 
@@
 \todo[author=Filip]{Cite the original source of the arity heuristic.}
-The structure of the problem contains much information that is relevant for the choice of symbol precedence,
+The structure of the problem contains a lot of information that is relevant for the choice of symbol precedence,
 but is completely ignored by the symbol properties that inform the symbol precedences.
 \todo[author=Filip]{Why do we believe this?}
-\todo[author=Martin]{Klicovou vetu ...
-by asi chtelo rozvest treba do celeho odstavce.
-Takhle vyzni dost krypticky a neni moc jasne, co se snazi vyjadrit: "The structure of the problem" neni predem vysvetleno.
-"completely ignored" - "ignored" trosku zavani nejakym agentem, pritom je zde predmetem neziva vec / abstraktum}
 
@@
 compared to the state-of-the-art heuristic.
-\todo[author=Martin]{Poslednimyu ostaveci by taky asi jeste mohlo neco predhazet, aby to mohl shrnout: "the architecture" ma urcity clen, ale predtim zadna "architecture" jeste neni.
-"graph convolution network" taky vlastne zminujes poprve}
 

### 2021-02-11 evaluation.tex
Migrate to Git

To demonstrate the capacity of the precedence recommender described in \cref{sec:architecture},
a series of experiments was performed.
\todo{MS: vzdycky kdyz to jen trochu jde, snaz se pouzivat cinny rod (a pritomny cas): To demonstrate ..., we performed ... Ale taky tu trochu chybi, co nas ceka dal, ve stylu: In this section, we report ... }
In this section, we describe the design and configuration of the experiments,
and then compare the performance of the trained models to baseline heuristics.

\subsection{Solver}

The empirical evaluation was performed using a modified version of the \gls{atp} Vampire 4.3.0.\cite{10.1007/978-3-642-39799-8_1}
The prover was used to generate the training data and to evaluate the trained precedence recommender.
To generate the training data,
Vampire was modified to output \gls{cnf} representations of the problems
and annotated problem signatures in a machine-readable format.
%in \gls{json} format and annotated problem signatures in \gls{csv} format.\todo{MS: Mentioning JSON or CSV seems to be too low level. ``programmer documatation'' material.}
For the evaluation of the precedences generated by the recommender,
Vampire was modified to allow the user to specify the predicate and function symbol precedences.
\todo[inline]{FB: Add a link to the modified Vampire.}

% All explicit options:
% vampire --encode on --statistics full --time_statistics on --proof off --avatar off --saturation_algorithm discount --age_weight_ratio 10 --literal_comparison_mode predicate --symbol_precedence frequency --time_limit 10

% Notable explicit options:
% vampire --avatar off --saturation_algorithm discount --age_weight_ratio 10 --literal_comparison_mode predicate --symbol_precedence frequency --time_limit 10

% Notable implicit options:
% --term_ordering kbo

\todo[inline,author=FB]{Describe the Vampire options.}
\todo{MS: Literal comparison mode is not a standard thing. Mentioning the option name is again too low level. Explaining the effect (point two) is appropriate, although a bit too vague. To kdyztak opravim ja. 
Popsat presne setup je dulezite, kvuli reprodukovatelnosti, ale ne nutne primo v clanku (budem nejspis stejne dodavat odkaz na nejake reproducibility repo).
Ted zminit AVATAR je nevhodne, pokud nevysvetlis, co to aspon ramcove je. A pokud to budes vysvetlovat, je otazka, proc tim ztracet misto, kdyz to neni bezprostredne relevantni pro dalsi vysvetlovani.}

%For the experiment, Vampire 4.3.0 was modified to convert the problems from the \gls{tptp} format to a representation that allows easy automated processing.
%More precisely, when the modified prover is run in the clausification mode (\texttt{vampire -mode clausify}),
%it outputs the \gls{cnf} form of the problem and the problem signature in formats that allow easy processing in Python.
%The \gls{cnf} clause and term structure of the problem is encoded into the \gls{json} format,
%and the signature along with additional symbol metadata is encoded into the \gls{csv} format.

\subsection{Training data}

The training data consists of examples of the form $(P, \PrecBetter, \PrecWorse)$,
where $P$ is a \gls{cnf} problem and $\PrecBetter, \PrecWorse$ are precedences of symbols of problem $P$
such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop.
\todo{Justify saturation loop iterations as a proxy for success.}
\todo{Reference a detailed explanation of saturation loop iterations.}

Since neither of the common \glspl{sot}, i.e., \gls{kbo} nor \gls{lpo}, ever compares a predicate symbol with a function symbol,
two separate precedences can be considered for each problem:
a predicate precedence and a function precedence.
A predicate precedence recommender is trained separately from a function precedence recommender
to simplify the training process and to isolate the effects of the predicate and function precedences.
This section describes how the training data for training a \emph{predicate} precedence recommender is generated.
Training data for training a function precedence recommender is generated analogously.

\subsubsection{Problem set}

The examples are generated by sampling the \gls{fol} part of the problem library \gls{tptp} v7.4.0.
A total of \num{17053} problems formulated in \gls{fof} and \gls{cnf} are sampled.
The problems formulated in \gls{fof} are converted to \gls{cnf} by Vampire.
% vampire --mode clausify
Let $\ProblemsTptp$ denote the set of all \num{17053} \gls{cnf} problems available for training and evaluation.

\subsubsection{Sampling}

The examples are generated by iterative sampling of $\ProblemsTptp$.
In each iteration, a problem $P \in \ProblemsTptp$ is chosen and Vampire is executed on $P$
with two predicate precedences chosen uniformly from the set of all predicate precedences on $P$.
A function precedence for $P$ is chosen uniformly and used for both executions.
\todo[author=FB]{Why do we sample function precedences randomly?}

The two executions are compared in terms of performance:
predicate precedence $\PrecBetter$ is recognized as better than precedence $\PrecWorse$,
denoted as $\Better{\PrecBetter}{\PrecWorse}$,
if the proof search finishes successfully with $\PrecBetter$ ($\SolverRun{P}{\Prec} = \top$)
and if the number of iterations of the saturation loop with $\PrecBetter$ is smaller than with $\PrecWorse$.
\todo{FB: Use notation for saturation loop iterations if the notation was established earlier.}
If one of the two precedences is recognized as better,
the example $(P, \PrecBetter, \PrecWorse)$ is produced,
where $\PrecBetter$ is the better precedence,
and $\PrecWorse$ is the other precedence.

To ensure the efficiency of the sampling, the process is interpreted as an instance of Bernoulli multi-armed bandit problem,
\todo{Cite?}
with the reward of a trial being 1 in case an example is produced, and 0 otherwise.
Adaptive sampling balances
exploring problems that have been tried relatively scarcely and
exploiting problems that have yielded examples relatively often.
For each problem $P \in \ProblemsTptp$,
the generator keeps track of the number of times the problem has been tried $n_P$
and the number of examples generated from that problem $s_P$.
The ratio of $s_P$ to $n_P$ corresponds to the average reward of problem $P$ observed so far.
The problems are sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
In each iteration, the generator samples the problem $P$ that maximizes
$$
\frac{s_P}{n_P} + \sqrt{\frac{2 \ln n}{n_P}}
$$
where $n = \sum_{P \in \ProblemsTptp} n_P$ is the total number of tries on all problems.
The parallelizing relaxation means that the $s_P$ values are only updated once in \num{1000} iterations,
allowing up to \num{2000} parallel solver executions.
\todo{Explain in detail?}

The sampling runs until a total of \num{1000000} examples are generated.
% sftp://cluster.ciirc.cvut.cz/home/bartefil/git/vampire-ml/out/20210108-generate-predicate/questions_generated
For example, while generating \num{1000000} examples for the predicate precedence dataset,
the least explored problem was tried 19 times, and the most exploited problem was tried 504 times.
\num{5349} out of the \num{17053} problems yielded at least one example.
\todo{FB: Remove these two sentences because the give too arbitrary detail?}

\subsubsection{Split}

The problems in $\ProblemsTptp$ are split roughly in half to form the train set and the validation set.
Both training and validation sets are restricted to problems whose graph representation consists of at most \num{100000} nodes
to limit the memory requirements of the training.
The train set is further restricted to problems that correspond to at least one training example.
In total there are \num{7648} problems in the validation set $\ProblemsVal$
and \num{2571} problems in the train set $\ProblemsTrain$.
\todo{FB: Unify the terminology: validation, or train set?}
% /home/filip/projects/vampire-ml/vampire-ml/outputs/2021-02-11/16-27-02/results.csv
% all: 17053
% train: 8527
% val: 8526
% with_questions: 5349
% graphified (not all attempted): 10219
% train&with_questions: 2647
% train&with_questions&graphified: 2571
% val&graphified: 7648
\todo{MS: tady ale lidi bude okamzite zajimat, kolik teda tech problemu na kazde strane zbylo. A jeste by nebylo lepsi vzit nejdriv ty ``male'' problemy a pak teprve pulit.}

\subsection{Training procedure}

A predicate symbol cost model is trained by gradient backpropagation
\todo{FB: Explain?}
on the precedence pair classification task
\todo{FB: Reference a section.}
using the examples generated from the problems in $\ProblemsTrain$.
\todo{Add references to the sections that describe the architecture.}
To avoid redundant computations, all examples generated from a problem are processed in the same training batch.
Thus, each training batch contains up to \num{128} problems and all the examples generated from these problems.
The symbol cost model is trained using the Adam optimizer \cite{Kingma2014}.
Learning rate starts at \num{1.28e-3}
and is halved each time the train loss stagnates for 10 consecutive epochs.
% tf.keras.callbacks.ReduceLROnPlateau(monitor='loss', factor=0.5, patience=10)
A \gls{gcn} with depth 4 and message size 16 is used.\todo{MS: zase pasivum. Tady to urcite bude chtit odkaz na sekci, kde se jasne definuje, co to znamena. Jinak recenzenti byvaji dost alergicti na hyperpametry, ktere se jen tak nahodi na nevysvetli. Minimalne nejaky komentar typu: treba, zkouseli jsme u ruzne dalsi hodnoty, ale dopadalo to podobne. Nebo, pozdeji rekeneme, co se deje, kdyz se tohle meni. Nebo: nemeli jsme cas zjistovat, co se deje, kdyz se to meni, tak berem rozumne hodnoty podle blabla.}

Each of the training examples of problem $P$ contributes to the training with the weight $\frac{1}{s_P}$,
where $s_P$ is the number of examples of problem $P$ in the training set,
so that each problem contributes to the training to the same degree irrespective of the relative numbers of examples.
\todo{FB: Shall we remind that the examples are further normalized by $k(n)$ to make even across signature lengths?}

\subsection{Results}

The final evaluation is performed on $\ProblemsVal$.
For each problem $P \in \ProblemsVal$,
a precedence is generated by the trained recommender
and Vampire is run using this precedence.
The results are averaged over 5 runs to reduce the effect of noise in the computation wall clock time.

\begin{table*}
\caption{
Results of the evaluation of various predicate precedence heuristics on $\ProblemsVal$.
Means and standard deviations over 5 runs are reported.
}
\label{table:results}
\centering
\begin{tabular}{l|ll|ll}

Model & \multicolumn{2}{l}{Successes out of \num{7648}} & \multicolumn{2}{l}{Successes rate} \\
& Mean & Std & Mean & Std \\
\hline

\acrshort{gcn} (predicate) & \num{3923.6} & \num{2.24} & \SI{51.30}{\percent} & \num{2.93e-4} \\
% Success rate: mean: 0.513023013, std: 0.000292887
% Evaluation results: https://ui.neptune.ai/filipbartek/vampire-ml/e/VML-553
% Total: validation_solver_eval/all/problems/measured&split&category: 7648
% Success mean: validation_solver_eval/all/success/count/mean: 3923.6
% Success std: validation_solver_eval/all/success/count/std 2.24
% Success rate: 0.513023013
% Difference in success count from baseline: 154 ~ 0.020135983
% Estimated difference from baseline (estimate on 891 problems): 0.021099888
% Checkpoint: outputs/2021-02-06/14-55-41/tf_ckpts/epoch/weights.00079-0.61.tf VML-540 0.511785

\texttt{vampire -lcm predicate} & \num{3769.6} & \num{3.07} & \SI{49.29}{\percent} & \num{4.01e-4} \\
% Success rate: mean: 0.492887029, std: 0.000401412
% https://ui.neptune.ai/filipbartek/vampire-ml/e/VML-490
% /home/filip/projects/vampire-ml/vampire-ml/outputs/2021-02-09/12-13-43
% Row: 'val&graphified&solver_eval'
% Problems total: 7648
% Success rate: 0.492887029

\texttt{vampire -lcm standard} & ? & ? \\

\end{tabular}
\end{table*}
\todo{FB: Add links to Neptune runs?}

\todo{Mention: time to compute graphs and precedences is excluded from the time.}

\todo{Add results for function precedences.}
\todo{Try to evaluate a recommender that uses both predicate and function models.}
\todo{Add discussion.}
\todo{FB: Evaluate on problems larger than 100k nodes.}

### 2021-02-11 abstract.tex
Migrate from Overleaf version 3920
Update to the current head in Overleaf.

Overleaf label: "Migrate to Git"

https://www.overleaf.com/project/5f75a50ba1a0930001ce1162

@@
 When trained on proof attempts with random symbol precedences,
-the heuristic outperforms the state of the art by more than 20~\%.
+the heuristic outperforms the state of the art by more than \SI{2}{\percent}.
 For the purpose of the evaluation, the symbol precedences predicted by the heuristic
@@
 by constraining the superposition calculus inferences.
-The evaluation is performed on \acrlong{fol} problems from the TPTP problem library.
+The evaluation is performed on \acrlong{fol} problems from the \acrshort{tptp} problem library.
+
+\keywords{saturation-based theorem proving \and
+term simplification ordering \and
+symbol precedence \and
+\acrlong{ml} \and
+\acrlong{gcn}}
 

### 2021-02-11 introduction.tex
Migrate from Overleaf version 3920
Update to the current head in Overleaf.

Overleaf label: "Migrate to Git"

https://www.overleaf.com/project/5f75a50ba1a0930001ce1162

--- 2020-12-11 introduction.tex
@@
 are saturation-based and
-infer new provable clauses by applying the rules of \definiendum{superposition calculus}.
+infer new provable clauses by applying the rules of the \definiendum{superposition calculus}.
 \todo[author=Filip]{Cite some source that explains superposition calculus.}

### 2021-02-11 main.tex
Migrate from Overleaf version 3920
Update to the current head in Overleaf.

Overleaf label: "Migrate to Git"

https://www.overleaf.com/project/5f75a50ba1a0930001ce1162

@@
-\documentclass{article}
+\documentclass[runningheads]{llncs}
 \usepackage[utf8]{inputenc}
@@
 \usepackage[english]{babel}
+\usepackage[binary-units=true,detect-weight=true]{siunitx}
 
@@
 
-% TODO: Compare to bag-of-words model.
-
 \input{preamble}
+\input{glossary}
+\input{front}
 
 \usepackage[pdf]{graphviz}
+\usepackage{tikz}
 
@@
 \begin{abstract}
-\input{abstract}
+\input{abstract}https://www.overleaf.com/project/5f75a50ba1a0930001ce1162
 \end{abstract}
@@
 
+\todo[inline]{Add: brief exposure of FOL and saturation-based proving with terms possibly emphasized.}
+\todo[inline]{If space is left: define KBO.}
+\todo[inline]{If space is left: show resolution and superposition rules. Explain how KBO influences them.}
+\todo[inline]{Mention lcm predicate. Cite the Vampire article. Voronkov: transfinite KBO - see section Notes on implementation
+
+Mention: Vampire sets all KBO symbol weights to 1.
+
+In Vampire: simple TKBO - level
+
+We use TKBO to increase the impact of predicate precedence.}
+\todo[inline]{Get inspiration from PAAR paper.}
+
 \vampire{} \cite{10.1007/978-3-642-39799-8_1}
-is representative
+is a representative
 of the state-of-the-art \gls{fol} \gls{atp} design.
-\vampire{} was awarded the first place
-in the \gls{fol} category of \gls{casc} \cite{},
-an annual international competition of \glspl{atp},
-in eleven times in the years between 2010 and 2020 \cite{}.
-Moreover, 7 of 10 provers that have placed in the top 50 \% in 2020
-are saturation-based, refutation-based and resolution-based,
-similarly to \vampire{} \cite{}.
+\todo{Move into Introduction.}
 
@@
 % AWR candidate
-Proof search in \vampire{} is crucially constrained
+Proof search in Vampire is crucially constrained
 by a simplification ordering on terms.
 Being refutation-based and saturation-based,
-\vampire{} searches for contradiction
+Vampire searches for a contradiction
 by iteratively inferring clauses provable from the input clauses.
@@
 from the input formulas
-by applying rules of superposition inference system.
+by applying the rules of superposition inference system.
 This process continues until a contradiction is inferred,
-the processed clauses set is saturated
+the processed clause set is saturated,
 or the execution hits a resource limit.
 
-During proof search,
-\vampire{} explores the space of provable clauses
+During the proof search,
+Vampire explores the space of provable clauses
 by applying inference rules to clauses
@@
 Simplification ordering on terms
-influences the proof search in \vampire{} on two levels.
+influences the proof search in Vampire on two levels.
 First, the inferences on each clause are limited
 to the selected literals.
+\todo{Cite Bachmair Ganzinger or Handbook of AR, chapter 2. For literal selection. Inspiration: Selecting the selection.}
 In each clause,
@@
 % Note: The selection function Total does not use the simplification ordering.
-Second, simplification ordering orients some of the equalities
+Second, the simplification ordering orients some of the equalities
 to prevent superposition and equality factoring
@@
 is parameterized by a simplification ordering on terms.
-\vampire{} uses superposition inference system \cite{}.
+\vampire{} uses the superposition inference system \cite{}.
 
@@
 Given a \gls{fol} problem,
-determining a symbol precedence that leads to a fast proof search is a non-trivial task.
+determining a symbol precedence that leads to a fast proof search is a nontrivial task.
+
+\todo[inline]{Define "CNF" as quantifier-free CNF FOL with equality.}
+\todo[inline]{Define "signature".}
+% https://en.wikipedia.org/wiki/First-order_logic
+
+\todo[inline]{GCN? Backprop?, gradient descent, loss, gradient}
 
@@
 
-This section describes the architecture of a precedence recommender system.
-When presented with a \gls{fol} problem $P$ with symbols $\symbols$,
-the system predicts a symbol precedence $\pi$ on $\symbols$
-that is expected to lead to a successful proof search.
+\subsection{Learning to generate good permutations}
 
-\subsection{Prediction pipeline}
+Generating good symbol precedences is an instance of a more general task
+of generating permutations of arbitrary length.
+Each input problem corresponds to an input object that specifies the length of a permutation.
 
-\subsection{Training pipeline}
+Let $X$ be a set of objects.
+Let $l: O \to \nat$ assign each object $x \in X$ its signature length $l(x)$.
+Let $\{x_1, \ldots, x_n\}$ be the training samples.\todo{MS: je mi jasny, ze tu neni poradek, ale i tak; posledni dva odstavce jsou dost zmateny.}
+
+\subsubsection{Binary classification}
+
+Let $p_\theta : X \to \re$ be a binary classification model.\todo{MS: Dobry priklad na to, ktere pojmy je treba vysvetlovat.
+model je znamy pojem v logice, tady ale pouzivame jiny, ML vyznam.
+To by si zaslouzilo komentar.
+Navic pisem
+``binary'' a ``classification'' a neni tu jasny, co je ``binary''
+a co jsou ``classes''. Z pohledu ctenare, ktery o tom zatim neslysel, se misto ``binary classficiation model'' mohlo
+psat ``housenka'' a vyslo by to pro nej na stejno.}
+The model predicts the probability of label $1$.
+Let $(x_i, y_i)$ be the training samples,
+where $x_i \in X$ and $y_i \in Y = \{0, 1\}$.\todo{MS:
+``training'', ``sample'' a ``loss'' jsou dalsi priklady pojmu,
+ktere najednou spadly z hury.}
+
+For a training sample $(x, y) \in \re \times \{0, 1\}$, the binary cross-entropy loss is:
+$$
+L(\theta) = y \log{f_\theta(x)} + (1-y) \log{(1-f_\theta(x))}
+$$
+
+If $y_i = 1$ for all $i$, then the loss can be written in a simpler form:
+$$
+L(\theta) = \log{f_\theta(x)}
+$$
+
+\subsubsection{Permutations}
+
+Let $O$ be a set of objects (or contexts).
+Given an object $o \in O$, let $\Sigma(o)$ be its signature.
+Let $x_i = (o_i, \pi_i, \rho_i)$, where $o_i \in O$
+and $\pi_i, \rho_i \in \Perm(\Sigma(o_i))$.
+Let $y_i \in \{0, 1\}$.
+
+Let $p_\theta: X \to Y$.
+
+Loss:
+$$
+L(\theta) = \log{p_\theta(x)}
+$$
+
+Let $c_\theta(o, s)$ be the predicted cost of symbol $s$.
+Then:
+$$
+p_\theta(o, \pi, \rho) = C_\theta(o, \pi) - C_\theta(o, \rho)
+$$
+
+$$
+C_\theta(o, \pi) = \sum_{i=1}^{l(o)}{c(o, \pi_i)}
+$$
+
+\begin{align*}
+L(\theta) &= \log{p_\theta(o, \pi, \rho)} \\
+&= \log{(C_\theta(o, \pi) - C_\theta(o, \rho))} \\
+&= \log{(\sum_{i=1}^{l(o)}{c(o, \pi_i)} - \sum_{i=1}^{l(o)}{c(o, \rho_i)})} \\
+&= \log{\sum_{i=1}^{l(o)}{c(o, \pi_i) - c(o, \rho_i)}} \\
+\end{align*}
+
+If $c$ is differentiable,
+we can propagate loss gradients into it.
+
+\subsection{Notation}
+
+We denote the set of all finite vectors over $\re$ by $\re^* = \bigcup_{n=1}^\infty{\re^n}$.
+
+Dot product: $\DotProd{x}{y} = \sum_{i=1}^n x_i \cdot y_i$ for $x, y \in \re^n$.
+
+For any $n \in \nat$, we denote the set of all permutations over the set $\{1, \ldots, n\}$ by $\Perm{n}$.
+Permuting a vector $x = (x_1, \ldots, x_n) \in \re^n$ by a permutation $\pi = (\pi_1, \ldots, \pi_n) \in \Perm{n}$ yields the vector $\pi(x) = (x_{\pi_1}, \ldots, x_{\pi_n})$.
+$\inv{\pi}$ denotes the permutation inverse to $\pi$.
+$\inv{\pi} = ...$.
+\todo{Define permutation inversion.}
+\todo{MS: Mozna ani ne.
+Ono je obcas tezky zavest a pouzivat presnout matematickou notaci, ktera se navic muze stavat neprehlednou, kvuli te presnosti.
+Na druhou stranu, intuitivne, kazdy vi, co by to mela byt inverzni permutace.
+Takze nerikam psat nepresne veci, ale obcas jde
+zustak vagni s tim, ze vim, ze existuje zpusob jak to udelat presnym.
+A povrchni ctenar to nemusi resit a matematicky zdatny by si ten detail odvodil spravne ...}
+
+\newcommand{\Prec}{\pi}
+\newcommand{\PrecBetter}{\pi}
+\newcommand{\PrecWorse}{\rho}
+
+\subsection{Overview}
+
+Let $\cnf$ be the set of all \gls{cnf} problems.
+Let $P \in \cnf$ be an arbitrary problem.
+\todo{Consider using $F$ (as formula) instead of $P$ to free up P for probability.}
+Let $\signature{P}$ be the signature of $P$, that is a list of all non-logical symbols (predicates and functions)
+\todo{Should we rather use either predicates or functions? Or use a compound signature?}
+that appear in the problem.
+Let $n = \card{\signature{P}}$.
+A symbol precedence $\Prec \in \Perm{n}$ for problem $P$ is a permutation of the symbols of $P$.
+
+\newcommand{\Solver}{S}
+\newcommand{\SolverRun}[2]{\Solver(#1, #2)}
+
+Let $\Solver$ be an \gls{atp} with a fixed computation environment, configuration and time limit.
+The computation of $\Solver$ is assumed to be parameterized by symbol precedence.
+\todo{Discuss. What does this mean?}
+$\SolverRun{P}{\Prec}$ denotes the result of a proof attempt on problem $P$ with symbol precedence $\Prec$.
+$\SolverRun{P}{\Prec} = \top$ if $S$ solves $P$ within the time limit, and $\SolverRun{P}{\Prec} = \bot$ otherwise.
+\todo{MS: vadi zminit pocet iteraci smycky tak, jako v minulem paperu?}
+Since the result is generally non-deterministic in case the time limit is specified in wall clock units,
+we consider $\SolverRun{P}{\Prec}$ to be a random variable with a Bernoulli distribution.
+\todo{Cite?}
+We denote the probability of a successful proof search $\Prob{\SolverRun{P}{\Prec} = \top}$.
+\todo{MS: asi bych se primlouval za to v teto fazi o Bernoullim pomlcet.
+Otazky jsme generovali tak, ze proste porovnavame pocty iteraci saturatcni smycky a pocitame s tim, ze beh je deterministicky.
+To, ze se pozdeji, pri evalu, pouzije perspektiva nahodnosti
+bych uz chapal jako metodiku experimentu a teorii tim nekomplikoval.}
+
+The main task this paper deals with is this:
+Given a problem $P \in \cnf$, generate a symbol precedence $\Prec \in \Perm{n}$ that maximizes $\Prob{\SolverRun{P}{\Prec} = \top}$.
+MS: (Nehlede na to, ze main task by nejspis mel byt vysvetlen mnohem drive...) Asi bych to takhle nestavel. Jak pisu vyse, precijen je
+beh dokazovace deterministicky a brat to nejak Bayesovsky by sice mohlo 
+byt zajimave, ale jeste mnohem tezsi na obhajeni jako ``svetonazor''.
+Co proste priznat nasledujici assumption:
+verime, ze pokud bude model spravne odpovidat na otazky $(P, \pi_1, \pi_2)$ (s pravdepodobnosti $> \SI{50}{\percent}$), povede podle nej vybrana permutace minimalizujici \eqref{eq:model_cost} k rychlemu vyreseni problemu (a tim i idealne k vyreseni problemu, ktere byly drive out of reach.)\todo{MS: koukni prosim, jestli nejaky takovy mame.
+Tj zadna random permutace ho nevyresila, ale naucena sit pak ano!}
+
+Instead of modeling $\Prob{\SolverRun{P}{\Prec} = \top}$ directly,
+the system described in this paper predicts, given a problem $P$ and a pair of precedences $\PrecBetter, \PrecWorse \in \Perm{n}$,
+the probability\todo{MS: tohle je jeden z oficialnich zpusobu,
+jak vysvetlovat neuronky, ale neni nijak jasne do jake miry byva
+$\sigma(\mathit{logits})$ blizko nejake pravdepodobnosti. Za mne by klidne stacilo mluvit o tom, ze se snazime klasifikovat co nejvic dvojic
+spravne a ze na to pouzivame standard techologii neuronek (Binary Cross Entropy loss (against the final layer’s sigmoid non-linearity)). Tj opet hlasuji za to nemluvit zde o pravdepodobnosti. :)}
+\todo{MS: jo, ale pak bude nekde dobre zminit, ze jsme si vedomi, ze dvojice skoro jiste neobsahuji stejne mnozstvi ``signalu'', ze ktereho je mozne se ucit.
+Je to proste vlastnost vybrane metody a v prumeru to nevadi.}
+that $\PrecBetter$ outperforms $\PrecWorse$ in terms of success of proof search.
+This proxy task allows learning from pairs of precedences that both yield a successful proof search but differ in the number of steps taken in the proof search.
+\todo{Explain more.}
+
+% By taking the pairs, we get more data esp. from easy problems.
+% Consider weighting the samples by the result type: quantitative / qualitative etc.
+
+% TODO: Experiments: Increase depth and message size
+
+\begin{figure}[h]
+\caption{System overview}
+\label{fig:SystemOverview}
+\centering
+\usetikzlibrary{shapes}
+\tikzstyle{object} = [rectangle, draw]
+\tikzstyle{input} = [ellipse, draw]
+\tikzstyle{output} = [ellipse, draw]
+
+\begin{tikzpicture}[node distance = 0.5 and 1, ->]
+% https://tex.stackexchange.com/a/332796/202639
+
+\node (problem) [input] {\gls{cnf} problem $P$};
+\node (symbol embeddings) [object] [below=of problem] {Symbol embeddings};
+\node (symbol costs) [object] [below=of symbol embeddings] {Symbol costs};
+\node (symbol precedence) [output] [below=of symbol costs] {Symbol precedence};
+
+\draw (problem) to node [left] {GCN} (symbol embeddings);
+\draw (symbol embeddings) to node [left] {MLP} (symbol costs);
+\draw (symbol costs) to node [left] {Order symbols by their costs} (symbol precedence);
+
+\node (PrecBetter) [input] [right=of problem] {Precedence $\PrecBetter$};
+\node (PrecBetterInv) [object] [below=of PrecBetter] {$\inv{\PrecBetter}$};
+\draw (PrecBetter) to node [right] {Invert} (PrecBetterInv);
+
+\node (PrecWorse) [input] [right=of PrecBetter] {Precedence $\PrecWorse$};
+\node (PrecWorseInv) [object] [below=of PrecWorse] {$\inv{\PrecWorse}$};
+\draw (PrecWorse) to node [right] {Invert} (PrecWorseInv);
+
+\node (PrecDiff) [object] [right=2 of symbol costs] {$\inv{\PrecWorse} - \inv{\PrecBetter}$};
+\node (PrecDiffNormalized) [object] [below=of PrecDiff] {Normalized};
+\node (PrecPairCost) [object] [below=of PrecDiffNormalized] {Precedence pair cost};
+\node (loss) [output] [below=of PrecPairCost] {Loss};
+
+\draw (PrecBetterInv) to (PrecDiff);
+\draw (PrecWorseInv) to (PrecDiff);
+\draw (PrecDiff) to node [right] {Normalize} (PrecDiffNormalized);
+\draw (PrecDiffNormalized) to (PrecPairCost);
+\draw (PrecPairCost) to (loss);
+
+\draw (symbol costs) to (PrecPairCost);
+
+\end{tikzpicture}
+\end{figure}
+
+Fig.~\ref{fig:SystemOverview} \todo{MS: Na figures/tables bez referneci v textu se pohlizi obzvlast nelibe.
+Predpokladam, zes planoval pozdeji popsat, presto zmninuji.
+Konkretne k Fig.~\ref{fig:SystemOverview}:
+Napada me: neslo by precedenci definovat tak, aby uz byla tim $\pi^{-1}$? Invertovani zabira v obrazku skoustu mista, ale pritom
+jde o technicky detail a hlavni myslenku nijak neosvetluje...}
+
+\subsection{Symbol cost model}
+
+The symbol costs are modeled by a \gls{rgcn}.\cite{Schlichtkrull2017}
+\todo{Can I use the term \gls{rgcn} when I use a modified version? Namely, the activation is called earlier.}
+The model is a stack of graph convolutional layers.
+Each layer consists of one differentiable module for each edge type.
+Each module is a dense layer.
+$$
+h_i^{(l+1)} =
+\mathrm{LayerNorm} \Parentheses{h_i^{(l)} + \sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in \mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}}
+$$
+\todo{Include dropout?}
+% Inspiration: https://ufal.mff.cuni.cz/~straka/courses/npfl114/1920/slides.pdf/npfl114-07.pdf - slide 27 - Transformer
+$h_i^{(l)}$ denotes the embedding of node $i$ at layer $l$.
+$\mathcal{R}$ denotes the set of all relations in the graph.
+$\sigma$ denotes the activation function, for example the \gls{relu}.
+$\mathcal{N}_i^r$ denotes the set of neighbors of node $i$ under relation $r$.
+$c_{j, i, r} = \sqrt{\card{\mathcal{N}_j^r}} \sqrt{\card{\mathcal{N}_i^r}}$ is a normalization constant.\cite{kipf2017semisupervised}
+$W_r^{(l)}$ is a trainable weight matrix representing relation $r$ at layer $l$.
+
+Residual...
+Layer norm...
+
+\todo{MS: neni uplne jiste, ze ``CADE people'' oceni presny zapis 
+strutury site, vcetne prvku jako $\mathrm{LayerNorm}$ ve vzorecku.
+Nerikam, ze bychom to meli uplne zatajit, ale popis, ktery je zde, spis
+patri do appendixu (ML paperu). Na te siti vlastne nic originalniho neni,
+tak neni treba vsechno vysvetlit do detailu. Zajimavejsi tu
+potom je az to, jak se problem $P$ ``otiskne'' v topologii grafu. 
+To uz originalni je (a soutezi to s representacemi jako ta Mirkova)
+a popisujes to pak dal.}
+
+\subsection{Loss function} \todo{MS: tady jsem zatim skoncil...}
+\label{sec:loss}
+
+Let $\cnf$ be the set of all \gls{cnf} problems.
+Let $P \in \cnf$ be an arbitrary problem.
+Let $\signature{P}$ be the signature of $P$.
+Let $n = \card{\signature{P}}$.
+
+Given a problem $P$, a symbol cost model $c : \cnf \to \re^*$
+\todo{Confusing?}
+returns a vector of costs of the symbols of $P$:
+$$
+c(P) = (c_1, \ldots, c_n)
+$$
+
+Let $\Prec \in \Perm{n}$ be a precedence of symbols of problem $P$.
+Let $k(n) = \frac{2}{n(n+1)}$ be a normalization factor for precedences of length $n$.
+The symbol cost model $c$ can be extended to a precedence cost model $C$
+by taking the weighted sum of symbol costs:
+$$
+C(\Prec | P)
+= k(n) \sum_{i=1}^n c_{\Prec_i} \cdot i
+= k(n) \sum_{i=1}^n c_i \cdot \inv{\Prec}_i
+= k(n) \DotProd{c(P)}{\inv{\Prec}}
+$$
+Note that the value of $C$ is minimized by a precedence that orders the symbols by their costs in non-increasing order.
+\todo{Discuss, prove.}
+
+Fixing the normalization factor $k(n)$ to the value $\frac{2}{n(n+1)}$
+ensures that costs of precedences of various lengths are commensurable.
+Observe namely that if $c$ assigns each symbol the same cost $c_0$,
+then the precedence cost is equal to $c_0$ irrespective of the signature length $n$:
+\begin{equation} \label{eq:model_cost}
+C(\Prec | P) = \frac{2}{n(n+1)} \sum_{i=1}^n c_0 \cdot i = c_0
+\end{equation}
+
+Let $\PrecBetter, \PrecWorse \in \Perm{n}$ be two symbol precedences over $P$.
+Let $\PrecBetter$ yield a faster proof search on $P$ than $\PrecWorse$, denoted as $\Better{\PrecBetter}{\PrecWorse}$.
+The precedence cost model can be extended to predict the probability that $\PrecBetter$ is better than $\PrecWorse$:
+\todo{Fix this. Ensure the polarity is sound.}
+\begin{align*}
+p(\Better{\PrecBetter}{\PrecWorse} | P)
+&= \sigmoid \SquareBracket{C(\PrecWorse | P) - C(\PrecBetter | P)} \\
+%&= \sigmoid \SquareBracket{k(n) \sum_{i=1}^n c_i \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)} \\
+&= \sigmoid \SquareBracket{k(n) \DotProd{c(P)}{\inv{\PrecWorse} - \inv{\PrecBetter}}}
+\end{align*}
+It is easy to see\todo{MS: Bez znalosti $\sigmoid$ uplne ne ;)} that $p(\Better{\PrecBetter}{\PrecWorse} | P) > 0.5$ if and only if $C(\PrecWorse | P) > C(\PrecBetter | P)$,
+and that the value of $p$ can be increased by increasing $C(\PrecWorse | P)$ or decreasing $C(\PrecBetter | P)$.
+
+We consider the difference $C(\PrecWorse | P) - C(\PrecBetter | P)$
+to be the "logit"\todo{MS: Logit je taky tezky pojem, urcite ne automaticky znamy u ATP people.} score of the pair of precedences $\PrecBetter, \PrecWorse$,
+and denote it by $C(\Better{\PrecBetter}{\PrecWorse} | P)$.
+
+We define the loss of $c$ on the training sample $(\PrecBetter, \PrecWorse, P)$ as binary cross-entropy
+with ground truth $\Better{\PrecBetter}{\PrecWorse}$:
+
+\begin{align*}
+L(\PrecBetter, \PrecWorse, P)
+&= - \log p(\Better{\PrecBetter}{\PrecWorse} | P) \\
+&= - \log \sigmoid \SquareBracket{k(n) \DotProd{c(P)}{\inv{\PrecWorse} - \inv{\PrecBetter}}} \\
+&= - \log \sigmoid \SquareBracket{k(n) \sum_{i=1}^n c_i \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)}
+\end{align*}
+
+The loss is differentiable with respect to the symbol costs:
+\begin{align*}
+\frac{\partial L}{\partial c_i}
+&= -\sigmoid(-C(\Better{\PrecBetter}{\PrecWorse} | P)) \cdot k(n) \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i) \\
+&= (p(\Better{\PrecBetter}{\PrecWorse} | P) - 1) \cdot k(n) \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)
+\end{align*}
+
+This means that it is possible to backpropagate the loss gradient into the symbol cost model. \todo{MS: tohle bude tezky,
+ale ackoliv ML people by tohle uz asi chapali, ATP crowd spis bude
+potrebovat obsirnejsi vysvetleni.}
+
+\subsubsection{Generalization}
+
+Note that this approach is generally applicable to all problems where it is necessary to generate permutations of arbitrary length.
+
+\todo[inline]{Finish.}
+
+\subsection{Symbol cost model}
+
+\subsection{Graph representation of problems}
+
+\newcommand{\ntype}[1]{\texttt{#1}}
+\newcommand{\etype}[1]{\texttt{#1}}
+\newcommand{\epos}{\etype{pos}}
+\newcommand{\eneg}{\etype{neg}}
+
+Every \gls{cnf} problem can be represented by a \gls{hin} with the network schema shown in \cref{fig:CnfSchema}.\todo{MS: Mel jsem chut to opravit na velke "Fig.", ale s makrem se mi hadat nechce ;)}
+% Cite: https://www.kdd.org/exploration_files/V14-02-03-Sun.pdf
+% Referenced from: https://docs.dgl.ai/en/0.5.x/generated/dgl.DGLHeteroGraph.metagraph.html
+
+\begin{figure}[ht]
+\caption{CNF network schema}
+\label{fig:CnfSchema}
+\centering
+\tikzstyle{token} = [rectangle, draw]
+
+\begin{tikzpicture}[node distance = 1 and 2, ->]
+% https://tex.stackexchange.com/a/332796/202639
+
+% Node and edge types:
+% https://docs.google.com/spreadsheets/d/1PCPHEgk6vLxpdpcvB_PGoLx7p4DID6WtvVWy2mDuv4A/edit?usp=sharing
+
+\node (formula) [token] {\ntype{problem}};
+% TODO: Consider removing the Formula nodes.
+\node (clause) [token, below=of formula] {\ntype{clause}};
+\node (atom) [token, below left=of clause] {\ntype{atom}};
+\node (equality) [token, below right=of clause] {\ntype{equality}};
+\node (predicate) [token, left=of atom] {\ntype{predicate}};
+\node (argument) [token, below=of atom] {\ntype{argument}};
+\node (term) [token, below=of argument] {\ntype{term}};
+\node (function) [token, left=of term] {\ntype{function}};
+\node (variable) [token, right=of term] {\ntype{variable}};
+
+\draw (formula) to node [right] {\etype{contains}} (clause);
+\draw (clause) to [bend right] node [above] {\epos{}} (atom);
+\draw (clause) to [bend left] node [below] {\eneg{}} (atom);
+\draw (clause) to [bend left] node [above] {\epos{}} (equality);
+\draw (clause) to [bend right] node [below] {\eneg{}} (equality);
+\draw (clause) to node [above] {\etype{binds}} (variable);
+\draw (atom) to node [above] {\etype{atom\_applies}} (predicate);
+\draw (atom) to node [left] {\etype{atom\_has}} (argument);
+\draw (equality) to node {\etype{equalizes}} (term);
+\draw (equality) to node {\etype{equalizes}} (variable);
+\draw (argument) to [bend right] node [left] {\etype{is}} (term);
+\draw (argument) to [loop left] node [left] {\etype{precedes}} (argument);
+\draw (argument) to node [below] {\etype{is}} (variable);
+\draw (term) to node [above] {\etype{term\_applies}} (function);
+\draw (term) to [bend right] node [right] {\etype{term\_has}} (argument);
+
+\end{tikzpicture}
+\end{figure}
+
+The network of a problem is a directed graph $G = (V, E)$.
+The function $\tau: V \rightarrow A$ maps the nodes to their types:
+
+$$
+A = \{\ntype{problem}, \ntype{predicate}, \ntype{function}, \ntype{clause}, \ntype{atom}, \ntype{equality}, \ntype{term}, \ntype{variable}, \ntype{argument}\}
+$$
+
+The function $\phi: E \rightarrow E$ maps the edges to their types.
+
+\begin{itemize}
+\item The graph representation of problem $P$ contains exactly one root node of type \ntype{problem}.
+\item Each clause is represented by a \ntype{clause} node connected to the root \ntype{problem} node.
+\item Each atom is represented by an \ntype{atom} node (in case the atom is not an equality)
+or an \ntype{equality} node (in case the atom is an equality).
+For each literal occurrence there is an edge connecting the respective atom to the respective clause.
+The type of the edge corresponds to the polarity of the literal:
+\epos{} for positive literal and \eneg{} for negative literal.
+\item Each \ntype{equality} node is connected to two nodes that represent the operands,
+each of which is of type \ntype{term} or \ntype{variable}.
+The commutativity of the equality operator is reflected by the fact that the operand edges are not ordered.
+\item Each \ntype{atom} node is connected to one \ntype{predicate} node that represents the predicate symbol being applied by this atom.
+Note that these edges connect the applications of a predicate symbol across the whole problem.
+\item Each \ntype{atom} node is connected to zero or more \ntype{argument} nodes that represent the argument positions of the atom.
+\item Each pair of \ntype{argument} nodes that correspond to consecutive argument positions is connected by an edge.
+\item Each \ntype{argument} node is connected to a node that represents the argument term,
+which is either a \ntype{term} node or a \ntype{variable} node.
+\item Each \ntype{term} node is connected to one \ntype{function} node that represents the function symbol being applied by this term.
+\item For each variable, there is an edge connecting the \ntype{clause} node of the clause that binds the variable to the \ntype{variable} node that represents the variable.
+\end{itemize}
+
+\todo[inline]{Abstract from the edge types. Focus on the main idea. Technical details may be in technical report or appendix.}
+
+Various levels of term sharing are possible. [continue]
+
+\todo[inline]{Give an example of a problem and its graph.}
+
+\subsection{Generating precedences}
+\label{sec:generating}
+
+When presented with a \gls{cnf} problem $P$ with signature $\symbols$,
+the recommender produces a precedence $\pi$ of symbols from $\symbols$.
+In order to generate the precedence,
+the recommender first assigns a cost value to each symbol
+by invoking a symbol cost model (a trained \gls{gcn}) on a graph representation of $P$.
+Ordering the symbols by their predicted costs in nondecreasing order yields the precedence $\pi$.
+
+\subsection{Training}
+
+The training is performed using a fixed \acrlong{atp}.
+The configuration of the prover,
+including for example saturation algorithm, age-weight ratio, and term ordering scheme,
+is arbitrary\todo{MS: tohle slovo je prilis silny.
+Veta by spis mela vysvetlit, ze jsme si neco vybrali, protoze je nam to v postate jedno.
+Ale zaroven si uvedomujeme, ze to nejak ovlivni vysledek a ze v ultimatnim super-toolu, by se na vsech ostatni paramatrech dalo conditionovat.} and fixed.
+The prover needs to support refutational reasoning on \gls{cnf} problems
+and use a term simplification ordering parameterized by a symbol precedence.
+For example, the \glspl{atp} \vampire{} and E satisfy this requirement.
+Note that both of these provers support the \gls{kbo} and \gls{lpo} term simplification ordering schemes,
+and that each of these schemes is parameterized by a symbol precedence.
+
+As outlined in \cref{sec:generating},
+it is necessary to train a model of symbol costs.
+The model is a \gls{gcn}.
+
+\todo[inline]{Include a metagraph and an example graph of a problem.}
+\todo[inline]{Compare to HINs}
+% https://medium.com/@jason_trost/heterogeneous-information-networks-and-applications-to-cyber-security-23b245461adb
+
+Since it is not obvious what the target symbol cost values should be,
+the symbol cost model is not trained directly.
+Instead, it is plugged into a classifier that predicts,
+given a problem $P$ and a pair of precedences $\pi_0, \pi_1$,
+which of the two precedences yields a better performance on $P$.
+
+The symbol cost model is trained by plugging the model into a classifier
+that is trained to predict which of a pair of precedences
+yields a better performance on an arbitrary problem.
 
@@
 
-We define precedence cost:
+We define the precedence cost:
 $$
@@
 
-Note that we can weight the symbols with an arbitrary non-decreasing function $f$ of symbol index:
+Note that we can weight the symbols with an arbitrary nondecreasing function $f$ of symbol index:
 $$
@@
 We model the probability of the event "$\pi_0$ is better than $\pi_1$"
-by the sigmoid of $\CostPrecPair(\pi_0, \pi_1)$:https://www.overleaf.com/project/5f75a50ba1a0930001ce1162
+by the sigmoid of $\CostPrecPair(\pi_0, \pi_1)$:
 $$
@@
 
-\section{Evaluation}
+\section{Experimental evaluation}
 \label{sec:evaluation}
+
+\input{evaluation}
 
@@
 
+MS: my sami (PAAR paper) jsem si related workem. Budem se vuci tomu muset vymezit.
+Jinak me ale nic moc bezprostredniho nenepada a nevim tedy, jestli se tedy primo
+nutit do sekce s timto nazvem!
+
 \section{Conclusion}
 
+\subsection{Future work}
+
+Generalization from trail acc to val acc may be improved.
+
+Highest val accuracy does not transfer to highest ATP success rate. Generalization to ATP is sub-par.
+
+\section*{Acknowledgments}
+% > Acknowledgements should generally be placed in an unnumbered subsection at the end of the paper.
+
+% https://sgs.cvut.cz/index.php?action=faq
+% This work was supported by the Grant Agency of the Czech Technical University in Prague, grant No. SGS...
+
+This work was supported by
+the Czech Science Foundation project 20-06390Y
+and
+the Grant Agency of the Czech Technical University in Prague, grant\\
+no.~SGS20/215/OHK3/3T/37.
+
+% > LaTeX users should avoid self-defined environments and use the bibliographic style MathPhySci for computer science proceedings.
+% > It is not possible to have hyperlinks in references.
+\bibliographystyle{splncs04}
 \bibliography{main}

### 2021-02-12 main.tex
Remove an accidentally inserted URL
Add a todo

@@
 \begin{abstract}
-\input{abstract}https://www.overleaf.com/project/5f75a50ba1a0930001ce1162
+\input{abstract}
 \end{abstract}
@@
 
-\subsection{Loss function} \todo{MS: tady jsem zatim skoncil...}
+\subsection{Loss function} 
 \label{sec:loss}
@@
 
-Given a problem $P$, a symbol cost model $c : \cnf \to \re^*$
-\todo{Confusing?}
+Given a problem $P$, a symbol cost model 
+\todo{MS: Zvidavy invalida Jirka Karasek: a co ze je to ten model? 
+Mohl byste to to prosim nekde driv vysvetlit?}
+$c : \cnf \to \re^*$
+\todo{MS: Mozna by se dalo zbavit lehce podivneho $\re^*$ tim,
+ze model bude funkce $(P \in \cnf, s \in \Sigma_P) \to \re$?
+Zas pak nepujde pouzivat zapis skalarniho soucinu; hmmm.}
 returns a vector of costs of the symbols of $P$:
@@
 by taking the weighted sum of symbol costs:
-$$
+\begin{equation} \label{eq:model_cost}
 C(\Prec | P)
@@
 = k(n) \DotProd{c(P)}{\inv{\Prec}}
-$$
+\end{equation}
 Note that the value of $C$ is minimized by a precedence that orders the symbols by their costs in non-increasing order.
 \todo{Discuss, prove.}
+\todo{Mention here that minimizing C yields the best precedence.}
 
@@
 then the precedence cost is equal to $c_0$ irrespective of the signature length $n$:
-\begin{equation} \label{eq:model_cost}
+$$
 C(\Prec | P) = \frac{2}{n(n+1)} \sum_{i=1}^n c_0 \cdot i = c_0
-\end{equation}
+$$
 
@@
 \todo{Fix this. Ensure the polarity is sound.}
+\todo{MS: zatim chybi vysvetleni $\sigmoid$.}
+\todo{MS: duvod proc mi v tomhle kontextu moc nesedi mluvit o pravdepodobnosti
+je ten, ze bez dalsiho vysvetlovani to vypada, ze si myslime, ze
+kdyz pomoci $\sigmoid$ splacnem v podstate libovolne hodnoty do
+intervalu $(0,1)$, zecne to automaticky fungovat jako pravdepodobnost.}
 \begin{align*}
@@
 \end{align*}
-It is easy to see\todo{MS: Bez znalosti $\sigmoid$ uplne ne ;)} that $p(\Better{\PrecBetter}{\PrecWorse} | P) > 0.5$ if and only if $C(\PrecWorse | P) > C(\PrecBetter | P)$,
+It is easy to see that $p(\Better{\PrecBetter}{\PrecWorse} | P) > 0.5$ if and only if $C(\PrecWorse | P) > C(\PrecBetter | P)$,
 and that the value of $p$ can be increased by increasing $C(\PrecWorse | P)$ or decreasing $C(\PrecBetter | P)$.
@@
 
+\todo{MS: HIN bych povazoval za pro CADE-people neznamuy pojem.
+Bude treba uvest aspon jednou vetou. Mozna neco citovat?}
+
 Every \gls{cnf} problem can be represented by a \gls{hin} with the network schema shown in \cref{fig:CnfSchema}.\todo{MS: Mel jsem chut to opravit na velke "Fig.", ale s makrem se mi hadat nechce ;)}
@@
 % Referenced from: https://docs.dgl.ai/en/0.5.x/generated/dgl.DGLHeteroGraph.metagraph.html
+\todo{MS: Filosoficka k ``can be represented''; mozna by se mohlo nekde objevit:
+Snazime se do struktury HIN ``otisknout'' celou strukturu CNF (jak jsem rikal,
+znamena to, ze zobrazeni je proste), abychom siti nevzali moznost ``vedet o problemu
+uplne vsechno'' (az na veci, na kterych nezalezi jako poradi literaly v klauzulich, etc).
+Ta filosoficka poznamka je o tom, ze pro dobre uceni tohle vlastne vubec nemusi byt treba,
+ze nejaky ``hrubsi otisk'' by mohl stacit tez (a byt treba mensi),
+ale my nevime, jak takovy zvolit. }
 
@@
 the recommender produces a precedence $\pi$ of symbols from $\symbols$.
+\todo{MS: proc nepouzivat znaceni z predchoziho clanku, kdy $P = (\symbols,\mathit{Cl})$?}
 In order to generate the precedence,
@@
 The training is performed using a fixed \acrlong{atp}.
+\todo{MS: zase spis preferuj cinny rod. A klidne muzes proste rict, ze pouzivame vampira :)}
 The configuration of the prover,
@@
 and that each of these schemes is parameterized by a symbol precedence.
+\todo{MS: Jak jsme se o tom bavili; v ramvi Occamovky neni treba zminovat LPO.}
 
@@
 
-We model the probability of the event "$\pi_0$ is better than $\pi_1$"
+We model the probability of the event ``$\pi_0$ is better than $\pi_1$''
 by the sigmoid of $\CostPrecPair(\pi_0, \pi_1)$:
@@
 
+\todo{MS: zvazit, jestli nerozepsat zvlast Martin, zvlast Filip.
+Pripadne se zeptat Hanky, jestli bychom nemeli nejak vypichnout
+jen GACR.}
+
 This work was supported by
-the Czech Science Foundation project 20-06390Y
+the Czech Science Foundation project 20-06390Y,
+the project RICAIP no. 857306 under the EU-H2020 programme,
 and

### 2021-02-13 main.tex
komenty; presun eq:model_cost

@@
 = k(n) \DotProd{c(P)}{\inv{\Prec}}
-$$
+\end{equation}
 Note that the value of $C$ is minimized by a precedence that orders the symbols by their costs in non-increasing order.

### 2021-02-13 evaluation.tex
Clean up some todos

@@
 such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop.
-\todo{Justify saturation loop iterations as a proxy for success.}
-\todo{Reference a detailed explanation of saturation loop iterations.}
+\todo{FB: Justify saturation loop iterations as a proxy for success.}
+\todo{FB: Reference a detailed explanation of saturation loop iterations.}
 
@@
 and if the number of iterations of the saturation loop with $\PrecBetter$ is smaller than with $\PrecWorse$.
-\todo{FB: Use notation for saturation loop iterations if the notation was established earlier.}
+\todo{FB: Use notation for saturation loop iterations if the notation was established earlier. If failure is denoted by $\infty$, we can simply use $<$.}
 If one of the two precedences is recognized as better,
@@
 % val&graphified: 7648
-\todo{MS: tady ale lidi bude okamzite zajimat, kolik teda tech problemu na kazde strane zbylo. A jeste by nebylo lepsi vzit nejdriv ty ``male'' problemy a pak teprve pulit.}
+\todo{MS: jeste by nebylo lepsi vzit nejdriv ty ``male'' problemy a pak teprve pulit.}
 
@@
 \todo{FB: Add links to Neptune runs?}
+\todo{FB: Add results for function precedences.}
+\todo{FB: Try to evaluate a recommender that uses both predicate and function models.}
 
@@
 
-\todo{Add results for function precedences.}
-\todo{Try to evaluate a recommender that uses both predicate and function models.}
-\todo{Add discussion.}
+\todo{FB: Add discussion.}
 \todo{FB: Evaluate on problems larger than 100k nodes.}

### 2021-02-13 evaluation.tex
Clarify the role of baselines

@@
 a precedence is generated by the trained recommender
-and Vampire is run using this precedence.
-The results are averaged over 5 runs to reduce the effect of noise in the computation wall clock time.
+and Vampire is run using this precedence and a wall clock time limit of 10 seconds.
+The results are averaged over 5 runs to reduce the effect of noise due to wall clock time limit.
+As a baseline, the performance of Vampire with the \texttt{frequency} precedence heuristic was evaluated
+with the same time limit.
 

### 2021-02-13 evaluation.tex
Explain that we ignore the time to preprocess

@@
 
+To generate a precedence for a problem,
+the recommender first converts the problem to a machine-friendly \gls{cnf} format,
+then converts the \gls{cnf} to a graph,
+then predicts symbol costs using the \gls{gcn} model
+and finally orders the symbols by their costs to produce the precedence.
+To simplify the experiment, the time limit is only imposed on the Vampire run
+and excludes the time taken by the recommender to generate the precedence.
+\todo{Update if we include the preprocessing time.}
+
 \begin{table*}
@@
 
-\todo{Mention: time to compute graphs and precedences is excluded from the time.}
-
 \todo{FB: Add discussion.}

### 2021-02-13 main.tex
par poznamek
Clean up some todos
Add some todos

--- 2021-02-12 main.tex
@@
 
-\todo[inline]{GCN? Backprop?, gradient descent, loss, gradient}
+\todo[inline]{GCN? Backprop?, gradient descent, loss, gradient, epoch}
 
@@
 \label{sec:architecture}
+
+\todo{Describe problem again, this time precisely / technically.}
+\todo{Prove that minimizing precedence cost corresponds to sorting by symbol cost.}
+\todo{Advantage of using pairs of precedences: we need to solve classification rather than regression.}
+\todo{Intuice: snazime se nastavit costy tak, aby co nejvic dvojic dopadlo spravne.}
+\todo{Some pairs of precedences are not informative. We hope that the non-systematic examples will cancel each other out.}
+\todo{Compare our GCN to Michael, Mirek etc.}
 

### 2021-02-13 architecture.tex
Clean up Preliminaries
and divide introduce dedicated files for sections
Preliminaries and Architecture.

--- 2021-02-13 main.tex
@@
-\documentclass[runningheads]{llncs}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage[english]{babel}
-\usepackage[binary-units=true,detect-weight=true]{siunitx}
-
-% How to write a paper:
-% https://mj.ucw.cz/papers/jakpsat.pdf
-% Jones 2016: https://www.microsoft.com/en-us/research/academic-program/write-great-research-paper/
-% AWR: https://jazyky.fel.cvut.cz/vyuka/RPP/BE9M04AKP/
-
-% PAAR paper: https://github.com/filipbartek/learning-precedences-from-elementary-symbol-features/releases/download/paar2020%2Fceur-2/Learning_Precedences_from_Simple_Symbol_Features.pdf
-
-\input{preamble}
-\input{glossary}
-\input{front}
-
-\usepackage[pdf]{graphviz}
-\usepackage{tikz}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-\input{abstract}
-\end{abstract}
-
-\section{Introduction}
-
-\input{introduction}
-
-\section{Preliminaries}
-% Terminology
-
-\todo[inline]{Add: brief exposure of FOL and saturation-based proving with terms possibly emphasized.}
-\todo[inline]{If space is left: define KBO.}
-\todo[inline]{If space is left: show resolution and superposition rules. Explain how KBO influences them.}
-\todo[inline]{Mention lcm predicate. Cite the Vampire article. Voronkov: transfinite KBO - see section Notes on implementation
-
-Mention: Vampire sets all KBO symbol weights to 1.
-
-In Vampire: simple TKBO - level
-
-We use TKBO to increase the impact of predicate precedence.}
-\todo[inline]{Get inspiration from PAAR paper.}
-
-\vampire{} \cite{10.1007/978-3-642-39799-8_1}
-is a representative
-of the state-of-the-art \gls{fol} \gls{atp} design.
-\todo{Move into Introduction.}
-
-%\vampire{} is a saturation-based prover.
-%Given a \gls{fol} problem,
-%\vampire{} converts the problem into \gls{cnf}.
-%and proceeds to saturate the set of clauses
-%by repeated application of inference rules.
-
-%\vampire{} searches for a proof by applying the rules
-%of the superposition inference system
-%\cite{10.1007/978-3-642-39799-8_1}.
-
-% AWR candidate
-Proof search in Vampire is crucially constrained
-by a simplification ordering on terms.
-Being refutation-based and saturation-based,
-Vampire searches for a contradiction
-by iteratively inferring clauses provable from the input clauses.
-The inferences
-
-explores the space of clauses provable
-from the input formulas
-by applying the rules of superposition inference system.
-This process continues until a contradiction is inferred,
-the processed clause set is saturated,
-or the execution hits a resource limit.
-
-During the proof search,
-Vampire explores the space of provable clauses
-by applying inference rules to clauses
-that have already been proven.
-
-% AWR candidate
-Simplification ordering on terms
-influences the proof search in Vampire on two levels.
-First, the inferences on each clause are limited
-to the selected literals.
-\todo{Cite Bachmair Ganzinger or Handbook of AR, chapter 2. For literal selection. Inspiration: Selecting the selection.}
-In each clause,
-either a negative literal or all the maximal literals are selected.
-The maximality is evaluated
-according to the simplification ordering.
-% Note: The selection function Total does not use the simplification ordering.
-Second, the simplification ordering orients some of the equalities
-to prevent superposition and equality factoring
-from inferring redundant complex conclusions.
-In each of these two roles,
-the simplification ordering may impact the direction and,
-in effect, the length of the proof search.
-
-The inference system used in the state-of-the-art \gls{fol} \gls{atp} \vampire{}
-is parameterized by a simplification ordering on terms.
-\vampire{} uses the superposition inference system \cite{}.
-
-The \gls{atp} \vampire{} uses superposition inference system.
-
-Vampire supports two simplification term ordering classes:
-\gls{lpo} and \gls{kbo}.
-
-The superposition inference system \cite{} used in Vampire is parameterized
-by symbol precedence.
-
-% Example: It seems that a classical example for KBO an orienting equations is group theory axioms.
-
-The choice of symbol precedence may affect the length of a proof search to a great extent.
-
-Given a \gls{fol} problem,
-determining a symbol precedence that leads to a fast proof search is a nontrivial task.
-
-\todo[inline]{Define "CNF" as quantifier-free CNF FOL with equality.}
-\todo[inline]{Define "signature".}
-% https://en.wikipedia.org/wiki/First-order_logic
-
-\todo[inline]{GCN? Backprop?, gradient descent, loss, gradient, epoch}
-
-\section{Architecture}
-\label{sec:architecture}
-
 \todo{Describe problem again, this time precisely / technically.}
@@
 $$
-
-\section{Experimental evaluation}
-\label{sec:evaluation}
-
-\input{evaluation}
-
-\section{Related work}
-
-MS: my sami (PAAR paper) jsem si related workem. Budem se vuci tomu muset vymezit.
-Jinak me ale nic moc bezprostredniho nenepada a nevim tedy, jestli se tedy primo
-nutit do sekce s timto nazvem!
-
-\section{Conclusion}
-
-\subsection{Future work}
-
-Generalization from trail acc to val acc may be improved.
-
-Highest val accuracy does not transfer to highest ATP success rate. Generalization to ATP is sub-par.
-
-\section*{Acknowledgments}
-% > Acknowledgements should generally be placed in an unnumbered subsection at the end of the paper.
-
-% https://sgs.cvut.cz/index.php?action=faq
-% This work was supported by the Grant Agency of the Czech Technical University in Prague, grant No. SGS...
-
-\todo{MS: zvazit, jestli nerozepsat zvlast Martin, zvlast Filip.
-Pripadne se zeptat Hanky, jestli bychom nemeli nejak vypichnout
-jen GACR.}
-
-This work was supported by
-the Czech Science Foundation project 20-06390Y,
-the project RICAIP no. 857306 under the EU-H2020 programme,
-and
-the Grant Agency of the Czech Technical University in Prague, grant\\
-no.~SGS20/215/OHK3/3T/37.
-
-% > LaTeX users should avoid self-defined environments and use the bibliographic style MathPhySci for computer science proceedings.
-% > It is not possible to have hyperlinks in references.
-\bibliographystyle{splncs04}
-\bibliography{main}
-
-\end{document}

### 2021-02-13 main.tex
Clean up Preliminaries
and divide introduce dedicated files for sections
Preliminaries and Architecture.

--- 2021-02-13 main.tex
@@
 \section{Preliminaries}
-% Terminology
 
-\todo[inline]{Add: brief exposure of FOL and saturation-based proving with terms possibly emphasized.}
-\todo[inline]{If space is left: define KBO.}
-\todo[inline]{If space is left: show resolution and superposition rules. Explain how KBO influences them.}
-\todo[inline]{Mention lcm predicate. Cite the Vampire article. Voronkov: transfinite KBO - see section Notes on implementation
-
-Mention: Vampire sets all KBO symbol weights to 1.
-
-In Vampire: simple TKBO - level
-
-We use TKBO to increase the impact of predicate precedence.}
-\todo[inline]{Get inspiration from PAAR paper.}
-
-\vampire{} \cite{10.1007/978-3-642-39799-8_1}
-is a representative
-of the state-of-the-art \gls{fol} \gls{atp} design.
-\todo{Move into Introduction.}
-
-%\vampire{} is a saturation-based prover.
-%Given a \gls{fol} problem,
-%\vampire{} converts the problem into \gls{cnf}.
-%and proceeds to saturate the set of clauses
-%by repeated application of inference rules.
-
-%\vampire{} searches for a proof by applying the rules
-%of the superposition inference system
-%\cite{10.1007/978-3-642-39799-8_1}.
-
-% AWR candidate
-Proof search in Vampire is crucially constrained
-by a simplification ordering on terms.
-Being refutation-based and saturation-based,
-Vampire searches for a contradiction
-by iteratively inferring clauses provable from the input clauses.
-The inferences
-
-explores the space of clauses provable
-from the input formulas
-by applying the rules of superposition inference system.
-This process continues until a contradiction is inferred,
-the processed clause set is saturated,
-or the execution hits a resource limit.
-
-During the proof search,
-Vampire explores the space of provable clauses
-by applying inference rules to clauses
-that have already been proven.
-
-% AWR candidate
-Simplification ordering on terms
-influences the proof search in Vampire on two levels.
-First, the inferences on each clause are limited
-to the selected literals.
-\todo{Cite Bachmair Ganzinger or Handbook of AR, chapter 2. For literal selection. Inspiration: Selecting the selection.}
-In each clause,
-either a negative literal or all the maximal literals are selected.
-The maximality is evaluated
-according to the simplification ordering.
-% Note: The selection function Total does not use the simplification ordering.
-Second, the simplification ordering orients some of the equalities
-to prevent superposition and equality factoring
-from inferring redundant complex conclusions.
-In each of these two roles,
-the simplification ordering may impact the direction and,
-in effect, the length of the proof search.
-
-The inference system used in the state-of-the-art \gls{fol} \gls{atp} \vampire{}
-is parameterized by a simplification ordering on terms.
-\vampire{} uses the superposition inference system \cite{}.
-
-The \gls{atp} \vampire{} uses superposition inference system.
-
-Vampire supports two simplification term ordering classes:
-\gls{lpo} and \gls{kbo}.
-
-The superposition inference system \cite{} used in Vampire is parameterized
-by symbol precedence.
-
-% Example: It seems that a classical example for KBO an orienting equations is group theory axioms.
-
-The choice of symbol precedence may affect the length of a proof search to a great extent.
-
-Given a \gls{fol} problem,
-determining a symbol precedence that leads to a fast proof search is a nontrivial task.
-
-\todo[inline]{Define "CNF" as quantifier-free CNF FOL with equality.}
-\todo[inline]{Define "signature".}
-% https://en.wikipedia.org/wiki/First-order_logic
-
-\todo[inline]{GCN? Backprop?, gradient descent, loss, gradient}
+\input{preliminaries}
 
@@
 
-\subsection{Learning to generate good permutations}
-
-Generating good symbol precedences is an instance of a more general task
-of generating permutations of arbitrary length.
-Each input problem corresponds to an input object that specifies the length of a permutation.
-
-Let $X$ be a set of objects.
-Let $l: O \to \nat$ assign each object $x \in X$ its signature length $l(x)$.
-Let $\{x_1, \ldots, x_n\}$ be the training samples.\todo{MS: je mi jasny, ze tu neni poradek, ale i tak; posledni dva odstavce jsou dost zmateny.}
-
-\subsubsection{Binary classification}
-
-Let $p_\theta : X \to \re$ be a binary classification model.\todo{MS: Dobry priklad na to, ktere pojmy je treba vysvetlovat.
-model je znamy pojem v logice, tady ale pouzivame jiny, ML vyznam.
-To by si zaslouzilo komentar.
-Navic pisem
-``binary'' a ``classification'' a neni tu jasny, co je ``binary''
-a co jsou ``classes''. Z pohledu ctenare, ktery o tom zatim neslysel, se misto ``binary classficiation model'' mohlo
-psat ``housenka'' a vyslo by to pro nej na stejno.}
-The model predicts the probability of label $1$.
-Let $(x_i, y_i)$ be the training samples,
-where $x_i \in X$ and $y_i \in Y = \{0, 1\}$.\todo{MS:
-``training'', ``sample'' a ``loss'' jsou dalsi priklady pojmu,
-ktere najednou spadly z hury.}
-
-For a training sample $(x, y) \in \re \times \{0, 1\}$, the binary cross-entropy loss is:
-$$
-L(\theta) = y \log{f_\theta(x)} + (1-y) \log{(1-f_\theta(x))}
-$$
-
-If $y_i = 1$ for all $i$, then the loss can be written in a simpler form:
-$$
-L(\theta) = \log{f_\theta(x)}
-$$
-
-\subsubsection{Permutations}
-
-Let $O$ be a set of objects (or contexts).
-Given an object $o \in O$, let $\Sigma(o)$ be its signature.
-Let $x_i = (o_i, \pi_i, \rho_i)$, where $o_i \in O$
-and $\pi_i, \rho_i \in \Perm(\Sigma(o_i))$.
-Let $y_i \in \{0, 1\}$.
-
-Let $p_\theta: X \to Y$.
-
-Loss:
-$$
-L(\theta) = \log{p_\theta(x)}
-$$
-
-Let $c_\theta(o, s)$ be the predicted cost of symbol $s$.
-Then:
-$$
-p_\theta(o, \pi, \rho) = C_\theta(o, \pi) - C_\theta(o, \rho)
-$$
-
-$$
-C_\theta(o, \pi) = \sum_{i=1}^{l(o)}{c(o, \pi_i)}
-$$
-
-\begin{align*}
-L(\theta) &= \log{p_\theta(o, \pi, \rho)} \\
-&= \log{(C_\theta(o, \pi) - C_\theta(o, \rho))} \\
-&= \log{(\sum_{i=1}^{l(o)}{c(o, \pi_i)} - \sum_{i=1}^{l(o)}{c(o, \rho_i)})} \\
-&= \log{\sum_{i=1}^{l(o)}{c(o, \pi_i) - c(o, \rho_i)}} \\
-\end{align*}
-
-If $c$ is differentiable,
-we can propagate loss gradients into it.
-
-\subsection{Notation}
-
-We denote the set of all finite vectors over $\re$ by $\re^* = \bigcup_{n=1}^\infty{\re^n}$.
-
-Dot product: $\DotProd{x}{y} = \sum_{i=1}^n x_i \cdot y_i$ for $x, y \in \re^n$.
-
-For any $n \in \nat$, we denote the set of all permutations over the set $\{1, \ldots, n\}$ by $\Perm{n}$.
-Permuting a vector $x = (x_1, \ldots, x_n) \in \re^n$ by a permutation $\pi = (\pi_1, \ldots, \pi_n) \in \Perm{n}$ yields the vector $\pi(x) = (x_{\pi_1}, \ldots, x_{\pi_n})$.
-$\inv{\pi}$ denotes the permutation inverse to $\pi$.
-$\inv{\pi} = ...$.
-\todo{Define permutation inversion.}
-\todo{MS: Mozna ani ne.
-Ono je obcas tezky zavest a pouzivat presnout matematickou notaci, ktera se navic muze stavat neprehlednou, kvuli te presnosti.
-Na druhou stranu, intuitivne, kazdy vi, co by to mela byt inverzni permutace.
-Takze nerikam psat nepresne veci, ale obcas jde
-zustak vagni s tim, ze vim, ze existuje zpusob jak to udelat presnym.
-A povrchni ctenar to nemusi resit a matematicky zdatny by si ten detail odvodil spravne ...}
-
-\newcommand{\Prec}{\pi}
-\newcommand{\PrecBetter}{\pi}
-\newcommand{\PrecWorse}{\rho}
-
-\subsection{Overview}
-
-Let $\cnf$ be the set of all \gls{cnf} problems.
-Let $P \in \cnf$ be an arbitrary problem.
-\todo{Consider using $F$ (as formula) instead of $P$ to free up P for probability.}
-Let $\signature{P}$ be the signature of $P$, that is a list of all non-logical symbols (predicates and functions)
-\todo{Should we rather use either predicates or functions? Or use a compound signature?}
-that appear in the problem.
-Let $n = \card{\signature{P}}$.
-A symbol precedence $\Prec \in \Perm{n}$ for problem $P$ is a permutation of the symbols of $P$.
-
-\newcommand{\Solver}{S}
-\newcommand{\SolverRun}[2]{\Solver(#1, #2)}
-
-Let $\Solver$ be an \gls{atp} with a fixed computation environment, configuration and time limit.
-The computation of $\Solver$ is assumed to be parameterized by symbol precedence.
-\todo{Discuss. What does this mean?}
-$\SolverRun{P}{\Prec}$ denotes the result of a proof attempt on problem $P$ with symbol precedence $\Prec$.
-$\SolverRun{P}{\Prec} = \top$ if $S$ solves $P$ within the time limit, and $\SolverRun{P}{\Prec} = \bot$ otherwise.
-\todo{MS: vadi zminit pocet iteraci smycky tak, jako v minulem paperu?}
-Since the result is generally non-deterministic in case the time limit is specified in wall clock units,
-we consider $\SolverRun{P}{\Prec}$ to be a random variable with a Bernoulli distribution.
-\todo{Cite?}
-We denote the probability of a successful proof search $\Prob{\SolverRun{P}{\Prec} = \top}$.
-\todo{MS: asi bych se primlouval za to v teto fazi o Bernoullim pomlcet.
-Otazky jsme generovali tak, ze proste porovnavame pocty iteraci saturatcni smycky a pocitame s tim, ze beh je deterministicky.
-To, ze se pozdeji, pri evalu, pouzije perspektiva nahodnosti
-bych uz chapal jako metodiku experimentu a teorii tim nekomplikoval.}
-
-The main task this paper deals with is this:
-Given a problem $P \in \cnf$, generate a symbol precedence $\Prec \in \Perm{n}$ that maximizes $\Prob{\SolverRun{P}{\Prec} = \top}$.
-MS: (Nehlede na to, ze main task by nejspis mel byt vysvetlen mnohem drive...) Asi bych to takhle nestavel. Jak pisu vyse, precijen je
-beh dokazovace deterministicky a brat to nejak Bayesovsky by sice mohlo 
-byt zajimave, ale jeste mnohem tezsi na obhajeni jako ``svetonazor''.
-Co proste priznat nasledujici assumption:
-verime, ze pokud bude model spravne odpovidat na otazky $(P, \pi_1, \pi_2)$ (s pravdepodobnosti $> \SI{50}{\percent}$), povede podle nej vybrana permutace minimalizujici \eqref{eq:model_cost} k rychlemu vyreseni problemu (a tim i idealne k vyreseni problemu, ktere byly drive out of reach.)\todo{MS: koukni prosim, jestli nejaky takovy mame.
-Tj zadna random permutace ho nevyresila, ale naucena sit pak ano!}
-
-Instead of modeling $\Prob{\SolverRun{P}{\Prec} = \top}$ directly,
-the system described in this paper predicts, given a problem $P$ and a pair of precedences $\PrecBetter, \PrecWorse \in \Perm{n}$,
-the probability\todo{MS: tohle je jeden z oficialnich zpusobu,
-jak vysvetlovat neuronky, ale neni nijak jasne do jake miry byva
-$\sigma(\mathit{logits})$ blizko nejake pravdepodobnosti. Za mne by klidne stacilo mluvit o tom, ze se snazime klasifikovat co nejvic dvojic
-spravne a ze na to pouzivame standard techologii neuronek (Binary Cross Entropy loss (against the final layer’s sigmoid non-linearity)). Tj opet hlasuji za to nemluvit zde o pravdepodobnosti. :)}
-\todo{MS: jo, ale pak bude nekde dobre zminit, ze jsme si vedomi, ze dvojice skoro jiste neobsahuji stejne mnozstvi ``signalu'', ze ktereho je mozne se ucit.
-Je to proste vlastnost vybrane metody a v prumeru to nevadi.}
-that $\PrecBetter$ outperforms $\PrecWorse$ in terms of success of proof search.
-This proxy task allows learning from pairs of precedences that both yield a successful proof search but differ in the number of steps taken in the proof search.
-\todo{Explain more.}
-
-% By taking the pairs, we get more data esp. from easy problems.
-% Consider weighting the samples by the result type: quantitative / qualitative etc.
-
-% TODO: Experiments: Increase depth and message size
-
-\begin{figure}[h]
-\caption{System overview}
-\label{fig:SystemOverview}
-\centering
-\usetikzlibrary{shapes}
-\tikzstyle{object} = [rectangle, draw]
-\tikzstyle{input} = [ellipse, draw]
-\tikzstyle{output} = [ellipse, draw]
-
-\begin{tikzpicture}[node distance = 0.5 and 1, ->]
-% https://tex.stackexchange.com/a/332796/202639
-
-\node (problem) [input] {\gls{cnf} problem $P$};
-\node (symbol embeddings) [object] [below=of problem] {Symbol embeddings};
-\node (symbol costs) [object] [below=of symbol embeddings] {Symbol costs};
-\node (symbol precedence) [output] [below=of symbol costs] {Symbol precedence};
-
-\draw (problem) to node [left] {GCN} (symbol embeddings);
-\draw (symbol embeddings) to node [left] {MLP} (symbol costs);
-\draw (symbol costs) to node [left] {Order symbols by their costs} (symbol precedence);
-
-\node (PrecBetter) [input] [right=of problem] {Precedence $\PrecBetter$};
-\node (PrecBetterInv) [object] [below=of PrecBetter] {$\inv{\PrecBetter}$};
-\draw (PrecBetter) to node [right] {Invert} (PrecBetterInv);
-
-\node (PrecWorse) [input] [right=of PrecBetter] {Precedence $\PrecWorse$};
-\node (PrecWorseInv) [object] [below=of PrecWorse] {$\inv{\PrecWorse}$};
-\draw (PrecWorse) to node [right] {Invert} (PrecWorseInv);
-
-\node (PrecDiff) [object] [right=2 of symbol costs] {$\inv{\PrecWorse} - \inv{\PrecBetter}$};
-\node (PrecDiffNormalized) [object] [below=of PrecDiff] {Normalized};
-\node (PrecPairCost) [object] [below=of PrecDiffNormalized] {Precedence pair cost};
-\node (loss) [output] [below=of PrecPairCost] {Loss};
-
-\draw (PrecBetterInv) to (PrecDiff);
-\draw (PrecWorseInv) to (PrecDiff);
-\draw (PrecDiff) to node [right] {Normalize} (PrecDiffNormalized);
-\draw (PrecDiffNormalized) to (PrecPairCost);
-\draw (PrecPairCost) to (loss);
-
-\draw (symbol costs) to (PrecPairCost);
-
-\end{tikzpicture}
-\end{figure}
-
-Fig.~\ref{fig:SystemOverview} \todo{MS: Na figures/tables bez referneci v textu se pohlizi obzvlast nelibe.
-Predpokladam, zes planoval pozdeji popsat, presto zmninuji.
-Konkretne k Fig.~\ref{fig:SystemOverview}:
-Napada me: neslo by precedenci definovat tak, aby uz byla tim $\pi^{-1}$? Invertovani zabira v obrazku skoustu mista, ale pritom
-jde o technicky detail a hlavni myslenku nijak neosvetluje...}
-
-\subsection{Symbol cost model}
-
-The symbol costs are modeled by a \gls{rgcn}.\cite{Schlichtkrull2017}
-\todo{Can I use the term \gls{rgcn} when I use a modified version? Namely, the activation is called earlier.}
-The model is a stack of graph convolutional layers.
-Each layer consists of one differentiable module for each edge type.
-Each module is a dense layer.
-$$
-h_i^{(l+1)} =
-\mathrm{LayerNorm} \Parentheses{h_i^{(l)} + \sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in \mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}}
-$$
-\todo{Include dropout?}
-% Inspiration: https://ufal.mff.cuni.cz/~straka/courses/npfl114/1920/slides.pdf/npfl114-07.pdf - slide 27 - Transformer
-$h_i^{(l)}$ denotes the embedding of node $i$ at layer $l$.
-$\mathcal{R}$ denotes the set of all relations in the graph.
-$\sigma$ denotes the activation function, for example the \gls{relu}.
-$\mathcal{N}_i^r$ denotes the set of neighbors of node $i$ under relation $r$.
-$c_{j, i, r} = \sqrt{\card{\mathcal{N}_j^r}} \sqrt{\card{\mathcal{N}_i^r}}$ is a normalization constant.\cite{kipf2017semisupervised}
-$W_r^{(l)}$ is a trainable weight matrix representing relation $r$ at layer $l$.
-
-Residual...
-Layer norm...
-
-\todo{MS: neni uplne jiste, ze ``CADE people'' oceni presny zapis 
-strutury site, vcetne prvku jako $\mathrm{LayerNorm}$ ve vzorecku.
-Nerikam, ze bychom to meli uplne zatajit, ale popis, ktery je zde, spis
-patri do appendixu (ML paperu). Na te siti vlastne nic originalniho neni,
-tak neni treba vsechno vysvetlit do detailu. Zajimavejsi tu
-potom je az to, jak se problem $P$ ``otiskne'' v topologii grafu. 
-To uz originalni je (a soutezi to s representacemi jako ta Mirkova)
-a popisujes to pak dal.}
-
-\subsection{Loss function} \todo{MS: tady jsem zatim skoncil...}
-\label{sec:loss}
-
-Let $\cnf$ be the set of all \gls{cnf} problems.
-Let $P \in \cnf$ be an arbitrary problem.
-Let $\signature{P}$ be the signature of $P$.
-Let $n = \card{\signature{P}}$.
-
-Given a problem $P$, a symbol cost model $c : \cnf \to \re^*$
-\todo{Confusing?}
-returns a vector of costs of the symbols of $P$:
-$$
-c(P) = (c_1, \ldots, c_n)
-$$
-
-Let $\Prec \in \Perm{n}$ be a precedence of symbols of problem $P$.
-Let $k(n) = \frac{2}{n(n+1)}$ be a normalization factor for precedences of length $n$.
-The symbol cost model $c$ can be extended to a precedence cost model $C$
-by taking the weighted sum of symbol costs:
-$$
-C(\Prec | P)
-= k(n) \sum_{i=1}^n c_{\Prec_i} \cdot i
-= k(n) \sum_{i=1}^n c_i \cdot \inv{\Prec}_i
-= k(n) \DotProd{c(P)}{\inv{\Prec}}
-$$
-Note that the value of $C$ is minimized by a precedence that orders the symbols by their costs in non-increasing order.
-\todo{Discuss, prove.}
-
-Fixing the normalization factor $k(n)$ to the value $\frac{2}{n(n+1)}$
-ensures that costs of precedences of various lengths are commensurable.
-Observe namely that if $c$ assigns each symbol the same cost $c_0$,
-then the precedence cost is equal to $c_0$ irrespective of the signature length $n$:
-\begin{equation} \label{eq:model_cost}
-C(\Prec | P) = \frac{2}{n(n+1)} \sum_{i=1}^n c_0 \cdot i = c_0
-\end{equation}
-
-Let $\PrecBetter, \PrecWorse \in \Perm{n}$ be two symbol precedences over $P$.
-Let $\PrecBetter$ yield a faster proof search on $P$ than $\PrecWorse$, denoted as $\Better{\PrecBetter}{\PrecWorse}$.
-The precedence cost model can be extended to predict the probability that $\PrecBetter$ is better than $\PrecWorse$:
-\todo{Fix this. Ensure the polarity is sound.}
-\begin{align*}
-p(\Better{\PrecBetter}{\PrecWorse} | P)
-&= \sigmoid \SquareBracket{C(\PrecWorse | P) - C(\PrecBetter | P)} \\
-%&= \sigmoid \SquareBracket{k(n) \sum_{i=1}^n c_i \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)} \\
-&= \sigmoid \SquareBracket{k(n) \DotProd{c(P)}{\inv{\PrecWorse} - \inv{\PrecBetter}}}
-\end{align*}
-It is easy to see\todo{MS: Bez znalosti $\sigmoid$ uplne ne ;)} that $p(\Better{\PrecBetter}{\PrecWorse} | P) > 0.5$ if and only if $C(\PrecWorse | P) > C(\PrecBetter | P)$,
-and that the value of $p$ can be increased by increasing $C(\PrecWorse | P)$ or decreasing $C(\PrecBetter | P)$.
-
-We consider the difference $C(\PrecWorse | P) - C(\PrecBetter | P)$
-to be the "logit"\todo{MS: Logit je taky tezky pojem, urcite ne automaticky znamy u ATP people.} score of the pair of precedences $\PrecBetter, \PrecWorse$,
-and denote it by $C(\Better{\PrecBetter}{\PrecWorse} | P)$.
-
-We define the loss of $c$ on the training sample $(\PrecBetter, \PrecWorse, P)$ as binary cross-entropy
-with ground truth $\Better{\PrecBetter}{\PrecWorse}$:
-
-\begin{align*}
-L(\PrecBetter, \PrecWorse, P)
-&= - \log p(\Better{\PrecBetter}{\PrecWorse} | P) \\
-&= - \log \sigmoid \SquareBracket{k(n) \DotProd{c(P)}{\inv{\PrecWorse} - \inv{\PrecBetter}}} \\
-&= - \log \sigmoid \SquareBracket{k(n) \sum_{i=1}^n c_i \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)}
-\end{align*}
-
-The loss is differentiable with respect to the symbol costs:
-\begin{align*}
-\frac{\partial L}{\partial c_i}
-&= -\sigmoid(-C(\Better{\PrecBetter}{\PrecWorse} | P)) \cdot k(n) \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i) \\
-&= (p(\Better{\PrecBetter}{\PrecWorse} | P) - 1) \cdot k(n) \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)
-\end{align*}
-
-This means that it is possible to backpropagate the loss gradient into the symbol cost model. \todo{MS: tohle bude tezky,
-ale ackoliv ML people by tohle uz asi chapali, ATP crowd spis bude
-potrebovat obsirnejsi vysvetleni.}
-
-\subsubsection{Generalization}
-
-Note that this approach is generally applicable to all problems where it is necessary to generate permutations of arbitrary length.
-
-\todo[inline]{Finish.}
-
-\subsection{Symbol cost model}
-
-\subsection{Graph representation of problems}
-
-\newcommand{\ntype}[1]{\texttt{#1}}
-\newcommand{\etype}[1]{\texttt{#1}}
-\newcommand{\epos}{\etype{pos}}
-\newcommand{\eneg}{\etype{neg}}
-
-Every \gls{cnf} problem can be represented by a \gls{hin} with the network schema shown in \cref{fig:CnfSchema}.\todo{MS: Mel jsem chut to opravit na velke "Fig.", ale s makrem se mi hadat nechce ;)}
-% Cite: https://www.kdd.org/exploration_files/V14-02-03-Sun.pdf
-% Referenced from: https://docs.dgl.ai/en/0.5.x/generated/dgl.DGLHeteroGraph.metagraph.html
-
-\begin{figure}[ht]
-\caption{CNF network schema}
-\label{fig:CnfSchema}
-\centering
-\tikzstyle{token} = [rectangle, draw]
-
-\begin{tikzpicture}[node distance = 1 and 2, ->]
-% https://tex.stackexchange.com/a/332796/202639
-
-% Node and edge types:
-% https://docs.google.com/spreadsheets/d/1PCPHEgk6vLxpdpcvB_PGoLx7p4DID6WtvVWy2mDuv4A/edit?usp=sharing
-
-\node (formula) [token] {\ntype{problem}};
-% TODO: Consider removing the Formula nodes.
-\node (clause) [token, below=of formula] {\ntype{clause}};
-\node (atom) [token, below left=of clause] {\ntype{atom}};
-\node (equality) [token, below right=of clause] {\ntype{equality}};
-\node (predicate) [token, left=of atom] {\ntype{predicate}};
-\node (argument) [token, below=of atom] {\ntype{argument}};
-\node (term) [token, below=of argument] {\ntype{term}};
-\node (function) [token, left=of term] {\ntype{function}};
-\node (variable) [token, right=of term] {\ntype{variable}};
-
-\draw (formula) to node [right] {\etype{contains}} (clause);
-\draw (clause) to [bend right] node [above] {\epos{}} (atom);
-\draw (clause) to [bend left] node [below] {\eneg{}} (atom);
-\draw (clause) to [bend left] node [above] {\epos{}} (equality);
-\draw (clause) to [bend right] node [below] {\eneg{}} (equality);
-\draw (clause) to node [above] {\etype{binds}} (variable);
-\draw (atom) to node [above] {\etype{atom\_applies}} (predicate);
-\draw (atom) to node [left] {\etype{atom\_has}} (argument);
-\draw (equality) to node {\etype{equalizes}} (term);
-\draw (equality) to node {\etype{equalizes}} (variable);
-\draw (argument) to [bend right] node [left] {\etype{is}} (term);
-\draw (argument) to [loop left] node [left] {\etype{precedes}} (argument);
-\draw (argument) to node [below] {\etype{is}} (variable);
-\draw (term) to node [above] {\etype{term\_applies}} (function);
-\draw (term) to [bend right] node [right] {\etype{term\_has}} (argument);
-
-\end{tikzpicture}
-\end{figure}
-
-The network of a problem is a directed graph $G = (V, E)$.
-The function $\tau: V \rightarrow A$ maps the nodes to their types:
-
-$$
-A = \{\ntype{problem}, \ntype{predicate}, \ntype{function}, \ntype{clause}, \ntype{atom}, \ntype{equality}, \ntype{term}, \ntype{variable}, \ntype{argument}\}
-$$
-
-The function $\phi: E \rightarrow E$ maps the edges to their types.
-
-\begin{itemize}
-\item The graph representation of problem $P$ contains exactly one root node of type \ntype{problem}.
-\item Each clause is represented by a \ntype{clause} node connected to the root \ntype{problem} node.
-\item Each atom is represented by an \ntype{atom} node (in case the atom is not an equality)
-or an \ntype{equality} node (in case the atom is an equality).
-For each literal occurrence there is an edge connecting the respective atom to the respective clause.
-The type of the edge corresponds to the polarity of the literal:
-\epos{} for positive literal and \eneg{} for negative literal.
-\item Each \ntype{equality} node is connected to two nodes that represent the operands,
-each of which is of type \ntype{term} or \ntype{variable}.
-The commutativity of the equality operator is reflected by the fact that the operand edges are not ordered.
-\item Each \ntype{atom} node is connected to one \ntype{predicate} node that represents the predicate symbol being applied by this atom.
-Note that these edges connect the applications of a predicate symbol across the whole problem.
-\item Each \ntype{atom} node is connected to zero or more \ntype{argument} nodes that represent the argument positions of the atom.
-\item Each pair of \ntype{argument} nodes that correspond to consecutive argument positions is connected by an edge.
-\item Each \ntype{argument} node is connected to a node that represents the argument term,
-which is either a \ntype{term} node or a \ntype{variable} node.
-\item Each \ntype{term} node is connected to one \ntype{function} node that represents the function symbol being applied by this term.
-\item For each variable, there is an edge connecting the \ntype{clause} node of the clause that binds the variable to the \ntype{variable} node that represents the variable.
-\end{itemize}
-
-\todo[inline]{Abstract from the edge types. Focus on the main idea. Technical details may be in technical report or appendix.}
-
-Various levels of term sharing are possible. [continue]
-
-\todo[inline]{Give an example of a problem and its graph.}
-
-\subsection{Generating precedences}
-\label{sec:generating}
-
-When presented with a \gls{cnf} problem $P$ with signature $\symbols$,
-the recommender produces a precedence $\pi$ of symbols from $\symbols$.
-In order to generate the precedence,
-the recommender first assigns a cost value to each symbol
-by invoking a symbol cost model (a trained \gls{gcn}) on a graph representation of $P$.
-Ordering the symbols by their predicted costs in nondecreasing order yields the precedence $\pi$.
-
-\subsection{Training}
-
-The training is performed using a fixed \acrlong{atp}.
-The configuration of the prover,
-including for example saturation algorithm, age-weight ratio, and term ordering scheme,
-is arbitrary\todo{MS: tohle slovo je prilis silny.
-Veta by spis mela vysvetlit, ze jsme si neco vybrali, protoze je nam to v postate jedno.
-Ale zaroven si uvedomujeme, ze to nejak ovlivni vysledek a ze v ultimatnim super-toolu, by se na vsech ostatni paramatrech dalo conditionovat.} and fixed.
-The prover needs to support refutational reasoning on \gls{cnf} problems
-and use a term simplification ordering parameterized by a symbol precedence.
-For example, the \glspl{atp} \vampire{} and E satisfy this requirement.
-Note that both of these provers support the \gls{kbo} and \gls{lpo} term simplification ordering schemes,
-and that each of these schemes is parameterized by a symbol precedence.
-
-As outlined in \cref{sec:generating},
-it is necessary to train a model of symbol costs.
-The model is a \gls{gcn}.
-
-\todo[inline]{Include a metagraph and an example graph of a problem.}
-\todo[inline]{Compare to HINs}
-% https://medium.com/@jason_trost/heterogeneous-information-networks-and-applications-to-cyber-security-23b245461adb
-
-Since it is not obvious what the target symbol cost values should be,
-the symbol cost model is not trained directly.
-Instead, it is plugged into a classifier that predicts,
-given a problem $P$ and a pair of precedences $\pi_0, \pi_1$,
-which of the two precedences yields a better performance on $P$.
-
-The symbol cost model is trained by plugging the model into a classifier
-that is trained to predict which of a pair of precedences
-yields a better performance on an arbitrary problem.
-
-\begin{figure}[ht]
-\caption{Architecture overview}
-\centering
-\digraph[scale=0.4]{precedencepairclassifierdetailed}{
-	graph [splines=ortho];
-	node [shape=renctangle, fontsize=20];
-	edge [fontsize=20];
-	fol [label="FOL problem", shape=oval];
-	pi0 [shape=oval, label=<&pi;<SUB>0</SUB>>];
-	pi1 [shape=oval, label=<&pi;<SUB>1</SUB>>];
-	invpi0 [label=<&pi;<SUB>0</SUB><SUP>-1</SUP>>];
-	invpi1 [label=<&pi;<SUB>1</SUB><SUP>-1</SUP>>];
-	cnf [label="Clause normal form (CNF)"];
-	symbolembeddings [label="Symbol embeddings"];
-	symbolcosts [label="Symbol costs"];
-	pi1pi0 [label="Inverse precedence difference"];
-	normalized [label="Normalized inverse precedence difference"];
-	paircost [label="Precedence pair cost"];
-	fol -> cnf [xlabel=" Vampire "];
-	cnf -> symbolembeddings [xlabel=< <B>Graph Convolution Network</B> >];
-	symbolembeddings -> symbolcosts [xlabel=< <B>Feed-forward neural network</B> >, style=bold];
-	symbolcosts -> paircost [style=bold];
-	paircost -> loss [xlabel=" Binary cross-entropy ", style=bold];
-	loss [label="Loss", shape=oval];
-	pi0 -> invpi0 [xlabel=" Invert "];
-	pi1 -> invpi1 [xlabel=" Invert "];
-	invpi0 -> pi1pi0;
-	invpi1 -> pi1pi0;
-	pi1pi0 -> normalized [xlabel=" Normalize "];
-	normalized -> paircost;
-	symbolprecedence [label="Symbol precedence", style=dashed];
-	symbolcosts -> symbolprecedence [xlabel=" Order symbols by their costs ", style=dashed];
-}
-\end{figure}
-
-\subsection{Layers}
-'
-\begin{enumerate}
-\item Problem -> symbol embeddings
-\item Symbol embedding -> symbol cost
-\item Symbol costs -> precedence cost
-\end{enumerate}
-
-\subsection{Cost models}
-
-%Let $\CostSym: \symbols \rightarrow \re$ be a differentiable symbol cost model.
-
-We define the precedence cost:
-$$
-\CostPrec(\pi) =
-C \sum_{1 \leq i \leq n} \CostSym(\pi(i)) \cdot i =
-C \sum_{1 \leq i \leq n} \CostSym(s_i) \cdot \inv{\pi}(s_i)
-$$
-Precedence cost is minimized by $\pi$ that orders the symbols by their costs in non-increasing order
-($\forall (1 \leq i < j \leq n) . (\CostSym(\pi(i)) \geq \CostSym(\pi(j)))$).
-
-Note that we can weight the symbols with an arbitrary nondecreasing function $f$ of symbol index:
-$$
-\CostPrec(\pi) =
-C \sum_{1 \leq i \leq n} \CostSym(\pi(i)) \cdot f(i) =
-C \sum_{1 \leq i \leq n} \CostSym(s_i) \cdot f(\inv{\pi}(s_i))
-$$
-
-We set $C = \frac{2}{n(n+1)}$ so that $\CostSym(s) = 1$ for all $s$ implies $\CostPrec(\pi) = 1$ for all $\pi$.
-
-% Note that we use this orientation because the TensorFlow metric BinaryCrossentropy classifies 0 as negative and we use the value 0 for "failed to classify" logits.
-Given a pair of precedences $\pi_0, \pi_1$,
-we define the log-odds of the event "$\pi_0$ is better than $\pi_1$":
-$$
-\CostPrecPair(\pi_0, \pi_1) =
-\CostPrec(\pi_1) - \CostPrec(\pi_0) =
-C \sum_{1 \leq i \leq n} \CostSym(s_i) \cdot [\inv{\pi_1}(s_i) - \inv{\pi_0}(s_i)]
-$$
-Clearly $\CostPrecPair(\pi_0, \pi_1) > 0$ iff $\CostPrec(\pi_0) < \CostPrec(\pi_1)$.
-For a pair of precedences about which we know that $\pi_0$ is better than $\pi_1$,
-we want $\CostPrecPair(\pi_0, \pi_1) > 0$.
-
-We model the probability of the event "$\pi_0$ is better than $\pi_1$"
-by the sigmoid of $\CostPrecPair(\pi_0, \pi_1)$:
-$$
-p(\pi_0, \pi_1) = \sigmoid(\CostPrecPair(\pi_0, \pi_1))
-$$
-
-We use the binary cross-entropy loss to train the model.
-Given a pair of precedences such that $\pi_0$ is better than $\pi_1$,
-the loss is as follows:
-$$
-Loss(\pi_0, \pi_1) = -\log(\sigmoid(\CostPrecPair(\pi_0, \pi_1)))
-$$
+\input{architecture}
 

### 2021-02-13 preliminaries.tex
Clean up Preliminaries
and divide introduce dedicated files for sections
Preliminaries and Architecture.

% Terminology

\todo[inline,author=FB]{Get inspiration from PAAR paper.}

\subsection{Saturation-based theorem proving}

A \emph{\acrfull{fol} problem} consists of a set of premise formulas and a conjecture formula.
In a \emph{refutation-based} \emph{\acrfull{atp}},
proving that the premises entail the conjecture
is reduced to proving that the premises together with the negated conjecture entail a \emph{contradiction}.
The most popular \gls{fol} \glspl{atp}, such as Vampire \cite{10.1007/978-3-642-39799-8_1}, E \cite{10.1007/978-3-030-29436-6_29}, or SPASS \cite{},
start the proof search by converting the input \gls{fol} formulas to an equisatisfiable representation in \emph{quantifier-free \gls{cnf}}.\cite{Harrison2009}
We denote a problem in \gls{cnf} as $P = (\Sigma, \mathrm{Cl})$,
where $\Sigma$ is a list of all non-logical symbols in the problem,
and $\mathrm{Cl}$ is the set of the clauses of the problem (including the negated conjecture).

Given a problem $P$ in \gls{cnf},
a \emph{saturation-based} \gls{atp} searches for a refutational proof
by iteratively applying the \emph{inference rules} from the given \emph{calculus}
to infer new clauses entailed by $\mathrm{Cl}$.
As soon as the empty clause, denoted by $\square$, is inferred,
the prover concludes that the premises entail the conjecture,
the sequence of inferences taken constituting a proof.
In case the premises do not entail the conjecture,
the proof search continues until
the set of the inferred clauses is saturated with respect to the inference rules.
In the common setting of time-restricted proof search, a timeout may end the process prematurely.

\todo[inline,author=FB]{Add terminology: saturation iteration, $\bot$.}

%\vampire{} is a saturation-based prover.
%Given a \gls{fol} problem,
%\vampire{} converts the problem into \gls{cnf}.
%and proceeds to saturate the set of clauses
%by repeated application of inference rules.

\subsection{Superposition calculus}

\todo[inline,author=FB]{Mention: Vampire, superposition calculus, inference rules (resolution, superposition), simplification ordering on terms, KBO, symbol precedence. How does the STO influence the rules? Mention transfinite KBO (lcm predicate), which is only relevant to literal selection. Cite Voronkov: transfinite KBO (see section Notes on implementation). We use TKBO to increase the impact of predicate precedence. Vampire sets all KBO weights to 1.}

%\vampire{} searches for a proof by applying the rules
%of the superposition inference system
%\cite{10.1007/978-3-642-39799-8_1}.

\subsubsection{\Gls{sot}}

% AWR candidate
Simplification ordering on terms
influences the proof search in Vampire on two levels.
First, the inferences on each clause are limited
to the selected literals.
\todo{Cite Bachmair Ganzinger or Handbook of AR, chapter 2. For literal selection. Inspiration: Selecting the selection.}
In each clause,
either a negative literal or all the maximal literals are selected.
The maximality is evaluated
according to the simplification ordering.
% Note: The selection function Total does not use the simplification ordering.
Second, the simplification ordering orients some of the equalities
to prevent superposition and equality factoring
from inferring redundant complex conclusions.
In each of these two roles,
the simplification ordering may impact the direction and,
in effect, the length of the proof search.

\subsubsection{\Acrfull{kbo}}

% Example: It seems that a classical example for KBO an orienting equations is group theory axioms.

\subsubsection{Symbol precedences}

\todo[inline,author=FB]{Define terminology.}

\subsection{\Acrlongpl{gcn}}

\todo[inline,author=FB]{GCN? Backprop?, gradient descent, loss, gradient, epoch}

### 2021-02-13 introduction.tex
a > an [FOL problem]

@@
 % For this reason the article is "an".
-When presented with an \gls{fol} problem,
+When presented with a \gls{fol} problem,
 a \definiendum{saturation-based} \gls{atp} negates the conjecture (as a first step of proof by contradiction)

### 2021-02-13 introduction.tex
Add a catchy paragraph in the beginning of Introduction

@@
 % State your thesis/claim
+
+\todo[inline,author=FB]{Try to use the first page for something more flashy than exposure of saturation-based automated proving.
+Ideas: catchy puzzle-like example, abstract description of the crucial challenge etc.}
+
+Choosing the next inference to apply is the most important decision point in the state-of-the-art
+\todo{FB: Add "saturation-based"?}
+\glspl{atp} for \gls{fol}.
+Since the most popular \glspl{atp} use the superposition calculus with literal selection,
+the \gls{sot}, such as the \gls{kbo}, plays a key role in guiding the proof search.
+The \gls{kbo} is typically specified by a symbol precedence,
+that is a permutation of the non-logical symbols of the input problem.
+Each of the commonly used precedence heuristics orders the symbols
+lexicographically according to a small number of simple symbol properties,
+such as the number of occurrences in the input problem,
+% vampire --symbol_precedence frequency
+the arity of the symbol, or
+% vampire --symbol_precedence arity
+%occurrence in the conjecture,
+% vampire --symbol_precedence_boost goal
+%number of occurrences in unit clauses, or
+% vampire --symbol_precedence_boost units
+whether or not the symbol was introduced by the Tseytin transformation or skolemization.
+% vampire --introduced_symbol_precedence top
+Since none of the simple heuristics fits all the problems,
+choosing a symbol precedence that guides the proof search on a problem efficiently towards the refutation
+remains to be an intriguing task.
+This paper explores the possibility of solving this task by training a neural networks
+on the results of running the \gls{atp} Vampire \cite{10.1007/978-3-642-39799-8_1} with randomly sampled precedences.
 

### 2021-02-14 preliminaries.tex
Qualify CNF as first-order

@@
 The most popular \gls{fol} \glspl{atp}, such as Vampire \cite{10.1007/978-3-642-39799-8_1}, E \cite{10.1007/978-3-030-29436-6_29}, or SPASS \cite{},
-start the proof search by converting the input \gls{fol} formulas to an equisatisfiable representation in \emph{quantifier-free \gls{cnf}}.\cite{Harrison2009}
+start the proof search by converting the input \gls{fol} formulas to an equisatisfiable representation in \emph{quantifier-free first-order \gls{cnf}}.\cite{Harrison2009}
 We denote a problem in \gls{cnf} as $P = (\Sigma, \mathrm{Cl})$,

### 2021-02-14 introduction.tex
Improve the first paragraph of Introduction

--- 2021-02-13 introduction.tex
@@
 % Formal methods for verification (survey): https://arxiv.org/pdf/1912.03028.pdf
-
-\todo[author=Filip,inline]{Consider an alternative approach: Start with an example problem, rewrite in two ways, describe how do state-of-the-art provers differentiate between these two ways (by symbol precedence), ...}
 
@@
 % State your thesis/claim
+
+Choosing the next inference to apply is arguably the most important decision point in the state-of-the-art
+\todo{FB: Add "saturation-based"?}
+\glspl{atp} for \gls{fol}.
+Since the most popular \glspl{atp} use the superposition calculus with literal selection \cite{},
+the \gls{sot}, such as the \gls{kbo} \cite{Knuth1983},
+plays an important role in restricting the inferences and thus guiding the proof search.
+The \gls{kbo} is typically specified by a symbol precedence,
+that is a permutation of non-logical symbols of the input problem.
+Each of the commonly used precedence heuristics orders the symbols
+lexicographically according to a small number of simple
+\todo{FB: Is using the "simple" terminology from PAAR paper better than trying to find a better term?}
+symbol properties,
+such as the number of occurrences in the input problem,
+% vampire --symbol_precedence frequency
+the arity of the symbol, or
+% vampire --symbol_precedence arity
+%occurrence in the conjecture,
+% vampire --symbol_precedence_boost goal
+%number of occurrences in unit clauses, or
+% vampire --symbol_precedence_boost units
+whether or not the symbol was introduced in the process of Tseitin transformation \cite{Tseitin1983} or Skolemization \cite{Harrison2009}.
+\todo{FB: Is citing Harrison better than nothing?}
+% vampire --introduced_symbol_precedence top
+Given that each of the heuristics used in practice, up to our knowledge, fails on some problems,
+\todo{Mention that we tried already to find a good simple heuristic by ML.}
+the general task of
+finding a symbol precedence that guides the proof search efficiently on an arbitrary problem
+remains to be intriguing.
+This paper explores the possibility of tackling this task by training a neural network
+on the results of running the \gls{atp} Vampire \cite{10.1007/978-3-642-39799-8_1} with randomly sampled precedences.
+\todo{Ensure that the first paragraph fits on the first page.}
+
+\todo[author=Filip,inline]{Consider an alternative approach: Start with an example problem, rewrite in two ways, describe how do state-of-the-art provers differentiate between these two ways (by symbol precedence), ...}
+
+\todo[inline,author=FB]{Try to use the first page for something more flashy than exposure of saturation-based automated proving.
+Ideas: catchy puzzle-like example, abstract description of the crucial challenge etc.}
 

### 2021-02-15 abstract.tex
comments to the abstract

@@
+% !TEX root = main.tex
+
 % AWR: Guidelines (Unit 7, page 5):
@@
 This paper describes and evaluates a symbol precedence heuristic based on a \acrlong{gcn}.
+\todo{MS: I think we are more than just what one typically understands as a heuristic.
+Because we learn what to recommend from the data.}
+\todo{MS: From that perspectively, the learning itself seems more important than the particular use of a GCN.}
 When trained on proof attempts with random symbol precedences,
 the heuristic outperforms the state of the art by more than \SI{2}{\percent}.
-For the purpose of the evaluation, the symbol precedences predicted by the heuristic
+For the purpose of the evaluation, 
+\todo{MS: ``For the purpose of the evaluation'' je matouci. 
+Ta heuristika prece nema vubec smysl ve svete bez ``symbol precedences for Knuth-Bendix term simplification orderings''.
+Nebo tim chces naznacit, ze by pripadne sla pouzit obecneji? To by se ale muselo asi rict explicitne 
+a nebude to lehke vysvetlit strucne.}
+the symbol precedences predicted by the heuristic
 are used to instantiate Knuth-Bendix term simplification orderings.
@@
 by constraining the superposition calculus inferences.
+\todo{MS: uz i ty ``random symbol precedences'', kterymi to vypraveni nahore zacina potrebuji vampira.
+Mozna bude lepsi, trochu nudne, zacit tim, odkud se berou a na co se pouzivaji precedence
+a teprve pak rict, ze se z nich ucime a pak umime navrhovat nove, lepsi?}
 The evaluation is performed on \acrlong{fol} problems from the \acrshort{tptp} problem library.

### 2021-02-15 introduction.tex
Add a paragraph in Introduction
Add a todo

@@
 
+Modern \gls{fol} \glspl{atp}, such as Vampire, E or SPASS,
+solve \gls{fol} problems by iteratively applying the inference rules of superposition calculus.
+Literal selection and equation orienting are employed to limit the ... while preserving the refutation completeness.
+Both literal selection and equation orienting are determined by \gls{sot}.
+
 A \gls{fol} problem consists of \gls{fol} formulas divided into two categories:
@@
 
+\todo[inline,author=FB]{Mention contributions explicitly.}
+
 \iffalse % AWR draft

### 2021-02-15 abstract.tex
Use the keyword "simplification ordering on terms"
instead of "term simplification ordering".
Update abstract according to MS's suggestions

--- 2021-02-11 abstract.tex
@@
 
-This paper describes and evaluates a symbol precedence heuristic based on a \acrlong{gcn}.
-When trained on proof attempts with random symbol precedences,
-the heuristic outperforms the state of the art by more than 20~\%.
-For the purpose of the evaluation, the symbol precedences predicted by the heuristic
-are used to instantiate Knuth-Bendix term simplification orderings.
-These orderings in turn guide the proof search in the state-of-the-art \acrlong{atp} \vampire{}
-by constraining the superposition calculus inferences.
-The evaluation is performed on \acrlong{fol} problems from the TPTP problem library.
+The state-of-the-art \acrlongpl{atp} for \acrlong{fol}, such as Vampire,
+use \glspl{sot} to constrain the proof search.
+The popular Knuth-Bendix simplification ordering is parameterized by the \emph{symbol precedence}
+\todo{FB: Is it ok to emphasize a word in abstract?}
+-- a permutation of the predicate and function symbols occurring in the input problem.
+The choice of the symbol precedence can have a substantial impact on the length of the proof search.
+
+This paper describes and evaluates a symbol precedence recommender based on a \acrlong{gcn}.
+When trained on proof attempts that use random symbol precedences,
+the recommender outperforms the state-of-the-art heuristic by more than \SI{2}{\percent}.
+The recommender is evaluated on \acrlong{fol} problems from the \acrshort{tptp} problem library.
+\todo{FB: Should I mention Vampire here?}
+\todo{FB: Try to mention that the recommender is signature-agnostic.}
+
+\iffalse
+This paper describes and evaluates a symbol precedence recommender based on a \acrlong{gcn}.
+When trained on proof attempts that use random symbol precedences,
+the recommender outperforms the state of the art heuristic by more than \SI{2}{\percent}.
+The symbol precedences predicted by the recommender
+specify Knuth-Bendix \glspl{sot}.
+These orderings in turn guide the proof search in the state-of-the-art \acrlong{atp} Vampire
+by constraining the inferences in the superposition calculus.
+\todo{MS: uz i ty ``random symbol precedences'', kterymi to vypraveni nahore zacina potrebuji vampira.
+Mozna bude lepsi, trochu nudne, zacit tim, odkud se berou a na co se pouzivaji precedence
+a teprve pak rict, ze se z nich ucime a pak umime navrhovat nove, lepsi?}
+The recommender is evaluated on \acrlong{fol} problems from the \acrshort{tptp} problem library.
+\fi
+
+\keywords{saturation-based theorem proving \and
+\gls{sot} \and
+symbol precedence \and
+\acrlong{ml} \and
+\acrlong{gcn}}
 

### 2021-02-16 abstract.tex
abstract update suggestions

@@
 
-The state-of-the-art \acrlongpl{atp} for \acrlong{fol}, such as Vampire,
-use \glspl{sot} to constrain the proof search.
-The popular Knuth-Bendix simplification ordering is parameterized by the \emph{symbol precedence}
-\todo{FB: Is it ok to emphasize a word in abstract?}
--- a permutation of the predicate and function symbols occurring in the input problem.
-The choice of the symbol precedence can have a substantial impact on the length of the proof search.
+% The state-of-the-art \acrlongpl{atp} for \acrlong{fol}, such as Vampire,
+State-of-the-art superposition-based theorem provers for \acrlong{fol} % such as E or Vampire,
+% - imho sem patri neurcity clen (the 0 clen v mnoznem cisle)
+% - byl specifictejsi z vymezenim katergorie dokazovacu
+% - to ``such as'' bych pripadne vynechal
+% use \glspl{sot} to constrain the proof search.
+rely on \glspl{sot} to constrain the applicability of inference rules 
+which in turn shapes the ensuing search space.
+The popular Knuth-Bendix simplification ordering is parameterized by 
+a \emph{symbol precedence}---a permutation of the predicate and function symbols
+% occurring in the input problem.
+% maybe:
+of the input problem's signature.
+The choice of the precedence thus has an indirect yet often substantial impact 
+% on the length of the proof search.
+on the ammount of work required to successfully complete a proof search.
 
-This paper describes and evaluates a symbol precedence recommender based on a \acrlong{gcn}.
-When trained on proof attempts that use random symbol precedences,
-the recommender outperforms the state-of-the-art heuristic by more than \SI{2}{\percent}.
-The recommender is evaluated on \acrlong{fol} problems from the \acrshort{tptp} problem library.
-\todo{FB: Should I mention Vampire here?}
-\todo{FB: Try to mention that the recommender is signature-agnostic.}
+\todo{MS: idea maybe to work out more in the introduction: 
+We could stress how the impact or the choice of a precedence is \emph{indirect}, 
+(as it's already obvious from the explanation here)
+all the more interesting one can learn from observing just this indirect impact 
+which precendences are good and which are bad!}
+
+This paper describes and evaluates a symbol precedence recommender,
+a machine learning system which estimates the best possible precedence
+based on observations of prover performance on a set of problems and random precedences.
+Using the graph convolutional neural network technology % \acrlong{gcn} % how to put neural in the middle?
+the system does not presuppose the problems to be related or share a common signature. 
+When coupled with the theorem prover Vampire and evaluated on the \acrshort{tptp} problem library
+the recommender is found to outperform a state-of-the-art heuristic by more than \SI{2}{\percent}.
+
+% When trained on proof attempts that use random symbol precedences,
+% the recommender outperforms the state-of-the-art heuristic by more than \SI{2}{\percent}.
+% The recommender is evaluated on \acrlong{fol} problems from the \acrshort{tptp} problem library.
+% \todo{FB: Should I mention Vampire here?}
+% \todo{FB: Try to mention that the recommender is signature-agnostic.}
 
@@
 \keywords{saturation-based theorem proving \and
-\gls{sot} \and
+% \gls{sot} \and
+simplification ordering \and % isn't it great to be sometimes able to say ``simplification ordering on terms'' and sometimes just "simplification ordering"?
 symbol precedence \and

### 2021-02-16 abstract.tex
Correct a typo: amount > ammount
Remove commented-out content from abstract

@@
 
-% The state-of-the-art \acrlongpl{atp} for \acrlong{fol}, such as Vampire,
-State-of-the-art superposition-based theorem provers for \acrlong{fol} % such as E or Vampire,
-% - imho sem patri neurcity clen (the 0 clen v mnoznem cisle)
-% - byl specifictejsi z vymezenim katergorie dokazovacu
-% - to ``such as'' bych pripadne vynechal
-% use \glspl{sot} to constrain the proof search.
+State-of-the-art superposition-based theorem provers for \acrlong{fol}
 rely on \glspl{sot} to constrain the applicability of inference rules 
@@
 a \emph{symbol precedence}---a permutation of the predicate and function symbols
-% occurring in the input problem.
-% maybe:
 of the input problem's signature.
 The choice of the precedence thus has an indirect yet often substantial impact 
-% on the length of the proof search.
-on the ammount of work required to successfully complete a proof search.
+on the amount of work required to successfully complete a proof search.
 
@@
 based on observations of prover performance on a set of problems and random precedences.
-Using the graph convolutional neural network technology % \acrlong{gcn} % how to put neural in the middle?
+Using the graph convolutional neural network technology
 the system does not presuppose the problems to be related or share a common signature. 
@@
 the recommender is found to outperform a state-of-the-art heuristic by more than \SI{2}{\percent}.
-
-% When trained on proof attempts that use random symbol precedences,
-% the recommender outperforms the state-of-the-art heuristic by more than \SI{2}{\percent}.
-% The recommender is evaluated on \acrlong{fol} problems from the \acrshort{tptp} problem library.
-% \todo{FB: Should I mention Vampire here?}
-% \todo{FB: Try to mention that the recommender is signature-agnostic.}
 
@@
 \keywords{saturation-based theorem proving \and
-% \gls{sot} \and
-simplification ordering \and % isn't it great to be sometimes able to say ``simplification ordering on terms'' and sometimes just "simplification ordering"?
+simplification ordering \and
 symbol precedence \and

### 2021-02-16 abstract.tex
abstract: Remove trailing whitespace
Add some commas to divide long compound sentences
Guidelines:
https://www.thepunctuationguide.com/comma.html#commasbasedonsentencestructure

Recommended by Writefull: https://revise-cvut-cz.writefull.ai/

@@
 State-of-the-art superposition-based theorem provers for \acrlong{fol}
-rely on \glspl{sot} to constrain the applicability of inference rules 
+rely on \glspl{sot} to constrain the applicability of inference rules,
 which in turn shapes the ensuing search space.
@@
 based on observations of prover performance on a set of problems and random precedences.
-Using the graph convolutional neural network technology
+Using the graph convolutional neural network technology,
 the system does not presuppose the problems to be related or share a common signature. 
-When coupled with the theorem prover Vampire and evaluated on the \acrshort{tptp} problem library
+When coupled with the theorem prover Vampire and evaluated on the \acrshort{tptp} problem library,
 the recommender is found to outperform a state-of-the-art heuristic by more than \SI{2}{\percent}.

### 2021-02-16 abstract.tex
Drop an article: choice of [the] precedence
Recommended by Writefull
Improve abstract following suggestions from Grammarly
Improve gra

@@
 The popular Knuth-Bendix simplification ordering is parameterized by 
-a \emph{symbol precedence}---a permutation of the predicate and function symbols
+\emph{symbol precedence}---a permutation of the predicate and function symbols
 of the input problem's signature.
-The choice of the precedence thus has an indirect yet often substantial impact
-on the amount of work required to successfully complete a proof search.
+Thus, the choice of precedence has an indirect yet often substantial impact
+on the amount of work required to complete a proof search.
 
@@
 This paper describes and evaluates a symbol precedence recommender,
-a machine learning system which estimates the best possible precedence
+a machine learning system that estimates the best possible precedence
 based on observations of prover performance on a set of problems and random precedences.

### 2021-02-16 abstract.tex
Remove an old disabled version of abstract

@@
 
-\iffalse
-This paper describes and evaluates a symbol precedence recommender based on a \acrlong{gcn}.
-When trained on proof attempts that use random symbol precedences,
-the recommender outperforms the state of the art heuristic by more than \SI{2}{\percent}.
-The symbol precedences predicted by the recommender
-specify Knuth-Bendix \glspl{sot}.
-These orderings in turn guide the proof search in the state-of-the-art \acrlong{atp} Vampire
-by constraining the inferences in the superposition calculus.
-\todo{MS: uz i ty ``random symbol precedences'', kterymi to vypraveni nahore zacina potrebuji vampira.
-Mozna bude lepsi, trochu nudne, zacit tim, odkud se berou a na co se pouzivaji precedence
-a teprve pak rict, ze se z nich ucime a pak umime navrhovat nove, lepsi?}
-The recommender is evaluated on \acrlong{fol} problems from the \acrshort{tptp} problem library.
-\fi
-
 \keywords{saturation-based theorem proving \and

### 2021-02-16 evaluation.tex
Extend a short table row
Reference the results table
Add a dummy row for function prec experiment
Add section Environment
Improve section Evaluation

@@
 a series of experiments was performed.
-\todo{MS: vzdycky kdyz to jen trochu jde, snaz se pouzivat cinny rod (a pritomny cas): To demonstrate ..., we performed ...
+%\todo{MS: vzdycky kdyz to jen trochu jde, snaz se pouzivat cinny rod (a pritomny cas): To demonstrate ..., we performed ...
 Ale taky tu trochu chybi, co nas ceka dal, ve stylu: In this section, we report ...
@@
 
-The empirical evaluation was performed using a modified version of the \gls{atp} Vampire 4.3.0.\cite{10.1007/978-3-642-39799-8_1}
+The empirical evaluation was performed using a modified version of the \gls{atp} Vampire 4.3.0 \cite{10.1007/978-3-642-39799-8_1}.
 The prover was used to generate the training data and to evaluate the trained precedence recommender.
@@
 For the evaluation of the precedences generated by the recommender,
-Vampire was modified to allow the user to specify the predicate and function symbol precedences.
+Vampire was modified to allow the user to specify the predicate and function symbol precedences
+for the proof search.
 \todo[inline]{FB: Add a link to the modified Vampire.}
@@
 \todo[inline,author=FB]{Describe the Vampire options.}
-\todo{MS: Literal comparison mode is not a standard thing.
+\todo[inline,author=MS]{Literal comparison mode is not a standard thing.
 Mentioning the option name is again too low level.
@@
 
-Since neither of the common \glspl{sot}, i.e., \gls{kbo} nor \gls{lpo}, ever compares a predicate symbol with a function symbol,
+Since neither of the common \glspl{sot}, i.e., \gls{kbo} nor \gls{lpo},
+\todo{FB: Consider omitting LPO completely if we don't discuss it anywhere in the paper.}
+ever compares a predicate symbol with a function symbol,
 two separate precedences can be considered for each problem:
@@
 to simplify the training process and to isolate the effects of the predicate and function precedences.
+\todo{FB: Weak, handwavy spot. Consider improving the argumentation.}
 This section describes how the training data for training a \emph{predicate} precedence recommender is generated.
@@
 
-The examples are generated by sampling the \gls{fol} part of the problem library \gls{tptp} v7.4.0.
+The examples are generated by sampling the \gls{fol} part of the problem library \gls{tptp} v7.4.0 \cite{10.1007/978-3-030-29436-6_29}.
 A total of \num{17053} problems formulated in \gls{fof} and \gls{cnf} are sampled.
@@
 In each iteration, a problem $P \in \ProblemsTptp$ is chosen and Vampire is executed on $P$
-with two predicate precedences chosen uniformly from the set of all predicate precedences on $P$.
-A function precedence for $P$ is chosen uniformly and used for both executions.
+with two predicate precedences chosen with uniform probability from the set of all predicate precedences on $P$.
+One function precedence for $P$ is chosen with uniform probability, and it is used for both executions.
 \todo[author=FB]{Why do we sample function precedences randomly?}
@@
 The two executions are compared in terms of performance:
-predicate precedence $\PrecBetter$ is recognized as better than precedence $\PrecWorse$,
+predicate precedence $\PrecBetter$ is recognized as better than predicate precedence $\PrecWorse$,
 denoted as $\Better{\PrecBetter}{\PrecWorse}$,
@@
 
+\subsection{Environment}
+
+All the experiments were run on a computer with the following specification:
+
+\begin{itemize}
+\item CPU: Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz})
+\item RAM: \SI{383}{GiB}
+\item OS: Ubuntu 20.04
+\item Kernel: GNU/Linux 5.4.0-40-generic x86\_64
+\end{itemize}
+
+% From the paper Reliable benchmarking [BenchExec]:
+% – CPU model and size of RAM,
+% – specified resource limits,
+% – name and version of OS,
+% – version of important software packages, such as the kernel or runtime environments like the Java VM,
+% – version and configuration of the benchmarked tool(s), and
+% – version of the benchmark set (input files)
+
 \subsection{Results}
@@
 
+\Cref{tab:results} shows the results.
+
 \begin{table*}
@@
 }
-\label{table:results}
 \centering
@@
 
+\acrshort{gcn} (function) & ? & ? & \SI{51.2}{\percent} & ? \\
+% TODO: This is a hot preview from VML-672. Replace with final results.
+
 \texttt{vampire -lcm predicate} & \num{3769.6} & \num{3.07} & \SI{49.29}{\percent} & \num{4.01e-4} \\
@@
 
-\texttt{vampire -lcm standard} & ? & ? \\
+\texttt{vampire -lcm standard} & ? & ? & ? & ? \\
 
 \end{tabular}
+\label{tab:results}
 \end{table*}
 \todo{FB: Add links to Neptune runs?}
-\todo{FB: Add results for function precedences.}
+\todo{FB: Finalize results for function precedences.}
 \todo{FB: Try to evaluate a recommender that uses both predicate and function models.}

### 2021-02-16 preliminaries.tex
Improve Preliminaries

--- 2021-02-13 preliminaries.tex
@@
 The most popular \gls{fol} \glspl{atp}, such as Vampire \cite{10.1007/978-3-642-39799-8_1}, E \cite{10.1007/978-3-030-29436-6_29}, or SPASS \cite{},
-start the proof search by converting the input \gls{fol} formulas to an equisatisfiable representation in \emph{quantifier-free \gls{cnf}}.\cite{Harrison2009}
-We denote a problem in \gls{cnf} as $P = (\Sigma, \mathrm{Cl})$,
-where $\Sigma$ is a list of all non-logical symbols in the problem,
-and $\mathrm{Cl}$ is the set of the clauses of the problem (including the negated conjecture).
+start the proof search by converting the input \gls{fol} formulas to an equisatisfiable representation in \emph{quantifier-free first-order \gls{cnf}} \cite{Harrison2009}.
+We denote a problem in \gls{cnf} as $P = (\Sigma, \mathit{Cl})$,
+where $\Sigma$ is a list of all non-logical (predicate and function)
+\emph{symbols} in the problem called the \emph{signature},
+and $\mathit{Cl}$ is the set of the clauses of the problem (including the negated conjecture).
 
@@
 by iteratively applying the \emph{inference rules} from the given \emph{calculus}
-to infer new clauses entailed by $\mathrm{Cl}$.
+to infer new clauses entailed by $\mathit{Cl}$.
 As soon as the empty clause, denoted by $\square$, is inferred,
@@
 the set of the inferred clauses is saturated with respect to the inference rules.
-In the common setting of time-restricted proof search, a timeout may end the process prematurely.
+In the common setting of time-restricted proof search, a time limit may end the process prematurely.
 
-\todo[inline,author=FB]{Add terminology: saturation iteration, $\bot$.}
+The common saturation-based \glspl{atp} structure the proof search
+by maintaining two classes of the inferred clauses: processed and unprocessed \cite{10.1007/978-3-030-29436-6_29}.
+In each \emph{iteration of the saturation loop}, one clause (so-called \emph{given clause})
+is selected from the unprocessed set
+and all the inferences between the given clause and the processed clauses are performed.
+The resulting new clauses are added to the unprocessed set.
 
-%\vampire{} is a saturation-based prover.
-%Given a \gls{fol} problem,
-%\vampire{} converts the problem into \gls{cnf}.
-%and proceeds to saturate the set of clauses
-%by repeated application of inference rules.
+\todo[inline,author=FB]{Add terminology: $\bot$.}
 
 \subsection{Superposition calculus}
+
+The superposition calculus is of special interest
+because it is used in the most successful \gls{fol} \glspl{atp}.
+
+The inference rules of superposition calculus are constrained by a \gls{sot}.
 
@@
 
-%\vampire{} searches for a proof by applying the rules
-%of the superposition inference system
-%\cite{10.1007/978-3-642-39799-8_1}.
-
 \subsubsection{\Gls{sot}}
 
-% AWR candidate
-Simplification ordering on terms
+An ordering on terms is called a \emph{simplification ordering} if it satisfies the following conditions:
+
+...
+
 influences the proof search in Vampire on two levels.
@@
 
-\subsection{\Acrlongpl{gcn}}
+\subsection{Neural networks}
 
+A \emph{feed-forward neural network} is a directed acyclic graph
+of differentiable \emph{modules} that operate on numeric vectors.
+The common modules include multiplication by a matrix, and nonlinearity such as ReLU or sigmoid.
+Some of the modules are parameterized by trainable parameters or hyperparameters.
+In a typical usage, the neural network is trained by \emph{gradient descent}.
+In this setting, the trained network outputs a single numeric value called \emph{loss}.
+Since the network is differentiable,
+a gradient of the loss is computed with respect to all the trainable parameters of the network.
+The gradients are typically computed by \emph{backpropagation}.
+The values of the parameters are then updated by taking a small step in the direction that minimizes the loss.
+
+\todo{Define sigmoid.}
+\todo{Maybe we don't need to make GCN a preliminary; we can define it later instead.}
 \todo[inline,author=FB]{GCN? Backprop?, gradient descent, loss, gradient, epoch}

### 2021-02-17 main.tex
Add some future work ideas
some additional future work

@@
 
+Larger graphs
+
+Joint model (trained jointly on predicate and function precedences)
+
+Differentiate questions due to satiterations from questions due to success and failure
+
+MS: Is there a knowledge transfer possible between related setups when we in vampire change
+options (seemingly?) orthogonal to precedence (saturation algorithm, additional inference rules / reductions, AVATAR on/off,
+clause selection strategies, etc.)?
+
+KBO is a also parametrized by weights (along with the precedence). Could we learn those as well? (Jointly?)
+
 \section*{Acknowledgments}

### 2021-02-17 evaluation.tex
experimenty, prvni stranka, poznamky a mirne reformulace

@@
+% !TEX root = main.tex
+
 To demonstrate the capacity of the precedence recommender described in \cref{sec:architecture},
@@
 and then compare the performance of the trained models to baseline heuristics.
+\todo{MS: az na to ``was performed'' dobry! ;)}
 
@@
 For the evaluation of the precedences generated by the recommender,
-Vampire was modified to allow the user to specify the predicate and function symbol precedences
-for the proof search.
+Vampire was modified to allow the user to supply explicit predicate and function symbol precedences for the proof search
+(normally, the user only picks a precedence generation heuristic).
 \todo[inline]{FB: Add a link to the modified Vampire.}
@@
 such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop.
-\todo{FB: Justify saturation loop iterations as a proxy for success.}
-\todo{FB: Reference a detailed explanation of saturation loop iterations.}
+\todo{FB: Justify saturation loop iterations as a proxy for success. MS: Ano, ale driv nez zde!}
+\todo{FB: Reference a detailed explanation of saturation loop iterations. MS: podobne jako v PAAR clanku. Dal bych to nekam okolo prelim.}
 
@@
 a predicate precedence and a function precedence.
-A predicate precedence recommender is trained separately from a function precedence recommender
+We trained a predicate precedence recommender separately from a function precedence recommender
 to simplify the training process and to isolate the effects of the predicate and function precedences.
-\todo{FB: Weak, handwavy spot. Consider improving the argumentation.}
-This section describes how the training data for training a \emph{predicate} precedence recommender is generated.
-Training data for training a function precedence recommender is generated analogously.
+\todo{FB: Weak, handwavy spot. Consider improving the argumentation. MS: tady activum dokonce pomuze 
+stim weak spotem. "A recommender is trained separately, because" zni trochu jako "autorita predepisuje delate to prave takto,
+protoze <dobre duvody>". Kdyz reknes "we trained, because", ty duvodu uz mohou byt pouze prakticke a ctenar to pochopi! }
+This section describes how the training data for training a \emph{predicate} precedence recommender was generated.
+Training data for training a function precedence recommender was generated analogously.
+\todo{MS: taky jsem to hodil do minuleho casu. Myslim, ze to je opet blizsi skutecnosti: V Cestine:
+"Takhle jsme to delali" (at vite, co presne kritizovat) vs "Takhle se to dela" (kritika pak muze byt o dost silnejsi,
+protoze jakoby tvrdis, ze prezentujes spravnou metodiku).}
 

### 2021-02-17 evaluation.tex
4.2 scanned. Taky moc pekny(vykricnik)

@@
 
+\todo{MS: mozna bych dal propagoval cinny rod a minuly cas ...}
+
 The examples are generated by sampling the \gls{fol} part of the problem library \gls{tptp} v7.4.0 \cite{10.1007/978-3-030-29436-6_29}.
@@
 The examples are generated by iterative sampling of $\ProblemsTptp$.
-In each iteration, a problem $P \in \ProblemsTptp$ is chosen and Vampire is executed on $P$
-with two predicate precedences chosen with uniform probability from the set of all predicate precedences on $P$.
-One function precedence for $P$ is chosen with uniform probability, and it is used for both executions.
-\todo[author=FB]{Why do we sample function precedences randomly?}
+In each iteration, a problem $P \in \ProblemsTptp$ is chosen and Vampire is executed twice on $P$
+with two (uniformly) random predicate precedences and a common random function precedence.
+% with two predicate precedences chosen with uniform probability from the set of all predicate precedences on $P$.
+% One function precedence for $P$ is chosen with uniform probability, and it is used for both executions.
+% \todo[author=FB]{Why do we sample function precedences randomly?}
+The ``background'' random function precedence serves as additional noise (in addition to the variability 
+contained in \gls{tptp}) and makes sure that the predicate precedence recommender
+will not be able to rely on any specificities that would come from fixing function precedences in the training data.
 
@@
 and if the number of iterations of the saturation loop with $\PrecBetter$ is smaller than with $\PrecWorse$.
-\todo{FB: Use notation for saturation loop iterations if the notation was established earlier. If failure is denoted by $\infty$, we can simply use $<$.}
+\todo{FB: Use notation for saturation loop iterations if the notation was established earlier. 
+If failure is denoted by $\infty$, we can simply use $<$.}
 If one of the two precedences is recognized as better,
@@
 To ensure the efficiency of the sampling, the process is interpreted as an instance of Bernoulli multi-armed bandit problem,
-\todo{Cite?}
+\todo{Cite? MS: kdyz bude dobra citace, sem by se urcite sikla:) Pri nejhorsim Sutton \& Barto to jisti.}
 with the reward of a trial being 1 in case an example is produced, and 0 otherwise.
@@
 allowing up to \num{2000} parallel solver executions.
-\todo{Explain in detail?}
+\todo{Explain in detail? MS: Myslim, ze takhle v kontextu uz dobry. Pusobi to hezky dojmem, 
+ze kdyz to nechapes, je to jen tim, zes necetl prislusne clanky. A zaroven jde tusit, ze to jsou pomerne
+standardni veci, ktere sice ovlivni dataset, ale zakldni myslenku ``ucit se z nahodnych permutaci'' nijak zasadne nemeni.}
 
@@
 \todo{FB: Remove these two sentences because the give too arbitrary detail?}
+\todo{MS: Ne, za mne naopak super! Trochu se to tim ozivi a dal to ukazuje, na prikladu, jak asi funguje ten UCB! }
 
@@
 and \num{2571} problems in the train set $\ProblemsTrain$.
-\todo{FB: Unify the terminology: validation, or train set?}
+\todo{MS: A kdyz pouzivas validation set behem uceni, ma taky mensi podmnozinu s limitem \num{100000} nodes?}
+\todo{FB: Unify the terminology: validation, or train set?
+MS: Co by znamenalo unify? Nebo myslis test set?}
 % /home/filip/projects/vampire-ml/vampire-ml/outputs/2021-02-11/16-27-02/results.csv
@@
 % val&graphified: 7648
-\todo{MS: jeste by nebylo lepsi vzit nejdriv ty ``male'' problemy a pak teprve pulit.}
+\todo{MS: jeste by nebylo lepsi vzit nejdriv ty ``male'' problemy a pak teprve pulit.
+MS2: tak ale ted uz to menit nebudeme!}
 

### 2021-02-17 evaluation.tex
be more explicit about what a failure to generate an example means during sampling...
jeste par poznamek

@@
 and $\PrecWorse$ is the other precedence.
+Otherwise, for example, if Vampire fails on both precedences, we go back to sampling another problem.
 
@@
 A predicate symbol cost model is trained by gradient backpropagation
-\todo{FB: Explain?}
+\todo{FB: Explain? MS: tohle by melo byt k pochopeni z predchozich sekci.}
 on the precedence pair classification task
-\todo{FB: Reference a section.}
+\todo{FB: Reference a section. MS: Ano!}
 using the examples generated from the problems in $\ProblemsTrain$.
@@
 \todo{FB: Shall we remind that the examples are further normalized by $k(n)$ to make even across signature lengths?}
+\todo{MS: asi dobry, pokud to bude jasne receny nejaky predchozi sekci.}
+
+MS: nechybi tu odstavec tom, jak klesala loss, ale validacni moc ne.
+(Mozna i o accuracy?) Pak o (continuous) ATP eval...
+and how we chose the final model?
 
@@
 \todo{Update if we include the preprocessing time.}
+\todo{MS: and if we don't, this would be the perfect place to summarize
+how long the just described procedure took on an average problem,
+or how it (roughly) scales with the graph/cnf/tptp\_file size.}
 

### 2021-02-17 evaluation.tex
Document notable Vampire options in section Evaluation

@@
 
+Vampire was run with a time limit of 10 seconds.
+To increase the potential impact of predicate precedences,
+we used a simple \gls{tkbo} \cite{Ludwig2007,Kovacs2011}
+that compares atoms according to the predicate precedence first,
+Using the ordinary \gls{kbo} as a tie-breaker.
+Ordinary \gls{kbo} was used to compare terms.
+\todo[inline,author=FB]{Describe the detailed configuration in an appendix and reference the appendix here.}
+
 % All explicit options:
@@
 
-\todo[inline,author=FB]{Describe the Vampire options.}
 \todo[inline,author=MS]{Literal comparison mode is not a standard thing.

### 2021-02-17 evaluation.tex
Remove a commented-out redundant paragraph
Move a todo
Reference "saturation iterations" from Evaluation

@@
 
+\todo[inline,author=MS]{Literal comparison mode is not a standard thing.
+Mentioning the option name is again too low level.
+Explaining the effect (point two) is appropriate, although a bit too vague.
+To kdyztak opravim ja.
+Popsat presne setup je dulezite, kvuli reprodukovatelnosti, ale ne nutne primo v clanku (budem nejspis stejne dodavat odkaz na nejake reproducibility repo).
+Ted zminit AVATAR je nevhodne, pokud nevysvetlis, co to aspon ramcove je.
+A pokud to budes vysvetlovat, je otazka, proc tim ztracet misto, kdyz to neni bezprostredne relevantni pro dalsi vysvetlovani.}
+
 Vampire was run with a time limit of 10 seconds.
@@
 
-\todo[inline,author=MS]{Literal comparison mode is not a standard thing.
-Mentioning the option name is again too low level.
-Explaining the effect (point two) is appropriate, although a bit too vague.
-To kdyztak opravim ja.
-Popsat presne setup je dulezite, kvuli reprodukovatelnosti, ale ne nutne primo v clanku (budem nejspis stejne dodavat odkaz na nejake reproducibility repo).
-Ted zminit AVATAR je nevhodne, pokud nevysvetlis, co to aspon ramcove je.
-A pokud to budes vysvetlovat, je otazka, proc tim ztracet misto, kdyz to neni bezprostredne relevantni pro dalsi vysvetlovani.}
-
-%For the experiment, Vampire 4.3.0 was modified to convert the problems from the \gls{tptp} format to a representation that allows easy automated processing.
-%More precisely, when the modified prover is run in the clausification mode (\texttt{vampire -mode clausify}),
-%it outputs the \gls{cnf} form of the problem and the problem signature in formats that allow easy processing in Python.
-%The \gls{cnf} clause and term structure of the problem is encoded into the \gls{json} format,
-%and the signature along with additional symbol metadata is encoded into the \gls{csv} format.
-
 \subsection{Training data}
@@
 where $P$ is a \gls{cnf} problem and $\PrecBetter, \PrecWorse$ are precedences of symbols of problem $P$
-such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop.
+such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop (see \cref{sec:saturation}).
 \todo{FB: Justify saturation loop iterations as a proxy for success. MS: Ano, ale driv nez zde!}
-\todo{FB: Reference a detailed explanation of saturation loop iterations. MS: podobne jako v PAAR clanku. Dal bych to nekam okolo prelim.}
 
@@
 allowing up to \num{2000} parallel solver executions.
-\todo{Explain in detail? MS: Myslim, ze takhle v kontextu uz dobry. Pusobi to hezky dojmem, 
-ze kdyz to nechapes, je to jen tim, zes necetl prislusne clanky. A zaroven jde tusit, ze to jsou pomerne
-standardni veci, ktere sice ovlivni dataset, ale zakldni myslenku ``ucit se z nahodnych permutaci'' nijak zasadne nemeni.}
+\todo{Explain in detail?}
 

### 2021-02-17 evaluation.tex
Evaluation: Remove a mention of LPO

@@
 
-Since neither of the common \glspl{sot}, i.e., \gls{kbo} nor \gls{lpo},
-\todo{FB: Consider omitting LPO completely if we don't discuss it anywhere in the paper.}
-ever compares a predicate symbol with a function symbol,
+Since the \gls{tkbo} never compares a predicate symbol with a function symbol,
 two separate precedences can be considered for each problem:

### 2021-02-17 evaluation.tex
Add a todo

@@
 Since the \gls{tkbo} never compares a predicate symbol with a function symbol,
+\todo{FB: Consider referencing an earlier section that explains KBO or TKBO.}
 two separate precedences can be considered for each problem:

### 2021-02-17 evaluation.tex
Improve Evaluation

@@
 
-To demonstrate the capacity of the precedence recommender described in \cref{sec:architecture},
-a series of experiments was performed.
-%\todo{MS: vzdycky kdyz to jen trochu jde, snaz se pouzivat cinny rod (a pritomny cas): To demonstrate ..., we performed ...
-Ale taky tu trochu chybi, co nas ceka dal, ve stylu: In this section, we report ...
-}
+To demonstrate the capacity of the trainable precedence recommender described in \cref{sec:architecture},
+we performed a series of experiments.
 In this section, we describe the design and configuration of the experiments,
-and then compare the performance of the trained models to baseline heuristics.
-\todo{MS: az na to ``was performed'' dobry! ;)}
+and then compare the performance of several trained models to a number of baseline heuristics.
 
-\subsection{Solver}
+\subsection{Environment}
+
+\subsubsection{System}
+
+All the experiments were run on a computer with the following specification:
+
+\begin{itemize}
+\item CPU: Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz})
+\item RAM: \SI{383}{GiB}
+\item OS: Ubuntu 20.04
+\item Kernel: GNU/Linux 5.4.0-40-generic x86\_64
+\end{itemize}
+
+% From the paper Reliable benchmarking [BenchExec]:
+% – CPU model and size of RAM,
+% – specified resource limits,
+% – name and version of OS,
+% – version of important software packages, such as the kernel or runtime environments like the Java VM,
+% – version and configuration of the benchmarked tool(s), and
+% – version of the benchmark set (input files)
+
+\subsubsection{Solver}
 
@@
 to simplify the training process and to isolate the effects of the predicate and function precedences.
-\todo{FB: Weak, handwavy spot. Consider improving the argumentation. MS: tady activum dokonce pomuze 
-stim weak spotem. "A recommender is trained separately, because" zni trochu jako "autorita predepisuje delate to prave takto,
-protoze <dobre duvody>". Kdyz reknes "we trained, because", ty duvodu uz mohou byt pouze prakticke a ctenar to pochopi! }
 This section describes how the training data for training a \emph{predicate} precedence recommender was generated.
 Training data for training a function precedence recommender was generated analogously.
-\todo{MS: taky jsem to hodil do minuleho casu. Myslim, ze to je opet blizsi skutecnosti: V Cestine:
-"Takhle jsme to delali" (at vite, co presne kritizovat) vs "Takhle se to dela" (kritika pak muze byt o dost silnejsi,
-protoze jakoby tvrdis, ze prezentujes spravnou metodiku).}
 
@@
 with two (uniformly) random predicate precedences and a common random function precedence.
-% with two predicate precedences chosen with uniform probability from the set of all predicate precedences on $P$.
-% One function precedence for $P$ is chosen with uniform probability, and it is used for both executions.
-% \todo[author=FB]{Why do we sample function precedences randomly?}
 The ``background'' random function precedence serves as additional noise (in addition to the variability 
@@
 
-The sampling runs until a total of \num{1000000} examples are generated.
+The sampling runs until a target number of examples is generated---\num{1000000} predicate precedence examples and \num{800000} function precedence examples.
 % sftp://cluster.ciirc.cvut.cz/home/bartefil/git/vampire-ml/out/20210108-generate-predicate/questions_generated
@@
 \num{5349} out of the \num{17053} problems yielded at least one example.
-\todo{FB: Remove these two sentences because the give too arbitrary detail?}
-\todo{MS: Ne, za mne naopak super! Trochu se to tim ozivi a dal to ukazuje, na prikladu, jak asi funguje ten UCB! }
 
@@
 % val&graphified: 7648
-\todo{MS: jeste by nebylo lepsi vzit nejdriv ty ``male'' problemy a pak teprve pulit.
-MS2: tak ale ted uz to menit nebudeme!}
+
+\subsection{Model}
+
+We used a \gls{gcn} as described in \cref{sec:architecture}
+with depth 4, message size 16, ReLU activation function,
+residual connections and layer normalization.
+\todo[inline]{MS: zase pasivum.
+Tady to urcite bude chtit odkaz na sekci, kde se jasne definuje, co to znamena.
+Jinak recenzenti byvaji dost alergicti na hyperpametry, ktere se jen tak nahodi na nevysvetli.
+Minimalne nejaky komentar typu: treba, zkouseli jsme u ruzne dalsi hodnoty, ale dopadalo to podobne.
+Nebo, pozdeji rekeneme, co se deje, kdyz se tohle meni.
+Nebo: nemeli jsme cas zjistovat, co se deje, kdyz se to meni, tak berem rozumne hodnoty podle blabla.}
 
@@
 % tf.keras.callbacks.ReduceLROnPlateau(monitor='loss', factor=0.5, patience=10)
-A \gls{gcn} with depth 4 and message size 16 is used.\todo{MS: zase pasivum.
-Tady to urcite bude chtit odkaz na sekci, kde se jasne definuje, co to znamena.
-Jinak recenzenti byvaji dost alergicti na hyperpametry, ktere se jen tak nahodi na nevysvetli.
-Minimalne nejaky komentar typu: treba, zkouseli jsme u ruzne dalsi hodnoty, ale dopadalo to podobne.
-Nebo, pozdeji rekeneme, co se deje, kdyz se tohle meni.
-Nebo: nemeli jsme cas zjistovat, co se deje, kdyz se to meni, tak berem rozumne hodnoty podle blabla.}
 
+\subsubsection{Sample weighting}
 Each of the training examples of problem $P$ contributes to the training with the weight $\frac{1}{s_P}$,
@@
 
-MS: nechybi tu odstavec tom, jak klesala loss, ale validacni moc ne.
-(Mozna i o accuracy?) Pak o (continuous) ATP eval...
-and how we chose the final model?
+\subsubsection{Metrics}
+To analyze the training process,
+we tracked the dynamics of three metrics on $\ProblemsTrain$ and $\ProblemsVal$:
+loss, accuracy and solver performance.
+The solver performance was estimated once per 10 training epochs by running Vampire
+on \num{1000} problems of the respective problem set
+and counting the number of problems successfully solved within the time limit.
+Since the accuracy is a proxy measure of solver performance and the loss is a proxy measure of the accuracy,
+we are interested in generalization from loss to accuracy and from both loss and accuracy to solver performance.
+Similarly, we are interested in generalization from training set to validation set.
 
-\subsection{Environment}
+\subsubsection{Termination}
+We run the training until the validation accuracy stopped increasing for 100 consecutive epochs.
 
-All the experiments were run on a computer with the following specification:
+\subsection{Final evaluation}
 
-\begin{itemize}
-\item CPU: Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz})
-\item RAM: \SI{383}{GiB}
-\item OS: Ubuntu 20.04
-\item Kernel: GNU/Linux 5.4.0-40-generic x86\_64
-\end{itemize}
-
-% From the paper Reliable benchmarking [BenchExec]:
-% – CPU model and size of RAM,
-% – specified resource limits,
-% – name and version of OS,
-% – version of important software packages, such as the kernel or runtime environments like the Java VM,
-% – version and configuration of the benchmarked tool(s), and
-% – version of the benchmark set (input files)
+After the training finished,
+we performed a final evaluation of the most promising intermediate trained model on the whole $\ProblemsVal$.
+The model that manifested the best estimated solver performance was chosen as the most promising.
+\todo{Watch out: This way we may overfit on the 1000 problems used for sample solver performance evaluation.}
 
@@
 
-The final evaluation is performed on $\ProblemsVal$.
+A predicate precedence recommender was trained on approximately \num{500000} examples,
+% Half of the 1M predicate examples was used for validation.
+and a function precedence recommender was trained on approximately \num{400000} examples.
+% Half of the 800k function examples was used for validation.
 For each problem $P \in \ProblemsVal$,
-a precedence is generated by the trained recommender
-and Vampire is run using this precedence and a wall clock time limit of 10 seconds.
-The results are averaged over 5 runs to reduce the effect of noise due to wall clock time limit.
+a pair of symbol precedences was generated by the respective trained recommender
+and Vampire was run using these precedences and a wall clock time limit of 10 seconds.
+% Note: We have mentioned the time limit above and here we repeat it for readers who only read Results.
+The results are averaged over 5 runs to reduce the effect of noise due to the wall clock time limit.
 As a baseline, the performance of Vampire with the \texttt{frequency} precedence heuristic was evaluated
 with the same time limit.
+For comparison, the two trained recommenders are evaluated separately,
+with the predicate precedence recommender using the \texttt{frequency} heuristic to generate the function precedences, and vice versa.
 
@@
 and excludes the time taken by the recommender to generate the precedence.
-\todo{Update if we include the preprocessing time.}
 \todo{MS: and if we don't, this would be the perfect place to summarize
@@
 or how it (roughly) scales with the graph/cnf/tptp\_file size.}
+When run with 1 thread on 1000 problems,
+the preprocessing took 1 second on average and at most 5 seconds,
+increasing linearly with the number of nodes of the graph representation of the problem.
+\todo{FB: Measure the times with joint recommender and TF restricted to 1 thread. Fix the numbers once we have a solid measurement. Add a comment with a reference to the data.}
 
@@
 
-Model & \multicolumn{2}{l}{Successes out of \num{7648}} & \multicolumn{2}{l}{Successes rate} \\
-& Mean & Std & Mean & Std \\
+Model & \multicolumn{2}{l}{Successes out of \num{7648}} & Mean success rate & Baseline multiple \\
+& Mean & Std & & \\
+
 \hline
 
-\acrshort{gcn} (predicate) & \num{3923.6} & \num{2.24} & \SI{51.30}{\percent} & \num{2.93e-4} \\
+\acrshort{gcn} (predicate and function) &&&&\\
+% VML-706
+
+\acrshort{gcn} (predicate only) &
 % Success rate: mean: 0.513023013, std: 0.000292887
@@
 % Total: validation_solver_eval/all/problems/measured&split&category: 7648
-% Success mean: validation_solver_eval/all/success/count/mean: 3923.6
-% Success std: validation_solver_eval/all/success/count/std 2.24
-% Success rate: 0.513023013
 % Difference in success count from baseline: 154 ~ 0.020135983
@@
 
-\acrshort{gcn} (function) & ? & ? & \SI{51.2}{\percent} & ? \\
-% TODO: This is a hot preview from VML-672. Replace with final results.
+\num{3923.6} &
+% Success mean: validation_solver_eval/all/success/count/mean: 3923.6
 
-\texttt{vampire -lcm predicate} & \num{3769.6} & \num{3.07} & \SI{49.29}{\percent} & \num{4.01e-4} \\
+\num{2.24} &
+% Success std: validation_solver_eval/all/success/count/std 2.24
+
+\SI{51.30}{\percent} &
+% Success rate: 0.513023013
+
+\num[round-mode=places,round-precision=4]{1.040853141} \\
+
+\acrshort{gcn} (function only) &
+% Final evaluation: VML-677
+% Evaluated checkpoint: outputs/2021-02-16/12-28-14/tf_ckpts/epoch/weights.00289.tf
+% Results file: sftp://cluster.ciirc.cvut.cz/home/bartefil/git/vampire-ml/outputs/2021-02-17/12-01-09/solver_eval/symbol_cost/epoch_-1/logs.yaml
+% Total: val/all/problems/measured&split&category: 7648
+
+\num{3874.2} &
+% Success mean: val/all/success/count/mean: 3874.2
+
+\num[round-mode=places,round-precision=2]{1.8330302779823362} &
+% Success std: val/all/success/count/mean: 1.8330302779823362
+
+\SI{50.66}{\percent} &
+% Success rate: val/all/success/count/mean: 0.5065638075313807
+
+\num[round-mode=places,round-precision=4]{1.027748302} \\
+
+\texttt{vampire -lcm predicate} &
 % Success rate: mean: 0.492887029, std: 0.000401412
@@
 % Success rate: 0.492887029
+
+\num{3769.6} &
+
+\num{3.07} &
+
+\SI{49.29}{\percent} &
+
+\num[round-mode=places,round-precision=4]{1.0} \\
 
@@
 \todo{FB: Evaluate on problems larger than 100k nodes.}
+
+The loss is merely a proxy measure of the accuracy,
+and the accuracy is merely a proxy measure of the solver performance.
+During the training, the validation loss typically started increasing after approximately 50 epochs,
+while both the train loss and validation accuracy continued improving.
+A natural possible explanation is that ...
+\todo{Finish.}
+While a higher granularity in the solver evaluation would be necessary to draw a clear conclusion,
+the trend in the solver performance seems mostly aligned with the validation accuracy.
+
+\todo[inline,author=FB]{Plot some learning curves?}

### 2021-02-17 architecture.tex
Add a todo
Add some content in Architecture

@@
 \todo{Compare our GCN to Michael, Mirek etc.}
+
+\iffalse
 
@@
 A povrchni ctenar to nemusi resit a matematicky zdatny by si ten detail odvodil spravne ...}
+
+\fi
+
+This section describes a structure of a symbol precedence recommender.
+When presented with a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$,
+the recommender generates a precedence $\pi^*$ of symbols $\Sigma$.
+
+\subsection{Precedence generator}
+
+The precedence generator, given a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$,
+generates a precedence over $\Sigma$
+that is expected to yield a successful proof search.
+
+The recommender first computes a cost value for each symbol of the input problem,
+and then orders the symbols by their costs in a non-increasing order.
+In this manner, the task of finding good precedences is reduced to the task
+of finding a good symbol cost function.
+We use a standard \gls{ml} terminology and denote
+the practical realization of the symbol cost function as \emph{symbol cost model}.
+
+Note here that the symbol precedence heuristics commonly used in practice
+conform to this scheme:
+they order the symbols by a numeric property, such as arity or number of occurrences.
+
+\subsection{Symbol cost model}
+
+The symbol cost model, given a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$,
+assigns each symbol in $s \in \Sigma$ a real value $c(s)$.
+It first uses a symbol embedding model to assign each symbol an embedding.
+The resulting symbol cost is a dot product of the symbol embedding with a trainable weight vector:
+
+$$
+c(s) = \DotProd{E(s)}{w} + b
+$$
+
+\subsection{Symbol embedding model}
+
+The symbol embedding model, given a problem,
+assigns each symbol $s \in \Sigma$ an embedding $E(s) \in \re^n$.
+Our implementation uses a \gls{rgcn} \cite{}.
+
+\todo[inline]{What is the structure of the graphs? What are the trainable parameters? Etc.}
+
+\subsection{Loss function}
+
+To train the symbol cost model,
+examples of the form $(P, \pi, \rho)$ are used.
+To be able to train the model by gradient descent,
+we need to define a loss function that is differentiable with respect to the model parameters,
+and that is minimized by a symbol cost model that produces good precedences.
+Optimizing the output precedence directly is not possible
+because the sorting operation is not differentiable
+and because we generally don't know the best precedence on a given problem.
+
+\todo[inline]{Idea for next project: Optimize precedence directly in a RL fashion: Generate precedence and evaluate with Vampire.
+If it is the best precedence seen so far, loss is 0 and gradient is 0.
+Otherwise ground truth is the best precedence seen so far on this problem and we use "differentiable ranking" to backpropagate.
+Possibly with some exploration, e.g.
+random swaps of pairs of symbols.}
+
+\subsection{Notes}
+
+The recommender consists of the following components:
+
+\begin{itemize}
+\item Symbol embedding model
+\item Symbol cost model
+\item Loss function
+\item Precedence generator
+\end{itemize}
+
+\begin{figure}[ht]
+\caption{Architecture overview}
+\centering
+\digraph[scale=0.4]{ArchitectureOverview}{
+graph [splines=ortho];
+node [shape=box, fontsize=20];
+edge [fontsize=20];
+
+Problem [label="CNF problem"];
+GCN [style=rounded, label="GCN"];
+SymbolEmbedding [label="Symbol embeddings"];
+SymbolCostModel [style=rounded, label="MLP"];
+SymbolCost [label="Symbol costs"];
+Sort [style=rounded, label="Sort"];
+Precedence [label="Output precedence"];
+
+Problem -> GCN -> SymbolEmbedding -> SymbolCostModel -> SymbolCost -> Sort -> Precedence;
+
+pi [label=<Precedence &pi;>];
+rho [label=<Precedence &rho;>];
+LossFunction [style=rounded, label="Loss function"];
+Loss [label="Loss value"];
+
+pi -> LossFunction;
+rho -> LossFunction;
+SymbolCost -> LossFunction;
+LossFunction -> Loss;
+}
+\end{figure}
 
@@
 % Inspiration: https://ufal.mff.cuni.cz/~straka/courses/npfl114/1920/slides.pdf/npfl114-07.pdf - slide 27 - Transformer
+\todo{FB: Mention inspiration: Transformer. See Straka's slides.}
 $h_i^{(l)}$ denotes the embedding of node $i$ at layer $l$.

### 2021-02-17 architecture.tex
Reformat source of some todos

@@
 Given a problem $P \in \cnf$, generate a symbol precedence $\Prec \in \Perm{n}$ that maximizes $\Prob{\SolverRun{P}{\Prec} = \top}$.
-MS: (Nehlede na to, ze main task by nejspis mel byt vysvetlen mnohem drive...) Asi bych to takhle nestavel. Jak pisu vyse, precijen je
+\todo[inline]{MS: (Nehlede na to, ze main task by nejspis mel byt vysvetlen mnohem drive...) Asi bych to takhle nestavel. Jak pisu vyse, precijen je
 beh dokazovace deterministicky a brat to nejak Bayesovsky by sice mohlo 
@@
 Co proste priznat nasledujici assumption:
-verime, ze pokud bude model spravne odpovidat na otazky $(P, \pi_1, \pi_2)$ (s pravdepodobnosti $> \SI{50}{\percent}$), povede podle nej vybrana permutace minimalizujici \eqref{eq:model_cost} k rychlemu vyreseni problemu (a tim i idealne k vyreseni problemu, ktere byly drive out of reach.)\todo{MS: koukni prosim, jestli nejaky takovy mame.
-Tj zadna random permutace ho nevyresila, ale naucena sit pak ano!}
+verime, ze pokud bude model spravne odpovidat na otazky $(P, \pi_1, \pi_2)$ (s pravdepodobnosti $> \SI{50}{\percent}$), povede podle nej vybrana permutace minimalizujici \eqref{eq:model_cost} k rychlemu vyreseni problemu (a tim i idealne k vyreseni problemu, ktere byly drive out of reach.)}
+\todo{MS: koukni prosim, jestli nejaky takovy mame. Tj zadna random permutace ho nevyresila, ale naucena sit pak ano!}
 
@@
 the system described in this paper predicts, given a problem $P$ and a pair of precedences $\PrecBetter, \PrecWorse \in \Perm{n}$,
-the probability\todo{MS: tohle je jeden z oficialnich zpusobu,
+the probability
+\todo{MS: tohle je jeden z oficialnich zpusobu,
 jak vysvetlovat neuronky, ale neni nijak jasne do jake miry byva
@@
 
-Fig.~\ref{fig:SystemOverview} \todo{MS: Na figures/tables bez referneci v textu se pohlizi obzvlast nelibe.
-Predpokladam, zes planoval pozdeji popsat, presto zmninuji.
-Konkretne k Fig.~\ref{fig:SystemOverview}:
+Fig.~\ref{fig:SystemOverview}
+\todo{MS: Na figures/tables bez referneci v textu se pohlizi obzvlast nelibe. Predpokladam, zes planoval pozdeji popsat, presto zmninuji. Konkretne k Fig.~\ref{fig:SystemOverview}:
 Napada me: neslo by precedenci definovat tak, aby uz byla tim $\pi^{-1}$? Invertovani zabira v obrazku skoustu mista, ale pritom

### 2021-02-17 abstract.tex
Move abstract guidelines below the abstract content
Improve the boast number in Abstract to 4 %
We can use a different methodology to establish the number:
we solve 1.04 times the number of problems that 'frequency' solves.

@@
 % !TEX root = main.tex
-
-% AWR: Guidelines (Unit 7, page 5):
-% At most 300 words
-% Content:
-% Purpose of the study
-% Research problems
-% Basic design of the study
-% Summary of interpretations and conclusions
-
-% AWR: Parts of an abstract (checklist) (Unit 7, page 6):
-% Motivation
-% Problem statement
-% Approach
-% Results
-% Conclusions
 
@@
 When coupled with the theorem prover Vampire and evaluated on the \acrshort{tptp} problem library,
-the recommender is found to outperform a state-of-the-art heuristic by more than \SI{2}{\percent}.
+the recommender is found to outperform a state-of-the-art heuristic by more than \SI{4}{\percent}.
 
@@
 
+% AWR: Guidelines (Unit 7, page 5):
+% At most 300 words
+% Content:
+% Purpose of the study
+% Research problems
+% Basic design of the study
+% Summary of interpretations and conclusions
+
+% AWR: Parts of an abstract (checklist) (Unit 7, page 6):
+% Motivation
+% Problem statement
+% Approach
+% Results
+% Conclusions
+
 % Motivation and purpose of the study are excluded because the audience at CADE need not be reminded of the motivation for making the provers faster.

### 2021-02-18 evaluation.tex
Reduce precision of factor to 3
Add results of final evaluation of combined model
nove poznamky k experimentum

@@
 Similarly, we are interested in generalization from training set to validation set.
+\todo{MS: kdyz se to tady tak pekne pripravi, asi ctenar ceka, ze se to pozdeji 
+nejak zuzitkuje. Pokud se rozhnodnem loss/accuracy/ATP zavislost dal nerozebirat,
+asi je tu navic i tento odstavec, nebo aspon jeho cast.}
 
@@
 \todo{Watch out: This way we may overfit on the 1000 problems used for sample solver performance evaluation.}
+\todo{MS: taky me to ted napadlo! Uplne oficialni metodika byva split na train,valid,test. 
+Kdy se trenuje na train, hyperparametry (vcetne early stopping) se ladi vuci valid 
+a pak se vyhodnocuje na test. Nekdy se pak valid rika devel a test se rika holdout.}
 
@@
 For each problem $P \in \ProblemsVal$,
-a pair of symbol precedences was generated by the respective trained recommender
+a pair\todo{MS: ja vim, ze sis to "vyplejtval" v predchozi vete,
+ale kde jinde nez tady rict explicitne "predicate precendence" a "function precedence"?
+Z toho "pair" ot nemusi byt jasny...}
+ of symbol precedences was generated by the respective trained recommender
 and Vampire was run using these precedences and a wall clock time limit of 10 seconds.
@@
 To generate a precedence for a problem,
+\todo{MS: tenhle odstavec mozna prehodit s predchozim?}
 the recommender first converts the problem to a machine-friendly \gls{cnf} format,
@@
 When run with 1 thread on 1000 problems,
+\todo{MS: 1) single-core bych chapal jako default. tj netreba zminovat?
+2) kterych 1000? To opet drazdi k otazkam. tj to bych asi taky vynechal, ale...
+3) to maximum prece zalezi na tom, kterych 1000 to bylo.}
 the preprocessing took 1 second on average and at most 5 seconds,
 increasing linearly with the number of nodes of the graph representation of the problem.
-\todo{FB: Measure the times with joint recommender and TF restricted to 1 thread. Fix the numbers once we have a solid measurement. Add a comment with a reference to the data.}
+\todo{MS: Idea: kdyz je to linearni: co cas potrebny na recommending
+vztahnout k casu klauzifikace? Jako rict, ze to trva x-krat dyl nez jen klauzifikovat?}
+\todo{FB: Measure the times with joint recommender and TF restricted to 1 thread.
+ Fix the numbers once we have a solid measurement.
+ Add a comment with a reference to the data.}
+ \todo{MS: To by bylo taky fajn!}
 
@@
 
-\acrshort{gcn} (predicate and function) &&&&\\
+\acrshort{gcn} (predicate and function) &
 % VML-706
+
+\num{3951.6} &
+\num[round-mode=places,round-precision=2]{1.624807680927192} &
+\SI{51.69}{\percent} &
+\num[round-mode=places,round-precision=3]{1.048280985} \\
 
@@
 
-\num[round-mode=places,round-precision=4]{1.040853141} \\
+\num[round-mode=places,round-precision=3]{1.040853141} \\
 
@@
 
-\num[round-mode=places,round-precision=4]{1.027748302} \\
+\num[round-mode=places,round-precision=3]{1.027748302} \\
 
@@
 
-\num[round-mode=places,round-precision=4]{1.0} \\
+\num[round-mode=places,round-precision=3]{1.0} \\
 

### 2021-02-18 evaluation.tex
Add section on input problem format and preprocessing

@@
 % --term_ordering kbo
+
+\subsubsection{Input problems}
+
+The raw input problems are assumed to be specified in the \gls{cnf} or the \gls{fof} fragment
+of the \acrshort{tptp} language \cite{Sutcliffe2017}.
+% http://www.tptp.org/TPTP/SyntaxBNF.html
+Each problem is first preprocessed by Vampire:
+\gls{fof} problems are converted into equisatisfiable \gls{cnf} problems,
+and basic simplifications are performed.
+\todo{FB: Explain in more detail or better terms.}
+New symbols may be introduced into the problems during preprocessing.
+We denote the preprocessed \gls{cnf} problem as $P = (\Sigma, \mathit{Cl})$,
+where $\Sigma$ denotes the list of all predicate and function symbols of the problem,
+and $\mathit{Cl}$ denotes a set of clauses over $\Sigma$ that constitute the problem.
+
+In addition to the signature and the structure of the problem,
+some metadata is extracted from the input problem to allow training a more efficient recommender.
+First, each clause is annotated with its role in the problem,
+which can be either axiom, assumption, or negated conjecture.
+% This is simplified. There are actually 7 clause roles defined internally in Vampire,
+% and it seems that only 4 of them are ever used in FOL problems:
+% AXIOM, ASSUMPTION, CONJECTURE, NEGATED_CONJECTURE
+% CONJECTURE is used in FOF problems and NEGATED_CONJECTURE is used in CNF problems,
+% so the recommender can actually differentiate between these two forms.
+Second, each symbol is annotated with two bits of data:
+whether it was introduced into the problem during preprocessing,
+and whether the symbol appears in a conjecture clause.
+% Note that the second bit is redundant, since the clauses are annotated with their roles.
 

### 2021-02-18 evaluation.tex
Update: We use 2 threads for analysis of preprocessing time

@@
 or how it (roughly) scales with the graph/cnf/tptp\_file size.}
-When run with 1 thread on 1000 problems,
+When run with 2 threads on uniformly random 1000 problems,
 \todo{MS: 1) single-core bych chapal jako default. tj netreba zminovat?

### 2021-02-18 architecture.tex
Remove an obsolete todo
Minor rewording: the > a
Add an intro paragraph for Architecture (WIP)

@@
 
-This section describes a structure of a symbol precedence recommender.
+This section describes the structure of a symbol precedence recommender.
 When presented with a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$,
 the recommender generates a precedence $\pi^*$ of symbols $\Sigma$.
+
+\subsection{System overview}
+
+The precedence recommender is a system that takes
+a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$ as the input,
+and produces a precedence of the symbols $\Sigma$ as the output.
+
+The input problem is assumed to be specified in the \gls{cnf} fragment
+of the \acrshort{tptp} language.
+% http://www.tptp.org/TPTP/SyntaxBNF.html
+Note that if the input problem is specified in \gls{fof},
+it can be converted to \gls{cnf} by an \gls{atp} such as Vampire.
 
@@
 % Consider weighting the samples by the result type: quantitative / qualitative etc.
-
-% TODO: Experiments: Increase depth and message size
 

### 2021-02-18 preliminaries.tex
4.2 scanned. Taky moc pekny(vykricnik)
Reference "saturation iterations" from Evaluation
added SPASS

@@
+% !TEX root = main.tex
+
 % Terminology
@@
 \subsection{Saturation-based theorem proving}
+\label{sec:saturation}
 
@@
 is reduced to proving that the premises together with the negated conjecture entail a \emph{contradiction}.
-The most popular \gls{fol} \glspl{atp}, such as Vampire \cite{10.1007/978-3-642-39799-8_1}, E \cite{10.1007/978-3-030-29436-6_29}, or SPASS \cite{},
+The most popular \gls{fol} \glspl{atp}, such as Vampire \cite{10.1007/978-3-642-39799-8_1}, E \cite{10.1007/978-3-030-29436-6_29}, or SPASS \cite{DBLP:conf/cade/WeidenbachDFKSW09},
 start the proof search by converting the input \gls{fol} formulas to an equisatisfiable representation in \emph{quantifier-free first-order \gls{cnf}} \cite{Harrison2009}.
@@
 
+Recall the two views:
+\begin{enumerate}
+\item
+	One is the view of complete literal selections (we influence which literals are maximal)
+
+\item
+	The other is that of the term rewriting world
+
+\end{enumerate}
+(The full landscape also contains LPO).
+
 \subsubsection{Symbol precedences}

### 2021-02-18 preliminaries.tex
tuning cnf

@@
 
-A \emph{\acrfull{fol} problem} consists of a set of premise formulas and a conjecture formula.
+A \emph{\acrfull{fol} problem} consists of a set of axiom formulas and a conjecture formula.
 In a \emph{refutation-based} \emph{\acrfull{atp}},
-proving that the premises entail the conjecture
-is reduced to proving that the premises together with the negated conjecture entail a \emph{contradiction}.
+proving that the axioms entail the conjecture
+is reduced to proving that the axioms together with the negated conjecture entail a \emph{contradiction}.
 The most popular \gls{fol} \glspl{atp}, such as Vampire \cite{10.1007/978-3-642-39799-8_1}, E \cite{10.1007/978-3-030-29436-6_29}, or SPASS \cite{DBLP:conf/cade/WeidenbachDFKSW09},
-start the proof search by converting the input \gls{fol} formulas to an equisatisfiable representation in \emph{quantifier-free first-order \gls{cnf}} \cite{Harrison2009}.
+start the proof search by converting the input \gls{fol} formulas to an equisatisfiable representation in 
+% \emph{quantifier-free first-order 
+\emph{\acrfull{cnf}} \cite{DBLP:books/el/RV01/NonnengartW01,Harrison2009}.
 We denote a problem in \gls{cnf} as $P = (\Sigma, \mathit{Cl})$,

### 2021-02-18 preliminaries.tex
defined ReLU/sigmoid

@@
 of differentiable \emph{modules} that operate on numeric vectors.
-The common modules include multiplication by a matrix, and nonlinearity such as ReLU or sigmoid.
+The common modules include multiplication by a matrix, and nonlinearity such as ReLU or sigmoid.\footnote{
+These are, respectively, $f(x) = \max\{0,x\}$ and $g(x) = 1/(1+e^{-x}$). }
 Some of the modules are parameterized by trainable parameters or hyperparameters.
@@
 
-\todo{Define sigmoid.}
 \todo{Maybe we don't need to make GCN a preliminary; we can define it later instead.}

### 2021-02-18 evaluation.tex
Add results of preprocessing time including a chart

--- 2021-02-18 evaluation.tex
@@
 or how it (roughly) scales with the graph/cnf/tptp\_file size.}
-When run with 1 thread on 1000 problems,
+When run with 2 threads on 1000 problems chosen uniformly randomly from $\ProblemsVal$,
 \todo{MS: 1) single-core bych chapal jako default. tj netreba zminovat?
@@
 3) to maximum prece zalezi na tom, kterych 1000 to bylo.}
-the preprocessing took 1 second on average and at most 5 seconds,
-increasing linearly with the number of nodes of the graph representation of the problem.
+the preprocessing took
+approximately \num[round-mode=places,round-precision=2]{1.024237694} seconds on average,
+increasing approximately linearly with the number of nodes of the graph representation of the problem
+(see \cref{fig:preprocessing}).
 \todo{MS: Idea: kdyz je to linearni: co cas potrebny na recommending
@@
  \todo{MS: To by bylo taky fajn!}
+
+\begin{figure}[h]
+\caption{The dependence of preprocessing time on the number of nodes in the problem graph on 1000 random validation problems}
+\label{fig:preprocessing}
+\centering
+\includesvg[width=\textwidth]{preprocessing}
+% Source: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit#gid=394425425&fvid=659935521
+% Experiment: VML-715
+\end{figure}
 

### 2021-02-18 architecture.tex
Improve architecture overview

--- 2021-02-17 architecture.tex
@@
 
-This section describes a structure of a symbol precedence recommender.
-When presented with a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$,
-the recommender generates a precedence $\pi^*$ of symbols $\Sigma$.
+\subsection{System overview}
+
+The precedence recommender is a system that takes
+a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$ as the input,
+and produces a precedence over the symbols $\Sigma$ as the output.
+
+The architecture is designed so that the recommender can be trained
+on the results of solver executions with random precedences.
+The recommender is parameterized by weight tensors
+whose values can be trained by gradient descent.
+\todo{Ensure we have defined this.}
+The goal of the training is to find parameter values
+such that the recommender produces precedences
+that are likely to yield a successful proof in few iterations of the saturation loop.
+
+The recommender consists of modules that perform specific subtasks (see \cref{fig:architecture}):
+\begin{enumerate}
+\item Graphifier converts the input \gls{cnf} problem into a problem graph.
+\item \gls{gcn} converts a problem graph into symbol embeddings.
+The \gls{gcn} contains one or more convolution layers.
+\item Projection converts the symbol embeddings into a vector of symbol costs.
+\item Sorting converts the symbol costs into a symbol precedence.
+It is only used in generating mode.
+\item Loss function converts the symbol costs and a pair of precedences into a loss value.
+It is only used in training mode.
+\end{enumerate}
+
+\begin{figure}[h]
+\caption{Recommender architecture overview.
+When recommending a precedence, the input is problem $P$ and the output is precedence $\pi^*$.
+When training on an example, the input is problem $P$ and precedences $\pi$ and $\rho$,
+and the output is the loss value.}
+\label{fig:architecture}
+\centering
+\digraph[scale=0.4]{ArchitectureOverview}{
+graph [splines=ortho,ranksep=0.2];
+node [shape=box, fontsize=20];
+edge [fontsize=20];
+
+Problem [label="CNF problem P"];
+Graphifier [style=rounded, label="Graphifier"];
+g [label="Graph"];
+GCN [style=rounded, label="GCN"];
+SymbolEmbedding [label="Symbol embeddings"];
+SymbolCostModel [style=rounded, label="Projection"];
+SymbolCost [label="Symbol costs"];
+Sort [style=rounded, label="Sort"];
+Precedence [label=<Output precedence &pi;*>];
+
+Problem -> Graphifier -> g -> GCN -> SymbolEmbedding -> SymbolCostModel -> SymbolCost -> Sort -> Precedence;
+
+pi [label=<Precedence &pi;>];
+rho [label=<Precedence &rho;>];
+LossFunction [style=rounded, label="Loss function"];
+Loss [label="Loss value"];
+
+pi -> LossFunction;
+rho -> LossFunction;
+SymbolCost -> LossFunction;
+LossFunction -> Loss;
+}
+\end{figure}
 
@@
 
-\begin{figure}[ht]
-\caption{Architecture overview}
-\centering
-\digraph[scale=0.4]{ArchitectureOverview}{
-graph [splines=ortho];
-node [shape=box, fontsize=20];
-edge [fontsize=20];
-
-Problem [label="CNF problem"];
-GCN [style=rounded, label="GCN"];
-SymbolEmbedding [label="Symbol embeddings"];
-SymbolCostModel [style=rounded, label="MLP"];
-SymbolCost [label="Symbol costs"];
-Sort [style=rounded, label="Sort"];
-Precedence [label="Output precedence"];
-
-Problem -> GCN -> SymbolEmbedding -> SymbolCostModel -> SymbolCost -> Sort -> Precedence;
-
-pi [label=<Precedence &pi;>];
-rho [label=<Precedence &rho;>];
-LossFunction [style=rounded, label="Loss function"];
-Loss [label="Loss value"];
-
-pi -> LossFunction;
-rho -> LossFunction;
-SymbolCost -> LossFunction;
-LossFunction -> Loss;
-}
-\end{figure}
-
 \newcommand{\Prec}{\pi}

### 2021-02-18 architecture.tex
Clarify a todo

@@
 whose values can be trained by gradient descent.
-\todo{Ensure we have defined this.}
+\todo{Ensure we have defined ``gradient descent''.}
 The goal of the training is to find parameter values

### 2021-02-18 evaluation.tex
Move a table label
Specify placement of a table
Add a placeholder for a simple model
Finalize the analysis of preprocessing time
by describing an upper bound for 80th percentile.

--- 2021-02-18 evaluation.tex
@@
 or how it (roughly) scales with the graph/cnf/tptp\_file size.}
-When run with 1 thread on 1000 problems,
+When run with 2 threads,
+the preprocessing of a single problem
+takes at most at most \num[round-mode=places,round-precision=2]{1.262744486} seconds
+for \SI{80}{\percent} of the problems
+according to data measured on a random sample of \num{1000} problems.
+% Analysis: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit?usp=sharing
+% VML-715
 \todo{MS: 1) single-core bych chapal jako default. tj netreba zminovat?
@@
 3) to maximum prece zalezi na tom, kterych 1000 to bylo.}
-the preprocessing took 1 second on average and at most 5 seconds,
-increasing linearly with the number of nodes of the graph representation of the problem.
 \todo{MS: Idea: kdyz je to linearni: co cas potrebny na recommending
 vztahnout k casu klauzifikace? Jako rict, ze to trva x-krat dyl nez jen klauzifikovat?}
-\todo{FB: Measure the times with joint recommender and TF restricted to 1 thread.
- Fix the numbers once we have a solid measurement.
- Add a comment with a reference to the data.}
- \todo{MS: To by bylo taky fajn!}
 
@@
 
-\begin{table*}
+\begin{table*}[h]
 \caption{
@@
 }
+\label{tab:results}
 \centering
@@
 
+Simple & ? & ? & ? & ? \\
+% Final vector from PAAR paper: [0,0.429306921481749,0.57069307851825,0,0,0,0,0,0,0,0,0]
+% Source: https://docs.google.com/spreadsheets/d/1HSsC7piUAtWt6uwA9SYOX5vmiF0Ab3Ae4FPyGsDALIg/edit#gid=99404775
+
 \texttt{vampire -lcm predicate} &
@@
 \end{tabular}
-\label{tab:results}
 \end{table*}

### 2021-02-18 main.tex
Use package hyperref
to decorate the PDF with hyperlinks and metadata.
Add results of preprocessing time including a chart
Finalize the analysis of preprocessing time
by describing an upper bound for 80th percentile.

@@
 
+\usepackage{svg}
+
 \usepackage[pdf]{graphviz}
 \usepackage{tikz}
+
+\usepackage{hyperref}
+\hypersetup{
+pdftitle={Neural Precedence Recommender},
+pdfauthor={Filip Bártek, Martin Suda},
+pdfkeywords={saturation-based theorem proving, simplification ordering, symbol precedence, machine learning, graph convolutional network}
+}
+
+\usepackage{cleveref}
 
@@
 
+\appendix
+
+\section{Experiment details}
+
+\begin{figure}[h]
+\caption{The dependence of preprocessing time on the number of nodes in the problem graph on 1000 random validation problems}
+\label{fig:preprocessing}
+\centering
+\includesvg[width=\textwidth]{preprocessing}
+% Source: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit#gid=394425425&fvid=659935521
+% Experiment: VML-715
+\end{figure}
+
 \end{document}

### 2021-02-18 evaluation.tex
Add results for simple model
Reword a sentence a bit

@@
  of symbol precedences was generated by the respective trained recommender
-and Vampire was run using these precedences and a wall clock time limit of 10 seconds.
+and Vampire was run using these precedences
+with a wall clock time limit of 10 seconds.
 % Note: We have mentioned the time limit above and here we repeat it for readers who only read Results.
@@
 
-Simple & ? & ? & ? & ? \\
+Simple &
+\num{3827.2} &
+\num[round-mode=places,round-precision=2]{1.9390719429665317} &
+\SI{50.04}{\percent} &
+\num[round-mode=places,round-precision=3]{1.015280136} \\
 % Final vector from PAAR paper: [0,0.429306921481749,0.57069307851825,0,0,0,0,0,0,0,0,0]

### 2021-02-18 evaluation.tex
Results: Include absolute improvement instead of percentage solved

@@
 \caption{
-Results of the evaluation of various predicate precedence heuristics on $\ProblemsVal$.
+Results of the evaluation of various predicate precedence heuristics on $\ProblemsVal$
+($\card{\ProblemsVal} = 7648$).
 Means and standard deviations over 5 runs are reported.
@@
 \centering
-\begin{tabular}{l|ll|ll}
+\begin{tabular}{l|ll|rl}
 
-Model & \multicolumn{2}{l}{Successes out of \num{7648}} & Mean success rate & Baseline multiple \\
-& Mean & Std & & \\
+Model & \multicolumn{2}{l}{Successes on $\ProblemsVal$} & \multicolumn{2}{l}{Improvement over baseline} \\
+& Mean & Std & Absolute & Relative \\
 
@@
 % VML-706
-
 \num{3951.6} &
 \num[round-mode=places,round-precision=2]{1.624807680927192} &
-\SI{51.69}{\percent} &
+%\SI{51.69}{\percent} &
++182.0 &
 \num[round-mode=places,round-precision=3]{1.048280985} \\
@@
 % Checkpoint: outputs/2021-02-06/14-55-41/tf_ckpts/epoch/weights.00079-0.61.tf VML-540 0.511785
-
 \num{3923.6} &
 % Success mean: validation_solver_eval/all/success/count/mean: 3923.6
-
 \num{2.24} &
 % Success std: validation_solver_eval/all/success/count/std 2.24
-
-\SI{51.30}{\percent} &
+%\SI{51.30}{\percent} &
 % Success rate: 0.513023013
-
++154.0 &
 \num[round-mode=places,round-precision=3]{1.040853141} \\
@@
 % Total: val/all/problems/measured&split&category: 7648
-
 \num{3874.2} &
 % Success mean: val/all/success/count/mean: 3874.2
-
 \num[round-mode=places,round-precision=2]{1.8330302779823362} &
 % Success std: val/all/success/count/mean: 1.8330302779823362
-
-\SI{50.66}{\percent} &
+%\SI{50.66}{\percent} &
 % Success rate: val/all/success/count/mean: 0.5065638075313807
-
++104.6 &
 \num[round-mode=places,round-precision=3]{1.027748302} \\
 
-Simple &
+Simple (predicate only) &
 \num{3827.2} &
 \num[round-mode=places,round-precision=2]{1.9390719429665317} &
-\SI{50.04}{\percent} &
+%\SI{50.04}{\percent} &
++57.6 &
 \num[round-mode=places,round-precision=3]{1.015280136} \\
@@
 % Success rate: 0.492887029
-
 \num{3769.6} &
-
 \num{3.07} &
-
-\SI{49.29}{\percent} &
-
+%\SI{49.29}{\percent} &
+0.0 &
 \num[round-mode=places,round-precision=3]{1.0} \\

### 2021-02-18 architecture.tex
Move list of edge types to appendix
(technical detail)

@@
 
-\begin{itemize}
-\item The graph representation of problem $P$ contains exactly one root node of type \ntype{problem}.
-\item Each clause is represented by a \ntype{clause} node connected to the root \ntype{problem} node.
-\item Each atom is represented by an \ntype{atom} node (in case the atom is not an equality)
-or an \ntype{equality} node (in case the atom is an equality).
-For each literal occurrence there is an edge connecting the respective atom to the respective clause.
-The type of the edge corresponds to the polarity of the literal:
-\epos{} for positive literal and \eneg{} for negative literal.
-\item Each \ntype{equality} node is connected to two nodes that represent the operands,
-each of which is of type \ntype{term} or \ntype{variable}.
-The commutativity of the equality operator is reflected by the fact that the operand edges are not ordered.
-\item Each \ntype{atom} node is connected to one \ntype{predicate} node that represents the predicate symbol being applied by this atom.
-Note that these edges connect the applications of a predicate symbol across the whole problem.
-\item Each \ntype{atom} node is connected to zero or more \ntype{argument} nodes that represent the argument positions of the atom.
-\item Each pair of \ntype{argument} nodes that correspond to consecutive argument positions is connected by an edge.
-\item Each \ntype{argument} node is connected to a node that represents the argument term,
-which is either a \ntype{term} node or a \ntype{variable} node.
-\item Each \ntype{term} node is connected to one \ntype{function} node that represents the function symbol being applied by this term.
-\item For each variable, there is an edge connecting the \ntype{clause} node of the clause that binds the variable to the \ntype{variable} node that represents the variable.
-\end{itemize}
-
 \todo[inline]{Abstract from the edge types. Focus on the main idea. Technical details may be in technical report or appendix.}

### 2021-02-18 main.tex
Move list of edge types to appendix
(technical detail)

@@
 
+\section{Graph structure}
+
+\begin{itemize}
+\item The graph representation of problem $P$ contains exactly one root node of type \ntype{problem}.
+\item Each clause is represented by a \ntype{clause} node connected to the root \ntype{problem} node.
+\item Each atom is represented by an \ntype{atom} node (in case the atom is not an equality)
+or an \ntype{equality} node (in case the atom is an equality).
+For each literal occurrence there is an edge connecting the respective atom to the respective clause.
+The type of the edge corresponds to the polarity of the literal:
+\epos{} for positive literal and \eneg{} for negative literal.
+\item Each \ntype{equality} node is connected to two nodes that represent the operands,
+each of which is of type \ntype{term} or \ntype{variable}.
+The commutativity of the equality operator is reflected by the fact that the operand edges are not ordered.
+\item Each \ntype{atom} node is connected to one \ntype{predicate} node that represents the predicate symbol being applied by this atom.
+Note that these edges connect the applications of a predicate symbol across the whole problem.
+\item Each \ntype{atom} node is connected to zero or more \ntype{argument} nodes that represent the argument positions of the atom.
+\item Each pair of \ntype{argument} nodes that correspond to consecutive argument positions is connected by an edge.
+\item Each \ntype{argument} node is connected to a node that represents the argument term,
+which is either a \ntype{term} node or a \ntype{variable} node.
+\item Each \ntype{term} node is connected to one \ntype{function} node that represents the function symbol being applied by this term.
+\item For each variable, there is an edge connecting the \ntype{clause} node of the clause that binds the variable to the \ntype{variable} node that represents the variable.
+\end{itemize}
+
 \section{Experiment details}

### 2021-02-18 evaluation.tex
Results: Add results of `vampire -lcm standard`
Improve Evaluation

@@
 
-The raw input problems are assumed to be specified in the \gls{cnf} or the \gls{fof} fragment
+The input problems are assumed to be specified in the \gls{cnf} or the \gls{fof} fragment
 of the \acrshort{tptp} language \cite{Sutcliffe2017}.
 % http://www.tptp.org/TPTP/SyntaxBNF.html
-Each problem is first preprocessed by Vampire:
-\gls{fof} problems are converted into equisatisfiable \gls{cnf} problems,
-and basic simplifications are performed.
-\todo{FB: Explain in more detail or better terms.}
-New symbols may be introduced into the problems during preprocessing.
+\Gls{fof} problems are first converted into equisatisfiable \gls{cnf} problems by Vampire.
+New symbols may be introduced during preprocessing,
+namely due to the Tseitin transformation and Skolemization.
 We denote the preprocessed \gls{cnf} problem as $P = (\Sigma, \mathit{Cl})$,
@@
 
+\texttt{vampire -lcm standard} &
+\num{3823.0} &
+\num[round-mode=places,round-precision=2]{3.40587727318528} &
+%\SI[round-mode=places,round-precision=2]{49.9869247}{\percent} &
++53.4 &
+\num[round-mode=places,round-precision=3]{1.014165959} \\
+% VML-741
+
 \texttt{vampire -lcm predicate} &
@@
 \num[round-mode=places,round-precision=3]{1.0} \\
-
-\texttt{vampire -lcm standard} & ? & ? & ? & ? \\
 

### 2021-02-18 architecture.tex
Improve Architecture

@@
 a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$ as the input,
-and produces a precedence over the symbols $\Sigma$ as the output.
+and produces a precedence $\pi^*$ over the symbols $\Sigma$ as the output.
 
 The architecture is designed so that the recommender can be trained
-on the results of solver executions with random precedences.
+on the results executions of an \gls{atp} on various problems with random precedences.
 The recommender is parameterized by weight tensors
@@
 that are likely to yield a successful proof in few iterations of the saturation loop.
+\todo{FB: Too vague?}
 

### 2021-02-18 architecture.tex
Architecture: Explain graphification

@@
 
-\subsection{Precedence generator}
+\subsection{From \gls{cnf} to graphs}
+
+As the first step of the recommender processing pipeline,
+the input problem is converted from a \gls{cnf} representation
+to a \emph{heterogeneous directed graph}.\footnote{Data mining literature often uses the term \gls{hin} \cite{Shi2015} for heterogeneous graphs.
+We prefer to conform to the terminology common in literature studying \glspl{gnn}.}
+\todo{FB: Consider removing the footnote because it is basically useless.}
+Each of the nodes is labeled with a node type,
+and each edge is labeled with an edge type,
+informing the heterogeneous nature of the graph.
+The nodes of the graph correspond to various elements that constitute the \gls{cnf} formula,
+such as clauses, atoms and predicate symbols.
+Each such category of elements corresponds to one node type.
+The edges represent the (oriented) relations between the elements,
+for example the relation between a clause and one of its atoms,
+or the relation between an atom and its predicate symbol.
+\Cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.
+
+\todo[inline]{Give an example of a problem and its graph.}
+
+\newcommand{\ntype}[1]{\texttt{#1}}
+\newcommand{\etype}[1]{\texttt{#1}}
+\newcommand{\epos}{\etype{pos}}
+\newcommand{\eneg}{\etype{neg}}
+
+\begin{figure}[h]
+\caption{CNF network schema}
+\label{fig:CnfSchema}
+\centering
+\tikzstyle{token} = [rectangle, draw]
+
+\begin{tikzpicture}[node distance = 1 and 2, ->]
+% https://tex.stackexchange.com/a/332796/202639
+
+% Node and edge types:
+% https://docs.google.com/spreadsheets/d/1PCPHEgk6vLxpdpcvB_PGoLx7p4DID6WtvVWy2mDuv4A/edit?usp=sharing
+
+\node (formula) [token] {\ntype{problem}};
+% TODO: Consider removing the Formula nodes.
+\node (clause) [token, below=of formula] {\ntype{clause}};
+\node (atom) [token, below left=of clause] {\ntype{atom}};
+\node (equality) [token, below right=of clause] {\ntype{equality}};
+\node (predicate) [token, left=of atom] {\ntype{predicate}};
+\node (argument) [token, below=of atom] {\ntype{argument}};
+\node (term) [token, below=of argument] {\ntype{term}};
+\node (function) [token, left=of term] {\ntype{function}};
+\node (variable) [token, right=of term] {\ntype{variable}};
+
+\draw (formula) to node [right] {\etype{contains}} (clause);
+\draw (clause) to [bend right] node [above] {\epos{}} (atom);
+\draw (clause) to [bend left] node [below] {\eneg{}} (atom);
+\draw (clause) to [bend left] node [above] {\epos{}} (equality);
+\draw (clause) to [bend right] node [below] {\eneg{}} (equality);
+\draw (clause) to node [above] {\etype{binds}} (variable);
+\draw (atom) to node [above] {\etype{atom\_applies}} (predicate);
+\draw (atom) to node [left] {\etype{atom\_has}} (argument);
+\draw (equality) to node {\etype{equalizes}} (term);
+\draw (equality) to node {\etype{equalizes}} (variable);
+\draw (argument) to [bend right] node [left] {\etype{is}} (term);
+\draw (argument) to [loop left] node [left] {\etype{precedes}} (argument);
+\draw (argument) to node [below] {\etype{is}} (variable);
+\draw (term) to node [above] {\etype{term\_applies}} (function);
+\draw (term) to [bend right] node [right] {\etype{term\_has}} (argument);
+
+\end{tikzpicture}
+\end{figure}
+
+The graph representation has the following properties:
+\begin{itemize}
+\item For each relation $r$, its inverse $\inv{r}$ is also present in the graph,
+represented by a different edge type (unless $r = \inv{r}$ is an identity).
+% Note: The relation is considered an identity if it is a subset of the complete identity relation.
+\item Lossless: The original problem can be reconstructed from the graph representation completely
+(up to equivalent modifications).
+\item Signature agnostic: Renaming the symbols and variables in the input problem yields an isomorphic graph.
+\item A singleton node of type \ntype{problem} is connected to all the clauses of the problem.
+\item The polarity of the literals is expressed by the type of the edge (\epos{} or \eneg{})
+connecting the respective atom to the clause it occurs in.
+\item For every non-equality atom and term, the order of its arguments is captured by a sequence of \ntype{argument} nodes chained by edges \cite{Rawson2020}.
+\item The two operands of equality are not ordered.
+This reflects the symmetry of equality.
+\item Term-sharing is employed: Redundant atoms and terms share a node representation \cite{}.
+Note that since each variable is bound by a clause,
+ground terms may be shared across clauses,
+but non-ground terms may only be shared within a clause.
+\todo{FB: Remove as of little interest?}
+\end{itemize}
+\todo{FB: Reference appendix if we describe the representation in more detail there.}
+\todo[inline]{MS: Filosoficka k ``can be represented''; mozna by se mohlo nekde objevit:
+Snazime se do struktury HIN ``otisknout'' celou strukturu CNF (jak jsem rikal,
+znamena to, ze zobrazeni je proste), abychom siti nevzali moznost ``vedet o problemu
+uplne vsechno'' (az na veci, na kterych nezalezi jako poradi literaly v klauzulich, etc).
+Ta filosoficka poznamka je o tom, ze pro dobre uceni tohle vlastne vubec nemusi byt treba,
+ze nejaky ``hrubsi otisk'' by mohl stacit tez (a byt treba mensi),
+ale my nevime, jak takovy zvolit. }
 
@@
 
-\subsection{Graph representation of problems}
-
-\newcommand{\ntype}[1]{\texttt{#1}}
-\newcommand{\etype}[1]{\texttt{#1}}
-\newcommand{\epos}{\etype{pos}}
-\newcommand{\eneg}{\etype{neg}}
-
-\todo{MS: HIN bych povazoval za pro CADE-people neznamuy pojem.
-Bude treba uvest aspon jednou vetou. Mozna neco citovat?}
-
-Every \gls{cnf} problem can be represented by a \gls{hin} with the network schema shown in \cref{fig:CnfSchema}.\todo{MS: Mel jsem chut to opravit na velke "Fig.", ale s makrem se mi hadat nechce ;)}
-% Cite: https://www.kdd.org/exploration_files/V14-02-03-Sun.pdf
-% Referenced from: https://docs.dgl.ai/en/0.5.x/generated/dgl.DGLHeteroGraph.metagraph.html
-\todo{MS: Filosoficka k ``can be represented''; mozna by se mohlo nekde objevit:
-Snazime se do struktury HIN ``otisknout'' celou strukturu CNF (jak jsem rikal,
-znamena to, ze zobrazeni je proste), abychom siti nevzali moznost ``vedet o problemu
-uplne vsechno'' (az na veci, na kterych nezalezi jako poradi literaly v klauzulich, etc).
-Ta filosoficka poznamka je o tom, ze pro dobre uceni tohle vlastne vubec nemusi byt treba,
-ze nejaky ``hrubsi otisk'' by mohl stacit tez (a byt treba mensi),
-ale my nevime, jak takovy zvolit. }
-
-\begin{figure}[ht]
-\caption{CNF network schema}
-\label{fig:CnfSchema}
-\centering
-\tikzstyle{token} = [rectangle, draw]
-
-\begin{tikzpicture}[node distance = 1 and 2, ->]
-% https://tex.stackexchange.com/a/332796/202639
-
-% Node and edge types:
-% https://docs.google.com/spreadsheets/d/1PCPHEgk6vLxpdpcvB_PGoLx7p4DID6WtvVWy2mDuv4A/edit?usp=sharing
-
-\node (formula) [token] {\ntype{problem}};
-% TODO: Consider removing the Formula nodes.
-\node (clause) [token, below=of formula] {\ntype{clause}};
-\node (atom) [token, below left=of clause] {\ntype{atom}};
-\node (equality) [token, below right=of clause] {\ntype{equality}};
-\node (predicate) [token, left=of atom] {\ntype{predicate}};
-\node (argument) [token, below=of atom] {\ntype{argument}};
-\node (term) [token, below=of argument] {\ntype{term}};
-\node (function) [token, left=of term] {\ntype{function}};
-\node (variable) [token, right=of term] {\ntype{variable}};
-
-\draw (formula) to node [right] {\etype{contains}} (clause);
-\draw (clause) to [bend right] node [above] {\epos{}} (atom);
-\draw (clause) to [bend left] node [below] {\eneg{}} (atom);
-\draw (clause) to [bend left] node [above] {\epos{}} (equality);
-\draw (clause) to [bend right] node [below] {\eneg{}} (equality);
-\draw (clause) to node [above] {\etype{binds}} (variable);
-\draw (atom) to node [above] {\etype{atom\_applies}} (predicate);
-\draw (atom) to node [left] {\etype{atom\_has}} (argument);
-\draw (equality) to node {\etype{equalizes}} (term);
-\draw (equality) to node {\etype{equalizes}} (variable);
-\draw (argument) to [bend right] node [left] {\etype{is}} (term);
-\draw (argument) to [loop left] node [left] {\etype{precedes}} (argument);
-\draw (argument) to node [below] {\etype{is}} (variable);
-\draw (term) to node [above] {\etype{term\_applies}} (function);
-\draw (term) to [bend right] node [right] {\etype{term\_has}} (argument);
-
-\end{tikzpicture}
-\end{figure}
-
-The network of a problem is a directed graph $G = (V, E)$.
-The function $\tau: V \rightarrow A$ maps the nodes to their types:
-
-$$
-A = \{\ntype{problem}, \ntype{predicate}, \ntype{function}, \ntype{clause}, \ntype{atom}, \ntype{equality}, \ntype{term}, \ntype{variable}, \ntype{argument}\}
-$$
-
-The function $\phi: E \rightarrow E$ maps the edges to their types.
-
-\todo[inline]{Abstract from the edge types. Focus on the main idea. Technical details may be in technical report or appendix.}
-
-Various levels of term sharing are possible. [continue]
-
-\todo[inline]{Give an example of a problem and its graph.}
-
 \subsection{Generating precedences}

### 2021-02-18 architecture.tex
Architecture: Describe GCN (WIP)

@@
 ale my nevime, jak takovy zvolit. }
+
+\subsection{\Gls{gcn}: From graphs to symbol embeddings}
+
+For each symbol in the problem,
+we seek to find a vector representation, i.e., an \emph{embedding},
+that captures the symbol's properties that are relevant
+for the desirable relative rank of the symbol in the symbol precedence.
+The symbol embeddings are modeled by a \gls{rgcn} \cite{Schlichtkrull2017},
+\todo{Can I use the term \gls{rgcn} when I use a modified version? Namely, the activation is called earlier.}
+which is a stack of graph convolutional layers.
+Each layer consists of a collection of differentiable modules --- one for each edge type.
+A pass through the convolutional layer takes the embeddings of all symbols,
+converts them by the edge modules of the adjacent edges to form the messages,
+passes the messages to the destination nodes
+and aggregates the incoming messages of each node.
+In the simple case that each edge module is a dense layer,
+the output embeddings $h^{(l+1)}$ is computed from the input embeddings $h^{(l)}$ in the following manner:
+$$
+h_i^{(l+1)} =
+\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in \mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}
+$$
+%$$
+%h_i^{(l+1)} =
+%\mathrm{LayerNorm} \Parentheses{h_i^{(l)} + \sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in %\mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}}
+%$$
+% Inspiration: https://ufal.mff.cuni.cz/~straka/courses/npfl114/1920/slides.pdf/npfl114-07.pdf - slide 27 - Transformer
+\todo{FB: Mention inspiration: Transformer. See Straka's slides.}
+$h_i^{(l)}$ denotes the embedding of node $i$ at layer $l$.
+$\mathcal{R}$ denotes the set of all relations in the graph.
+$\sigma$ denotes the activation function, for example the \gls{relu}.
+$\mathcal{N}_i^r$ denotes the set of neighbors of node $i$ under relation $r$.
+$c_{j, i, r} = \sqrt{\card{\mathcal{N}_j^r}} \sqrt{\card{\mathcal{N}_i^r}}$ is a normalization constant \cite{kipf2017semisupervised}.
+$W_r^{(l)}$ is a trainable weight matrix representing relation $r$ at layer $l$.
+
+\todo[inline]{Explain residual connections and layer normalization.}
+\todo[inline]{MS: neni uplne jiste, ze ``CADE people'' oceni presny zapis 
+strutury site, vcetne prvku jako $\mathrm{LayerNorm}$ ve vzorecku.
+Nerikam, ze bychom to meli uplne zatajit, ale popis, ktery je zde, spis
+patri do appendixu (ML paperu). Na te siti vlastne nic originalniho neni,
+tak neni treba vsechno vysvetlit do detailu. Zajimavejsi tu
+potom je az to, jak se problem $P$ ``otiskne'' v topologii grafu. 
+To uz originalni je (a soutezi to s representacemi jako ta Mirkova)
+a popisujes to pak dal.}
 

### 2021-02-19 architecture.tex
Remove some redundant content from Architecture
Name a section with alternative content
Add dummy subsections in Architecture
zatim par poznamek

@@
+% !TEX root = main.tex
+
 \todo{Describe problem again, this time precisely / technically.}
@@
 The architecture is designed so that the recommender can be trained
-on the results executions of an \gls{atp} on various problems with random precedences.
+on the results of \gls{atp} executions on various problems with random precedences.
 The recommender is parameterized by weight tensors
@@
 \todo{Ensure we have defined ``gradient descent''.}
+\todo{MS: chapu ucel (a vidim, ze dalsi veta navazuje na ``parameters'', ale je to kostrbate.
+Recommender = system, chapu jako program. Programy vetsinou neparametrizujeme tenzorama a gradient descent zije na jine urovni,
+nez aby parametrizovane programy primo ucil. Uceni je spis nejaka technologie, kterou recommender pouziva, aby ... ``produces precedences
+that are likely to yield a successful proof''.  }
 The goal of the training is to find parameter values
@@
 that are likely to yield a successful proof in few iterations of the saturation loop.
-\todo{FB: Too vague?}
+\todo{FB: Too vague? MS: v tomhle momente mi to prijde dobry!}
 
@@
 \begin{enumerate}
-\item Graphifier converts the input \gls{cnf} problem into a problem graph.
+\item Graphifier\todo{MS: Zatim nevidim Graphifier ve \cref{fig:architecture}.} converts the input \gls{cnf} problem into a problem graph.
 \item \gls{gcn} converts a problem graph into symbol embeddings.
@@
 \end{enumerate}
+\todo{MS: tohle zatim chapu jako predbezny nastrel. Leda by uz pred tim bylo vysvetleno:
+embedding, \gls{gcn}/convolution layers, ... }
 
@@
 \todo{FB: Consider removing the footnote because it is basically useless.}
+\todo{MS: Footnote asi remove, ale neexistuje citace pro ``heterogeneous directed graph''?}
 Each of the nodes is labeled with a node type,
 and each edge is labeled with an edge type,
-informing the heterogeneous nature of the graph.
+informing\todo{MS: maybe better ``defining''?} the heterogeneous nature of the graph.
 The nodes of the graph correspond to various elements that constitute the \gls{cnf} formula,
-such as clauses, atoms and predicate symbols.
+such as predicate symbols, atoms, and clauses.
 Each such category of elements corresponds to one node type.
 The edges represent the (oriented) relations between the elements,
-for example the relation between a clause and one of its atoms,
+for example the incidence relation between a clause and one of its (literal's) atoms,
 or the relation between an atom and its predicate symbol.
@@
 % Note: The relation is considered an identity if it is a subset of the complete identity relation.
-\item Lossless: The original problem can be reconstructed from the graph representation completely
-(up to equivalent modifications).
+\todo{MS: tohle jsem nepochopil. Nemuzeme rict, ze (az na nejakou vyjimkou) jsou edges v obou smerech?}
+\item Lossless: The original problem can be faithfully reconstructed from the corresponding graph representation
+(up to logical equivalence).
 \item Signature agnostic: Renaming the symbols and variables in the input problem yields an isomorphic graph.
@@
 This reflects the symmetry of equality.
-\item Term-sharing is employed: Redundant atoms and terms share a node representation \cite{}.
+\item Term-sharing is employed:\todo{MS: Mozna presneji ``perfect sub-expression sharing''? 
+Predpokladam ze dva ruzne ground literaly p(c) tam budou taky jen jendnou?}
+Redundant atoms and terms share a node representation \cite{}.
 Note that since each variable is bound by a clause,
@@
 Ta filosoficka poznamka je o tom, ze pro dobre uceni tohle vlastne vubec nemusi byt treba,
-ze nejaky ``hrubsi otisk'' by mohl stacit tez (a byt treba mensi),
-ale my nevime, jak takovy zvolit. }
+ze nejaky ``hrubsi otisk'' by mohl stacit tez (a byt treba mensi), ale my nevime, jak takovy zvolit. }
 
@@
 that captures the symbol's properties that are relevant
-for the desirable relative rank of the symbol in the symbol precedence.
-The symbol embeddings are modeled by a \gls{rgcn} \cite{Schlichtkrull2017},
-\todo{Can I use the term \gls{rgcn} when I use a modified version? Namely, the activation is called earlier.}
+for the correctly ranking the symbol in the observed symbol precedences.
+The symbol embeddings are modeled\todo{MS: embeddings are ``output''? } by a \gls{rgcn} \cite{Schlichtkrull2017},
+\todo{Can I use the term \gls{rgcn} when I use a modified version? Namely, the activation is called earlier. MS: sounds good.}
 which is a stack of graph convolutional layers.
@@
 A pass through the convolutional layer takes the embeddings of all symbols,
-converts them by the edge modules of the adjacent edges to form the messages,
+converts them by the edge modules of the adjacent edges to form the messages,\todo{MS: ``message'' occurs for the first time. 
+Maybe ``a message'', or explain beforehand.}
 passes the messages to the destination nodes
 and aggregates the incoming messages of each node.
-In the simple case that each edge module is a dense layer,
-the output embeddings $h^{(l+1)}$ is computed from the input embeddings $h^{(l)}$ in the following manner:
+In the simple case that each edge module is a dense layer,\todo{MS: hnidopich nevi, co to znamena ``dense layer''}
+the output embedding $h^{(l+1)}$ is computed from the input embeddings $h^{(l)}$ in the following manner:
 $$
@@
 a popisujes to pak dal.}
+
+\subsection{Projection: From symbol embeddings to symbol costs}
+
+\subsection{Sort: From symbol costs to precedence}
+
+\subsection{Loss}
+
+\subsection{[Alternative: Top-down approach]}
 
@@
 random swaps of pairs of symbols.}
-
-\subsection{Notes}
-
-The recommender consists of the following components:
-
-\begin{itemize}
-\item Symbol embedding model
-\item Symbol cost model
-\item Loss function
-\item Precedence generator
-\end{itemize}
 
@@
 
-\subsection{Symbol cost model}
-
 \subsection{Generating precedences}

### 2021-02-19 architecture.tex
Improve wording in Architecture

@@
 on the results of \gls{atp} executions on various problems with random precedences.
-The recommender is parameterized by weight tensors
+Since the recommender contains a neural network,
+it is parameterized by weight tensors
 whose values can be trained by gradient descent.
@@
 \item \gls{gcn} converts a problem graph into symbol embeddings.
-The \gls{gcn} contains one or more convolution layers.
+%The \gls{gcn} contains one or more convolution layers.
 \item Projection converts the symbol embeddings into a vector of symbol costs.
@@
 informing\todo{MS: maybe better ``defining''?} the heterogeneous nature of the graph.
-The nodes of the graph correspond to various elements that constitute the \gls{cnf} formula,
-such as predicate symbols, atoms, and clauses.
+Each node corresponds to one of the elements that constitute the \gls{cnf} formula,
+such as a clause, an atom or a predicate symbol.
 Each such category of elements corresponds to one node type.
@@
 \begin{itemize}
-\item For each relation $r$, its inverse $\inv{r}$ is also present in the graph,
-represented by a different edge type (unless $r = \inv{r}$ is an identity).
-% Note: The relation is considered an identity if it is a subset of the complete identity relation.
-\todo{MS: tohle jsem nepochopil. Nemuzeme rict, ze (az na nejakou vyjimkou) jsou edges v obou smerech?}
 \item Lossless: The original problem can be faithfully reconstructed from the corresponding graph representation
@@
 \item Signature agnostic: Renaming the symbols and variables in the input problem yields an isomorphic graph.
+\item For each relation $r$, its inverse $\inv{r}$ is also present in the graph,
+typically represented by a different edge type.
+\todo{MS: tohle jsem nepochopil. Nemuzeme rict, ze (az na nejakou vyjimkou) jsou edges v obou smerech?}
 \item A singleton node of type \ntype{problem} is connected to all the clauses of the problem.
@@
 Note that since each variable is bound by a clause,
-ground terms may be shared across clauses,
-but non-ground terms may only be shared within a clause.
+ground terms are shared across clauses,
+but non-ground terms are only shared within the context of a clause.
 \todo{FB: Remove as of little interest?}
@@
 
-Note here that the symbol precedence heuristics commonly used in practice
+Note that the symbol precedence heuristics commonly used in practice
 conform to this scheme:
 they order the symbols by a numeric property, such as arity or number of occurrences.
+\todo{MS: tohle se mi libi!}
 
@@
 assigns each symbol in $s \in \Sigma$ a real value $c(s)$.
-It first uses a symbol embedding model to assign each symbol an embedding.
+It first uses a symbol embedding model to assign each symbol $s$ an embedding $E(s)$.
 The resulting symbol cost is a dot product of the symbol embedding with a trainable weight vector:

### 2021-02-19 architecture.tex
Include an example graph of a simple problem

@@
 \Cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.
-
-\todo[inline]{Give an example of a problem and its graph.}
+\Cref{fig:GcnExample} shows an example of a graph representation of a simple problem.
 
@@
 \end{tikzpicture}
+\end{figure}
+
+\begin{figure}[h]
+\caption{Graph representation of the \gls{cnf} formula $a=b \wedge f(a,b) \neq f(b,b)$.}
+\label{fig:GcnExample}
+\centering
+\digraph[scale=0.3]{GcnExample}{
+	node [fontsize=32, shape=record];
+	edge [fontsize=32, dir=both, arrowtail=empty];
+	problem [label=<problem|a=b &and; f(a,b)&ne;f(b,b)>];
+	c0 [label="clause|a=b"];
+	c1 [label=<clause|f(a,b)&ne;f(b,b)>];
+	problem -> c0;
+	problem -> c1;
+	t0 [label="equality atom|a=b"];
+	t1 [label="equality atom|f(a,b)=f(b,b)"];
+	c0 -> t0 [label=" + "];
+	c1 -> t1 [label=" &ndash; "];
+	ta [label="term|a"];
+	tb [label="term|b"];
+	ff [label="function|f", style=bold];
+	fa [label="function|a", style=bold];
+	fb [label="function|b", style=bold];
+	tfab [label="term|f(a,b)"];
+	tfbb [label="term|f(b,b)"];
+	tfab0 [label="argument|1", style=dotted];
+	tfab1 [label="argument|2", style=dotted];
+	tfbb0 [label="argument|1", style=dotted];
+	tfbb1 [label="argument|2", style=dotted];
+	t0 -> ta;
+	t0 -> tb;
+	t1 -> tfab;
+	t1 -> tfbb;
+	tfab -> ff;
+	tfab -> tfab0;
+	tfab0 -> tfab1;
+	tfab0 -> ta;
+	tfab1 -> tb;
+	tfbb -> ff;
+	tfbb -> tfbb0;
+	tfbb0 -> tfbb1;
+	tfbb0 -> tb;
+	tfbb1 -> tb;
+	ta -> fa;
+	tb -> fb;
+}
 \end{figure}

### 2021-02-19 architecture.tex
Add a complete description of the GCN

@@
 which is a stack of graph convolutional layers.
-Each layer consists of a collection of differentiable modules --- one for each edge type.
-A pass through the convolutional layer takes the embeddings of all symbols,
-converts them by the edge modules of the adjacent edges to form the messages,\todo{MS: ``message'' occurs for the first time. 
+Each layer consists of a collection of differentiable modules---one module per edge type.
+The computation of the \gls{gcn} starts with assigning each node an initial embedding
+and then repeatedly updates the embeddings by passing them through convolutional layers.
+\todo{Ensure terms are clear (preferably defined): embedding, vector, trainable vector, feature vector.}
+
+The initial embedding is a concatenation of two vectors:
+a node feature vector (typically empty)
+and a trainable vector shared by all nodes of the same type.
+In our particular implementation,
+feature vectors are used in nodes that correspond to clauses and symbols.
+Each clause node has a feature vector with a one-hot encoding of the role of the clause,
+which can be either axiom, assumption, or negated conjecture.
+Each symbol node has a feature vector with two bits of data:
+whether the symbol was introduced into the problem during preprocessing,
+and whether the symbol appears in a conjecture clause.
+
+One pass through the convolutional layer
+updates the node embeddings by passing a message along each of the edges.
+\todo{MS: ``message'' occurs for the first time. 
 Maybe ``a message'', or explain beforehand.}
-passes the messages to the destination nodes
-and aggregates the incoming messages of each node.
-In the simple case that each edge module is a dense layer,\todo{MS: hnidopich nevi, co to znamena ``dense layer''}
-the output embedding $h^{(l+1)}$ is computed from the input embeddings $h^{(l)}$ in the following manner:
+For an edge of type $r \in \mathcal{R}$ going from source node $s$ to destination node $d$ at layer $l$,
+the message is composed by converting the embedding of the source node $h_s^{(l)}$
+using the module associated with the edge type $r$.
+In the simple case that the module is a dense layer with weights $W_r^{(l)}$,
+\todo{MS: hnidopich nevi, co to znamena ``dense layer''}
+the message is $h_s^{(l)} W_r^{(l)}$.
+Each message is then divided by a normalization constant
+$c_{s,d} = \sqrt{\card{\mathcal{N}_s^r}} \sqrt{\card{\mathcal{N}_d^r}}$ \cite{kipf2017semisupervised},
+where $\mathcal{N}_n^r$ is the set of neighbors of node $n$ under the relation $r$.
+\todo{FB: Mention that we mean both in- and out-neighbors?}
+Once all the messages are computed,
+they are aggregated by the destination nodes to form the new node embedding.
+Each node $d$ aggregates all the incoming messages of a given edge type $r$ by summation,
+then passes the sum through an activation function $\sigma$ such as the \gls{relu},
+and finally aggregates the messages across the edge types by summation,
+yielding the new embedding $h_d^{(l+1)}$.
+The following formula captures the update of embedding of node $d$:
 $$
-h_i^{(l+1)} =
-\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in \mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}
+h_d^{(l+1)} =
+\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in \mathcal{N}_s^r} \frac{1}{c_{s,d}} h_s^{(l)} W_r^{(l)}}
 $$
@@
 % Inspiration: https://ufal.mff.cuni.cz/~straka/courses/npfl114/1920/slides.pdf/npfl114-07.pdf - slide 27 - Transformer
-\todo{FB: Mention inspiration: Transformer. See Straka's slides.}
-$h_i^{(l)}$ denotes the embedding of node $i$ at layer $l$.
-$\mathcal{R}$ denotes the set of all relations in the graph.
-$\sigma$ denotes the activation function, for example the \gls{relu}.
-$\mathcal{N}_i^r$ denotes the set of neighbors of node $i$ under relation $r$.
-$c_{j, i, r} = \sqrt{\card{\mathcal{N}_j^r}} \sqrt{\card{\mathcal{N}_i^r}}$ is a normalization constant \cite{kipf2017semisupervised}.
-$W_r^{(l)}$ is a trainable weight matrix representing relation $r$ at layer $l$.
+%\todo{FB: Mention inspiration: Transformer. See Straka's slides.}
 

### 2021-02-19 architecture.tex
Reference the GCN description from Evaluation
Add a todo

@@
 \subsection{\Gls{gcn}: From graphs to symbol embeddings}
+\label{sec:gcn}
 
@@
 that captures the symbol's properties that are relevant
-for the correctly ranking the symbol in the observed symbol precedences.
+for correctly ranking the symbol in the observed symbol precedences.
 The symbol embeddings are modeled\todo{MS: embeddings are ``output''? } by a \gls{rgcn} \cite{Schlichtkrull2017},

### 2021-02-19 architecture.tex
jeste neco

--- 2021-02-19 architecture.tex
@@
 on the results of \gls{atp} executions on various problems with random precedences.
-Since the recommender contains a neural network,
-it is parameterized by weight tensors
+The recommender is parameterized by weight tensors
 whose values can be trained by gradient descent.
@@
 \item \gls{gcn} converts a problem graph into symbol embeddings.
-%The \gls{gcn} contains one or more convolution layers.
+The \gls{gcn} contains one or more convolution layers.
 \item Projection converts the symbol embeddings into a vector of symbol costs.
@@
 informing\todo{MS: maybe better ``defining''?} the heterogeneous nature of the graph.
-Each node corresponds to one of the elements that constitute the \gls{cnf} formula,
-such as a clause, an atom or a predicate symbol.
+The nodes of the graph correspond to various elements that constitute the \gls{cnf} formula,
+such as predicate symbols, atoms, and clauses.
 Each such category of elements corresponds to one node type.
@@
 \Cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.
-\Cref{fig:GcnExample} shows an example of a graph representation of a simple problem.
+
+\todo[inline]{Give an example of a problem and its graph.}
 
@@
 
-\begin{figure}[h]
-\caption{Graph representation of the \gls{cnf} formula $a=b \wedge f(a,b) \neq f(b,b)$.}
-\label{fig:GcnExample}
-\centering
-\digraph[scale=0.3]{GcnExample}{
-	node [fontsize=32, shape=record];
-	edge [fontsize=32, dir=both, arrowtail=empty];
-	problem [label=<problem|a=b &and; f(a,b)&ne;f(b,b)>];
-	c0 [label="clause|a=b"];
-	c1 [label=<clause|f(a,b)&ne;f(b,b)>];
-	problem -> c0;
-	problem -> c1;
-	t0 [label="equality atom|a=b"];
-	t1 [label="equality atom|f(a,b)=f(b,b)"];
-	c0 -> t0 [label=" + "];
-	c1 -> t1 [label=" &ndash; "];
-	ta [label="term|a"];
-	tb [label="term|b"];
-	ff [label="function|f", style=bold];
-	fa [label="function|a", style=bold];
-	fb [label="function|b", style=bold];
-	tfab [label="term|f(a,b)"];
-	tfbb [label="term|f(b,b)"];
-	tfab0 [label="argument|1", style=dotted];
-	tfab1 [label="argument|2", style=dotted];
-	tfbb0 [label="argument|1", style=dotted];
-	tfbb1 [label="argument|2", style=dotted];
-	t0 -> ta;
-	t0 -> tb;
-	t1 -> tfab;
-	t1 -> tfbb;
-	tfab -> ff;
-	tfab -> tfab0;
-	tfab0 -> tfab1;
-	tfab0 -> ta;
-	tfab1 -> tb;
-	tfbb -> ff;
-	tfbb -> tfbb0;
-	tfbb0 -> tfbb1;
-	tfbb0 -> tb;
-	tfbb1 -> tb;
-	ta -> fa;
-	tb -> fb;
-}
-\end{figure}
-
 The graph representation has the following properties:
 \begin{itemize}
+\item For each relation $r$, its inverse $\inv{r}$ is also present in the graph,
+represented by a different edge type (unless $r = \inv{r}$ is an identity).
+% Note: The relation is considered an identity if it is a subset of the complete identity relation.
+\todo{MS: tohle jsem nepochopil. Nemuzeme rict, ze (az na nejakou vyjimkou) jsou edges v obou smerech?}
 \item Lossless: The original problem can be faithfully reconstructed from the corresponding graph representation
@@
 \item Signature agnostic: Renaming the symbols and variables in the input problem yields an isomorphic graph.
-\item For each relation $r$, its inverse $\inv{r}$ is also present in the graph,
-typically represented by a different edge type.
-\todo{MS: tohle jsem nepochopil. Nemuzeme rict, ze (az na nejakou vyjimkou) jsou edges v obou smerech?}
 \item A singleton node of type \ntype{problem} is connected to all the clauses of the problem.
@@
 Note that since each variable is bound by a clause,
-ground terms are shared across clauses,
-but non-ground terms are only shared within the context of a clause.
+ground terms may be shared across clauses,
+but non-ground terms may only be shared within a clause.
 \todo{FB: Remove as of little interest?}

### 2021-02-19 architecture.tex
Respond to MS's notes about Architecture

--- 2021-02-19 architecture.tex
@@
 that are likely to yield a successful proof in few iterations of the saturation loop.
-\todo{FB: Too vague? MS: v tomhle momente mi to prijde dobry!}
 
-The recommender consists of modules that perform specific subtasks (see \cref{fig:architecture}):
+The recommender consists of modules that perform specific subtasks,
+each of which is described in detail in one of the following sections (see also \cref{fig:architecture}):
 \begin{enumerate}
-\item Graphifier\todo{MS: Zatim nevidim Graphifier ve \cref{fig:architecture}.} converts the input \gls{cnf} problem into a problem graph.
+\item Graphifier converts the input \gls{cnf} problem into a problem graph.
 \item \gls{gcn} converts a problem graph into symbol embeddings.
@@
 \todo{MS: tohle zatim chapu jako predbezny nastrel. Leda by uz pred tim bylo vysvetleno:
-embedding, \gls{gcn}/convolution layers, ... }
+embedding, \gls{gcn}/convolution layers, ... \\
+FB: Staci predestrit, ze detaily vysvetlim pozdeji?}
 
@@
 the input problem is converted from a \gls{cnf} representation
-to a \emph{heterogeneous directed graph}.\footnote{Data mining literature often uses the term \gls{hin} \cite{Shi2015} for heterogeneous graphs.
-We prefer to conform to the terminology common in literature studying \glspl{gnn}.}
-\todo{FB: Consider removing the footnote because it is basically useless.}
-\todo{MS: Footnote asi remove, ale neexistuje citace pro ``heterogeneous directed graph''?}
+to a \emph{heterogeneous (directed) graph} \cite{Zhou2018}.
+% Zhou uses the term "heterogeneous graph".
+%\footnote{Data mining literature often uses the term \gls{hin} \cite{Shi2015} for heterogeneous graphs.
+%We prefer to conform to the terminology common in literature studying \glspl{gnn}.}
 Each of the nodes is labeled with a node type,
 and each edge is labeled with an edge type,
-informing\todo{MS: maybe better ``defining''?} the heterogeneous nature of the graph.
+defining the heterogeneous nature of the graph.
 Each node corresponds to one of the elements that constitute the \gls{cnf} formula,
@@
 The edges represent the (oriented) relations between the elements,
-for example the incidence relation between a clause and one of its (literal's) atoms,
+for example the incidence relation between a clause and one of its (literals') atoms,
 or the relation between an atom and its predicate symbol.
@@
 typically represented by a different edge type.
-\todo{MS: tohle jsem nepochopil. Nemuzeme rict, ze (az na nejakou vyjimkou) jsou edges v obou smerech?}
+\todo{MS: tohle jsem nepochopil. Nemuzeme rict, ze (az na nejakou vyjimkou) jsou edges v obou smerech?\\
+FB: Chci vyjasnit, ze inverzni edge ma jiny edge type.}
 \item A singleton node of type \ntype{problem} is connected to all the clauses of the problem.
@@
 This reflects the symmetry of equality.
-\item Term-sharing is employed:\todo{MS: Mozna presneji ``perfect sub-expression sharing''? 
-Predpokladam ze dva ruzne ground literaly p(c) tam budou taky jen jendnou?}
+\item Perfect sub-expression sharing:
+\todo{MS: Predpokladam ze dva ruzne ground literaly p(c) tam budou taky jen jendnou?\\
+FB: Literaly nemaji nody. Atomy maji nody a polarita literalu je zakodovana v typu hrany, ktery jej spojuje s klauzuli.}
 Redundant atoms and terms share a node representation \cite{}.
@@
 Ta filosoficka poznamka je o tom, ze pro dobre uceni tohle vlastne vubec nemusi byt treba,
-ze nejaky ``hrubsi otisk'' by mohl stacit tez (a byt treba mensi), ale my nevime, jak takovy zvolit. }
+ze nejaky ``hrubsi otisk'' by mohl stacit tez (a byt treba mensi), ale my nevime, jak takovy zvolit.\\
+FB: Zkusim to popsat, kdyz zbyde cas.}
+\todo{FB: Mention other encodings that have been proposed by Mirek and Michael.}
 
@@
 for correctly ranking the symbol in the observed symbol precedences.
-The symbol embeddings are modeled\todo{MS: embeddings are ``output''? } by a \gls{rgcn} \cite{Schlichtkrull2017},
-\todo{Can I use the term \gls{rgcn} when I use a modified version? Namely, the activation is called earlier. MS: sounds good.}
+\todo{FB: What does "correct" mean?}
+The symbol embeddings are output by a \gls{rgcn} \cite{Schlichtkrull2017},
 which is a stack of graph convolutional layers.
@@
 and then repeatedly updates the embeddings by passing them through convolutional layers.
-\todo{Ensure terms are clear (preferably defined): embedding, vector, trainable vector, feature vector.}
+\todo{FB: Ensure terms are clear (preferably defined): embedding, vector, trainable vector, feature vector.}
 
@@
 updates the node embeddings by passing a message along each of the edges.
-\todo{MS: ``message'' occurs for the first time. 
-Maybe ``a message'', or explain beforehand.}
 For an edge of type $r \in \mathcal{R}$ going from source node $s$ to destination node $d$ at layer $l$,

### 2021-02-21 architecture.tex
GCN layer: Add intercept
Update architecture overview module list

@@
 \item Graphifier converts the input \gls{cnf} problem into a problem graph.
-\item \gls{gcn} converts a problem graph into symbol embeddings.
-%The \gls{gcn} contains one or more convolution layers.
-\item Projection converts the symbol embeddings into a vector of symbol costs.
-\item Sorting converts the symbol costs into a symbol precedence.
+\item \Gls{gcn} converts a problem graph into symbol embeddings.
+\item Output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
+\item Ranking converts the symbol costs into a symbol precedence.
 It is only used in generating mode.
@@
 h_d^{(l+1)} =
-\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in \mathcal{N}_s^r} \frac{1}{c_{s,d}} h_s^{(l)} W_r^{(l)}}
+\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (h_s^{(l)} W_r^{(l)} + b_r^{(l)})}
 $$

### 2021-02-21 architecture.tex
Remove an empty line
Describe output layer

@@
 
-\subsection{Projection: From symbol embeddings to symbol costs}
+\subsection{Output layer: From symbol embeddings to symbol costs}
+
+The symbol cost of each symbol is computed by passing the symbol's embedding through a dense layer with a single output unit.
+No activation function is applied so that the output values can span the whole $\re$.
+
+Note that it is possible to use a more complex projection module,
+e.g., a feed-forward network with one or more hidden layers.
+\todo{FB: Ensure the term is defined.}
+Our experiments showed no significant improvement when a hidden layer is added,
+arguably because the underlying \gls{gcn} learns a sufficiently complex transformation.
+
+For input problem $P$
+with signature $\Sigma = (s_1, \ldots, s_n)$,
+we denote the cost of the $i$-th symbol as $c(i)$.
 

### 2021-02-21 architecture.tex
Describe ranking (symbol cost to precedence)

@@
 
-\subsection{Sort: From symbol costs to precedence}
+\subsection{Ranking: From symbol costs to precedence}
+
+We extend the notion of cost from symbols to precedences
+by summing up the symbol costs
+weighted by their positions in the given precedence $\pi$:
+$$
+C(\pi) = \sum_{i=1}^n c(\pi(i)) \cdot i
+$$
+
+\begin{lemma}
+Precedence cost $C$ is minimized by the precedence that ranks the symbols by their costs in non-increasing order:
+% FB: The ranking terminology is from Fast Differentiable [...] Ranking.
+$$
+\argmin_\pi C(\pi) \in \argsort^- (c(1), \ldots, c(n))
+$$
+\end{lemma}
+
+\begin{proof}
+We prove the lemma by contradiction.
+Let $\pi$ minimize $C$ and let $\pi$ not rank the costs in non-increasing order.
+Then there exist $k < l$ such that $c(\pi(k)) < c(\pi(l))$.
+Let $\bar{\pi}$ be a precedence obtained from $\pi$ by swapping the elements $k$ and $l$.
+%$\bar{\pi} = (\pi(1), \ldots, \pi(k-1), \pi(l), \pi(k+1), \ldots, \pi(l-1), \pi(k), \pi(l+1), \ldots, \pi(n))$.
+\begin{align*}
+C(\bar{\pi}) - C(\pi)
+&= kc(\bar{\pi}(k)) + lc(\bar{\pi}(l)) - kc(\pi(k)) - lc(\pi(l)) \\
+&= kc(\pi(l)) + lc(\pi(k)) - kc(\pi(k)) - lc(\pi(l)) \\
+&= k(c(\pi(l)) - c(\pi(k))) - l(c(\pi(l)) - c(\pi(k))) \\
+&= (k-l) (c(\pi(l)) - c(\pi(k))) \\
+&< 0
+\end{align*}
+The final inequality is due to the assumption that $k-l < 0$ and
+$c(\pi(l)) - c(\pi(k)) > 0$.
+Thus, $C(\bar{\pi}) < C(\pi)$, which is contradicts the assumption that $\pi$ minimizes $C$. \qed
+\end{proof}
+
+Once the symbol costs are known,
+producing a precedence that minimizes the precedence cost is cheap
+because ranking is a fast operation.
+
+Note that the precedence that minimizes $C$
+orders the symbols with the lowest cost as the last,
+prioritizing them for early inferences.
+
+\todo[inline]{FB: Why is the equality predicate always the first in the precedence?}
 

### 2021-02-21 introduction.tex
Write our contributions in Introduction

@@
 
-\todo[inline,author=FB]{Mention contributions explicitly.}
+Our contributions:
+\begin{itemize}
+\item Up to our knowledge, \cref{sec:architecture} constitutes the first attempt
+to propose good symbol precedences automatically using a non-linear transformation of the input problem structure.
+Specifically, we explore the possibility of using a \gls{gnn} to learn symbol representations conducive for creating good precedences.
+\item The experimental evaluation in \cref{sec:evaluation} proves practical feasibility of the proposed approach.
+\item Besides tackling the particular task of generating symbol precedences,
+the approach described in \cref{sec:architecture} may be of a more general interest
+for a researcher trying to apply statistical learning to produce arbitrarily long permutations
+that optimize some non-differentiable quantitative criterion.
+\todo{FB: Give examples of such tasks. How about constructive TSP?}
+\end{itemize}
 

### 2021-02-21 architecture.tex
Rename section Loss to Loss function
Add abstract description of training (WIP)

@@
 \subsection{From \gls{cnf} to graphs}
+\label{sec:graphifier}
 
@@
 \subsection{Output layer: From symbol embeddings to symbol costs}
+\label{sec:output}
 
@@
 we denote the cost of the $i$-th symbol as $c(i)$.
+\todo{FB: Consider using $c(s_i)$.}
+\todo{FB: Consider making the background problem explicit by using $c(i|P)$ or $C(i,P)$.}
 
 \subsection{Ranking: From symbol costs to precedence}
+\label{sec:ranking}
 
@@
 $$
+\todo{FB: Consider making the background problem explicit by using $C(\pi|P)$ or $C(\pi,P)$.}
+\todo[inline]{FB: Consider accessing elements $\pi$ as vector elements $\pi_i$ instead of $\pi(i)$.
+Keep in mind that $\inv{\pi}$ must be updated as well.
+The motivation for using $\pi(i)$ is that $\inv{\pi}(i)$ looks clearer than $\inv{\pi}_i$.
+How about using $(\inv{\pi})_i$?
+We may also omit the inversion completely.}
 
@@
 \todo[inline]{FB: Why is the equality predicate always the first in the precedence?}
+\todo[inline]{FB: Mention that the common heuristics fit this scheme.}
 
-\subsection{Loss}
+\subsection{Training}
+
+In \cref{sec:graphifier,sec:gcn,sec:output,sec:ranking} we described the structure of a recommender system that generates a precedence for an arbitrary input problem.
+The efficacy of the recommender depends on the quality of the underlying symbol cost function.
+In theory, the symbol cost function can assign the costs so that
+ranking the symbols by their costs yields an optimum precedence,
+and all the information necessary to determine the optimum precedence is present in the graph representation of the input problem.
+Our approach to defining an appropriate symbol cost function is based on statistical learning
+from executions of an \gls{atp} on a set of problems with various precedences.
+
+\subsubsection{Training data}
+
+Each training example has the form $(P, \PrecBetter, \PrecWorse)$,
+where $P = (\Sigma, \mathit{Cl})$ is a problem
+and $\PrecBetter, \PrecWorse$ are precedences over $\Sigma$
+such that $\PrecBetter$ solves $P$ in fewer iterations of the saturation loop than $\PrecWorse$,
+denoted as $\Better{\PrecBetter}{\PrecWorse}$.
+\todo{Is this sufficient?}
+
+\subsubsection{Loss function}
+
+\todo{Two levels of proxy metrics: 0-1 loss, differentiable loss (hinge, logistic)}
+
+To ensure that ranking the symbols by their costs
+yields a good precedence,
+we want the symbol cost function $c$
+to satisfy the inequality $C(\PrecBetter) < C(\PrecWorse)$
+which can alternatively be expressed as $s(\PrecBetter, \PrecWorse) = C(\PrecBetter) - C(\PrecWorse) < 0$.
+We consider the value $s(\PrecBetter, \PrecWorse)$
+to be the score of the (ordered) precedence pair $(\PrecBetter, \PrecWorse)$.
+Given a set of examples of the form $(P, \PrecBetter, \PrecWorse)$
+where $\Better{\PrecBetter}{\PrecWorse}$,
+our goal is to maximize the accuracy
+$\frac{1}{m} \sum_x \iverson{s(\PrecBetter, \PrecWorse) < 0}$.
+% Alternative: We actually don't care about the relative order of non-minimum precedences.
+
+A common approach to training a binary classifier is to relax the non-differentiable accuracy $[s(\PrecBetter, \PrecWorse) < 0]$
+to a differentiable proxy
+such as the logistic loss
+$L = - \log \sigmoid s(\PrecBetter, \PrecWorse)$.
+
+\subsection{Notes}
+
+We need to train $c$ in a way that ensures that $C$ is minimized by a good precedence.
+On pairs,
+$C(\pi)$ should be smaller than $C(\rho)$ iff $\Better{\pi}{\rho}$.
+
+% What if we trained the binary classifier on vector:
+% C(\pi), C(\rho), C(\pi)^2, C(\rho)^2 (kernel trick?)
+
+Let $P = (\Sigma, \mathit{Cl})$ be a problem.
+Let $\PrecBetter, \PrecWorse$ be two precedences over $\Sigma$.
+% that are comparable according to AST.
+Let $y = 1$ if $\PrecBetter$ is better than $\PrecWorse$,
+denoted as $\Better{\PrecBetter}{\PrecWorse}$,
+and $y = 0$ otherwise.
+
+The examples that the recommender will be trained on have the form
+$(P, \PrecBetter, \PrecWorse)$, where $P = (\Sigma, \mathit{Cl})$ is a \gls{cnf} problem, and $\PrecBetter, \PrecWorse$ are precedences over $\Sigma$
+where $\PrecBetter$ yields a faster proof search than $\PrecWorse$,
+\todo{FB: Rephrase?}
+denoted as $\Better{\PrecBetter}{\PrecWorse}$.
+
+Given an example $x$,
+a binary classifier predicts the probability of event $1$,
+denoted as $p(x)$.
+The classifier is trained on samples of the form $(x, y)$,
+where $x$ is the observable state and $y \in \{0, 1\}$ is the target label.
+Logistic regression is a popular approach to train a binary classifier.
+Logistic regression is based on the logistic loss:
+$$
+L(x, y) = - y \log p(x) - (1-y) \log (1-p(x))
+$$
+
+% Hinge loss (y \in {-1, 1}):
+% L = max(0, 1 - ty)
+% t = 1: L = max(0, 1-y)
+
+% Binary crossentropy (y \in {0, 1}):
+% L = - y log p(1)) - (1-y) log p(0)
+% y = 1: L = - log p(1) = - log sigmoid c
+
+We train the system on results of \gls{atp} executions on problems with random precedences.
+Let $P = (\Sigma, \mathit{Cl})$ be a problem
+and let $\PrecBetter, \PrecWorse$ be two precedences over $\Sigma$.
+We run an \gls{atp} on $P$ with the two precedences.
+If the run with $\PrecBetter$ finds the proof successfully and uses less saturation loop iterations than the run with $\PrecWorse$,
+we can be certain that $\PrecBetter$ is a better precedence for $P$ than $\PrecWorse$,
+denoted as $\Better{\PrecBetter}{\PrecWorse}$.
+
+A binary classifier predicts the probability of complementary events $0$ and $1$,
+denoted as $p(0)$ and $p(1)$ respectively.
+The events are complementary,
+meaning $p(0) = 1 - p(1)$ and $p(0) + p(1) = 1$.
+
+A binary classifier with a binary crossentropy loss
+takes the predicted probability $p$ of events $0, 1$
+and computes the loss:
+$$
+L(y) = y log(p(1)) + (1-y) log(p(0))
+$$
+
+The examples that the recommender will be trained on have the form
+$(P, \PrecBetter, \PrecWorse)$, where $P = (\Sigma, \mathit{Cl})$ is a \gls{cnf} problem, and $\PrecBetter, \PrecWorse$ are precedences over $\Sigma$
+where $\PrecBetter$ yields a faster proof search than $\PrecWorse$,
+\todo{FB: Rephrase?}
+denoted as $\Better{\PrecBetter}{\PrecWorse}$.
+
+We train a binary classifier that decides,
+for a pair of precedences $\PrecBetter, \PrecWorse$,
+whether $\Better{\PrecBetter}{\PrecWorse}$.
+Since all the training examples are oriented so that $\Better{\PrecBetter}{\PrecWorse}$,
+the classification target value for all the samples is $1$.
+\todo{FB: Somebody might think that this is a problem because the classifier can simply learn to always say "1".
+The structure of the classifier ($C(x_1) - C(x_2)$) prevents that.
+Consider explaining.}
+Thus the binary crossentropy loss can be expressed as a simple expression:
+$$
+L(P, \PrecBetter, \PrecWorse) = - \log \sigmoid (C(\PrecWorse) - C(\PrecBetter))
+$$
+
+Derivation:
+$$
+L(P, \PrecBetter, \PrecWorse) = - \sum y \log p(y)
+$$
+
+$$
+p(0) = \sigmoid (C(\PrecBetter) - C(\PrecWorse)) \\
+p(1) = \sigmoid (C(\PrecWorse) - C(\PrecBetter))
+$$
+
+\todo{Mention normalization.}
 
@@
 random swaps of pairs of symbols.}
-
-\newcommand{\Prec}{\pi}
-\newcommand{\PrecBetter}{\pi}
-\newcommand{\PrecWorse}{\rho}
 

### 2021-02-22 architecture.tex
architecture notes

@@
 that are likely to yield a successful proof''.  }
-The goal of the training is to find parameter values
-such that the recommender produces precedences
-that are likely to yield a successful proof in few iterations of the saturation loop.
+The goal of the training is to find parameter values such that the recommender produces precedences
+that are likely to yield a successful proof in as few iterations of the saturation loop as possible.\todo{MS: mozna udernejsi?}
 
@@
 \item \Gls{gcn} converts a problem graph into symbol embeddings.
-\item Output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
+\todo{MS: Kdyz embeddingy nebudou v preliminaries, je asi OK ctenare, ktery by o nich neslysel, zde trochu vydesit.
+Ale v te prislusne podsekci tim zas zacit.}
+\item An output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
+\todo{MS: ``output function \cite{Zhou2018}'' my nic nerika, mel bych to znat?}
 \item Ranking converts the symbol costs into a symbol precedence.
@@
 embedding, \gls{gcn}/convolution layers, ... \\
-FB: Staci predestrit, ze detaily vysvetlim pozdeji?}
+FB: Staci predestrit, ze detaily vysvetlim pozdeji? MS: asi jo :)}
 
@@
 \Cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.
-\Cref{fig:GcnExample} shows an example of a graph representation of a simple problem.
+\Cref{fig:GcnExample}\todo{MS: ten se mi libi!} shows an example of a graph representation of a simple problem.
 
@@
 \todo{MS: Predpokladam ze dva ruzne ground literaly p(c) tam budou taky jen jendnou?\\
-FB: Literaly nemaji nody. Atomy maji nody a polarita literalu je zakodovana v typu hrany, ktery jej spojuje s klauzuli.}
+FB: Literaly nemaji nody. Atomy maji nody a polarita literalu je zakodovana v typu hrany, ktery jej spojuje s klauzuli.
+MS: O to my, neslo. Slo o to, jestli se sdily ground termy mezi klauzulemi, ted uz dobry! :)}
 Redundant atoms and terms share a node representation \cite{}.
+\todo{MS: Ale mezitim se to tu zmenilo a ja prestavam chapat, co je ``Redundant''.}
 Note that since each variable is bound by a clause,
@@
 for correctly ranking the symbol in the observed symbol precedences.
-\todo{FB: What does "correct" mean?}
+\todo{FB: What does "correct" mean? MS: nic moc, ale v prvnim paragrafu sekce se to snad snese a zni to imho dobre:)
+Nebo mas lepsi napad? "successfully"?
+Napsat presne ale strucne, ze ty embeddingy jsou takove, aby siti pomohly mit co nejnizsi loss na proxy tasku 
+hadani dvojic otazek, bude o dost tezsi...}
 The symbol embeddings are output by a \gls{rgcn} \cite{Schlichtkrull2017},
@@
 and then repeatedly updates the embeddings by passing them through convolutional layers.
-\todo{FB: Ensure terms are clear (preferably defined): embedding, vector, trainable vector, feature vector.}
+\todo{MS: to se mi libi, ze to nekde zacina a nekam to smeruje.}
+\todo{FB: Ensure terms are clear (preferably defined): embedding, vector, trainable vector, feature vector.
+MS: (convolutional, layers, ...)}
 
@@
 using the module associated with the edge type $r$.
-In the simple case that the module is a dense layer with weights $W_r^{(l)}$,
+In the simple case that the module is a dense layer with weight matrix $W_r^{(l)}$,
 \todo{MS: hnidopich nevi, co to znamena ``dense layer''}
-the message is $h_s^{(l)} W_r^{(l)}$.
+the message is $h_s^{(l)} W_r^{(l)}$.\todo{MS: mas nejakou preferenci pro column/row vectors a z jake strany je prirozene nasobit?
+Ja bych mozna spis psal $W_r^{(l)} h_s^{(l)}$, a mozna s explicitnim  $W_r^{(l)} \cdot h_s^{(l)}$.}
 Each message is then divided by a normalization constant
@@
 No activation function is applied so that the output values can span the whole $\re$.
+\todo{MS: provided the input embeddings can...}
 
@@
 \todo{FB: Ensure the term is defined.}
-Our experiments showed no significant improvement when a hidden layer is added,
-arguably because the underlying \gls{gcn} learns a sufficiently complex transformation.
+Our experiments showed no significant improvement when a hidden layer was added,
+likely because the underlying \gls{gcn} learns a sufficiently complex transformation.
 
@@
 Let $\bar{\pi}$ be a precedence obtained from $\pi$ by swapping the elements $k$ and $l$.
+Then we obtain
 %$\bar{\pi} = (\pi(1), \ldots, \pi(k-1), \pi(l), \pi(k+1), \ldots, \pi(l-1), \pi(k), \pi(l+1), \ldots, \pi(n))$.
@@
 \end{align*}
-The final inequality is due to the assumption that $k-l < 0$ and
-$c(\pi(l)) - c(\pi(k)) > 0$.
+The final inequality is because $k-l < 0$ and $c(\pi(l)) - c(\pi(k)) > 0$.
 Thus, $C(\bar{\pi}) < C(\pi)$, which is contradicts the assumption that $\pi$ minimizes $C$. \qed
@@
 producing a precedence that minimizes the precedence cost is cheap
-because ranking is a fast operation.
-
-Note that the precedence that minimizes $C$
-orders the symbols with the lowest cost as the last,
-prioritizing them for early inferences.
-
-\todo[inline]{FB: Why is the equality predicate always the first in the precedence?}
+because ranking is a fast operation.\todo{MS: can we not say ``sorting''? Also slightly earlier.}
+
+Note that a precedence that minimizes $C$\todo{MS: Indefinite article; there can be more than one such...}
+orders the symbols with the lowest cost as the last, prioritizing them for early inferences.
+
+\todo[inline]{FB: Why is the equality predicate always the first in the precedence?
+MS: Andrei Voronokov reasons. It's typically better in practice to postpone equational reasoning,
+so we want equalities to be generally small.}
 \todo[inline]{FB: Mention that the common heuristics fit this scheme.}
@@
 ranking the symbols by their costs yields an optimum precedence,
+\todo{MS: hezky, to zacina dobre!}
 and all the information necessary to determine the optimum precedence is present in the graph representation of the input problem.
+\todo{MS: ``because the of the lossless property of the graph encoding mentioned before.''
+(Na druhou stranu nevime, jestli to dokaze zvladnout navrzena architectura.)}
+\todo{MS: Hlavne tady ale jakoby chybi druha pulky ty vety. Neco jako ``In practice, however, ...'' Nemyslis?} 
 Our approach to defining an appropriate symbol cost function is based on statistical learning
-from executions of an \gls{atp} on a set of problems with various precedences.
+from executions of an \gls{atp} on a set of problems with various\todo{MS: proc ne ``random''?} precedences.
 
@@
 and $\PrecBetter, \PrecWorse$ are precedences over $\Sigma$
-such that $\PrecBetter$ solves $P$ in fewer iterations of the saturation loop than $\PrecWorse$,
-denoted as $\Better{\PrecBetter}{\PrecWorse}$.
+such that the prover using $\PrecBetter$ solves $P$ in fewer iterations of the saturation loop than with $\PrecWorse$,
+denoted as $\Better{\PrecBetter}{\PrecWorse}$.\todo{MS: Could we have $\PrecBetter \prec_P\PrecWorse$?}
 \todo{Is this sufficient?}
@@
 \todo{Two levels of proxy metrics: 0-1 loss, differentiable loss (hinge, logistic)}
-
 To ensure that ranking the symbols by their costs
@@
 to satisfy the inequality $C(\PrecBetter) < C(\PrecWorse)$
-which can alternatively be expressed as $s(\PrecBetter, \PrecWorse) = C(\PrecBetter) - C(\PrecWorse) < 0$.
-We consider the value $s(\PrecBetter, \PrecWorse)$
-to be the score of the (ordered) precedence pair $(\PrecBetter, \PrecWorse)$.
+for as many training examples $(P, \PrecBetter, \PrecWorse)$ as possible.
+%
+This can alternatively be expressed as $s(\PrecBetter, \PrecWorse) := C(\PrecBetter) - C(\PrecWorse) < 0$,
+introducing a new quantity
+$s(\PrecBetter, \PrecWorse)$
+as the \emph{score} of the (ordered) precedence pair $(\PrecBetter, \PrecWorse)$.
 Given a set of examples of the form $(P, \PrecBetter, \PrecWorse)$
@@
 $\frac{1}{m} \sum_x \iverson{s(\PrecBetter, \PrecWorse) < 0}$.
+\todo{MS: Not sure if we can assume $\iverson{X}$ to be universally understandable.}
 % Alternative: We actually don't care about the relative order of non-minimum precedences.
 
-A common approach to training a binary classifier is to relax the non-differentiable accuracy $[s(\PrecBetter, \PrecWorse) < 0]$
+A common approach to training a binary classifier\todo{MS: First mention of a ``binary classifier''!
+We classify the examples, sure, but you did not say it yet.}
+is to relax the non-differentiable accuracy $\iverson{s(\PrecBetter, \PrecWorse) < 0}$
 to a differentiable proxy
@@
 $L = - \log \sigmoid s(\PrecBetter, \PrecWorse)$.
+\todo{MS: neni tu ted spatne zniminko? Nebo spis uz v definici score? Cekal bych, ze pro positivni examply (coz jsou u nas vsechny)
+bude chit $s$ kladne.}
 

### 2021-02-22 architecture.tex
Improve Loss function description

@@
 In theory, the symbol cost function can assign the costs so that
-ranking the symbols by their costs yields an optimum precedence,
+ranking the symbols by their costs yields an optimum precedence.
 \todo{MS: hezky, to zacina dobre!}
-and all the information necessary to determine the optimum precedence is present in the graph representation of the input problem.
+Furthermore, all the information necessary to determine the optimum precedence is present in the graph representation of the input problem.
 \todo{MS: ``because the of the lossless property of the graph encoding mentioned before.''
@@
 
+Our ultimate goal is to train the precedence cost function $C$ so that it is minimized by the best precedence,
+measuring the quality of a precedence by the number of iterations of the saturation loop taken to solve the problem.
+Since the number of possible precedences grows with the factorial of the signature size,
+it is not feasible to determine the best precedence conclusively on most practical problems.
+Instead of learning to classify one or more precedences on each problem as the best,
+we train the system to decide which of a pair of arbitrary precedences is better.
+We do this by training $C$ so that better precedences are assigned lower costs.
+The motivation for learning to order pairs of precedences
+is that it may allow the system to generalize to precedences that are better than any of those seen during training.
+\todo{FB: We should test this hypothesis by training on one problem in isolation.}
+\todo{FB: Argue better.}
+
 \subsubsection{Training data}
@@
 denoted as $\Better{\PrecBetter}{\PrecWorse}$.\todo{MS: Could we have $\PrecBetter \prec_P\PrecWorse$?}
-\todo{Is this sufficient?}
+\todo{FB: Is this sufficient?}
+\todo{FB: Describe the distribution of problems and precedences.}
 
@@
 
-\todo{Two levels of proxy metrics: 0-1 loss, differentiable loss (hinge, logistic)}
-To ensure that ranking the symbols by their costs
-yields a good precedence,
-we want the symbol cost function $c$
-to satisfy the inequality $C(\PrecBetter) < C(\PrecWorse)$
-for as many training examples $(P, \PrecBetter, \PrecWorse)$ as possible.
-%
-This can alternatively be expressed as $s(\PrecBetter, \PrecWorse) := C(\PrecBetter) - C(\PrecWorse) < 0$,
-introducing a new quantity
-$s(\PrecBetter, \PrecWorse)$
-as the \emph{score} of the (ordered) precedence pair $(\PrecBetter, \PrecWorse)$.
-Given a set of examples of the form $(P, \PrecBetter, \PrecWorse)$
-where $\Better{\PrecBetter}{\PrecWorse}$,
-our goal is to maximize the accuracy
-$\frac{1}{m} \sum_x \iverson{s(\PrecBetter, \PrecWorse) < 0}$.
-\todo{MS: Not sure if we can assume $\iverson{X}$ to be universally understandable.}
-% Alternative: We actually don't care about the relative order of non-minimum precedences.
-
-A common approach to training a binary classifier\todo{MS: First mention of a ``binary classifier''!
+Let $(P, \PrecBetter, \PrecWorse)$ be a training example ($\Better{\PrecBetter}{\PrecWorse}$).
+The precedence cost classifies this example correctly if $C(\PrecBetter) < C(\PrecWorse)$,
+or alternatively $C_2(\PrecBetter, \PrecWorse) = C(\PrecBetter) - C(\PrecWorse) < 0$.
+We approach this problem as an instance of binary classification with the logistic loss \cite{Mohri2018}:
+\todo{MS: First mention of a ``binary classifier''!
 We classify the examples, sure, but you did not say it yet.}
-is to relax the non-differentiable accuracy $\iverson{s(\PrecBetter, \PrecWorse) < 0}$
-to a differentiable proxy
-such as the logistic loss
-$L = - \log \sigmoid s(\PrecBetter, \PrecWorse)$.
+\begin{align*}
+L(P, \PrecBetter, \PrecWorse)
+&= - \log \sigmoid C_2(\PrecBetter, \PrecWorse)
+%&= - \log \sigmoid (C(\PrecBetter) - C(\PrecWorse)) \\
+%&= - \log \sigmoid \sum_{i=1}^n i (c(\PrecBetter(i)) - c(\PrecWorse(i)))
+\end{align*}
 \todo{MS: neni tu ted spatne zniminko? Nebo spis uz v definici score? Cekal bych, ze pro positivni examply (coz jsou u nas vsechny)
 bude chit $s$ kladne.}
+
+Note that the classifier cannot simply train $C_2$ to output a negative number on all pairs of precedences,
+because $C_2$ is a difference of two precedence costs.
+By training on the example $(P, \PrecBetter, \PrecWorse)$,
+we are effectively pushing $C(\PrecBetter)$ down and $C(\PrecWorse)$ up.
+
+Also note that it is possible to use a differentiable classification loss other than the logistic loss.
+\todo{FB: Consider leaving this detail out.}
+
+\subsubsection{Normalization}
+
+\todo[inline]{FB: "We normalize against various signature sizes and various numbers of examples per problem."}
 

### 2021-02-22 main.tex
docasne vypinam svg plot
Add a WIP content into Future work

@@
 
+Reinforcement learning will allow using a trained recommender to generate data from harder problems.
+
+In our experiments, too much attention is spent on uninteresting examples.
+We learn to order pairs of non-optimal precedences.
+However, if the recommender ordered a non-optimal pair wrong, it could still produce the optimum precedence correctly.
+Besides, we train from pairs of successful runs that only differ in number of iterations.
+
 \section*{Acknowledgments}
@@
 \centering
-\includesvg[width=\textwidth]{preprocessing}
+% \includesvg[width=\textwidth]{preprocessing}
 % Source: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit#gid=394425425&fvid=659935521

### 2021-02-22 architecture.tex
Mention problem P when comparing precedences

@@
 such that the prover using $\PrecBetter$ solves $P$ in fewer iterations of the saturation loop than with $\PrecWorse$,
-denoted as $\Better{\PrecBetter}{\PrecWorse}$.\todo{MS: Could we have $\PrecBetter \prec_P\PrecWorse$?}
+denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$.
 \todo{FB: Is this sufficient?}
@@
 
-Let $(P, \PrecBetter, \PrecWorse)$ be a training example ($\Better{\PrecBetter}{\PrecWorse}$).
+Let $(P, \PrecBetter, \PrecWorse)$ be a training example ($\Better{\PrecBetter}{\PrecWorse}{P}$).
 The precedence cost classifies this example correctly if $C(\PrecBetter) < C(\PrecWorse)$,
@@
 On pairs,
-$C(\pi)$ should be smaller than $C(\rho)$ iff $\Better{\pi}{\rho}$.
+$C(\pi)$ should be smaller than $C(\rho)$ iff $\Better{\pi}{\rho}{P}$.
 
@@
 Let $y = 1$ if $\PrecBetter$ is better than $\PrecWorse$,
-denoted as $\Better{\PrecBetter}{\PrecWorse}$,
+denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$,
 and $y = 0$ otherwise.
@@
 \todo{FB: Rephrase?}
-denoted as $\Better{\PrecBetter}{\PrecWorse}$.
+denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$.
 
@@
 we can be certain that $\PrecBetter$ is a better precedence for $P$ than $\PrecWorse$,
-denoted as $\Better{\PrecBetter}{\PrecWorse}$.
+denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$.
 
@@
 for a pair of precedences $\PrecBetter, \PrecWorse$,
-whether $\Better{\PrecBetter}{\PrecWorse}$.
-Since all the training examples are oriented so that $\Better{\PrecBetter}{\PrecWorse}$,
+whether $\Better{\PrecBetter}{\PrecWorse}{P}$.
+Since all the training examples are oriented so that $\Better{\PrecBetter}{\PrecWorse}{P}$,
 the classification target value for all the samples is $1$.
@@
 Let $\PrecBetter, \PrecWorse \in \Perm{n}$ be two symbol precedences over $P$.
-Let $\PrecBetter$ yield a faster proof search on $P$ than $\PrecWorse$, denoted as $\Better{\PrecBetter}{\PrecWorse}$.
+Let $\PrecBetter$ yield a faster proof search on $P$ than $\PrecWorse$, denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$.
 The precedence cost model can be extended to predict the probability that $\PrecBetter$ is better than $\PrecWorse$:
@@
 \begin{align*}
-p(\Better{\PrecBetter}{\PrecWorse} | P)
+p(\Better{\PrecBetter}{\PrecWorse}{P})
 &= \sigmoid \SquareBracket{C(\PrecWorse | P) - C(\PrecBetter | P)} \\
@@
 to be the "logit"\todo{MS: Logit je taky tezky pojem, urcite ne automaticky znamy u ATP people.} score of the pair of precedences $\PrecBetter, \PrecWorse$,
-and denote it by $C(\Better{\PrecBetter}{\PrecWorse} | P)$.
+and denote it by $C(\Better{\PrecBetter}{\PrecWorse}{P})$.
 
 We define the loss of $c$ on the training sample $(\PrecBetter, \PrecWorse, P)$ as binary cross-entropy
-with ground truth $\Better{\PrecBetter}{\PrecWorse}$:
+with ground truth $\Better{\PrecBetter}{\PrecWorse}{P}$:
 
@@
 L(\PrecBetter, \PrecWorse, P)
-&= - \log p(\Better{\PrecBetter}{\PrecWorse} | P) \\
+&= - \log p(\Better{\PrecBetter}{\PrecWorse}{P}) \\
 &= - \log \sigmoid \SquareBracket{k(n) \DotProd{c(P)}{\inv{\PrecWorse} - \inv{\PrecBetter}}} \\
@@
 \frac{\partial L}{\partial c_i}
-&= -\sigmoid(-C(\Better{\PrecBetter}{\PrecWorse} | P)) \cdot k(n) \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i) \\
-&= (p(\Better{\PrecBetter}{\PrecWorse} | P) - 1) \cdot k(n) \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)
+&= -\sigmoid(-C(\Better{\PrecBetter}{\PrecWorse}{P})) \cdot k(n) \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i) \\
+&= (p(\Better{\PrecBetter}{\PrecWorse}{P}) - 1) \cdot k(n) \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)
 \end{align*}

### 2021-02-22 evaluation.tex
Reference the GCN description from Evaluation
Mention problem P when comparing precedences

@@
 % Note that the second bit is redundant, since the clauses are annotated with their roles.
+This metadata is used to construct the initial embeddings of the respective nodes
+in the graph representation of the problem (see \cref{sec:gcn}).
+\todo{FB: Consider simplifying the paragraph by removing overlap with \cref{sec:gcn}.}
 
@@
 predicate precedence $\PrecBetter$ is recognized as better than predicate precedence $\PrecWorse$,
-denoted as $\Better{\PrecBetter}{\PrecWorse}$,
+denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$,
 if the proof search finishes successfully with $\PrecBetter$ ($\SolverRun{P}{\Prec} = \top$)

### 2021-02-22 architecture.tex
Resolve some of MS's notes in Architecture

@@
 The goal of the training is to find parameter values such that the recommender produces precedences
-that are likely to yield a successful proof in as few iterations of the saturation loop as possible.\todo{MS: mozna udernejsi?}
+that are likely to yield a successful proof in as few iterations of the saturation loop as possible.
 
@@
 \item An output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
-\todo{MS: ``output function \cite{Zhou2018}'' my nic nerika, mel bych to znat?}
+\todo{MS: ``output function \cite{Zhou2018}'' my nic nerika, mel bych to znat?\\
+FB: Zhou2018 je review GNNs. Output function je termin, ktery se tam pouziva. Ta citace je nejspis tady nepotrebna.}
 \item Ranking converts the symbol costs into a symbol precedence.
@@
 \Cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.
-\Cref{fig:GcnExample}\todo{MS: ten se mi libi!} shows an example of a graph representation of a simple problem.
+\Cref{fig:GcnExample} shows an example of a graph representation of a simple problem.
 
@@
 for correctly ranking the symbol in the observed symbol precedences.
-\todo{FB: What does "correct" mean? MS: nic moc, ale v prvnim paragrafu sekce se to snad snese a zni to imho dobre:)
-Nebo mas lepsi napad? "successfully"?
-Napsat presne ale strucne, ze ty embeddingy jsou takove, aby siti pomohly mit co nejnizsi loss na proxy tasku 
-hadani dvojic otazek, bude o dost tezsi...}
 The symbol embeddings are output by a \gls{rgcn} \cite{Schlichtkrull2017},
@@
 and then repeatedly updates the embeddings by passing them through convolutional layers.
-\todo{MS: to se mi libi, ze to nekde zacina a nekam to smeruje.}
 \todo{FB: Ensure terms are clear (preferably defined): embedding, vector, trainable vector, feature vector.
@@
 \todo{MS: hnidopich nevi, co to znamena ``dense layer''}
-the message is $h_s^{(l)} W_r^{(l)}$.\todo{MS: mas nejakou preferenci pro column/row vectors a z jake strany je prirozene nasobit?
-Ja bych mozna spis psal $W_r^{(l)} h_s^{(l)}$, a mozna s explicitnim  $W_r^{(l)} \cdot h_s^{(l)}$.}
+the message is $W_r^{(l)} h_s^{(l)}$.
+% Notation is from Kipf: RGCN paper.
 Each message is then divided by a normalization constant
@@
 h_d^{(l+1)} =
-\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (h_s^{(l)} W_r^{(l)} + b_r^{(l)})}
+\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (W_r^{(l)} h_s^{(l)} + b_r^{(l)})}
 $$
@@
 producing a precedence that minimizes the precedence cost is cheap
-because ranking is a fast operation.\todo{MS: can we not say ``sorting''? Also slightly earlier.}
-
-Note that a precedence that minimizes $C$\todo{MS: Indefinite article; there can be more than one such...}
+because ranking is a fast operation.\todo{MS: can we not say ``sorting''? Also slightly earlier.\\
+FB: This terminology is from the "Fast differentiable ranking" paper. Sorting rearranges the input vector. Ranking is argsort.}
+
+Note that a precedence that minimizes $C$
 orders the symbols with the lowest cost as the last, prioritizing them for early inferences.
@@
 ranking the symbols by their costs yields an optimum precedence.
-\todo{MS: hezky, to zacina dobre!}
-Furthermore, all the information necessary to determine the optimum precedence is present in the graph representation of the input problem.
-\todo{MS: ``because the of the lossless property of the graph encoding mentioned before.''
-(Na druhou stranu nevime, jestli to dokaze zvladnout navrzena architectura.)}
+Furthermore, all the information necessary to determine the optimum precedence is present in the graph representation of the input problem
+thanks to the lossless property of the graph encoding mentioned before.
 \todo{MS: Hlavne tady ale jakoby chybi druha pulky ty vety. Neco jako ``In practice, however, ...'' Nemyslis?} 
 Our approach to defining an appropriate symbol cost function is based on statistical learning
-from executions of an \gls{atp} on a set of problems with various\todo{MS: proc ne ``random''?} precedences.
+from executions of an \gls{atp} on a set of problems with random precedences.
 
@@
 The precedence cost classifies this example correctly if $C(\PrecBetter) < C(\PrecWorse)$,
-or alternatively $C_2(\PrecBetter, \PrecWorse) = C(\PrecBetter) - C(\PrecWorse) < 0$.
+or alternatively $C_2(\PrecBetter, \PrecWorse) = C(\PrecWorse) - C(\PrecBetter) > 0$.
+% We have positive C_2 score for correctly predicted examples.
+% The loss function transorms that into a loss value close to 0.
 We approach this problem as an instance of binary classification with the logistic loss \cite{Mohri2018}:
+% p. 128
 \todo{MS: First mention of a ``binary classifier''!
@@
 \end{align*}
-\todo{MS: neni tu ted spatne zniminko? Nebo spis uz v definici score? Cekal bych, ze pro positivni examply (coz jsou u nas vsechny)
-bude chit $s$ kladne.}
 

### 2021-02-22 abstract.tex
some a's in the abstract

@@
 The popular Knuth-Bendix simplification ordering is parameterized by 
-\emph{symbol precedence}---a permutation of the predicate and function symbols
+a \emph{symbol precedence}---a permutation of the predicate and function symbols
 of the input problem's signature.
-Thus, the choice of precedence has an indirect yet often substantial impact
-on the amount of work required to complete a proof search.
+Thus, the choice of a precedence has an indirect yet often substantial impact
+on the amount of work required to successfully complete a proof search.
 

### 2021-02-22 introduction.tex
literal selection

@@
+% !TEX root = main.tex
+
 % General motivation for FOL ATPing:
@@
 \glspl{atp} for \gls{fol}.
-Since the most popular \glspl{atp} use the superposition calculus with literal selection \cite{},
+Since the most popular \glspl{atp} use the superposition calculus with literal selection \cite{DBLP:journals/logcom/BachmairG94},
 the \gls{sot}, such as the \gls{kbo} \cite{Knuth1983},

### 2021-02-22 architecture.tex
Architecture: Disable typesetting the WIP sections
Add some todos
S > C_2

@@
 It is only used in generating mode.
+\todo{FB: Define ranking.}
 \item Loss function converts the symbol costs and a pair of precedences into a loss value.
@@
 
+\todo[inline]{FB: Define ranking and argsort.}
+
 We extend the notion of cost from symbols to precedences
@@
 The precedence cost classifies this example correctly if $C(\PrecBetter) < C(\PrecWorse)$,
-or alternatively $C_2(\PrecBetter, \PrecWorse) = C(\PrecWorse) - C(\PrecBetter) > 0$.
-% We have positive C_2 score for correctly predicted examples.
+or alternatively $S(\PrecBetter, \PrecWorse) = C(\PrecWorse) - C(\PrecBetter) > 0$.
+% We have positive S score for correctly predicted examples.
 % The loss function transorms that into a loss value close to 0.
@@
 L(P, \PrecBetter, \PrecWorse)
-&= - \log \sigmoid C_2(\PrecBetter, \PrecWorse)
+&= - \log \sigmoid S(\PrecBetter, \PrecWorse)
 %&= - \log \sigmoid (C(\PrecBetter) - C(\PrecWorse)) \\
@@
 
-Note that the classifier cannot simply train $C_2$ to output a negative number on all pairs of precedences,
-because $C_2$ is a difference of two precedence costs.
+Note that the classifier cannot simply train $S$ to output a negative number on all pairs of precedences,
+because $S$ is a difference of two precedence costs.
 By training on the example $(P, \PrecBetter, \PrecWorse)$,
@@
 \todo[inline]{FB: "We normalize against various signature sizes and various numbers of examples per problem."}
+
+\iffalse
 
@@
 A symbol precedence $\Prec \in \Perm{n}$ for problem $P$ is a permutation of the symbols of $P$.
-
-\newcommand{\Solver}{S}
-\newcommand{\SolverRun}[2]{\Solver(#1, #2)}
 
@@
 $$
+
+\fi

### 2021-02-22 architecture.tex
Use \ell for loss
to follow the convention set in Elements of Statistical Learning
(section 4.4.1).
Remove a resolved todo
Add normalization for commensurability across signature sizes

@@
 \todo{Describe problem again, this time precisely / technically.}
-\todo{Prove that minimizing precedence cost corresponds to sorting by symbol cost.}
 \todo{Advantage of using pairs of precedences: we need to solve classification rather than regression.}
@@
 $$
-C(\pi) = \sum_{i=1}^n c(\pi(i)) \cdot i
-$$
+C(\pi) = Z_n \sum_{i=1}^n i \cdot c(\pi(i))
+% We call the normalization factor Z_n to follow convention from Foundations of Machine Learning, p. 122.
+$$
+$Z_n = \frac{2}{n(n+1)}$ is a normalization factor
+that ensures the commensurability of precedence costs across signature sizes.
+More precisely, normalizing by $Z_n$ makes the expected value of precedence cost
+independent of the signature size $n$:
+\begin{align*}
+\mathbb{E}_\pi [C(\pi)]
+&= \mathbb{E}_\pi \SquareBracket{Z_n \sum_{i=1}^n i \cdot c(\pi(i))} \\
+&= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_{\pi, i} [c(\pi(i))] \\
+&= Z_n \Parentheses{\sum_{i=1}^n i} \mathbb{E}_i [c(i)] \\
+&= \frac{2}{n(n+1)} \frac{n(n+1)}{2} \mathbb{E}_i [c(i)] \\
+&= \mathbb{E}_i [c(i)]
+\end{align*}
 \todo{FB: Consider making the background problem explicit by using $C(\pi|P)$ or $C(\pi,P)$.}
@@
 \begin{align*}
-C(\bar{\pi}) - C(\pi)
+\frac{C(\bar{\pi}) - C(\pi)}{Z_n}
 &= kc(\bar{\pi}(k)) + lc(\bar{\pi}(l)) - kc(\pi(k)) - lc(\pi(l)) \\
@@
 \end{align*}
+\todo{FB: Isn't the inclusion of $Z_n$ too confusing?}
 The final inequality is because $k-l < 0$ and $c(\pi(l)) - c(\pi(k)) > 0$.
+Clearly, $Z_n > 0$ for any $n \geq 0$.
 Thus, $C(\bar{\pi}) < C(\pi)$, which is contradicts the assumption that $\pi$ minimizes $C$. \qed
@@
 \begin{align*}
-L(P, \PrecBetter, \PrecWorse)
+\loss(P, \PrecBetter, \PrecWorse)
 &= - \log \sigmoid S(\PrecBetter, \PrecWorse)

### 2021-02-22 architecture.tex
Update todos regarding LayerNorm and Residual
Forward-reference architecture subsections in the summary

@@
 each of which is described in detail in one of the following sections (see also \cref{fig:architecture}):
-\begin{enumerate}
-\item Graphifier converts the input \gls{cnf} problem into a problem graph.
-\item \Gls{gcn} converts a problem graph into symbol embeddings.
+\begin{itemize}
+\item \Cref{sec:graphifier}: Graphifier converts the input \gls{cnf} problem into a problem graph.
+\item \Cref{sec:gcn}: \Gls{gcn} converts a problem graph into symbol embeddings.
 \todo{MS: Kdyz embeddingy nebudou v preliminaries, je asi OK ctenare, ktery by o nich neslysel, zde trochu vydesit.
 Ale v te prislusne podsekci tim zas zacit.}
-\item An output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
+\item \Cref{sec:output}: An output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
 \todo{MS: ``output function \cite{Zhou2018}'' my nic nerika, mel bych to znat?\\
 FB: Zhou2018 je review GNNs. Output function je termin, ktery se tam pouziva. Ta citace je nejspis tady nepotrebna.}
-\item Ranking converts the symbol costs into a symbol precedence.
+\item \Cref{sec:ranking}: Ranking converts the symbol costs into a symbol precedence.
 It is only used in generating mode.
 \todo{FB: Define ranking.}
-\item Loss function converts the symbol costs and a pair of precedences into a loss value.
+\item \Cref{sec:training}: Loss function converts the symbol costs and a pair of precedences into a loss value.
 It is only used in training mode.
-\end{enumerate}
+\end{itemize}
 \todo{MS: tohle zatim chapu jako predbezny nastrel. Leda by uz pred tim bylo vysvetleno:
@@
 $$
+\todo{FB: Include LayerNorm and Residual if we end up using them.}
 %$$
@@
 
-\todo[inline]{Explain residual connections and layer normalization.}
 \todo[inline]{MS: neni uplne jiste, ze ``CADE people'' oceni presny zapis 
@@
 \subsection{Training}
+\label{sec:training}
 

### 2021-02-22 architecture.tex
Explain why we use logistic loss

@@
 % The loss function transorms that into a loss value close to 0.
-We approach this problem as an instance of binary classification with the logistic loss \cite{Mohri2018}:
+We approach this problem as an instance of binary classification with the logistic loss \cite{Mohri2018},
 % p. 128
-\todo{MS: First mention of a ``binary classifier''!
-We classify the examples, sure, but you did not say it yet.}
+a loss function routinely used in classification tasks in \acrlong{ml}:
+\todo[inline]{MS: First mention of a ``binary classifier''!
+We classify the examples, sure, but you did not say it yet.\\
+FB: Is it ok to mention binary classification for the first time here if we cite \cite{Mohri2018} immediately?}
 \begin{align*}

### 2021-02-22 architecture.tex
Clean up and finish Architecture

@@
 
-\iffalse
-
-\subsection{Learning to generate good permutations}
-
-Generating good symbol precedences is an instance of a more general task
-of generating permutations of arbitrary length.
-Each input problem corresponds to an input object that specifies the length of a permutation.
-
-Let $X$ be a set of objects.
-Let $l: O \to \nat$ assign each object $x \in X$ its signature length $l(x)$.
-Let $\{x_1, \ldots, x_n\}$ be the training samples.\todo{MS: je mi jasny, ze tu neni poradek, ale i tak; posledni dva odstavce jsou dost zmateny.}
-
-\subsubsection{Binary classification}
-
-Let $p_\theta : X \to \re$ be a binary classification model.\todo{MS: Dobry priklad na to, ktere pojmy je treba vysvetlovat.
-model je znamy pojem v logice, tady ale pouzivame jiny, ML vyznam.
-To by si zaslouzilo komentar.
-Navic pisem
-``binary'' a ``classification'' a neni tu jasny, co je ``binary''
-a co jsou ``classes''. Z pohledu ctenare, ktery o tom zatim neslysel, se misto ``binary classficiation model'' mohlo
-psat ``housenka'' a vyslo by to pro nej na stejno.}
-The model predicts the probability of label $1$.
-Let $(x_i, y_i)$ be the training samples,
-where $x_i \in X$ and $y_i \in Y = \{0, 1\}$.\todo{MS:
-``training'', ``sample'' a ``loss'' jsou dalsi priklady pojmu,
-ktere najednou spadly z hury.}
-
-For a training sample $(x, y) \in \re \times \{0, 1\}$, the binary cross-entropy loss is:
-$$
-L(\theta) = y \log{f_\theta(x)} + (1-y) \log{(1-f_\theta(x))}
-$$
-
-If $y_i = 1$ for all $i$, then the loss can be written in a simpler form:
-$$
-L(\theta) = \log{f_\theta(x)}
-$$
-
-\subsubsection{Permutations}
-
-Let $O$ be a set of objects (or contexts).
-Given an object $o \in O$, let $\Sigma(o)$ be its signature.
-Let $x_i = (o_i, \pi_i, \rho_i)$, where $o_i \in O$
-and $\pi_i, \rho_i \in \Perm(\Sigma(o_i))$.
-Let $y_i \in \{0, 1\}$.
-
-Let $p_\theta: X \to Y$.
-
-Loss:
-$$
-L(\theta) = \log{p_\theta(x)}
-$$
-
-Let $c_\theta(o, s)$ be the predicted cost of symbol $s$.
-Then:
-$$
-p_\theta(o, \pi, \rho) = C_\theta(o, \pi) - C_\theta(o, \rho)
-$$
-
-$$
-C_\theta(o, \pi) = \sum_{i=1}^{l(o)}{c(o, \pi_i)}
-$$
-
-\begin{align*}
-L(\theta) &= \log{p_\theta(o, \pi, \rho)} \\
-&= \log{(C_\theta(o, \pi) - C_\theta(o, \rho))} \\
-&= \log{(\sum_{i=1}^{l(o)}{c(o, \pi_i)} - \sum_{i=1}^{l(o)}{c(o, \rho_i)})} \\
-&= \log{\sum_{i=1}^{l(o)}{c(o, \pi_i) - c(o, \rho_i)}} \\
-\end{align*}
-
-If $c$ is differentiable,
-we can propagate loss gradients into it.
-
-\subsection{Notation}
-
-We denote the set of all finite vectors over $\re$ by $\re^* = \bigcup_{n=1}^\infty{\re^n}$.
-
-Dot product: $\DotProd{x}{y} = \sum_{i=1}^n x_i \cdot y_i$ for $x, y \in \re^n$.
-
-For any $n \in \nat$, we denote the set of all permutations over the set $\{1, \ldots, n\}$ by $\Perm{n}$.
-Permuting a vector $x = (x_1, \ldots, x_n) \in \re^n$ by a permutation $\pi = (\pi_1, \ldots, \pi_n) \in \Perm{n}$ yields the vector $\pi(x) = (x_{\pi_1}, \ldots, x_{\pi_n})$.
-$\inv{\pi}$ denotes the permutation inverse to $\pi$.
-$\inv{\pi} = ...$.
-\todo{Define permutation inversion.}
-\todo{MS: Mozna ani ne.
-Ono je obcas tezky zavest a pouzivat presnout matematickou notaci, ktera se navic muze stavat neprehlednou, kvuli te presnosti.
-Na druhou stranu, intuitivne, kazdy vi, co by to mela byt inverzni permutace.
-Takze nerikam psat nepresne veci, ale obcas jde
-zustak vagni s tim, ze vim, ze existuje zpusob jak to udelat presnym.
-A povrchni ctenar to nemusi resit a matematicky zdatny by si ten detail odvodil spravne ...}
-
-\fi
-
 \subsection{System overview}
@@
 and produces a precedence $\pi^*$ over the symbols $\Sigma$ as the output.
+For the recommender to be useful, it needs to produce a precedence
+that solves the input problem in a timely fashion.
+
+The recommender described in this section
+first computes a cost value for each symbol of the input problem,
+and then orders the symbols by their costs in a non-increasing order.
+In this manner, the task of finding good precedences is reduced to the task
+of finding a good symbol cost function.
+Note that the symbol precedence heuristics commonly used in the \glspl{atp}
+conform to this general scheme:
+they order the symbols by a numeric property, such as arity or number of occurrences.
 
@@
 }
+
+\iffalse
+
+\usetikzlibrary{shapes}
+\tikzstyle{object} = [rectangle, draw]
+\tikzstyle{input} = [ellipse, draw]
+\tikzstyle{output} = [ellipse, draw]
+
+\begin{tikzpicture}[node distance = 0.5 and 1, ->]
+% https://tex.stackexchange.com/a/332796/202639
+
+\node (problem) [input] {\gls{cnf} problem $P$};
+\node (symbol embeddings) [object] [below=of problem] {Symbol embeddings};
+\node (symbol costs) [object] [below=of symbol embeddings] {Symbol costs};
+\node (symbol precedence) [output] [below=of symbol costs] {Symbol precedence};
+
+\draw (problem) to node [left] {GCN} (symbol embeddings);
+\draw (symbol embeddings) to node [left] {MLP} (symbol costs);
+\draw (symbol costs) to node [left] {Order symbols by their costs} (symbol precedence);
+
+\node (PrecBetter) [input] [right=of problem] {Precedence $\PrecBetter$};
+\node (PrecBetterInv) [object] [below=of PrecBetter] {$\inv{\PrecBetter}$};
+\draw (PrecBetter) to node [right] {Invert} (PrecBetterInv);
+
+\node (PrecWorse) [input] [right=of PrecBetter] {Precedence $\PrecWorse$};
+\node (PrecWorseInv) [object] [below=of PrecWorse] {$\inv{\PrecWorse}$};
+\draw (PrecWorse) to node [right] {Invert} (PrecWorseInv);
+
+\node (PrecDiff) [object] [right=2 of symbol costs] {$\inv{\PrecWorse} - \inv{\PrecBetter}$};
+\node (PrecDiffNormalized) [object] [below=of PrecDiff] {Normalized};
+\node (PrecPairCost) [object] [below=of PrecDiffNormalized] {Precedence pair cost};
+\node (loss) [output] [below=of PrecPairCost] {Loss};
+
+\draw (PrecBetterInv) to (PrecDiff);
+\draw (PrecWorseInv) to (PrecDiff);
+\draw (PrecDiff) to node [right] {Normalize} (PrecDiffNormalized);
+\draw (PrecDiffNormalized) to (PrecPairCost);
+\draw (PrecPairCost) to (loss);
+
+\draw (symbol costs) to (PrecPairCost);
+
+\end{tikzpicture}
+
+\fi
+
 \end{figure}
+\todo{FB: Improve the diagram. Consider using tikz. See the disabled tikz figure in the source file.}
 
@@
 FB: Is it ok to mention binary classification for the first time here if we cite \cite{Mohri2018} immediately?}
+\todo[inline]{MS: [...] pisem
+``binary'' a ``classification'' a neni tu jasny, co je ``binary''
+a co jsou ``classes''. Z pohledu ctenare, ktery o tom zatim neslysel, se misto ``binary classficiation model'' mohlo
+psat ``housenka'' a vyslo by to pro nej na stejno.}
 \begin{align*}
 \loss(P, \PrecBetter, \PrecWorse)
-&= - \log \sigmoid S(\PrecBetter, \PrecWorse)
-%&= - \log \sigmoid (C(\PrecBetter) - C(\PrecWorse)) \\
-%&= - \log \sigmoid \sum_{i=1}^n i (c(\PrecBetter(i)) - c(\PrecWorse(i)))
+&= - \log \sigmoid S(\PrecBetter, \PrecWorse) \\
+&= - \log \sigmoid (C(\PrecWorse) - C(\PrecBetter)) \\
+&= - \log \sigmoid Z_n \sum_{i=1}^n i (c(\PrecWorse(i)) - c(\PrecBetter(i))) \\
+&= - \log \sigmoid Z_n \sum_{i=1}^n c(i) (\inv{\PrecWorse}(i) - \inv{\PrecBetter}(i))
 \end{align*}
 
-Note that the classifier cannot simply train $S$ to output a negative number on all pairs of precedences,
-because $S$ is a difference of two precedence costs.
-By training on the example $(P, \PrecBetter, \PrecWorse)$,
-we are effectively pushing $C(\PrecBetter)$ down and $C(\PrecWorse)$ up.
+Note that the classifier cannot simply train $S$ to output a positive number on all pairs of precedences
+because $S$ is defined as a difference of two precedence costs.
+Intuitively, by training on the example $(P, \PrecBetter, \PrecWorse)$
+we are pushing $C(\PrecBetter)$ down and $C(\PrecWorse)$ up.
 
-Also note that it is possible to use a differentiable classification loss other than the logistic loss.
-\todo{FB: Consider leaving this detail out.}
-
-\subsubsection{Normalization}
-
-\todo[inline]{FB: "We normalize against various signature sizes and various numbers of examples per problem."}
-
-\iffalse
-
-\subsection{Notes}
-
-We need to train $c$ in a way that ensures that $C$ is minimized by a good precedence.
-On pairs,
-$C(\pi)$ should be smaller than $C(\rho)$ iff $\Better{\pi}{\rho}{P}$.
-
-% What if we trained the binary classifier on vector:
-% C(\pi), C(\rho), C(\pi)^2, C(\rho)^2 (kernel trick?)
-
-Let $P = (\Sigma, \mathit{Cl})$ be a problem.
-Let $\PrecBetter, \PrecWorse$ be two precedences over $\Sigma$.
-% that are comparable according to AST.
-Let $y = 1$ if $\PrecBetter$ is better than $\PrecWorse$,
-denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$,
-and $y = 0$ otherwise.
-
-The examples that the recommender will be trained on have the form
-$(P, \PrecBetter, \PrecWorse)$, where $P = (\Sigma, \mathit{Cl})$ is a \gls{cnf} problem, and $\PrecBetter, \PrecWorse$ are precedences over $\Sigma$
-where $\PrecBetter$ yields a faster proof search than $\PrecWorse$,
-\todo{FB: Rephrase?}
-denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$.
-
-Given an example $x$,
-a binary classifier predicts the probability of event $1$,
-denoted as $p(x)$.
-The classifier is trained on samples of the form $(x, y)$,
-where $x$ is the observable state and $y \in \{0, 1\}$ is the target label.
-Logistic regression is a popular approach to train a binary classifier.
-Logistic regression is based on the logistic loss:
-$$
-L(x, y) = - y \log p(x) - (1-y) \log (1-p(x))
-$$
-
-% Hinge loss (y \in {-1, 1}):
-% L = max(0, 1 - ty)
-% t = 1: L = max(0, 1-y)
-
-% Binary crossentropy (y \in {0, 1}):
-% L = - y log p(1)) - (1-y) log p(0)
-% y = 1: L = - log p(1) = - log sigmoid c
-
-We train the system on results of \gls{atp} executions on problems with random precedences.
-Let $P = (\Sigma, \mathit{Cl})$ be a problem
-and let $\PrecBetter, \PrecWorse$ be two precedences over $\Sigma$.
-We run an \gls{atp} on $P$ with the two precedences.
-If the run with $\PrecBetter$ finds the proof successfully and uses less saturation loop iterations than the run with $\PrecWorse$,
-we can be certain that $\PrecBetter$ is a better precedence for $P$ than $\PrecWorse$,
-denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$.
-
-A binary classifier predicts the probability of complementary events $0$ and $1$,
-denoted as $p(0)$ and $p(1)$ respectively.
-The events are complementary,
-meaning $p(0) = 1 - p(1)$ and $p(0) + p(1) = 1$.
-
-A binary classifier with a binary crossentropy loss
-takes the predicted probability $p$ of events $0, 1$
-and computes the loss:
-$$
-L(y) = y log(p(1)) + (1-y) log(p(0))
-$$
-
-The examples that the recommender will be trained on have the form
-$(P, \PrecBetter, \PrecWorse)$, where $P = (\Sigma, \mathit{Cl})$ is a \gls{cnf} problem, and $\PrecBetter, \PrecWorse$ are precedences over $\Sigma$
-where $\PrecBetter$ yields a faster proof search than $\PrecWorse$,
-\todo{FB: Rephrase?}
-denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$.
-
-We train a binary classifier that decides,
-for a pair of precedences $\PrecBetter, \PrecWorse$,
-whether $\Better{\PrecBetter}{\PrecWorse}{P}$.
-Since all the training examples are oriented so that $\Better{\PrecBetter}{\PrecWorse}{P}$,
-the classification target value for all the samples is $1$.
-\todo{FB: Somebody might think that this is a problem because the classifier can simply learn to always say "1".
-The structure of the classifier ($C(x_1) - C(x_2)$) prevents that.
-Consider explaining.}
-Thus the binary crossentropy loss can be expressed as a simple expression:
-$$
-L(P, \PrecBetter, \PrecWorse) = - \log \sigmoid (C(\PrecWorse) - C(\PrecBetter))
-$$
-
-Derivation:
-$$
-L(P, \PrecBetter, \PrecWorse) = - \sum y \log p(y)
-$$
-
-$$
-p(0) = \sigmoid (C(\PrecBetter) - C(\PrecWorse)) \\
-p(1) = \sigmoid (C(\PrecWorse) - C(\PrecBetter))
-$$
-
-\todo{Mention normalization.}
-
-\subsection{[Alternative: Top-down approach]}
-
-The precedence generator, given a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$,
-generates a precedence over $\Sigma$
-that is expected to yield a successful proof search.
-
-The recommender first computes a cost value for each symbol of the input problem,
-and then orders the symbols by their costs in a non-increasing order.
-In this manner, the task of finding good precedences is reduced to the task
-of finding a good symbol cost function.
-We use a standard \gls{ml} terminology and denote
-the practical realization of the symbol cost function as \emph{symbol cost model}.
-
-Note that the symbol precedence heuristics commonly used in practice
-conform to this scheme:
-they order the symbols by a numeric property, such as arity or number of occurrences.
-\todo{MS: tohle se mi libi!}
-
-\subsection{Symbol cost model}
-
-The symbol cost model, given a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$,
-assigns each symbol in $s \in \Sigma$ a real value $c(s)$.
-It first uses a symbol embedding model to assign each symbol $s$ an embedding $E(s)$.
-The resulting symbol cost is a dot product of the symbol embedding with a trainable weight vector:
-
-$$
-c(s) = \DotProd{E(s)}{w} + b
-$$
-
-\subsection{Symbol embedding model}
-
-The symbol embedding model, given a problem,
-assigns each symbol $s \in \Sigma$ an embedding $E(s) \in \re^n$.
-Our implementation uses a \gls{rgcn} \cite{}.
-
-\todo[inline]{What is the structure of the graphs? What are the trainable parameters? Etc.}
-
-\subsection{Loss function}
-
-To train the symbol cost model,
-examples of the form $(P, \pi, \rho)$ are used.
-To be able to train the model by gradient descent,
-we need to define a loss function that is differentiable with respect to the model parameters,
-and that is minimized by a symbol cost model that produces good precedences.
-Optimizing the output precedence directly is not possible
-because the sorting operation is not differentiable
-and because we generally don't know the best precedence on a given problem.
-
-\todo[inline]{Idea for next project: Optimize precedence directly in a RL fashion: Generate precedence and evaluate with Vampire.
-If it is the best precedence seen so far, loss is 0 and gradient is 0.
-Otherwise ground truth is the best precedence seen so far on this problem and we use "differentiable ranking" to backpropagate.
-Possibly with some exploration, e.g.
-random swaps of pairs of symbols.}
-
-\subsection{Overview}
-
-Let $\cnf$ be the set of all \gls{cnf} problems.
-Let $P \in \cnf$ be an arbitrary problem.
-\todo{Consider using $F$ (as formula) instead of $P$ to free up P for probability.}
-Let $\signature{P}$ be the signature of $P$, that is a list of all non-logical symbols (predicates and functions)
-\todo{Should we rather use either predicates or functions? Or use a compound signature?}
-that appear in the problem.
-Let $n = \card{\signature{P}}$.
-A symbol precedence $\Prec \in \Perm{n}$ for problem $P$ is a permutation of the symbols of $P$.
-
-Let $\Solver$ be an \gls{atp} with a fixed computation environment, configuration and time limit.
-The computation of $\Solver$ is assumed to be parameterized by symbol precedence.
-\todo{Discuss. What does this mean?}
-$\SolverRun{P}{\Prec}$ denotes the result of a proof attempt on problem $P$ with symbol precedence $\Prec$.
-$\SolverRun{P}{\Prec} = \top$ if $S$ solves $P$ within the time limit, and $\SolverRun{P}{\Prec} = \bot$ otherwise.
-\todo{MS: vadi zminit pocet iteraci smycky tak, jako v minulem paperu?}
-Since the result is generally non-deterministic in case the time limit is specified in wall clock units,
-we consider $\SolverRun{P}{\Prec}$ to be a random variable with a Bernoulli distribution.
-\todo{Cite?}
-We denote the probability of a successful proof search $\Prob{\SolverRun{P}{\Prec} = \top}$.
-\todo{MS: asi bych se primlouval za to v teto fazi o Bernoullim pomlcet.
-Otazky jsme generovali tak, ze proste porovnavame pocty iteraci saturatcni smycky a pocitame s tim, ze beh je deterministicky.
-To, ze se pozdeji, pri evalu, pouzije perspektiva nahodnosti
-bych uz chapal jako metodiku experimentu a teorii tim nekomplikoval.}
-
-The main task this paper deals with is this:
-Given a problem $P \in \cnf$, generate a symbol precedence $\Prec \in \Perm{n}$ that maximizes $\Prob{\SolverRun{P}{\Prec} = \top}$.
-\todo[inline]{MS: (Nehlede na to, ze main task by nejspis mel byt vysvetlen mnohem drive...) Asi bych to takhle nestavel. Jak pisu vyse, precijen je
-beh dokazovace deterministicky a brat to nejak Bayesovsky by sice mohlo 
-byt zajimave, ale jeste mnohem tezsi na obhajeni jako ``svetonazor''.
-Co proste priznat nasledujici assumption:
-verime, ze pokud bude model spravne odpovidat na otazky $(P, \pi_1, \pi_2)$ (s pravdepodobnosti $> \SI{50}{\percent}$), povede podle nej vybrana permutace minimalizujici \eqref{eq:model_cost} k rychlemu vyreseni problemu (a tim i idealne k vyreseni problemu, ktere byly drive out of reach.)}
-\todo{MS: koukni prosim, jestli nejaky takovy mame. Tj zadna random permutace ho nevyresila, ale naucena sit pak ano!}
-
-Instead of modeling $\Prob{\SolverRun{P}{\Prec} = \top}$ directly,
-the system described in this paper predicts, given a problem $P$ and a pair of precedences $\PrecBetter, \PrecWorse \in \Perm{n}$,
-the probability
-\todo{MS: tohle je jeden z oficialnich zpusobu,
-jak vysvetlovat neuronky, ale neni nijak jasne do jake miry byva
-$\sigma(\mathit{logits})$ blizko nejake pravdepodobnosti. Za mne by klidne stacilo mluvit o tom, ze se snazime klasifikovat co nejvic dvojic
-spravne a ze na to pouzivame standard techologii neuronek (Binary Cross Entropy loss (against the final layer’s sigmoid non-linearity)). Tj opet hlasuji za to nemluvit zde o pravdepodobnosti. :)}
-\todo{MS: jo, ale pak bude nekde dobre zminit, ze jsme si vedomi, ze dvojice skoro jiste neobsahuji stejne mnozstvi ``signalu'', ze ktereho je mozne se ucit.
-Je to proste vlastnost vybrane metody a v prumeru to nevadi.}
-that $\PrecBetter$ outperforms $\PrecWorse$ in terms of success of proof search.
-This proxy task allows learning from pairs of precedences that both yield a successful proof search but differ in the number of steps taken in the proof search.
-\todo{Explain more.}
-
-% By taking the pairs, we get more data esp. from easy problems.
-% Consider weighting the samples by the result type: quantitative / qualitative etc.
-
-\begin{figure}[h]
-\caption{System overview}
-\label{fig:SystemOverview}
-\centering
-\usetikzlibrary{shapes}
-\tikzstyle{object} = [rectangle, draw]
-\tikzstyle{input} = [ellipse, draw]
-\tikzstyle{output} = [ellipse, draw]
-
-\begin{tikzpicture}[node distance = 0.5 and 1, ->]
-% https://tex.stackexchange.com/a/332796/202639
-
-\node (problem) [input] {\gls{cnf} problem $P$};
-\node (symbol embeddings) [object] [below=of problem] {Symbol embeddings};
-\node (symbol costs) [object] [below=of symbol embeddings] {Symbol costs};
-\node (symbol precedence) [output] [below=of symbol costs] {Symbol precedence};
-
-\draw (problem) to node [left] {GCN} (symbol embeddings);
-\draw (symbol embeddings) to node [left] {MLP} (symbol costs);
-\draw (symbol costs) to node [left] {Order symbols by their costs} (symbol precedence);
-
-\node (PrecBetter) [input] [right=of problem] {Precedence $\PrecBetter$};
-\node (PrecBetterInv) [object] [below=of PrecBetter] {$\inv{\PrecBetter}$};
-\draw (PrecBetter) to node [right] {Invert} (PrecBetterInv);
-
-\node (PrecWorse) [input] [right=of PrecBetter] {Precedence $\PrecWorse$};
-\node (PrecWorseInv) [object] [below=of PrecWorse] {$\inv{\PrecWorse}$};
-\draw (PrecWorse) to node [right] {Invert} (PrecWorseInv);
-
-\node (PrecDiff) [object] [right=2 of symbol costs] {$\inv{\PrecWorse} - \inv{\PrecBetter}$};
-\node (PrecDiffNormalized) [object] [below=of PrecDiff] {Normalized};
-\node (PrecPairCost) [object] [below=of PrecDiffNormalized] {Precedence pair cost};
-\node (loss) [output] [below=of PrecPairCost] {Loss};
-
-\draw (PrecBetterInv) to (PrecDiff);
-\draw (PrecWorseInv) to (PrecDiff);
-\draw (PrecDiff) to node [right] {Normalize} (PrecDiffNormalized);
-\draw (PrecDiffNormalized) to (PrecPairCost);
-\draw (PrecPairCost) to (loss);
-
-\draw (symbol costs) to (PrecPairCost);
-
-\end{tikzpicture}
-\end{figure}
-
-Fig.~\ref{fig:SystemOverview}
-\todo{MS: Na figures/tables bez referneci v textu se pohlizi obzvlast nelibe. Predpokladam, zes planoval pozdeji popsat, presto zmninuji. Konkretne k Fig.~\ref{fig:SystemOverview}:
-Napada me: neslo by precedenci definovat tak, aby uz byla tim $\pi^{-1}$? Invertovani zabira v obrazku skoustu mista, ale pritom
-jde o technicky detail a hlavni myslenku nijak neosvetluje...}
-
-\subsection{Symbol cost model}
-
-The symbol costs are modeled by a \gls{rgcn}.\cite{Schlichtkrull2017}
-\todo{Can I use the term \gls{rgcn} when I use a modified version? Namely, the activation is called earlier.}
-The model is a stack of graph convolutional layers.
-Each layer consists of one differentiable module for each edge type.
-Each module is a dense layer.
-$$
-h_i^{(l+1)} =
-\mathrm{LayerNorm} \Parentheses{h_i^{(l)} + \sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in \mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}}
-$$
-\todo{Include dropout?}
-% Inspiration: https://ufal.mff.cuni.cz/~straka/courses/npfl114/1920/slides.pdf/npfl114-07.pdf - slide 27 - Transformer
-\todo{FB: Mention inspiration: Transformer. See Straka's slides.}
-$h_i^{(l)}$ denotes the embedding of node $i$ at layer $l$.
-$\mathcal{R}$ denotes the set of all relations in the graph.
-$\sigma$ denotes the activation function, for example the \gls{relu}.
-$\mathcal{N}_i^r$ denotes the set of neighbors of node $i$ under relation $r$.
-$c_{j, i, r} = \sqrt{\card{\mathcal{N}_j^r}} \sqrt{\card{\mathcal{N}_i^r}}$ is a normalization constant.\cite{kipf2017semisupervised}
-$W_r^{(l)}$ is a trainable weight matrix representing relation $r$ at layer $l$.
-
-Residual...
-Layer norm...
-
-\todo{MS: neni uplne jiste, ze ``CADE people'' oceni presny zapis 
-strutury site, vcetne prvku jako $\mathrm{LayerNorm}$ ve vzorecku.
-Nerikam, ze bychom to meli uplne zatajit, ale popis, ktery je zde, spis
-patri do appendixu (ML paperu). Na te siti vlastne nic originalniho neni,
-tak neni treba vsechno vysvetlit do detailu. Zajimavejsi tu
-potom je az to, jak se problem $P$ ``otiskne'' v topologii grafu. 
-To uz originalni je (a soutezi to s representacemi jako ta Mirkova)
-a popisujes to pak dal.}
-
-\subsection{Loss function} 
-\label{sec:loss}
-
-Let $\cnf$ be the set of all \gls{cnf} problems.
-Let $P \in \cnf$ be an arbitrary problem.
-Let $\signature{P}$ be the signature of $P$.
-Let $n = \card{\signature{P}}$.
-
-Given a problem $P$, a symbol cost model 
-\todo{MS: Zvidavy invalida Jirka Karasek: a co ze je to ten model? 
-Mohl byste to to prosim nekde driv vysvetlit?}
-$c : \cnf \to \re^*$
-\todo{MS: Mozna by se dalo zbavit lehce podivneho $\re^*$ tim,
-ze model bude funkce $(P \in \cnf, s \in \Sigma_P) \to \re$?
-Zas pak nepujde pouzivat zapis skalarniho soucinu; hmmm.}
-returns a vector of costs of the symbols of $P$:
-$$
-c(P) = (c_1, \ldots, c_n)
-$$
-
-Let $\Prec \in \Perm{n}$ be a precedence of symbols of problem $P$.
-Let $k(n) = \frac{2}{n(n+1)}$ be a normalization factor for precedences of length $n$.
-The symbol cost model $c$ can be extended to a precedence cost model $C$
-by taking the weighted sum of symbol costs:
-\begin{equation} \label{eq:model_cost}
-C(\Prec | P)
-= k(n) \sum_{i=1}^n c_{\Prec_i} \cdot i
-= k(n) \sum_{i=1}^n c_i \cdot \inv{\Prec}_i
-= k(n) \DotProd{c(P)}{\inv{\Prec}}
-\end{equation}
-Note that the value of $C$ is minimized by a precedence that orders the symbols by their costs in non-increasing order.
-\todo{Discuss, prove.}
-\todo{Mention here that minimizing C yields the best precedence.}
-
-Fixing the normalization factor $k(n)$ to the value $\frac{2}{n(n+1)}$
-ensures that costs of precedences of various lengths are commensurable.
-Observe namely that if $c$ assigns each symbol the same cost $c_0$,
-then the precedence cost is equal to $c_0$ irrespective of the signature length $n$:
-$$
-C(\Prec | P) = \frac{2}{n(n+1)} \sum_{i=1}^n c_0 \cdot i = c_0
-$$
-
-Let $\PrecBetter, \PrecWorse \in \Perm{n}$ be two symbol precedences over $P$.
-Let $\PrecBetter$ yield a faster proof search on $P$ than $\PrecWorse$, denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$.
-The precedence cost model can be extended to predict the probability that $\PrecBetter$ is better than $\PrecWorse$:
-\todo{Fix this. Ensure the polarity is sound.}
-\todo{MS: zatim chybi vysvetleni $\sigmoid$.}
-\todo{MS: duvod proc mi v tomhle kontextu moc nesedi mluvit o pravdepodobnosti
-je ten, ze bez dalsiho vysvetlovani to vypada, ze si myslime, ze
-kdyz pomoci $\sigmoid$ splacnem v podstate libovolne hodnoty do
-intervalu $(0,1)$, zecne to automaticky fungovat jako pravdepodobnost.}
-\begin{align*}
-p(\Better{\PrecBetter}{\PrecWorse}{P})
-&= \sigmoid \SquareBracket{C(\PrecWorse | P) - C(\PrecBetter | P)} \\
-%&= \sigmoid \SquareBracket{k(n) \sum_{i=1}^n c_i \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)} \\
-&= \sigmoid \SquareBracket{k(n) \DotProd{c(P)}{\inv{\PrecWorse} - \inv{\PrecBetter}}}
-\end{align*}
-It is easy to see that $p(\Better{\PrecBetter}{\PrecWorse} | P) > 0.5$ if and only if $C(\PrecWorse | P) > C(\PrecBetter | P)$,
-and that the value of $p$ can be increased by increasing $C(\PrecWorse | P)$ or decreasing $C(\PrecBetter | P)$.
-
-We consider the difference $C(\PrecWorse | P) - C(\PrecBetter | P)$
-to be the "logit"\todo{MS: Logit je taky tezky pojem, urcite ne automaticky znamy u ATP people.} score of the pair of precedences $\PrecBetter, \PrecWorse$,
-and denote it by $C(\Better{\PrecBetter}{\PrecWorse}{P})$.
-
-We define the loss of $c$ on the training sample $(\PrecBetter, \PrecWorse, P)$ as binary cross-entropy
-with ground truth $\Better{\PrecBetter}{\PrecWorse}{P}$:
-
-\begin{align*}
-L(\PrecBetter, \PrecWorse, P)
-&= - \log p(\Better{\PrecBetter}{\PrecWorse}{P}) \\
-&= - \log \sigmoid \SquareBracket{k(n) \DotProd{c(P)}{\inv{\PrecWorse} - \inv{\PrecBetter}}} \\
-&= - \log \sigmoid \SquareBracket{k(n) \sum_{i=1}^n c_i \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)}
-\end{align*}
-
-The loss is differentiable with respect to the symbol costs:
-\begin{align*}
-\frac{\partial L}{\partial c_i}
-&= -\sigmoid(-C(\Better{\PrecBetter}{\PrecWorse}{P})) \cdot k(n) \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i) \\
-&= (p(\Better{\PrecBetter}{\PrecWorse}{P}) - 1) \cdot k(n) \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)
-\end{align*}
-
-This means that it is possible to backpropagate the loss gradient into the symbol cost model. \todo{MS: tohle bude tezky,
+The loss function is clearly differentiable with respect to the symbol costs,
+\todo{Shall we include the derivative?}
+and the symbol cost function $c$ is differentiable with respect to its trainable parameters.
+This enables the use of gradient descent to find the values of the parameters of $c$
+that minimize the loss value.
+\todo{MS: tohle bude tezky,
 ale ackoliv ML people by tohle uz asi chapali, ATP crowd spis bude
 potrebovat obsirnejsi vysvetleni.}
-
-\subsubsection{Generalization}
-
-Note that this approach is generally applicable to all problems where it is necessary to generate permutations of arbitrary length.
-
-\todo[inline]{Finish.}
-
-\subsection{Generating precedences}
-\label{sec:generating}
-
-When presented with a \gls{cnf} problem $P$ with signature $\symbols$,
-the recommender produces a precedence $\pi$ of symbols from $\symbols$.
-\todo{MS: proc nepouzivat znaceni z predchoziho clanku, kdy $P = (\symbols,\mathit{Cl})$?}
-In order to generate the precedence,
-the recommender first assigns a cost value to each symbol
-by invoking a symbol cost model (a trained \gls{gcn}) on a graph representation of $P$.
-Ordering the symbols by their predicted costs in nondecreasing order yields the precedence $\pi$.
-
-\subsection{Training}
-
-The training is performed using a fixed \acrlong{atp}.
-\todo{MS: zase spis preferuj cinny rod. A klidne muzes proste rict, ze pouzivame vampira :)}
-The configuration of the prover,
-including for example saturation algorithm, age-weight ratio, and term ordering scheme,
-is arbitrary\todo{MS: tohle slovo je prilis silny.
-Veta by spis mela vysvetlit, ze jsme si neco vybrali, protoze je nam to v postate jedno.
-Ale zaroven si uvedomujeme, ze to nejak ovlivni vysledek a ze v ultimatnim super-toolu, by se na vsech ostatni paramatrech dalo conditionovat.} and fixed.
-The prover needs to support refutational reasoning on \gls{cnf} problems
-and use a term simplification ordering parameterized by a symbol precedence.
-For example, the \glspl{atp} \vampire{} and E satisfy this requirement.
-Note that both of these provers support the \gls{kbo} and \gls{lpo} term simplification ordering schemes,
-and that each of these schemes is parameterized by a symbol precedence.
-\todo{MS: Jak jsme se o tom bavili; v ramvi Occamovky neni treba zminovat LPO.}
-
-As outlined in \cref{sec:generating},
-it is necessary to train a model of symbol costs.
-The model is a \gls{gcn}.
-
-\todo[inline]{Include a metagraph and an example graph of a problem.}
-\todo[inline]{Compare to HINs}
-% https://medium.com/@jason_trost/heterogeneous-information-networks-and-applications-to-cyber-security-23b245461adb
-
-Since it is not obvious what the target symbol cost values should be,
-the symbol cost model is not trained directly.
-Instead, it is plugged into a classifier that predicts,
-given a problem $P$ and a pair of precedences $\pi_0, \pi_1$,
-which of the two precedences yields a better performance on $P$.
-
-The symbol cost model is trained by plugging the model into a classifier
-that is trained to predict which of a pair of precedences
-yields a better performance on an arbitrary problem.
-
-\begin{figure}[ht]
-\caption{Architecture overview}
-\centering
-\digraph[scale=0.4]{precedencepairclassifierdetailed}{
-	graph [splines=ortho];
-	node [shape=renctangle, fontsize=20];
-	edge [fontsize=20];
-	fol [label="FOL problem", shape=oval];
-	pi0 [shape=oval, label=<&pi;<SUB>0</SUB>>];
-	pi1 [shape=oval, label=<&pi;<SUB>1</SUB>>];
-	invpi0 [label=<&pi;<SUB>0</SUB><SUP>-1</SUP>>];
-	invpi1 [label=<&pi;<SUB>1</SUB><SUP>-1</SUP>>];
-	cnf [label="Clause normal form (CNF)"];
-	symbolembeddings [label="Symbol embeddings"];
-	symbolcosts [label="Symbol costs"];
-	pi1pi0 [label="Inverse precedence difference"];
-	normalized [label="Normalized inverse precedence difference"];
-	paircost [label="Precedence pair cost"];
-	fol -> cnf [xlabel=" Vampire "];
-	cnf -> symbolembeddings [xlabel=< <B>Graph Convolution Network</B> >];
-	symbolembeddings -> symbolcosts [xlabel=< <B>Feed-forward neural network</B> >, style=bold];
-	symbolcosts -> paircost [style=bold];
-	paircost -> loss [xlabel=" Binary cross-entropy ", style=bold];
-	loss [label="Loss", shape=oval];
-	pi0 -> invpi0 [xlabel=" Invert "];
-	pi1 -> invpi1 [xlabel=" Invert "];
-	invpi0 -> pi1pi0;
-	invpi1 -> pi1pi0;
-	pi1pi0 -> normalized [xlabel=" Normalize "];
-	normalized -> paircost;
-	symbolprecedence [label="Symbol precedence", style=dashed];
-	symbolcosts -> symbolprecedence [xlabel=" Order symbols by their costs ", style=dashed];
-}
-\end{figure}
-
-\subsection{Layers}
-'
-\begin{enumerate}
-\item Problem -> symbol embeddings
-\item Symbol embedding -> symbol cost
-\item Symbol costs -> precedence cost
-\end{enumerate}
-
-\subsection{Cost models}
-
-%Let $\CostSym: \symbols \rightarrow \re$ be a differentiable symbol cost model.
-
-We define the precedence cost:
-$$
-\CostPrec(\pi) =
-C \sum_{1 \leq i \leq n} \CostSym(\pi(i)) \cdot i =
-C \sum_{1 \leq i \leq n} \CostSym(s_i) \cdot \inv{\pi}(s_i)
-$$
-Precedence cost is minimized by $\pi$ that orders the symbols by their costs in non-increasing order
-($\forall (1 \leq i < j \leq n) . (\CostSym(\pi(i)) \geq \CostSym(\pi(j)))$).
-
-Note that we can weight the symbols with an arbitrary nondecreasing function $f$ of symbol index:
-$$
-\CostPrec(\pi) =
-C \sum_{1 \leq i \leq n} \CostSym(\pi(i)) \cdot f(i) =
-C \sum_{1 \leq i \leq n} \CostSym(s_i) \cdot f(\inv{\pi}(s_i))
-$$
-
-We set $C = \frac{2}{n(n+1)}$ so that $\CostSym(s) = 1$ for all $s$ implies $\CostPrec(\pi) = 1$ for all $\pi$.
-
-% Note that we use this orientation because the TensorFlow metric BinaryCrossentropy classifies 0 as negative and we use the value 0 for "failed to classify" logits.
-Given a pair of precedences $\pi_0, \pi_1$,
-we define the log-odds of the event "$\pi_0$ is better than $\pi_1$":
-$$
-\CostPrecPair(\pi_0, \pi_1) =
-\CostPrec(\pi_1) - \CostPrec(\pi_0) =
-C \sum_{1 \leq i \leq n} \CostSym(s_i) \cdot [\inv{\pi_1}(s_i) - \inv{\pi_0}(s_i)]
-$$
-Clearly $\CostPrecPair(\pi_0, \pi_1) > 0$ iff $\CostPrec(\pi_0) < \CostPrec(\pi_1)$.
-For a pair of precedences about which we know that $\pi_0$ is better than $\pi_1$,
-we want $\CostPrecPair(\pi_0, \pi_1) > 0$.
-
-We model the probability of the event ``$\pi_0$ is better than $\pi_1$''
-by the sigmoid of $\CostPrecPair(\pi_0, \pi_1)$:
-$$
-p(\pi_0, \pi_1) = \sigmoid(\CostPrecPair(\pi_0, \pi_1))
-$$
-
-We use the binary cross-entropy loss to train the model.
-Given a pair of precedences such that $\pi_0$ is better than $\pi_1$,
-the loss is as follows:
-$$
-Loss(\pi_0, \pi_1) = -\log(\sigmoid(\CostPrecPair(\pi_0, \pi_1)))
-$$
-
-\fi

### 2021-02-22 main.tex
Add loss derivative into the appendix
Add some todos

@@
 
+\todo[inline]{Related problem: Ranking. See Mohri etc.}
+
 \section{Conclusion}
@@
 Besides, we train from pairs of successful runs that only differ in number of iterations.
+
+\todo[inline]{Idea for next project: Optimize precedence directly in a RL fashion: Generate precedence and evaluate with Vampire.
+If it is the best precedence seen so far, loss is 0 and gradient is 0.
+Otherwise ground truth is the best precedence seen so far on this problem and we use "differentiable ranking" to backpropagate.
+Possibly with some exploration, e.g.
+random swaps of pairs of symbols.}
 
@@
 
+\section{Loss derivative}
+
+The loss is differentiable with respect to the symbol costs:
+\begin{align*}
+\frac{\partial \loss}{\partial c_i}
+&= -\sigmoid(-C(\Better{\PrecBetter}{\PrecWorse}{P})) \cdot k(n) \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i) \\
+&= (p(\Better{\PrecBetter}{\PrecWorse}{P}) - 1) \cdot k(n) \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)
+\end{align*}
+
+This means that it is possible to backpropagate the loss gradient into the symbol cost model. \todo{MS: tohle bude tezky,
+ale ackoliv ML people by tohle uz asi chapali, ATP crowd spis bude
+potrebovat obsirnejsi vysvetleni.}
+
 \section{Experiment details}

### 2021-02-22 abstract.tex
prvni odstavec abstractu -> prvni ctyri v uvodu

@@
 on the amount of work required to successfully complete a proof search.
-
-\todo{MS: idea maybe to work out more in the introduction: 
-We could stress how the impact or the choice of a precedence is \emph{indirect}, 
-(as it's already obvious from the explanation here)
-all the more interesting one can learn from observing just this indirect impact 
-which precendences are good and which are bad!}
 

### 2021-02-22 introduction.tex
prvni odstavec abstractu -> prvni ctyri v uvodu

@@
 % State your thesis/claim
+
+Modern saturation-based Automatic Theorem Provers (ATPs) such as E \cite{SCV:CADE-2019}, SPASS \cite{DBLP:conf/cade/WeidenbachDFKSW09} 
+or {\sc Vampire}~\cite{DBLP:conf/cav/KovacsV13}
+employ the superposition calculus \cite{DBLP:journals/logcom/BachmairG94,DBLP:books/el/RV01/NieuwenhuisR01} as their underlying inference system.
+Integrating flavours of resolution \cite{DBLP:books/el/RV01/BachmairG01}, paramodulation \cite{Robinson1983}, and 
+the unfailing completion \cite{Bachmair89completionwithout}, superposition is a powerful calculus with 
+a native support for equational reasoning. The calculus is parametrized by a simplification ordering on terms % and literals,
+and uses it to constrain the applicability of inferences, with a significant impact on performance.
+
+Both of the two main classes of simplification orderings used in practice,
+the \acrlong*{kbo} \cite{Knuth1983}
+and the \acrlong*{lpo} \cite{Kamin1980},
+are specified with the help of a 
+\emph{symbol precedence}, an ordering on the signature symbols. %.\footnote{KBO is further parameterized by symbol weights.}
+% but our reference implementation in Vampire~\cite{DBLP:conf/cav/KovacsV13} 
+% uses for efficiency reasons only weights equal to one \cite{DBLP:conf/cade/KovacsMV11} and so we do not consider this parameter here.}
+While the superposition calculus is refutationally complete for any simplification ordering \cite{DBLP:journals/logcom/BachmairG94},
+the choice of the precedence has a significant impact on how long it takes to solve a given problem.
+
+Certain orderings help to make superposition a decision procedure on certain fragments of first-order logic 
+(see, e.g., \cite{DBLP:conf/lics/GanzingerN99,DBLP:conf/cade/HustadtKS05}).
+It is also well known that giving the highest precedence to the predicate symbols introduced as names 
+during the Tseitin transformation % of the input formula 
+\cite{Tseitin1983} can immediately make saturation produce the exponential 
+set of clauses that the transformation is designed to avoid \cite{Reger2016}.
+%
+However, the precise way by which the choice of a precedence 
+influences the follow-up proof search on a general problem is extremely hard to predict. % indirect
+
+% neslo by rict na tvrdo, ze je to takovy ten mytus o tom, ze se uzivatel zamysli a zvoli si tu skvelou precedenci pro svuj problem?
+
+Several general-purpose precedence generating schemes are available to ATP users,
+such as the successful \texttt{invfreq} scheme in E \cite{E-manual}, which orders the symbols 
+by the number of occurrences in the input problem. However, experiments with random precedences
+indicate that the existing schemes often fail to come close to the optimum precedence \cite{RegerSuda2017},
+suggesting room for further improvements.
+
+In this work,
+
+\newpage
+
+%\todo{MS: idea maybe to work out more in the introduction: 
+%We could stress how the impact or the choice of a precedence is \emph{indirect}, 
+%(as it's already obvious from the explanation here)
+%all the more interesting one can learn from observing just this indirect impact 
+%which precendences are good and which are bad!}
+
+% Two aspects: 
+% -selection of \emph{maximals} 
+% -rewriting from \emph{large to small}
+
+% CITE us: co tehdy, co ted!
 

### 2021-02-22 appendix.tex
Move the appendix content into a dedicated file

--- 2021-02-18 main.tex
@@
-\documentclass[runningheads]{llncs}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage[english]{babel}
-\usepackage[binary-units=true,detect-weight=true]{siunitx}
-
-% How to write a paper:
-% https://mj.ucw.cz/papers/jakpsat.pdf
-% Jones 2016: https://www.microsoft.com/en-us/research/academic-program/write-great-research-paper/
-% AWR: https://jazyky.fel.cvut.cz/vyuka/RPP/BE9M04AKP/
-
-% PAAR paper: https://github.com/filipbartek/learning-precedences-from-elementary-symbol-features/releases/download/paar2020%2Fceur-2/Learning_Precedences_from_Simple_Symbol_Features.pdf
-
-\input{preamble}
-\input{glossary}
-\input{front}
-
-\usepackage{svg}
-
-\usepackage[pdf]{graphviz}
-\usepackage{tikz}
-
-\usepackage{hyperref}
-\hypersetup{
-pdftitle={Neural Precedence Recommender},
-pdfauthor={Filip Bártek, Martin Suda},
-pdfkeywords={saturation-based theorem proving, simplification ordering, symbol precedence, machine learning, graph convolutional network}
-}
-
-\usepackage{cleveref}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-\input{abstract}
-\end{abstract}
-
-\section{Introduction}
-
-\input{introduction}
-
-\section{Preliminaries}
-
-\input{preliminaries}
-
-\section{Architecture}
-\label{sec:architecture}
-
-\input{architecture}
-
-\section{Experimental evaluation}
-\label{sec:evaluation}
-
-\input{evaluation}
-
-\section{Related work}
-
-MS: my sami (PAAR paper) jsem si related workem. Budem se vuci tomu muset vymezit.
-Jinak me ale nic moc bezprostredniho nenepada a nevim tedy, jestli se tedy primo
-nutit do sekce s timto nazvem!
-
-\section{Conclusion}
-
-\subsection{Future work}
-
-Generalization from trail acc to val acc may be improved.
-
-Highest val accuracy does not transfer to highest ATP success rate. Generalization to ATP is sub-par.
-
-Larger graphs
-
-Joint model (trained jointly on predicate and function precedences)
-
-Differentiate questions due to satiterations from questions due to success and failure
-
-MS: Is there a knowledge transfer possible between related setups when we in vampire change
-options (seemingly?) orthogonal to precedence (saturation algorithm, additional inference rules / reductions, AVATAR on/off,
-clause selection strategies, etc.)?
-
-KBO is a also parametrized by weights (along with the precedence). Could we learn those as well? (Jointly?)
-
-\section*{Acknowledgments}
-% > Acknowledgements should generally be placed in an unnumbered subsection at the end of the paper.
-
-% https://sgs.cvut.cz/index.php?action=faq
-% This work was supported by the Grant Agency of the Czech Technical University in Prague, grant No. SGS...
-
-\todo{MS: zvazit, jestli nerozepsat zvlast Martin, zvlast Filip.
-Pripadne se zeptat Hanky, jestli bychom nemeli nejak vypichnout
-jen GACR.}
-
-This work was supported by
-the Czech Science Foundation project 20-06390Y,
-the project RICAIP no. 857306 under the EU-H2020 programme,
-and
-the Grant Agency of the Czech Technical University in Prague, grant\\
-no.~SGS20/215/OHK3/3T/37.
-
-% > LaTeX users should avoid self-defined environments and use the bibliographic style MathPhySci for computer science proceedings.
-% > It is not possible to have hyperlinks in references.
-\bibliographystyle{splncs04}
-\bibliography{main}
-
-\appendix
-
 \section{Graph structure}
@@
 \end{figure}
-
-\end{document}

### 2021-02-22 main.tex
prvni odstavec abstractu -> prvni ctyri v uvodu
Re-enable the disabled content
Move the appendix content into a dedicated file

--- 2021-02-22 main.tex
@@
 \section{Preliminaries}
-
 \input{preliminaries}
@@
 \label{sec:architecture}
-
 \input{architecture}
@@
 \label{sec:evaluation}
-
 \input{evaluation}
@@
 nutit do sekce s timto nazvem!
+
+\todo[inline]{Related problem: Ranking. See Mohri etc.}
 
@@
 
+\todo[inline]{Idea for next project: Optimize precedence directly in a RL fashion: Generate precedence and evaluate with Vampire.
+If it is the best precedence seen so far, loss is 0 and gradient is 0.
+Otherwise ground truth is the best precedence seen so far on this problem and we use "differentiable ranking" to backpropagate.
+Possibly with some exploration, e.g.
+random swaps of pairs of symbols.}
+
 \section*{Acknowledgments}
@@
 \appendix
-
-\section{Graph structure}
-
-\begin{itemize}
-\item The graph representation of problem $P$ contains exactly one root node of type \ntype{problem}.
-\item Each clause is represented by a \ntype{clause} node connected to the root \ntype{problem} node.
-\item Each atom is represented by an \ntype{atom} node (in case the atom is not an equality)
-or an \ntype{equality} node (in case the atom is an equality).
-For each literal occurrence there is an edge connecting the respective atom to the respective clause.
-The type of the edge corresponds to the polarity of the literal:
-\epos{} for positive literal and \eneg{} for negative literal.
-\item Each \ntype{equality} node is connected to two nodes that represent the operands,
-each of which is of type \ntype{term} or \ntype{variable}.
-The commutativity of the equality operator is reflected by the fact that the operand edges are not ordered.
-\item Each \ntype{atom} node is connected to one \ntype{predicate} node that represents the predicate symbol being applied by this atom.
-Note that these edges connect the applications of a predicate symbol across the whole problem.
-\item Each \ntype{atom} node is connected to zero or more \ntype{argument} nodes that represent the argument positions of the atom.
-\item Each pair of \ntype{argument} nodes that correspond to consecutive argument positions is connected by an edge.
-\item Each \ntype{argument} node is connected to a node that represents the argument term,
-which is either a \ntype{term} node or a \ntype{variable} node.
-\item Each \ntype{term} node is connected to one \ntype{function} node that represents the function symbol being applied by this term.
-\item For each variable, there is an edge connecting the \ntype{clause} node of the clause that binds the variable to the \ntype{variable} node that represents the variable.
-\end{itemize}
-
-\section{Experiment details}
-
-\begin{figure}[h]
-\caption{The dependence of preprocessing time on the number of nodes in the problem graph on 1000 random validation problems}
-\label{fig:preprocessing}
-\centering
-% \includesvg[width=\textwidth]{preprocessing}
-% Source: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit#gid=394425425&fvid=659935521
-% Experiment: VML-715
-\end{figure}
+\input{appendix}
 

### 2021-02-22 architecture.tex
Add a note in source
Minor clarification
Reference formula roles

@@
 %We prefer to conform to the terminology common in literature studying \glspl{gnn}.}
-Each of the nodes is labeled with a node type,
+Each of the nodes of the graph is labeled with a node type,
 and each edge is labeled with an edge type,
@@
 Each clause node has a feature vector with a one-hot encoding of the role of the clause,
-which can be either axiom, assumption, or negated conjecture.
+which can be either axiom, assumption, or negated conjecture \cite{TptpSyntax,Sutcliffe2017}.
 Each symbol node has a feature vector with two bits of data:
@@
 \end{align*}
+% FB: Note: I have included the full expansion to make it visible how the loss depends on $c$.
+% To a skilled NN practitioner, it should now be obvious that the loss is differentiable w.r.t. $c$.
 

### 2021-02-22 architecture.tex
Clarify why we omit problem in notation of c

@@
 
-The symbol cost of each symbol is computed by passing the symbol's embedding through a dense layer with a single output unit.
-No activation function is applied so that the output values can span the whole $\re$.
-\todo{MS: provided the input embeddings can...}
+The symbol cost of each symbol is computed by passing the symbol's embedding through a fully-connected layer
+with a single output unit.
+No activation function is applied on the output values.
+\todo{FB: Explain why.}
 
-Note that it is possible to use a more complex projection module,
-e.g., a feed-forward network with one or more hidden layers.
-\todo{FB: Ensure the term is defined.}
+It is possible to use a more complex output layer,
+e.g., a feedforward network with one or more hidden layers.
 Our experiments showed no significant improvement when a hidden layer was added,
@@
 
-For input problem $P$
-with signature $\Sigma = (s_1, \ldots, s_n)$,
-we denote the cost of the $i$-th symbol as $c(i)$.
-\todo{FB: Consider using $c(s_i)$.}
-\todo{FB: Consider making the background problem explicit by using $c(i|P)$ or $C(i,P)$.}
+Let $\theta$ denote the vector of all the parameters of the \gls{gcn} and the output layer.
+Given an input problem $P$ with signature $\Sigma = (s_1, \ldots, s_n)$,
+we denote the cost of symbol $s_i$ as $c_{\theta,P}(i)$,
+or simply $c(i)$ in case the parameters $\theta$ and the problem $P$ are fixed in the context.
 

### 2021-02-23 preliminaries.tex
citace k neuronkam obecne?
Improve architecture overview
Write up preliminary description of NNs

--- 2021-02-18 preliminaries.tex
@@
 
-\subsection{Neural networks}
+\subsection{\Acrlongpl{nn}}
 
-A \emph{feed-forward neural network} is a directed acyclic graph
-of differentiable \emph{modules} that operate on numeric vectors.
-The common modules include multiplication by a matrix, and nonlinearity such as ReLU or sigmoid.
-Some of the modules are parameterized by trainable parameters or hyperparameters.
-In a typical usage, the neural network is trained by \emph{gradient descent}.
-In this setting, the trained network outputs a single numeric value called \emph{loss}.
-Since the network is differentiable,
-a gradient of the loss is computed with respect to all the trainable parameters of the network.
-The gradients are typically computed by \emph{backpropagation}.
-The values of the parameters are then updated by taking a small step in the direction that minimizes the loss.
+A \emph{feedforward \acrlong{ann}} \cite{DBLP:books/daglib/0040158} is a \acrlong{dag} of \emph{modules}.
+Each module is an operation that consumes a numeric (input) \emph{vector} and outputs a numeric vector.
+Each of the components of the output vector is called a \emph{unit} of the module.
+The output of each module is differentiable with respect to the input.
 
-\todo{Define sigmoid.}
-\todo{Maybe we don't need to make GCN a preliminary; we can define it later instead.}
-\todo[inline,author=FB]{GCN? Backprop?, gradient descent, loss, gradient, epoch}
+The common modules include
+the \emph{fully connected layer}, which performs an affine transformation,
+and non-linear \emph{activation functions} such as the \emph{\gls{relu}} or \emph{sigmoid}.\footnote{
+These are, respectively, $f(x) = \max\{0,x\}$ and $g(x) = \frac{1}{1+e^{-x}}$.}
+A fully connected layer with a single unit is called the \emph{linear unit}.
+
+Some of the modules are parameterized by numeric \emph{parameters}.
+For example, the fully connected layer that transforms the input $x$ by the affine transformation $Wx + b$
+is parameterized by the weight matrix $W$ and the bias vector $b$.
+If the output of a module is differentiable with respect to a parameter,
+that parameter is considered \emph{trainable}.
+
+In a typical use case, the \acrlong{nn} is trained by \emph{gradient descent} on a \emph{training set} of \emph{examples}.
+% Note: In case of GCN, the example is actually a set of edge matrices.
+In such setting, the network outputs a single numeric value called \emph{loss} when evaluated on a \emph{batch} of examples.
+The loss of a batch is typically computed as a weighted sum of the losses of the individual examples.
+Since each of the modules is differentiable with respect to its inputs and trainable parameters,
+the gradient of the loss in the trainable parameters
+\todo{FB: Is this terminology correct?}
+can be computed using the chain rule \cite{DBLP:books/daglib/0040158}.
+The trainable parameters are then updated by taking a small step
+against the gradient---in the direction that is expected to make the loss value smaller.
+An \emph{epoch} is a sequence of iterations that updates the trainable parameters
+using each example in the training set exactly once.

### 2021-02-23 architecture.tex
Update Architecture using the new NN terminology

@@
 or the relation between an atom and its predicate symbol.
+$\mathcal{R}$ denotes the set of all relations in the graph.
 \Cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.
@@
 \item Signature agnostic: Renaming the symbols and variables in the input problem yields an isomorphic graph.
-\item For each relation $r$, its inverse $\inv{r}$ is also present in the graph,
+\item For each relation $r \in \mathcal{R}$, its inverse $\inv{r}$ is also present in the graph,
 typically represented by a different edge type.
@@
 MS: O to my, neslo. Slo o to, jestli se sdily ground termy mezi klauzulemi, ted uz dobry! :)}
-Redundant atoms and terms share a node representation \cite{}.
+Redundant atoms and terms share a node representation.
+\todo{FB: Cite some text about sub-expression sharing. Perhaps Rawson2020?}
 \todo{MS: Ale mezitim se to tu zmenilo a ja prestavam chapat, co je ``Redundant''.}
@@
 
-For each symbol in the problem,
+For each symbol in the input problem $P$,
 we seek to find a vector representation, i.e., an \emph{embedding},
 that captures the symbol's properties that are relevant
-for correctly ranking the symbol in the observed symbol precedences.
+for correctly ranking the symbol in the symbol precedences over $P$.
+
 The symbol embeddings are output by a \gls{rgcn} \cite{Schlichtkrull2017},
-which is a stack of graph convolutional layers.
+which is a stack of \emph{graph convolutional layers}.
 Each layer consists of a collection of differentiable modules---one module per edge type.
 The computation of the \gls{gcn} starts with assigning each node an initial embedding
-and then repeatedly updates the embeddings by passing them through convolutional layers.
+and then iteratively updates the embeddings by passing them through the convolutional layers.
 \todo{FB: Ensure terms are clear (preferably defined): embedding, vector, trainable vector, feature vector.
@@
 
-The initial embedding is a concatenation of two vectors:
-a node feature vector (typically empty)
+The initial embedding $h_a^{(0)}$ of a node $a$ is a concatenation of two vectors:
+a \emph{feature vector} specific for that node (typically empty)
 and a trainable vector shared by all nodes of the same type.
@@
 using the module associated with the edge type $r$.
-In the simple case that the module is a dense layer with weight matrix $W_r^{(l)}$,
-\todo{MS: hnidopich nevi, co to znamena ``dense layer''}
-the message is $W_r^{(l)} h_s^{(l)}$.
+In the simple case that the module is a fully connected layer with weight matrix $W_r^{(l)}$ and bias vector $b_r^{(l)}$,
+the message is $W_r^{(l)} h_s^{(l)} + b_r^{(l)}$.
 % Notation is from Kipf: RGCN paper.
-Each message is then divided by a normalization constant
+Each message is then divided by the normalization constant
 $c_{s,d} = \sqrt{\card{\mathcal{N}_s^r}} \sqrt{\card{\mathcal{N}_d^r}}$ \cite{kipf2017semisupervised},
-where $\mathcal{N}_n^r$ is the set of neighbors of node $n$ under the relation $r$.
+where $\mathcal{N}_a^r$ is the set of neighbors of node $a$ under the relation $r$.
 \todo{FB: Mention that we mean both in- and out-neighbors?}
+
 Once all the messages are computed,
-they are aggregated by the destination nodes to form the new node embedding.
+they are aggregated at the destination nodes to form the new node embeddings.
 Each node $d$ aggregates all the incoming messages of a given edge type $r$ by summation,
@@
 yielding the new embedding $h_d^{(l+1)}$.
-The following formula captures the update of embedding of node $d$:
+
+The following formula captures the complete update of embedding of node $d$ by layer $l$:
 $$
@@
 \label{sec:output}
+% Terminology: Deep Learning Book
 
-The symbol cost of each symbol is computed by passing the symbol's embedding through a fully-connected layer
-with a single output unit.
-No activation function is applied on the output values.
-\todo{FB: Explain why.}
+The symbol cost of each symbol is computed by passing the symbol's embedding through a linear output unit,
+which is an affine transformation with no activation function.
+\todo{FB: Is this clear at this point?}
 
-It is possible to use a more complex output layer,
+It is possible to use a more complex output layer in place of the linear unit,
 e.g., a feedforward network with one or more hidden layers.
@@
 
-Let $\theta$ denote the vector of all the parameters of the \gls{gcn} and the output layer.
+Let $\theta$ denote the vector of all the parameters of the whole \acrlong{nn} consisting of the \gls{gcn} and the output unit.
 Given an input problem $P$ with signature $\Sigma = (s_1, \ldots, s_n)$,
-we denote the cost of symbol $s_i$ as $c_{\theta,P}(i)$,
-or simply $c(i)$ in case the parameters $\theta$ and the problem $P$ are fixed in the context.
+we denote the cost of symbol $s_i$ predicted by the \acrlong{nn} as $c(i, P; \theta)$.
+In the rest of this text,
+we refer to the predicted cost of $s_i$ simply as $c(i)$
+because the problem $P$ and the parameters $\theta$ are fixed in each respective context.
 
@@
 that minimize the loss value.
-\todo{MS: tohle bude tezky,
-ale ackoliv ML people by tohle uz asi chapali, ATP crowd spis bude
-potrebovat obsirnejsi vysvetleni.}

### 2021-02-23 abstract.tex
Typeset Vampire in small caps

@@
 the system does not presuppose the problems to be related or share a common signature. 
-When coupled with the theorem prover Vampire and evaluated on the \acrshort{tptp} problem library,
+When coupled with the theorem prover \Vampire{} and evaluated on the \acrshort{tptp} problem library,
 the recommender is found to outperform a state-of-the-art heuristic by more than \SI{4}{\percent}.

### 2021-02-23 evaluation.tex
Add a todo
Typeset Vampire in small caps

@@
 
-The empirical evaluation was performed using a modified version of the \gls{atp} Vampire 4.3.0 \cite{10.1007/978-3-642-39799-8_1}.
+The empirical evaluation was performed using a modified version of the \gls{atp} \Vampire{} 4.3.0 \cite{10.1007/978-3-642-39799-8_1}.
 The prover was used to generate the training data and to evaluate the trained precedence recommender.
 To generate the training data,
-Vampire was modified to output \gls{cnf} representations of the problems
+\Vampire{} was modified to output \gls{cnf} representations of the problems
 and annotated problem signatures in a machine-readable format.
@@
 For the evaluation of the precedences generated by the recommender,
-Vampire was modified to allow the user to supply explicit predicate and function symbol precedences for the proof search
+\Vampire{} was modified to allow the user to supply explicit predicate and function symbol precedences for the proof search
 (normally, the user only picks a precedence generation heuristic).
-\todo[inline]{FB: Add a link to the modified Vampire.}
+\todo[inline]{FB: Add a link to the modified \Vampire{}.}
 
@@
 
-Vampire was run with a time limit of 10 seconds.
+\Vampire{} was run with a time limit of 10 seconds.
 To increase the potential impact of predicate precedences,
@@
 % http://www.tptp.org/TPTP/SyntaxBNF.html
-\Gls{fof} problems are first converted into equisatisfiable \gls{cnf} problems by Vampire.
+\Gls{fof} problems are first converted into equisatisfiable \gls{cnf} problems by \Vampire{}.
 New symbols may be introduced during preprocessing,
@@
 A total of \num{17053} problems formulated in \gls{fof} and \gls{cnf} are sampled.
-The problems formulated in \gls{fof} are converted to \gls{cnf} by Vampire.
+The problems formulated in \gls{fof} are converted to \gls{cnf} by \Vampire{}.
 % vampire --mode clausify
@@
 The examples are generated by iterative sampling of $\ProblemsTptp$.
-In each iteration, a problem $P \in \ProblemsTptp$ is chosen and Vampire is executed twice on $P$
+In each iteration, a problem $P \in \ProblemsTptp$ is chosen and \Vampire{} is executed twice on $P$
 with two (uniformly) random predicate precedences and a common random function precedence.
@@
 and $\PrecWorse$ is the other precedence.
-Otherwise, for example, if Vampire fails on both precedences, we go back to sampling another problem.
+Otherwise, for example, if \Vampire{} fails on both precedences, we go back to sampling another problem.
+\todo{FB: Discuss: How come we mix examples in which both precedences terminate with examples in which only one precedence terminates?}
 
@@
 loss, accuracy and solver performance.
-The solver performance was estimated once per 10 training epochs by running Vampire
+The solver performance was estimated once per 10 training epochs by running \Vampire{}
 on \num{1000} problems of the respective problem set
@@
  of symbol precedences was generated by the respective trained recommender
-and Vampire was run using these precedences
+and \Vampire{} was run using these precedences
 with a wall clock time limit of 10 seconds.
@@
 The results are averaged over 5 runs to reduce the effect of noise due to the wall clock time limit.
-As a baseline, the performance of Vampire with the \texttt{frequency} precedence heuristic was evaluated
+As a baseline, the performance of \Vampire{} with the \texttt{frequency} precedence heuristic was evaluated
 with the same time limit.
@@
 and finally orders the symbols by their costs to produce the precedence.
-To simplify the experiment, the time limit is only imposed on the Vampire run
+To simplify the experiment, the time limit is only imposed on the \Vampire{} run
 and excludes the time taken by the recommender to generate the precedence.

### 2021-02-23 introduction.tex
Typeset Vampire in small caps

@@
 Modern saturation-based Automatic Theorem Provers (ATPs) such as E \cite{SCV:CADE-2019}, SPASS \cite{DBLP:conf/cade/WeidenbachDFKSW09} 
-or {\sc Vampire}~\cite{DBLP:conf/cav/KovacsV13}
+or \Vampire{} \cite{DBLP:conf/cav/KovacsV13}
 employ the superposition calculus \cite{DBLP:journals/logcom/BachmairG94,DBLP:books/el/RV01/NieuwenhuisR01} as their underlying inference system.
@@
 \emph{symbol precedence}, an ordering on the signature symbols. %.\footnote{KBO is further parameterized by symbol weights.}
-% but our reference implementation in Vampire~\cite{DBLP:conf/cav/KovacsV13} 
+% but our reference implementation in \Vampire{}~\cite{DBLP:conf/cav/KovacsV13} 
 % uses for efficiency reasons only weights equal to one \cite{DBLP:conf/cade/KovacsMV11} and so we do not consider this parameter here.}
@@
 This paper explores the possibility of tackling this task by training a neural network
-on the results of running the \gls{atp} Vampire \cite{10.1007/978-3-642-39799-8_1} with randomly sampled precedences.
+on the results of running the \gls{atp} \Vampire{} \cite{10.1007/978-3-642-39799-8_1} with randomly sampled precedences.
 \todo{Ensure that the first paragraph fits on the first page.}
@@
 
-Modern \gls{fol} \glspl{atp}, such as Vampire, E or SPASS,
+Modern \gls{fol} \glspl{atp}, such as \Vampire{}, E or SPASS,
 solve \gls{fol} problems by iteratively applying the inference rules of superposition calculus.
@@
 The state-of-the-art \gls{fol} \glspl{atp},
-such as \vampire{} \cite{10.1007/978-3-642-39799-8_1} and E \cite{10.1007/978-3-030-29436-6_29},
+such as \Vampire{} \cite{10.1007/978-3-642-39799-8_1} and E \cite{10.1007/978-3-030-29436-6_29},
 are saturation-based and
@@
 The performance of the state-of-the-art \acrfullpl{atp} is severely limited by some of the design decisions that constitute the provers' architecture.
-For example, the \frequency{} symbol precedence heuristic of the \acrfull{fol} \acrshort{atp} \vampire{} is easily outperformed by the best of 10 random precedences.\cite{}
+For example, the \frequency{} symbol precedence heuristic of the \acrfull{fol} \acrshort{atp} \Vampire{} is easily outperformed by the best of 10 random precedences.\cite{}
 The gap in performance suggests that a more elaborate precedence heuristic with a superior performance exists.

### 2021-02-23 preliminaries.tex
Typeset Vampire in small caps

@@
 is reduced to proving that the axioms together with the negated conjecture entail a \emph{contradiction}.
-The most popular \gls{fol} \glspl{atp}, such as Vampire \cite{10.1007/978-3-642-39799-8_1}, E \cite{10.1007/978-3-030-29436-6_29}, or SPASS \cite{DBLP:conf/cade/WeidenbachDFKSW09},
+The most popular \gls{fol} \glspl{atp}, such as \Vampire{} \cite{10.1007/978-3-642-39799-8_1}, E \cite{10.1007/978-3-030-29436-6_29}, or SPASS \cite{DBLP:conf/cade/WeidenbachDFKSW09},
 start the proof search by converting the input \gls{fol} formulas to an equisatisfiable representation in 
@@
 
-influences the proof search in Vampire on two levels.
+influences the proof search in \Vampire{} on two levels.
 First, the inferences on each clause are limited

### 2021-02-23 evaluation.tex
Correct specification of kernel version
Reduce whitespace around a todo
so that it does not interfere with typesetting with todos disabled.

@@
 \item OS: Ubuntu 20.04
-\item Kernel: GNU/Linux 5.4.0-40-generic x86\_64
+\item Kernel: 5.4.0-40-generic
 \end{itemize}
@@
 \subsubsection{Problem set}
-
-\todo{MS: mozna bych dal propagoval cinny rod a minuly cas ...}
-
+\todo[inline]{MS: mozna bych dal propagoval cinny rod a minuly cas ...}
 The examples are generated by sampling the \gls{fol} part of the problem library \gls{tptp} v7.4.0 \cite{10.1007/978-3-030-29436-6_29}.

### 2021-02-23 introduction.tex
Simplify description of a contribution

@@
 for a researcher trying to apply statistical learning to produce arbitrarily long permutations
-that optimize some non-differentiable quantitative criterion.
+that optimize a quantitative criterion.
 \todo{FB: Give examples of such tasks. How about constructive TSP?}

### 2021-02-23 architecture.tex
sort > rank

@@
 FB: Zhou2018 je review GNNs. Output function je termin, ktery se tam pouziva. Ta citace je nejspis tady nepotrebna.}
-\item \Cref{sec:ranking}: Ranking converts the symbol costs into a symbol precedence.
+\item \Cref{sec:ranking}: Sorting converts the symbol costs into a symbol precedence.
 It is only used in generating mode.
-\todo{FB: Define ranking.}
 \item \Cref{sec:training}: Loss function converts the symbol costs and a pair of precedences into a loss value.
@@
 
-\subsection{Ranking: From symbol costs to precedence}
+\subsection{Sorting: From symbol costs to precedence}
 \label{sec:ranking}
-
-\todo[inline]{FB: Define ranking and argsort.}
 
@@
 \begin{lemma}
-Precedence cost $C$ is minimized by the precedence that ranks the symbols by their costs in non-increasing order:
-% FB: The ranking terminology is from Fast Differentiable [...] Ranking.
+Precedence cost $C$ is minimized by the precedence that sorts the symbols by their costs in non-increasing order:
 $$
@@
 $$
+where $\argsort^-(x)$ is the set of all permutations $\rho$ that sort vector $x$ in non-increasing order ($x_{\rho(1)} \geq x_{\rho(2)} \geq \ldots \geq x_{\rho(n)}$).
 \end{lemma}
@@
 We prove the lemma by contradiction.
-Let $\pi$ minimize $C$ and let $\pi$ not rank the costs in non-increasing order.
+Let $\pi$ minimize $C$ and let $\pi$ not sort the costs in non-increasing order.
 Then there exist $k < l$ such that $c(\pi(k)) < c(\pi(l))$.
@@
 producing a precedence that minimizes the precedence cost is cheap
-because ranking is a fast operation.\todo{MS: can we not say ``sorting''? Also slightly earlier.\\
-FB: This terminology is from the "Fast differentiable ranking" paper. Sorting rearranges the input vector. Ranking is argsort.}
+because sorting is a fast operation.
 
@@
 In theory, the symbol cost function can assign the costs so that
-ranking the symbols by their costs yields an optimum precedence.
+sorting the symbols by their costs yields an optimum precedence.
 Furthermore, all the information necessary to determine the optimum precedence is present in the graph representation of the input problem

### 2021-02-23 architecture.tex
Divide Sorting into subsubsections

@@
 
+\subsubsection{Precedence cost}
 We extend the notion of cost from symbols to precedences
@@
 
+\subsubsection{Cost minimization by sorting}
 \begin{lemma}

### 2021-02-23 evaluation.tex
Remove some resolved todos

@@
 and excludes the time taken by the recommender to generate the precedence.
-\todo{MS: and if we don't, this would be the perfect place to summarize
-how long the just described procedure took on an average problem,
-or how it (roughly) scales with the graph/cnf/tptp\_file size.}
 When run with 2 threads,

### 2021-02-23 architecture.tex
Remove some resolved todos
Cosmetic change

@@
 
-\todo{Describe problem again, this time precisely / technically.}
 \todo{Advantage of using pairs of precedences: we need to solve classification rather than regression.}
@@
 that ensures the commensurability of precedence costs across signature sizes.
-More precisely, normalizing by $Z_n$ makes the expected value of precedence cost
+More precisely, normalizing by $Z_n$ makes the expected value of the precedence cost
 independent of the signature size $n$:
@@
 \end{align*}
-\todo{FB: Consider making the background problem explicit by using $C(\pi|P)$ or $C(\pi,P)$.}
 \todo[inline]{FB: Consider accessing elements $\pi$ as vector elements $\pi_i$ instead of $\pi(i)$.

### 2021-02-23 introduction.tex
uvod

@@
 
-Certain orderings help to make superposition a decision procedure on certain fragments of first-order logic 
-(see, e.g., \cite{DBLP:conf/lics/GanzingerN99,DBLP:conf/cade/HustadtKS05}).
-It is also well known that giving the highest precedence to the predicate symbols introduced as names 
+It is well known that giving the highest precedence to the predicate symbols introduced as names 
 during the Tseitin transformation % of the input formula 
@@
 set of clauses that the transformation is designed to avoid \cite{Reger2016}.
-%
+Also, certain orderings help to make superposition a decision procedure on certain fragments of first-order logic 
+(see, e.g., \cite{DBLP:conf/lics/GanzingerN99,DBLP:conf/cade/HustadtKS05}).
 However, the precise way by which the choice of a precedence 
@@
 
-In this work,
+In this work, we propose a machine learning system that learns to predict for an ATP
+whether one precedence is going to lead to a faster proof search on a given problem than another.
+Given a previously unseen problem, it can then be asked to recommend the best possible precedence for an ATP to run with.
+Relying only on the logical structure of the problems, % for the learning, 
+the system generalizes the knowledge about favourable precedences across problems with different signatures.
 
-\newpage
+Our recommender uses a graph convolutional neural network \cite{kipf2017semisupervised}
+to represent the problem structure. It learns from the ATP performance on selected problems
+and \emph{pairs of randomly sampled} precedences. This information is then used to train
+a \emph{symbol cost model}, which realizes the recommendation by simply sorting 
+the problem's symbols according the obtained costs.
+
+This work strictly improves on our previous experiments with linear regression models and simple hand-crafted symbol features \cite{DBLP:conf/cade/Bartek020}
+and is, to the best of our knowledge, a first method able to propose good symbol precedences automatically 
+using a non-linear transformation of the input problem structure.
+
+The rest of this paper is organized as follows. \ldots
+% explicit contributions (mixed with ``as follows'')?
+
+\todo{Asi bych znovu (po abstraktu) nerikal, kolik nam vyjde. Spis jen ze sekce ta a ta je to tom, ze se tam evaluu s vampirem na TPTP. }
+When coupled with the ATP Vampire and trained on problems from the TPTP library,
+the recommender improves on the state-of-the art general-purpose precedence generating scheme
+\texttt{invfreq} by more than \SI{4}{\percent}.
 
@@
 
-% CITE us: co tehdy, co ted!
+\iffalse
 
@@
 
-\iffalse % AWR draft
+% \iffalse % AWR draft
 

### 2021-02-23 main.tex
Comment out appendix
Add an idea for future work
uvod

@@
 
+Thorough analysis of the model: how does it work? how does it generalize?
+
+Besides tackling the particular task of generating symbol precedences,
+the approach described in \cref{sec:architecture} may be of a more general interest
+for a researcher trying to apply statistical learning to produce arbitrarily long permutations
+that optimize some non-differentiable quantitative criterion.
+\todo{FB: Give examples of such tasks. How about constructive TSP?}
+
 \section*{Acknowledgments}
@@
 
-\appendix
-\input{appendix}
+%\appendix
+%\input{appendix}
 

### 2021-02-23 preliminaries.tex
Finish preliminaries

@@
 
-The superposition calculus is of special interest
-because it is used in the most successful \gls{fol} \glspl{atp}.
+The \emph{superposition calculus} is of special interest
+because it is used in the most successful contemporary \gls{fol} \glspl{atp}.
+The inferences of superposition calculus are constrained by a \emph{\gls{sot}}.
 
-The inference rules of superposition calculus are constrained by a \gls{sot}.
-
-\todo[inline,author=FB]{Mention: Vampire, superposition calculus, inference rules (resolution, superposition), simplification ordering on terms, KBO, symbol precedence.
-How does the STO influence the rules?
-Mention transfinite KBO (lcm predicate), which is only relevant to literal selection.
-Cite Voronkov: transfinite KBO (see section Notes on implementation).
-We use TKBO to increase the impact of predicate precedence.
-Vampire sets all KBO weights to 1.}
-
-\subsubsection{\Gls{sot}}
-
-An ordering on terms is called a \emph{simplification ordering} if it satisfies the following conditions:
-
-...
-
-influences the proof search in \Vampire{} on two levels.
+The \gls{sot} influences the superposition calculus in two ways.
 First, the inferences on each clause are limited
@@
 
-\subsubsection{\Acrfull{kbo}}
-
-% Example: It seems that a classical example for KBO an orienting equations is group theory axioms.
-
-Recall the two views:
-\begin{enumerate}
-\item
-	One is the view of complete literal selections (we influence which literals are maximal)
-
-\item
-	The other is that of the term rewriting world
-
-\end{enumerate}
-(The full landscape also contains LPO).
-
-\subsubsection{Symbol precedences}
-
-\todo[inline,author=FB]{Define terminology.}
+The \emph{\acrfull{kbo}}, a commonly used simplification ordering scheme,
+is parameterized by symbol weights and a \emph{symbol precedence},
+a permutation of the non-logical symbols of the input problem.
+In this work we focus on finding a symbol precedence achieves a good performance when plugged into the \gls{kbo},
+leaving all the symbol weights at the default value 1 as set by the \gls{atp} \Vampire{}.
 

### 2021-02-23 evaluation.tex
Add a link to the scripts
Improve section with hyperparameters

@@
 and then compare the performance of several trained models to a number of baseline heuristics.
+
+The scripts that were used to generate the training data and to train and evaluate the recommender
+are available at the following URL:
+\url{https://github.com/filipbartek/vampire-ml/tree/6907ee35}
 
@@
 
-\subsection{Model}
+\subsection{Hyperparameters}
 
 We used a \gls{gcn} as described in \cref{sec:architecture}
-with depth 4, message size 16, ReLU activation function,
+with depth 4, message size 16, \gls{relu} activation function,
 residual connections and layer normalization.
+We tuned the hyperparameters by a small manual grid search.
 \todo[inline]{MS: zase pasivum.

### 2021-02-23 architecture.tex
Finalize the text for first submission

@@
 \end{figure}
+\todo{FB: Clean up the diagram.}
 
@@
 $$
-where $\argsort^-(x)$ is the set of all permutations $\rho$ that sort vector $x$ in non-increasing order ($x_{\rho(1)} \geq x_{\rho(2)} \geq \ldots \geq x_{\rho(n)}$).
+where $\argsort^-(x)$ is the set of permutations $\rho$ that sort vector $x$ in non-increasing order ($x_{\rho(1)} \geq x_{\rho(2)} \geq \ldots \geq x_{\rho(n)}$).
 \end{lemma}

### 2021-02-23 introduction.tex
Finalize the text for first submission

@@
 employ the superposition calculus \cite{DBLP:journals/logcom/BachmairG94,DBLP:books/el/RV01/NieuwenhuisR01} as their underlying inference system.
-Integrating flavours of resolution \cite{DBLP:books/el/RV01/BachmairG01}, paramodulation \cite{Robinson1983}, and 
+Integrating flavors of resolution \cite{DBLP:books/el/RV01/BachmairG01}, paramodulation \cite{Robinson1983}, and 
 the unfailing completion \cite{Bachmair89completionwithout}, superposition is a powerful calculus with 
-a native support for equational reasoning. The calculus is parametrized by a simplification ordering on terms % and literals,
+a native support for equational reasoning. The calculus is parameterized by a simplification ordering on terms % and literals,
 and uses it to constrain the applicability of inferences, with a significant impact on performance.
@@
 Relying only on the logical structure of the problems, % for the learning, 
-the system generalizes the knowledge about favourable precedences across problems with different signatures.
+the system generalizes the knowledge about favorable precedences across problems with different signatures.
 
@@
 to represent the problem structure. It learns from the ATP performance on selected problems
-and \emph{pairs of randomly sampled} precedences. This information is then used to train
+and pairs of randomly sampled precedences. This information is then used to train
 a \emph{symbol cost model}, which realizes the recommendation by simply sorting 
@@
 
-The rest of this paper is organized as follows. \ldots
-% explicit contributions (mixed with ``as follows'')?
-
-\todo{Asi bych znovu (po abstraktu) nerikal, kolik nam vyjde. Spis jen ze sekce ta a ta je to tom, ze se tam evaluu s vampirem na TPTP. }
-When coupled with the ATP Vampire and trained on problems from the TPTP library,
-the recommender improves on the state-of-the art general-purpose precedence generating scheme
-\texttt{invfreq} by more than \SI{4}{\percent}.
+The rest of this paper is organized as follows.
+\Cref{sec:preliminaries} exposes the basic terminology used throughout the remaining sections.
+\Cref{sec:architecture} proposes a structure of the precedence recommender that can be trained on pairs of symbol precedences.
+\Cref{sec:evaluation} summarizes and discusses experiments performed
+using an implementation of the precedence recommender.
+\Cref{sec:related} compares the system proposed in this work with notable related works.
+\Cref{sec:conclusion} concludes the investigation and outlines possible directions for future research.
 

### 2021-02-23 main.tex
Finalize the text for first submission

--- 2021-02-22 main.tex
@@
 \section{Preliminaries}
+\label{sec:preliminaries}
 \input{preliminaries}
@@
 \section{Related work}
+\label{sec:related}
 
-MS: my sami (PAAR paper) jsem si related workem. Budem se vuci tomu muset vymezit.
-Jinak me ale nic moc bezprostredniho nenepada a nevim tedy, jestli se tedy primo
-nutit do sekce s timto nazvem!
+Our previous text \cite{DBLP:conf/cade/Bartek020} marked the initial investigation of applying techniques of \gls{ml}
+to generating good symbol precedences.
+The neural recommender uses a \gls{gnn} to model symbol costs,
+while \cite{DBLP:conf/cade/Bartek020} used a linear combination of symbol features readily available in the \gls{atp} \Vampire{}.
+The \gls{gnn}-based approach yields more performant precedences at the cost of longer training and preprocessing time.
+
+\cite{Olsak2019} and \cite{Rawson2020} propose similar \gls{gnn} architectures to solve tasks on \gls{fol} problems.
+They use the \glspl{gnn} to solve classification tasks such as premise selection.
+While our system is trained on a proxy classification task,
+the main task it is evaluated against is generating useful precedences.
 
@@
 \section{Conclusion}
+\label{sec:conclusion}
+
+We have described a system that extracts useful symbol precedences from the graph representations of \gls{cnf} problems.
+Comparison against a conventional symbol precedence heuristic shows that using a \gls{gcn}
+to consider the whole structure of the input problem is beneficial.
+\todo{FB: Should we boast that the reduction of ranking to training of differentiable element scores is innovative?}
 
@@
 
-Generalization from trail acc to val acc may be improved.
+An analysis of the trained recommender could reveal new insights into how the symbol precedence influences the proof search,
+and how a symbol precedence should be chosen in the context of a problem so that it is likely to lead to an efficient proof search.
+This might lead to a design of a new precedence heuristic
+that focuses relies on aspects of input problems
+that have been overlooked so far in the context of generating symbol precedences.
 
-Highest val accuracy does not transfer to highest ATP success rate. Generalization to ATP is sub-par.
+While using the \gls{kbo} as our simplification ordering scheme of choice,
+we restricted ourselves to generating the symbol precedences,
+leaving the symbol weights fixed to the constant 1 (the default behavior of \Vampire{}).
+Learning to recommend the symbol weights in addition to the symbol precedences would be interesting.
+\todo{FB: Be more fancy in wording.}
 
-Larger graphs
+Training both the predicate and the function precedence using a single \gls{gcn} would yield a recommender
+that only needs one pass through a \gls{gcn} to generate both predicate and function precedences for a problem.
+Moreover, the model would have the possibility to exploit the properties of the function precedence
+when generating the predicate precedence, and vice versa.
+Finally, higher training data efficiency could be achieved by considering all pairs of measured executions on a problem
+in one training batch.
+\todo{FB: Confusing?}
 
-Joint model (trained jointly on predicate and function precedences)
+A more detailed analysis of the training process might yield insights into how the performance generalizes
+from the training set to the validation set
+and from proxy metrics, such as the loss and the accuracy, to the final solver performance.
+Ultimately, this might reveal modifications that make the training more efficient and the final recommender more performant.
 
-Differentiate questions due to satiterations from questions due to success and failure
+The training examples take the form of pairs of precedences,
+where one of the precedences is preferable over the other.
+In this work, the amount by which the quality of the precedences differs is ignored.
+Taking the exact or estimated numbers of saturation loop iterations into account
+might help the recommender to prioritize the more significant gains.
 
-MS: Is there a knowledge transfer possible between related setups when we in vampire change
-options (seemingly?) orthogonal to precedence (saturation algorithm, additional inference rules / reductions, AVATAR on/off,
-clause selection strategies, etc.)?
+Applying techniques of reinforcement learning to focus the training data on the cases that yield high performance gains
+could further improve the recommender performance.
 
-KBO is a also parametrized by weights (along with the precedence). Could we learn those as well? (Jointly?)
+We restricted our experiments to problems whose graph representation does not exceed \num{100000} nodes.
+Evaluating the recommender on larger problems would be an interesting test of generalization.
+Training on larger problems may be facilitated by employing a lossy graphification.
 
-Reinforcement learning will allow using a trained recommender to generate data from harder problems.
+We performed all experiments with a fixed \gls{atp} \Vampire{} and a fixed configuration
+we consider to be a reasonable baseline.
+Introducing other prover configurations (namely other \glspl{sot})
+or other provers could make the resulting recommender more robust
+and possibly help extract more general knowledge about the structure of good symbol precedences.
 
-In our experiments, too much attention is spent on uninteresting examples.
-We learn to order pairs of non-optimal precedences.
-However, if the recommender ordered a non-optimal pair wrong, it could still produce the optimum precedence correctly.
-Besides, we train from pairs of successful runs that only differ in number of iterations.
+Finally, the approach outlined in \cref{sec:architecture}
+could be adjusted to solve tasks on \gls{fol} formulas other than recommending symbol precedences,
+such as premise selection of given clause selection.
+On the other hand, we could try to solve other tasks that involve generating permutations of arbitrary length.
+\todo{FB: TSP? Probably not because it is too combinatorial.}
 
-\todo[inline]{Idea for next project: Optimize precedence directly in a RL fashion: Generate precedence and evaluate with Vampire.
-If it is the best precedence seen so far, loss is 0 and gradient is 0.
-Otherwise ground truth is the best precedence seen so far on this problem and we use "differentiable ranking" to backpropagate.
-Possibly with some exploration, e.g.
-random swaps of pairs of symbols.}
+%KBO is a also parametrized by weights (along with the precedence). Could we learn those as well? (Jointly?)
 

### 2021-02-23 architecture.tex
Shave off content by commenting out to reduce page count to 15

@@
 The recommender consists of modules that perform specific subtasks,
-each of which is described in detail in one of the following sections (see also \cref{fig:architecture}):
-\begin{itemize}
-\item \Cref{sec:graphifier}: Graphifier converts the input \gls{cnf} problem into a problem graph.
-\item \Cref{sec:gcn}: \Gls{gcn} converts a problem graph into symbol embeddings.
-\todo{MS: Kdyz embeddingy nebudou v preliminaries, je asi OK ctenare, ktery by o nich neslysel, zde trochu vydesit.
-Ale v te prislusne podsekci tim zas zacit.}
-\item \Cref{sec:output}: An output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
-\todo{MS: ``output function \cite{Zhou2018}'' my nic nerika, mel bych to znat?\\
-FB: Zhou2018 je review GNNs. Output function je termin, ktery se tam pouziva. Ta citace je nejspis tady nepotrebna.}
-\item \Cref{sec:ranking}: Sorting converts the symbol costs into a symbol precedence.
-It is only used in generating mode.
-\item \Cref{sec:training}: Loss function converts the symbol costs and a pair of precedences into a loss value.
-It is only used in training mode.
-\end{itemize}
-\todo{MS: tohle zatim chapu jako predbezny nastrel. Leda by uz pred tim bylo vysvetleno:
-embedding, \gls{gcn}/convolution layers, ... \\
-FB: Staci predestrit, ze detaily vysvetlim pozdeji? MS: asi jo :)}
+each of which is described in detail in one of the following sections.
+%\begin{itemize}
+%\item \Cref{sec:graphifier}: Graphifier converts the input \gls{cnf} problem into a problem graph.
+%\item \Cref{sec:gcn}: \Gls{gcn} converts a problem graph into symbol embeddings.
+%\todo{MS: Kdyz embeddingy nebudou v preliminaries, je asi OK ctenare, ktery by o nich neslysel, zde trochu vydesit.
+%Ale v te prislusne podsekci tim zas zacit.}
+%\item \Cref{sec:output}: An output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
+%\todo{MS: ``output function \cite{Zhou2018}'' my nic nerika, mel bych to znat?\\
+%FB: Zhou2018 je review GNNs. Output function je termin, ktery se tam pouziva. Ta citace je nejspis tady nepotrebna.}
+%\item \Cref{sec:ranking}: Sorting converts the symbol costs into a symbol precedence.
+%It is only used in generating mode.
+%\item \Cref{sec:training}: Loss function converts the symbol costs and a pair of precedences into a loss value.
+%It is only used in training mode.
+%\end{itemize}
+%\todo{MS: tohle zatim chapu jako predbezny nastrel. Leda by uz pred tim bylo vysvetleno:
+%embedding, \gls{gcn}/convolution layers, ... \\
+%FB: Staci predestrit, ze detaily vysvetlim pozdeji? MS: asi jo :)}
 
-\begin{figure}[h]
-\caption{Recommender architecture overview.
-When recommending a precedence, the input is problem $P$ and the output is precedence $\pi^*$.
-When training on an example, the input is problem $P$ and precedences $\pi$ and $\rho$,
-and the output is the loss value.}
-\label{fig:architecture}
-\centering
-\digraph[scale=0.4]{ArchitectureOverview}{
-graph [splines=ortho,ranksep=0.2];
-node [shape=box, fontsize=20];
-edge [fontsize=20];
-
-Problem [label="CNF problem P"];
-Graphifier [style=rounded, label="Graphifier"];
-g [label="Graph"];
-GCN [style=rounded, label="GCN"];
-SymbolEmbedding [label="Symbol embeddings"];
-SymbolCostModel [style=rounded, label="Projection"];
-SymbolCost [label="Symbol costs"];
-Sort [style=rounded, label="Sort"];
-Precedence [label=<Output precedence &pi;*>];
-
-Problem -> Graphifier -> g -> GCN -> SymbolEmbedding -> SymbolCostModel -> SymbolCost -> Sort -> Precedence;
-
-pi [label=<Precedence &pi;>];
-rho [label=<Precedence &rho;>];
-LossFunction [style=rounded, label="Loss function"];
-Loss [label="Loss value"];
-
-pi -> LossFunction;
-rho -> LossFunction;
-SymbolCost -> LossFunction;
-LossFunction -> Loss;
-}
-
-\iffalse
-
-\usetikzlibrary{shapes}
-\tikzstyle{object} = [rectangle, draw]
-\tikzstyle{input} = [ellipse, draw]
-\tikzstyle{output} = [ellipse, draw]
-
-\begin{tikzpicture}[node distance = 0.5 and 1, ->]
-% https://tex.stackexchange.com/a/332796/202639
-
-\node (problem) [input] {\gls{cnf} problem $P$};
-\node (symbol embeddings) [object] [below=of problem] {Symbol embeddings};
-\node (symbol costs) [object] [below=of symbol embeddings] {Symbol costs};
-\node (symbol precedence) [output] [below=of symbol costs] {Symbol precedence};
-
-\draw (problem) to node [left] {GCN} (symbol embeddings);
-\draw (symbol embeddings) to node [left] {MLP} (symbol costs);
-\draw (symbol costs) to node [left] {Order symbols by their costs} (symbol precedence);
-
-\node (PrecBetter) [input] [right=of problem] {Precedence $\PrecBetter$};
-\node (PrecBetterInv) [object] [below=of PrecBetter] {$\inv{\PrecBetter}$};
-\draw (PrecBetter) to node [right] {Invert} (PrecBetterInv);
-
-\node (PrecWorse) [input] [right=of PrecBetter] {Precedence $\PrecWorse$};
-\node (PrecWorseInv) [object] [below=of PrecWorse] {$\inv{\PrecWorse}$};
-\draw (PrecWorse) to node [right] {Invert} (PrecWorseInv);
-
-\node (PrecDiff) [object] [right=2 of symbol costs] {$\inv{\PrecWorse} - \inv{\PrecBetter}$};
-\node (PrecDiffNormalized) [object] [below=of PrecDiff] {Normalized};
-\node (PrecPairCost) [object] [below=of PrecDiffNormalized] {Precedence pair cost};
-\node (loss) [output] [below=of PrecPairCost] {Loss};
-
-\draw (PrecBetterInv) to (PrecDiff);
-\draw (PrecWorseInv) to (PrecDiff);
-\draw (PrecDiff) to node [right] {Normalize} (PrecDiffNormalized);
-\draw (PrecDiffNormalized) to (PrecPairCost);
-\draw (PrecPairCost) to (loss);
-
-\draw (symbol costs) to (PrecPairCost);
-
-\end{tikzpicture}
-
-\fi
-
-\end{figure}
-\todo{FB: Improve the diagram. Consider using tikz. See the disabled tikz figure in the source file.}
+%\begin{figure}[h]
+%\caption{Recommender architecture overview.
+%When recommending a precedence, the input is problem $P$ and the output is precedence $\pi^*$.
+%When training on an example, the input is problem $P$ and precedences $\pi$ and $\rho$,
+%and the output is the loss value.}
+%\label{fig:architecture}
+%\centering
+%\digraph[scale=0.4]{ArchitectureOverview}{
+%graph [splines=ortho,ranksep=0.2];
+%node [shape=box, fontsize=20];
+%edge [fontsize=20];
+%
+%Problem [label="CNF problem P"];
+%Graphifier [style=rounded, label="Graphifier"];
+%g [label="Graph"];
+%GCN [style=rounded, label="GCN"];
+%SymbolEmbedding [label="Symbol embeddings"];
+%SymbolCostModel [style=rounded, label="Projection"];
+%SymbolCost [label="Symbol costs"];
+%Sort [style=rounded, label="Sort"];
+%Precedence [label=<Output precedence &pi;*>];
+%
+%Problem -> Graphifier -> g -> GCN -> SymbolEmbedding -> SymbolCostModel -> SymbolCost -> Sort -> Precedence;
+%
+%pi [label=<Precedence &pi;>];
+%rho [label=<Precedence &rho;>];
+%LossFunction [style=rounded, label="Loss function"];
+%Loss [label="Loss value"];
+%
+%pi -> LossFunction;
+%rho -> LossFunction;
+%SymbolCost -> LossFunction;
+%LossFunction -> Loss;
+%}
+%
+%\iffalse
+%
+%\usetikzlibrary{shapes}
+%\tikzstyle{object} = [rectangle, draw]
+%\tikzstyle{input} = [ellipse, draw]
+%\tikzstyle{output} = [ellipse, draw]
+%
+%\begin{tikzpicture}[node distance = 0.5 and 1, ->]
+%% https://tex.stackexchange.com/a/332796/202639
+%
+%\node (problem) [input] {\gls{cnf} problem $P$};
+%\node (symbol embeddings) [object] [below=of problem] {Symbol embeddings};
+%\node (symbol costs) [object] [below=of symbol embeddings] {Symbol costs};
+%\node (symbol precedence) [output] [below=of symbol costs] {Symbol precedence};
+%
+%\draw (problem) to node [left] {GCN} (symbol embeddings);
+%\draw (symbol embeddings) to node [left] {MLP} (symbol costs);
+%\draw (symbol costs) to node [left] {Order symbols by their costs} (symbol precedence);
+%
+%\node (PrecBetter) [input] [right=of problem] {Precedence $\PrecBetter$};
+%\node (PrecBetterInv) [object] [below=of PrecBetter] {$\inv{\PrecBetter}$};
+%\draw (PrecBetter) to node [right] {Invert} (PrecBetterInv);
+%
+%\node (PrecWorse) [input] [right=of PrecBetter] {Precedence $\PrecWorse$};
+%\node (PrecWorseInv) [object] [below=of PrecWorse] {$\inv{\PrecWorse}$};
+%\draw (PrecWorse) to node [right] {Invert} (PrecWorseInv);
+%
+%\node (PrecDiff) [object] [right=2 of symbol costs] {$\inv{\PrecWorse} - \inv{\PrecBetter}$};
+%\node (PrecDiffNormalized) [object] [below=of PrecDiff] {Normalized};
+%\node (PrecPairCost) [object] [below=of PrecDiffNormalized] {Precedence pair cost};
+%\node (loss) [output] [below=of PrecPairCost] {Loss};
+%
+%\draw (PrecBetterInv) to (PrecDiff);
+%\draw (PrecWorseInv) to (PrecDiff);
+%\draw (PrecDiff) to node [right] {Normalize} (PrecDiffNormalized);
+%\draw (PrecDiffNormalized) to (PrecPairCost);
+%\draw (PrecPairCost) to (loss);
+%
+%\draw (symbol costs) to (PrecPairCost);
+%
+%\end{tikzpicture}
+%
+%\fi
+%
+%\end{figure}
+%\todo{FB: Improve the diagram. Consider using tikz. See the disabled tikz figure in the source file.}
 
@@
 $\mathcal{R}$ denotes the set of all relations in the graph.
-\Cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.
+%\Cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.
 \Cref{fig:GcnExample} shows an example of a graph representation of a simple problem.
@@
 
-\begin{figure}[h]
-\caption{CNF network schema}
-\label{fig:CnfSchema}
-\centering
-\tikzstyle{token} = [rectangle, draw]
-
-\begin{tikzpicture}[node distance = 1 and 2, ->]
-% https://tex.stackexchange.com/a/332796/202639
-
-% Node and edge types:
-% https://docs.google.com/spreadsheets/d/1PCPHEgk6vLxpdpcvB_PGoLx7p4DID6WtvVWy2mDuv4A/edit?usp=sharing
-
-\node (formula) [token] {\ntype{problem}};
-% TODO: Consider removing the Formula nodes.
-\node (clause) [token, below=of formula] {\ntype{clause}};
-\node (atom) [token, below left=of clause] {\ntype{atom}};
-\node (equality) [token, below right=of clause] {\ntype{equality}};
-\node (predicate) [token, left=of atom] {\ntype{predicate}};
-\node (argument) [token, below=of atom] {\ntype{argument}};
-\node (term) [token, below=of argument] {\ntype{term}};
-\node (function) [token, left=of term] {\ntype{function}};
-\node (variable) [token, right=of term] {\ntype{variable}};
-
-\draw (formula) to node [right] {\etype{contains}} (clause);
-\draw (clause) to [bend right] node [above] {\epos{}} (atom);
-\draw (clause) to [bend left] node [below] {\eneg{}} (atom);
-\draw (clause) to [bend left] node [above] {\epos{}} (equality);
-\draw (clause) to [bend right] node [below] {\eneg{}} (equality);
-\draw (clause) to node [above] {\etype{binds}} (variable);
-\draw (atom) to node [above] {\etype{atom\_applies}} (predicate);
-\draw (atom) to node [left] {\etype{atom\_has}} (argument);
-\draw (equality) to node {\etype{equalizes}} (term);
-\draw (equality) to node {\etype{equalizes}} (variable);
-\draw (argument) to [bend right] node [left] {\etype{is}} (term);
-\draw (argument) to [loop left] node [left] {\etype{precedes}} (argument);
-\draw (argument) to node [below] {\etype{is}} (variable);
-\draw (term) to node [above] {\etype{term\_applies}} (function);
-\draw (term) to [bend right] node [right] {\etype{term\_has}} (argument);
-
-\end{tikzpicture}
-\end{figure}
-\todo{FB: Clean up the diagram.}
+%\begin{figure}[h]
+%\caption{CNF network schema}
+%\label{fig:CnfSchema}
+%\centering
+%\tikzstyle{token} = [rectangle, draw]
+%
+%\begin{tikzpicture}[node distance = 1 and 2, ->]
+%% https://tex.stackexchange.com/a/332796/202639
+%
+%% Node and edge types:
+%% https://docs.google.com/spreadsheets/d/1PCPHEgk6vLxpdpcvB_PGoLx7p4DID6WtvVWy2mDuv4A/edit?usp=sharing
+%
+%\node (formula) [token] {\ntype{problem}};
+%% TODO: Consider removing the Formula nodes.
+%\node (clause) [token, below=of formula] {\ntype{clause}};
+%\node (atom) [token, below left=of clause] {\ntype{atom}};
+%\node (equality) [token, below right=of clause] {\ntype{equality}};
+%\node (predicate) [token, left=of atom] {\ntype{predicate}};
+%\node (argument) [token, below=of atom] {\ntype{argument}};
+%\node (term) [token, below=of argument] {\ntype{term}};
+%\node (function) [token, left=of term] {\ntype{function}};
+%\node (variable) [token, right=of term] {\ntype{variable}};
+%
+%\draw (formula) to node [right] {\etype{contains}} (clause);
+%\draw (clause) to [bend right] node [above] {\epos{}} (atom);
+%\draw (clause) to [bend left] node [below] {\eneg{}} (atom);
+%\draw (clause) to [bend left] node [above] {\epos{}} (equality);
+%\draw (clause) to [bend right] node [below] {\eneg{}} (equality);
+%\draw (clause) to node [above] {\etype{binds}} (variable);
+%\draw (atom) to node [above] {\etype{atom\_applies}} (predicate);
+%\draw (atom) to node [left] {\etype{atom\_has}} (argument);
+%\draw (equality) to node {\etype{equalizes}} (term);
+%\draw (equality) to node {\etype{equalizes}} (variable);
+%\draw (argument) to [bend right] node [left] {\etype{is}} (term);
+%\draw (argument) to [loop left] node [left] {\etype{precedes}} (argument);
+%\draw (argument) to node [below] {\etype{is}} (variable);
+%\draw (term) to node [above] {\etype{term\_applies}} (function);
+%\draw (term) to [bend right] node [right] {\etype{term\_has}} (argument);
+%
+%\end{tikzpicture}
+%\end{figure}
+%\todo{FB: Clean up the diagram.}
 

### 2021-02-23 evaluation.tex
Add a todo
Shave off content by commenting out to reduce page count to 15

@@
 \url{https://github.com/filipbartek/vampire-ml/tree/6907ee35}
+\todo{FB: Tag the version and link to the tag.}
+\todo{FB: Add some wrapper scripts and readme for ease of use.}
 
@@
 (normally, the user only picks a precedence generation heuristic).
-\todo[inline]{FB: Add a link to the modified \Vampire{}.}
+The modified version of \Vampire{} is available at the following URL:
+\url{https://github.com/filipbartek/vampire/tree/3bbfa9e6}
 
@@
 that compares atoms according to the predicate precedence first,
-Using the ordinary \gls{kbo} as a tie-breaker.
-Ordinary \gls{kbo} was used to compare terms.
+using the regular \gls{kbo} to break ties between atoms
+and to compare terms.
 \todo[inline,author=FB]{Describe the detailed configuration in an appendix and reference the appendix here.}
@@
 % http://www.tptp.org/TPTP/SyntaxBNF.html
+\todo{FB: Mention TPTP version. Consider joining with section Problem set below.}
 \Gls{fof} problems are first converted into equisatisfiable \gls{cnf} problems by \Vampire{}.
@@
 we performed a final evaluation of the most promising intermediate trained model on the whole $\ProblemsVal$.
-The model that manifested the best estimated solver performance was chosen as the most promising.
-\todo{Watch out: This way we may overfit on the 1000 problems used for sample solver performance evaluation.}
+The model that manifested the best estimated solver performance on a sample of \num{1000} validation problems
+was chosen as the most promising.
+\todo{FB: Watch out: This way we may overfit on the 1000 problems used for sample solver performance evaluation. We should leave out these 1000 problems from the final evaluation.}
 \todo{MS: taky me to ted napadlo! Uplne oficialni metodika byva split na train,valid,test. 
@@
 and finally orders the symbols by their costs to produce the precedence.
-To simplify the experiment, the time limit is only imposed on the \Vampire{} run
+To simplify the experiment, the time limit of 10 seconds is only imposed on the \Vampire{} run
 and excludes the time taken by the recommender to generate the precedence.
@@
 for \SI{80}{\percent} of the problems
-according to data measured on a random sample of \num{1000} problems.
+by extrapolation from a sample of \num{1000} problems.
 % Analysis: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit?usp=sharing
@@
 \caption{
-Results of the evaluation of various predicate precedence heuristics on $\ProblemsVal$
-($\card{\ProblemsVal} = 7648$).
+Results of the evaluation of symbol precedence heuristics based on various symbol cost models
+on $\ProblemsVal$ ($\card{\ProblemsVal} = 7648$).
 Means and standard deviations over 5 runs are reported.
+The \gls{gcn} models are trained according to the description in \cref{sec:architecture,sec:evaluation}.
+The simple model is the final model from \cite{DBLP:conf/cade/Bartek020}.
+The models that use machine learning for the predicate precedence only
+use the \texttt{frequency} heuristic for the function precedence, and vice versa.
+The frequency models use the standard \texttt{frequency} heuristic implemented in \Vampire{}.
 }
@@
 
-Model & \multicolumn{2}{l}{Successes on $\ProblemsVal$} & \multicolumn{2}{l}{Improvement over baseline} \\
+Symbol cost model & \multicolumn{2}{l}{Successes on $\ProblemsVal$} & \multicolumn{2}{l}{Improvement over baseline} \\
 & Mean & Std & Absolute & Relative \\
@@
 
-\texttt{vampire -lcm standard} &
-\num{3823.0} &
-\num[round-mode=places,round-precision=2]{3.40587727318528} &
+%Frequency (regular \acrshort{kbo}) &
+%\texttt{vampire -lcm standard} &
+%\num{3823.0} &
+%\num[round-mode=places,round-precision=2]{3.40587727318528} &
 %\SI[round-mode=places,round-precision=2]{49.9869247}{\percent} &
-+53.4 &
-\num[round-mode=places,round-precision=3]{1.014165959} \\
+%+53.4 &
+%\num[round-mode=places,round-precision=3]{1.014165959} \\
 % VML-741
 
-\texttt{vampire -lcm predicate} &
+Frequency &
+%\texttt{vampire -lcm predicate} &
 % Success rate: mean: 0.492887029, std: 0.000401412
@@
 \todo{FB: Add links to Neptune runs?}
-\todo{FB: Finalize results for function precedences.}
-\todo{FB: Try to evaluate a recommender that uses both predicate and function models.}
 
@@
 
-The loss is merely a proxy measure of the accuracy,
-and the accuracy is merely a proxy measure of the solver performance.
-During the training, the validation loss typically started increasing after approximately 50 epochs,
-while both the train loss and validation accuracy continued improving.
-A natural possible explanation is that ...
-\todo{Finish.}
-While a higher granularity in the solver evaluation would be necessary to draw a clear conclusion,
-the trend in the solver performance seems mostly aligned with the validation accuracy.
+The results show that the \gls{gcn}-based model outperforms the \texttt{frequency} heuristic by a significant margin.
+Since the predicate precedence recommender was trained against randomly distributed function precedences,
+it is expected to perform well irrespective of the function precedence heuristic it is combined with.
+Combining the trained recommenders for predicate and function precedences manifests better performance
+than any of the two in combination with the standard \texttt{frequency} heuristic,
+outperforming the \texttt{frequency} heuristic by approximately \SI{4.8}{\percent}.
 
-\todo[inline,author=FB]{Plot some learning curves?}
+We have verified that the simple linear predicate precedence heuristic
+trained in \cite{DBLP:conf/cade/Bartek020} outperforms the \texttt{frequency} heuristic.
+Moreover, we have confirmed the conjecture that using a \gls{gnn} may yield an even better performance \cite{DBLP:conf/cade/Bartek020}.
+
+%In the process of training,
+%we tracked three metrics on the training and validation sets:
+%loss, accuracy, and solver performance on a sample of 1000 problems.
+%A typical training ran for approximately 500 epochs
+%with training loss steadily decreasing and
+%validation loss decreasing for the initial 50 epochs and then increasing.
+%Both training and validation accuracy were steadily increasing (training accuracy significantly faster than validation accuracy),
+%with validation loss entering a plateau around epoch 100.
+%The solver performance approximately followed the dynamics of the accuracy on the respective problem set.
+% Predicate: https://ui.neptune.ai/filipbartek/vampire-ml/e/VML-540/charts
+% Function: https://ui.neptune.ai/filipbartek/vampire-ml/e/VML-672/charts
+
+\todo[inline]{FB: Discuss the phenomenon of increasing validation loss and accuracy.}
+%A possible explanation of the discrepancy between the improving validation accuracy and deteriorating validation loss
+%in the latter part of the training process
+%is that the improvements of training loss generalize to improvements of loss on some, but not all of the validation examples.
+%
+%is that due to the limited generalization from training to validation set,
+%some improvements of training loss come at the cost of an increase of loss on validation examples that are already misclassified
+%(assigned a negative score).
+%Such change increases the validation loss but does not affect the validation accuracy.
+%At the same time there are validation examples whose loss is decreasing,

### 2021-02-23 main.tex
Shave off content by commenting out to reduce page count to 15

@@
 
-A more detailed analysis of the training process might yield insights into how the performance generalizes
-from the training set to the validation set
-and from proxy metrics, such as the loss and the accuracy, to the final solver performance.
-Ultimately, this might reveal modifications that make the training more efficient and the final recommender more performant.
-
-The training examples take the form of pairs of precedences,
-where one of the precedences is preferable over the other.
-In this work, the amount by which the quality of the precedences differs is ignored.
-Taking the exact or estimated numbers of saturation loop iterations into account
-might help the recommender to prioritize the more significant gains.
-
-Applying techniques of reinforcement learning to focus the training data on the cases that yield high performance gains
-could further improve the recommender performance.
-
-We restricted our experiments to problems whose graph representation does not exceed \num{100000} nodes.
-Evaluating the recommender on larger problems would be an interesting test of generalization.
-Training on larger problems may be facilitated by employing a lossy graphification.
-
-We performed all experiments with a fixed \gls{atp} \Vampire{} and a fixed configuration
-we consider to be a reasonable baseline.
-Introducing other prover configurations (namely other \glspl{sot})
-or other provers could make the resulting recommender more robust
-and possibly help extract more general knowledge about the structure of good symbol precedences.
-
-Finally, the approach outlined in \cref{sec:architecture}
-could be adjusted to solve tasks on \gls{fol} formulas other than recommending symbol precedences,
-such as premise selection of given clause selection.
-On the other hand, we could try to solve other tasks that involve generating permutations of arbitrary length.
-\todo{FB: TSP? Probably not because it is too combinatorial.}
-
-%KBO is a also parametrized by weights (along with the precedence). Could we learn those as well? (Jointly?)
+%A more detailed analysis of the training process might yield insights into how the performance generalizes
+%from the training set to the validation set
+%and from proxy metrics, such as the loss and the accuracy, to the final solver performance.
+%Ultimately, this might reveal modifications that make the training more efficient and the final recommender more performant.
+%
+%The training examples take the form of pairs of precedences,
+%where one of the precedences is preferable over the other.
+%In this work, the amount by which the quality of the precedences differs is ignored.
+%Taking the exact or estimated numbers of saturation loop iterations into account
+%might help the recommender to prioritize the more significant gains.
+%
+%Applying techniques of reinforcement learning to focus the training data on the cases that yield high performance gains
+%could further improve the recommender performance.
+%
+%We restricted our experiments to problems whose graph representation does not exceed \num{100000} nodes.
+%Evaluating the recommender on larger problems would be an interesting test of generalization.
+%Training on larger problems may be facilitated by employing a lossy graphification.
+%
+%We performed all experiments with a fixed \gls{atp} \Vampire{} and a fixed configuration
+%we consider to be a reasonable baseline.
+%Introducing other prover configurations (namely other \glspl{sot})
+%or other provers could make the resulting recommender more robust
+%and possibly help extract more general knowledge about the structure of good symbol precedences.
+%
+%Finally, the approach outlined in \cref{sec:architecture}
+%could be adjusted to solve tasks on \gls{fol} formulas other than recommending symbol precedences,
+%such as premise selection of given clause selection.
+%On the other hand, we could try to solve other tasks that involve generating permutations of arbitrary length.
+%\todo{FB: TSP? Probably not because it is too combinatorial.}
 

### 2021-02-23 main.tex
just a small touch in Related work; good job

@@
 to generating good symbol precedences.
-The neural recommender uses a \gls{gnn} to model symbol costs,
+The neural recommender presented here uses a \gls{gnn} to model symbol costs,
 while \cite{DBLP:conf/cade/Bartek020} used a linear combination of symbol features readily available in the \gls{atp} \Vampire{}.
@@
 
-\cite{Olsak2019} and \cite{Rawson2020} propose similar \gls{gnn} architectures to solve tasks on \gls{fol} problems.
+In \cite{Olsak2019} and \cite{Rawson2020}, the authors propose similar \gls{gnn} architectures to solve tasks on \gls{fol} problems.
 They use the \glspl{gnn} to solve classification tasks such as premise selection.
 While our system is trained on a proxy classification task,
-the main task it is evaluated against is generating useful precedences.
+the main task it is evaluated on is the generation of useful precedences.
 

### 2021-02-23 architecture.tex
s pripadnou kompresi tez pomuze (mozno opet zacomentovat a tim ziskat llncs default)

@@
 $$
+
 \todo{FB: Include LayerNorm and Residual if we end up using them.}
@@
 $$
-C(\pi) = Z_n \sum_{i=1}^n i \cdot c(\pi(i))
-% We call the normalization factor Z_n to follow convention from Foundations of Machine Learning, p. 122.
+C(\pi) = Z_n \sum_{i=1}^n i \cdot c(\pi(i))% We call the normalization factor Z_n to follow convention from Foundations of Machine Learning, p. 122.
 $$
@@
 \end{align*}
+
 \todo[inline]{FB: Consider accessing elements $\pi$ as vector elements $\pi_i$ instead of $\pi(i)$.

### 2021-02-23 main.tex
s pripadnou kompresi tez pomuze (mozno opet zacomentovat a tim ziskat llncs default)

@@
 \usepackage{cleveref}
+
+% Some mild shrinkage:
+
+% for Section and subsection headings:
+%% Save the class definition of \subparagraph
+\let\llncssubparagraph\subparagraph
+%% Provide a definition to \subparagraph to keep titlesec happy
+\let\subparagraph\paragraph
+%% Load titlesec
+\usepackage{titlesec}
+%% Revert \subparagraph to the llncs definition
+\let\subparagraph\llncssubparagraph
+\titlespacing*{\subsection}
+  {0pt}{0.9\baselineskip}{0.8\baselineskip}
+
+% For figures
+% https://tex.stackexchange.com/questions/60477/remove-space-after-figure-and-before-text
+\setlength{\textfloatsep}{0.7\baselineskip plus 0.2\baselineskip minus 0.2\baselineskip} % between a float at the top and text
+\setlength{\floatsep}{0.3\baselineskip plus 0.2\baselineskip minus 0.2\baselineskip} % between two floats at the top
+\setlength{\intextsep}{0.7\baselineskip plus 0.2\baselineskip minus 0.2\baselineskip} % between a float in text and text
 

### 2021-02-23 evaluation.tex
Revert "Shave off content by commenting out to reduce page count to 15"
This reverts commit 8bcb7bd7cfc6eae12b44593c1d66122cb987f2a6.

@@
 
-%In the process of training,
-%we tracked three metrics on the training and validation sets:
-%loss, accuracy, and solver performance on a sample of 1000 problems.
-%A typical training ran for approximately 500 epochs
-%with training loss steadily decreasing and
-%validation loss decreasing for the initial 50 epochs and then increasing.
-%Both training and validation accuracy were steadily increasing (training accuracy significantly faster than validation accuracy),
-%with validation loss entering a plateau around epoch 100.
-%The solver performance approximately followed the dynamics of the accuracy on the respective problem set.
+In the process of training,
+we tracked three metrics on the training and validation sets:
+loss, accuracy, and solver performance on a sample of 1000 problems.
+A typical training ran for approximately 500 epochs
+with training loss steadily decreasing and
+validation loss decreasing for the initial 50 epochs and then increasing.
+Both training and validation accuracy were steadily increasing (training accuracy significantly faster than validation accuracy),
+with validation loss entering a plateau around epoch 100.
+The solver performance approximately followed the dynamics of the accuracy on the respective problem set.
 % Predicate: https://ui.neptune.ai/filipbartek/vampire-ml/e/VML-540/charts

### 2021-02-23 main.tex
Revert "Shave off content by commenting out to reduce page count to 15"
This reverts commit 8bcb7bd7cfc6eae12b44593c1d66122cb987f2a6.

@@
 
-%A more detailed analysis of the training process might yield insights into how the performance generalizes
-%from the training set to the validation set
-%and from proxy metrics, such as the loss and the accuracy, to the final solver performance.
-%Ultimately, this might reveal modifications that make the training more efficient and the final recommender more performant.
-%
-%The training examples take the form of pairs of precedences,
-%where one of the precedences is preferable over the other.
-%In this work, the amount by which the quality of the precedences differs is ignored.
-%Taking the exact or estimated numbers of saturation loop iterations into account
-%might help the recommender to prioritize the more significant gains.
-%
-%Applying techniques of reinforcement learning to focus the training data on the cases that yield high performance gains
-%could further improve the recommender performance.
-%
-%We restricted our experiments to problems whose graph representation does not exceed \num{100000} nodes.
-%Evaluating the recommender on larger problems would be an interesting test of generalization.
-%Training on larger problems may be facilitated by employing a lossy graphification.
-%
-%We performed all experiments with a fixed \gls{atp} \Vampire{} and a fixed configuration
-%we consider to be a reasonable baseline.
-%Introducing other prover configurations (namely other \glspl{sot})
-%or other provers could make the resulting recommender more robust
-%and possibly help extract more general knowledge about the structure of good symbol precedences.
-%
-%Finally, the approach outlined in \cref{sec:architecture}
-%could be adjusted to solve tasks on \gls{fol} formulas other than recommending symbol precedences,
-%such as premise selection of given clause selection.
-%On the other hand, we could try to solve other tasks that involve generating permutations of arbitrary length.
-%\todo{FB: TSP? Probably not because it is too combinatorial.}
+A more detailed analysis of the training process might yield insights into how the performance generalizes
+from the training set to the validation set
+and from proxy metrics, such as the loss and the accuracy, to the final solver performance.
+Ultimately, this might reveal modifications that make the training more efficient and the final recommender more performant.
+
+The training examples take the form of pairs of precedences,
+where one of the precedences is preferable over the other.
+In this work, the amount by which the quality of the precedences differs is ignored.
+Taking the exact or estimated numbers of saturation loop iterations into account
+might help the recommender to prioritize the more significant gains.
+
+Applying techniques of reinforcement learning to focus the training data on the cases that yield high performance gains
+could further improve the recommender performance.
+
+We restricted our experiments to problems whose graph representation does not exceed \num{100000} nodes.
+Evaluating the recommender on larger problems would be an interesting test of generalization.
+Training on larger problems may be facilitated by employing a lossy graphification.
+
+We performed all experiments with a fixed \gls{atp} \Vampire{} and a fixed configuration
+we consider to be a reasonable baseline.
+Introducing other prover configurations (namely other \glspl{sot})
+or other provers could make the resulting recommender more robust
+and possibly help extract more general knowledge about the structure of good symbol precedences.
+
+Finally, the approach outlined in \cref{sec:architecture}
+could be adjusted to solve tasks on \gls{fol} formulas other than recommending symbol precedences,
+such as premise selection of given clause selection.
+On the other hand, we could try to solve other tasks that involve generating permutations of arbitrary length.
+\todo{FB: TSP? Probably not because it is too combinatorial.}
+
+%KBO is a also parametrized by weights (along with the precedence). Could we learn those as well? (Jointly?)
 

### 2021-02-23 architecture.tex
Graph constructor > Graphifier
Jelle found the word "graphifier" confusing.

@@
 \begin{itemize}
-\item \Cref{sec:graphifier}: Graphifier converts the input \gls{cnf} problem into a problem graph.
+\item \Cref{sec:graphifier}: A graph constructor converts the input \gls{cnf} problem into a problem graph.
 \item \Cref{sec:gcn}: \Gls{gcn} converts a problem graph into symbol embeddings.
@@
 Problem [label="CNF problem P"];
-Graphifier [style=rounded, label="Graphifier"];
+Graphifier [style=rounded, label="Graph constructor"];
 g [label="Graph"];

### 2021-02-23 evaluation.tex
Clarify how the problem set is split
following Jelle's remarks.

@@
 
-The problems in $\ProblemsTptp$ are split roughly in half to form the train set and the validation set.
-Both training and validation sets are restricted to problems whose graph representation consists of at most \num{100000} nodes
+The \num{17053} problems in $\ProblemsTptp$ are first split roughly in half to form the training set and the validation set.
+Next, both training and validation sets are restricted
+to problems whose graph representation consists of at most \num{100000} nodes
 to limit the memory requirements of the training.
-The train set is further restricted to problems that correspond to at least one training example.
-In total there are \num{7648} problems in the validation set $\ProblemsVal$
-and \num{2571} problems in the train set $\ProblemsTrain$.
-\todo{MS: A kdyz pouzivas validation set behem uceni, ma taky mensi podmnozinu s limitem \num{100000} nodes?}
+Approximately \SI{90}{\percent} of the problems fit into this limit
+%a total of \num{15282} out of the \num{17053} (approximately \SI{90}{\percent}) problems satisfy this requirement.
+and there are \num{7648} problems in the resulting validation set $\ProblemsVal$.
+The training set $\ProblemsTrain$ is further restricted to problems that correspond to at least one training example,
+leaving \num{2571} problems when training predicate precedence recommender,
+and \num{1953} problems when training function precedence recommender.
 \todo{FB: Unify the terminology: validation, or train set?
@@
 % with_questions: 5349
-% graphified (not all attempted): 10219
+% graphified: 15282
 % train&with_questions: 2647

### 2021-02-23 abstract.tex
Minor corrections thanks to Jelle

--- 2021-02-22 abstract.tex
@@
 the system does not presuppose the problems to be related or share a common signature. 
-When coupled with the theorem prover Vampire and evaluated on the \acrshort{tptp} problem library,
-the recommender is found to outperform a state-of-the-art heuristic by more than \SI{4}{\percent}.
+When coupled with the theorem prover \Vampire{} and evaluated on the \acrshort{tptp} problem library,
+the recommender is found to outperform a state-of-the-art heuristic by more than \SI{4}{\percent}
+on unseen problems.
 

### 2021-02-23 introduction.tex
Minor corrections thanks to Jelle

@@
 This work strictly improves on our previous experiments with linear regression models and simple hand-crafted symbol features \cite{DBLP:conf/cade/Bartek020}
-and is, to the best of our knowledge, a first method able to propose good symbol precedences automatically 
+and is, to the best of our knowledge, the first method able to propose good symbol precedences automatically 
 using a non-linear transformation of the input problem structure.

### 2021-02-23 architecture.tex
Remove a confusing reference for "output function"

@@
 Ale v te prislusne podsekci tim zas zacit.}
-\item \Cref{sec:output}: An output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
-\todo{MS: ``output function \cite{Zhou2018}'' my nic nerika, mel bych to znat?\\
-FB: Zhou2018 je review GNNs. Output function je termin, ktery se tam pouziva. Ta citace je nejspis tady nepotrebna.}
+\item \Cref{sec:output}: An output function converts the symbol embeddings into a vector of symbol costs.
 \item \Cref{sec:ranking}: Sorting converts the symbol costs into a symbol precedence.

### 2021-02-23 architecture.tex
Clean up some todos

@@
 \todo{Some pairs of precedences are not informative. We hope that the non-systematic examples will cancel each other out.}
-\todo{Compare our GCN to Michael, Mirek etc.}
 
@@
 whose values can be trained by gradient descent.
-\todo{Ensure we have defined ``gradient descent''.}
-\todo{MS: chapu ucel (a vidim, ze dalsi veta navazuje na ``parameters'', ale je to kostrbate.
+\todo[inline]{MS: chapu ucel (a vidim, ze dalsi veta navazuje na ``parameters'', ale je to kostrbate.
 Recommender = system, chapu jako program. Programy vetsinou neparametrizujeme tenzorama a gradient descent zije na jine urovni,
@@
 \item \Cref{sec:gcn}: \Gls{gcn} converts a problem graph into symbol embeddings.
-\todo{MS: Kdyz embeddingy nebudou v preliminaries, je asi OK ctenare, ktery by o nich neslysel, zde trochu vydesit.
-Ale v te prislusne podsekci tim zas zacit.}
 \item \Cref{sec:output}: An output function converts the symbol embeddings into a vector of symbol costs.
@@
 \end{itemize}
-\todo{MS: tohle zatim chapu jako predbezny nastrel. Leda by uz pred tim bylo vysvetleno:
-embedding, \gls{gcn}/convolution layers, ... \\
-FB: Staci predestrit, ze detaily vysvetlim pozdeji? MS: asi jo :)}
 
@@
 a popisujes to pak dal.}
+\todo{Compare our GCN to Michael, Mirek etc.}
 

### 2021-02-23 evaluation.tex
Minor corrections thanks to Jelle
Remove some resolved todos

@@
 using the examples generated from the problems in $\ProblemsTrain$.
-\todo{Add references to the sections that describe the architecture.}
 To avoid redundant computations, all examples generated from a problem are processed in the same training batch.
@@
 so that each problem contributes to the training to the same degree irrespective of the relative numbers of examples.
-\todo{FB: Shall we remind that the examples are further normalized by $k(n)$ to make even across signature lengths?}
-\todo{MS: asi dobry, pokud to bude jasne receny nejaky predchozi sekci.}
 
@@
 vztahnout k casu klauzifikace? Jako rict, ze to trva x-krat dyl nez jen klauzifikovat?}
-
 \Cref{tab:results} shows the results.
@@
 
-\todo{FB: Add discussion.}
-\todo{FB: Evaluate on problems larger than 100k nodes.}
-
 The results show that the \gls{gcn}-based model outperforms the \texttt{frequency} heuristic by a significant margin.

### 2021-02-23 evaluation.tex
Some small improvements

@@
 
-We used a \gls{gcn} as described in \cref{sec:architecture}
+We used a \gls{gcn} described in \cref{sec:gcn}
 with depth 4, message size 16, \gls{relu} activation function,
@@
 
-A predicate symbol cost model is trained by gradient backpropagation
-\todo{FB: Explain? MS: tohle by melo byt k pochopeni z predchozich sekci.}
-on the precedence pair classification task
-\todo{FB: Reference a section. MS: Ano!}
+A predicate symbol cost model is trained by gradient descent
+on the precedence pair classification task (described in \cref{sec:training})
 using the examples generated from the problems in $\ProblemsTrain$.
@@
 For each problem $P \in \ProblemsVal$,
-a pair\todo{MS: ja vim, ze sis to "vyplejtval" v predchozi vete,
-ale kde jinde nez tady rict explicitne "predicate precendence" a "function precedence"?
-Z toho "pair" ot nemusi byt jasny...}
- of symbol precedences was generated by the respective trained recommender
+a predicate and a function precedence
+was generated by the respective trained recommender,
 and \Vampire{} was run using these precedences

### 2021-02-23 architecture.tex
Remove some resolved todos
Some small improvements
Update some todos

@@
 \item Perfect sub-expression sharing:
-\todo{MS: Predpokladam ze dva ruzne ground literaly p(c) tam budou taky jen jendnou?\\
+\todo[inline]{MS: Predpokladam ze dva ruzne ground literaly p(c) tam budou taky jen jendnou?\\
 FB: Literaly nemaji nody. Atomy maji nody a polarita literalu je zakodovana v typu hrany, ktery jej spojuje s klauzuli.
@@
 and then iteratively updates the embeddings by passing them through the convolutional layers.
-\todo{FB: Ensure terms are clear (preferably defined): embedding, vector, trainable vector, feature vector.
-MS: (convolutional, layers, ...)}
 
@@
 
-\subsection{Training}
+\subsection{Training: Classification of pairs of precedences}
 \label{sec:training}

### 2021-02-23 evaluation.tex
Update some todos

@@
 % http://www.tptp.org/TPTP/SyntaxBNF.html
-\todo{FB: Mention TPTP version. Consider joining with section Problem set below.}
+\todo{FB: Consider joining with section Problem set below.}
 \Gls{fof} problems are first converted into equisatisfiable \gls{cnf} problems by \Vampire{}.
@@
 if the proof search finishes successfully with $\PrecBetter$ ($\SolverRun{P}{\Prec} = \top$)
+\todo{FB: Alias: We use $S$ for both solver and score of precedence pair.}
 and if the number of iterations of the saturation loop with $\PrecBetter$ is smaller than with $\PrecWorse$.
@@
 $$
+\todo{FB: Shrink into text to save space.}
 where $n = \sum_{P \in \ProblemsTptp} n_P$ is the total number of tries on all problems.
@@
 was chosen as the most promising.
-\todo{FB: Watch out: This way we may overfit on the 1000 problems used for sample solver performance evaluation. We should leave out these 1000 problems from the final evaluation.}
-\todo{MS: taky me to ted napadlo! Uplne oficialni metodika byva split na train,valid,test. 
+\todo[inline]{FB: Watch out: This way we may overfit on the 1000 problems used for sample solver performance evaluation. We should leave out these 1000 problems from the final evaluation.}
+\todo[inline]{MS: taky me to ted napadlo! Uplne oficialni metodika byva split na train,valid,test. 
 Kdy se trenuje na train, hyperparametry (vcetne early stopping) se ladi vuci valid 

### 2021-02-23 architecture.tex
Remove the line with inverse permutations
because it was confusing.
Mark some content for omission if toggle LONG is false

@@
 The recommender consists of modules that perform specific subtasks,
-each of which is described in detail in one of the following sections (see also \cref{fig:architecture}):
+each of which is described in detail in one of the following
+\iftoggle{LONG}{
+sections (see also \cref{fig:architecture}):
 \begin{itemize}
@@
 \end{itemize}
+}{
+sections (see also \cref{fig:architecture}).
+}
 
@@
 &= - \log \sigmoid (C(\PrecWorse) - C(\PrecBetter)) \\
-&= - \log \sigmoid Z_n \sum_{i=1}^n i (c(\PrecWorse(i)) - c(\PrecBetter(i))) \\
-&= - \log \sigmoid Z_n \sum_{i=1}^n c(i) (\inv{\PrecWorse}(i) - \inv{\PrecBetter}(i))
+&= - \log \sigmoid Z_n \sum_{i=1}^n i (c(\PrecWorse(i)) - c(\PrecBetter(i)))
+%&= - \log \sigmoid Z_n \sum_{i=1}^n c(i) (\inv{\PrecWorse}(i) - \inv{\PrecBetter}(i))
 \end{align*}

### 2021-02-23 evaluation.tex
Mark some content for omission if toggle LONG is false

@@
 
+\iftoggle{LONG}{
 \subsubsection{Metrics}
@@
 asi je tu navic i tento odstavec, nebo aspon jeho cast.}
+}
 
@@
 
+\iftoggle{LONG}{
 In the process of training,
@@
 % Function: https://ui.neptune.ai/filipbartek/vampire-ml/e/VML-672/charts
+}
 

### 2021-02-23 main.tex
Remove subdivision of Future work
because section Conclusion was unbalanced.
Remove some resolved todos
Make space shrinking togglable
Mark some content for omission if toggle LONG is false

@@
 \usepackage[english]{babel}
+
+\usepackage{etoolbox}
+
+\newtoggle{LONG}
+\toggletrue{LONG}
+%\togglefalse{LONG}
+
+\newtoggle{SHRINK}
+\toggletrue{LONG}
+%\togglefalse{SHRINK}
+
 \usepackage[binary-units=true,detect-weight=true]{siunitx}
@@
 
+\iftoggle{SHRINK}{
 % Some mild shrinkage:
@@
   {0pt}{0.9\baselineskip}{0.8\baselineskip}
+}
 
@@
 
-\section{Conclusion}
+\section{Conclusion and future work}
 \label{sec:conclusion}
@@
 \todo{FB: Should we boast that the reduction of ranking to training of differentiable element scores is innovative?}
-
-\subsection{Future work}
 
@@
 
+\iftoggle{LONG}{
 A more detailed analysis of the training process might yield insights into how the performance generalizes
@@
 \todo{FB: TSP? Probably not because it is too combinatorial.}
-
-%KBO is a also parametrized by weights (along with the precedence). Could we learn those as well? (Jointly?)
+}
 

### 2021-02-23 main.tex
some reformulations in the RW

@@
 when generating the predicate precedence, and vice versa.
+
+\subsection{Future work - Martins new version (the first three paragraphs)}
+
+A manual analysis of the trained recommender could produce new insights into how the choice of the symbol precedence influences the proof search,
+% and how a symbol precedence should be chosen in the context of a problem so that it is likely to lead to an efficient proof search.
+% This might lead to a design of a new precedence heuristic
+% that focuses relies on aspects of input problems
+% that have been overlooked so far in the context of generating symbol precedences.
+which could in turn help designing new efficient precedence generating schemes.
+Indeed, a trained cost model summarizes the observed behaviours of the ATP on the random precedences
+and is able to discover patterns in them (as we know implicitly from its accuracy) 
+despite their seemingly chaotic behaviour as perceived by a human observer.
+The challenge is to extract these pattern to a human-understandable form.
+
+\gls{kbo}, that we choose in our experiments, is in addition to a symbol precedences
+also determined by symbol \emph{weights} (we kept these fixed to the default value 1 in this work).
+% While using the \gls{kbo} as our simplification ordering scheme of choice,
+% we restricted ourselves to generating the symbol precedences,
+% leaving the symbol weights fixed to the constant 1 (the default behavior of \Vampire{}).
+Learning to recommend also the symbol weights in addition to the precedences
+represents an interesting avenue for future research.
+
+The same applies to the idea of learning to recommend 
+both the predicate and the function precedences using a single \gls{gcn}.
+The joint learning, although more complex to design, could 
+additionally discover interdependencies
+between the effects of the function precedence and predicate precedence on the proof search,
+while the current setup implicitly assumes that the effects are independent.
 Finally, higher training data efficiency could be achieved by considering all pairs of measured executions on a problem
@@
 \todo{FB: Confusing?}
+% would yield a recommender
+% that only needs one pass through a \gls{gcn} to generate both predicate and function precedences for a problem.
+% Moreover, the model would have the possibility to exploit the properties of the function precedence
+ %when generating the predicate precedence, and vice versa.
+
+\todo{MS: continue from here to the end. (Or will these be in the end left out)?}
 

### 2021-02-23 evaluation.tex
Clean up the inclusion of layer norm and residual connections

@@
 with depth 4, message size 16, \gls{relu} activation function,
-residual connections and layer normalization.
+skip connections \cite{Zhou2018}, and layer normalization \cite{Ba2016}.
 We tuned the hyperparameters by a small manual grid search.

### 2021-02-23 main.tex
Remove leftover content from new Conclusion by MS

--- 2021-02-23 main.tex
@@
 
-An analysis of the trained recommender could reveal new insights into how the symbol precedence influences the proof search,
-and how a symbol precedence should be chosen in the context of a problem so that it is likely to lead to an efficient proof search.
-This might lead to a design of a new precedence heuristic
-that focuses relies on aspects of input problems
-that have been overlooked so far in the context of generating symbol precedences.
+A manual analysis of the trained recommender could produce new insights into how the choice of the symbol precedence influences the proof search,
+which could in turn help designing new efficient precedence generating schemes.
+Indeed, a trained cost model summarizes the observed behaviours of the ATP on the random precedences
+and is able to discover patterns in them (as we know implicitly from its accuracy) 
+despite their seemingly chaotic behaviour as perceived by a human observer.
+The challenge is to extract these pattern to a human-understandable form.
 
-While using the \gls{kbo} as our simplification ordering scheme of choice,
-we restricted ourselves to generating the symbol precedences,
-leaving the symbol weights fixed to the constant 1 (the default behavior of \Vampire{}).
-Learning to recommend the symbol weights in addition to the symbol precedences would be interesting.
-\todo{FB: Be more fancy in wording.}
+\gls{kbo}, that we choose in our experiments, is in addition to a symbol precedences
+also determined by symbol \emph{weights} (we kept these fixed to the default value 1 in this work).
+Learning to recommend also the symbol weights in addition to the precedences
+represents an interesting avenue for future research.
 
-Training both the predicate and the function precedence using a single \gls{gcn} would yield a recommender
-that only needs one pass through a \gls{gcn} to generate both predicate and function precedences for a problem.
-Moreover, the model would have the possibility to exploit the properties of the function precedence
-when generating the predicate precedence, and vice versa.
+The same applies to the idea of learning to recommend 
+both the predicate and the function precedences using a single \gls{gcn}.
+The joint learning, although more complex to design, could 
+additionally discover interdependencies
+between the effects of the function precedence and predicate precedence on the proof search,
+while the current setup implicitly assumes that the effects are independent.
 Finally, higher training data efficiency could be achieved by considering all pairs of measured executions on a problem
 in one training batch.
-\todo{FB: Confusing?}
 

### 2021-02-23 conclusion.tex
Move content of Conclusion into a dedicated file

--- 2021-02-23 main.tex
@@
-\documentclass[runningheads]{llncs}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage[english]{babel}
-
-\usepackage{etoolbox}
-
-\newtoggle{LONG}
-\toggletrue{LONG}
-%\togglefalse{LONG}
-
-\newtoggle{SHRINK}
-\toggletrue{LONG}
-%\togglefalse{SHRINK}
-
-\usepackage[binary-units=true,detect-weight=true]{siunitx}
-
-% How to write a paper:
-% https://mj.ucw.cz/papers/jakpsat.pdf
-% Jones 2016: https://www.microsoft.com/en-us/research/academic-program/write-great-research-paper/
-% AWR: https://jazyky.fel.cvut.cz/vyuka/RPP/BE9M04AKP/
-
-% PAAR paper: https://github.com/filipbartek/learning-precedences-from-elementary-symbol-features/releases/download/paar2020%2Fceur-2/Learning_Precedences_from_Simple_Symbol_Features.pdf
-
-\input{preamble}
-\input{glossary}
-\input{front}
-
-\usepackage{svg}
-
-\usepackage[pdf]{graphviz}
-\usepackage{tikz}
-
-\usepackage{hyperref}
-\hypersetup{
-pdftitle={Neural Precedence Recommender},
-pdfauthor={Filip Bártek, Martin Suda},
-pdfkeywords={saturation-based theorem proving, simplification ordering, symbol precedence, machine learning, graph convolutional network}
-}
-
-\usepackage{cleveref}
-
-\iftoggle{SHRINK}{
-% Some mild shrinkage:
-
-% for Section and subsection headings:
-%% Save the class definition of \subparagraph
-\let\llncssubparagraph\subparagraph
-%% Provide a definition to \subparagraph to keep titlesec happy
-\let\subparagraph\paragraph
-%% Load titlesec
-\usepackage{titlesec}
-%% Revert \subparagraph to the llncs definition
-\let\subparagraph\llncssubparagraph
-\titlespacing*{\subsection}
-  {0pt}{0.9\baselineskip}{0.8\baselineskip}
-}
-
-% For figures
-% https://tex.stackexchange.com/questions/60477/remove-space-after-figure-and-before-text
-\setlength{\textfloatsep}{0.7\baselineskip plus 0.2\baselineskip minus 0.2\baselineskip} % between a float at the top and text
-\setlength{\floatsep}{0.3\baselineskip plus 0.2\baselineskip minus 0.2\baselineskip} % between two floats at the top
-\setlength{\intextsep}{0.7\baselineskip plus 0.2\baselineskip minus 0.2\baselineskip} % between a float in text and text
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-\input{abstract}
-\end{abstract}
-
-\section{Introduction}
-
-\input{introduction}
-
-\section{Preliminaries}
-\label{sec:preliminaries}
-\input{preliminaries}
-
-\section{Architecture}
-\label{sec:architecture}
-\input{architecture}
-
-\section{Experimental evaluation}
-\label{sec:evaluation}
-\input{evaluation}
-
-\section{Related work}
-\label{sec:related}
-
-Our previous text \cite{DBLP:conf/cade/Bartek020} marked the initial investigation of applying techniques of \gls{ml}
-to generating good symbol precedences.
-The neural recommender presented here uses a \gls{gnn} to model symbol costs,
-while \cite{DBLP:conf/cade/Bartek020} used a linear combination of symbol features readily available in the \gls{atp} \Vampire{}.
-The \gls{gnn}-based approach yields more performant precedences at the cost of longer training and preprocessing time.
-
-In \cite{Olsak2019} and \cite{Rawson2020}, the authors propose similar \gls{gnn} architectures to solve tasks on \gls{fol} problems.
-They use the \glspl{gnn} to solve classification tasks such as premise selection.
-While our system is trained on a proxy classification task,
-the main task it is evaluated on is the generation of useful precedences.
-
-\todo[inline]{Related problem: Ranking. See Mohri etc.}
-
-\section{Conclusion and future work}
-\label{sec:conclusion}
-
 We have described a system that extracts useful symbol precedences from the graph representations of \gls{cnf} problems.
@@
 \todo{FB: TSP? Probably not because it is too combinatorial.}
-}
-
-\section*{Acknowledgments}
-% > Acknowledgements should generally be placed in an unnumbered subsection at the end of the paper.
-
-% https://sgs.cvut.cz/index.php?action=faq
-% This work was supported by the Grant Agency of the Czech Technical University in Prague, grant No. SGS...
-
-\todo{MS: zvazit, jestli nerozepsat zvlast Martin, zvlast Filip.
-Pripadne se zeptat Hanky, jestli bychom nemeli nejak vypichnout
-jen GACR.}
-
-This work was supported by
-the Czech Science Foundation project 20-06390Y,
-the project RICAIP no. 857306 under the EU-H2020 programme,
-and
-the Grant Agency of the Czech Technical University in Prague, grant\\
-no.~SGS20/215/OHK3/3T/37.
-
-% > LaTeX users should avoid self-defined environments and use the bibliographic style MathPhySci for computer science proceedings.
-% > It is not possible to have hyperlinks in references.
-\bibliographystyle{splncs04}
-\bibliography{main}
-
-%\appendix
-%\input{appendix}
-
-\end{document}
+}{}

### 2021-02-23 main.tex
Move content of Conclusion into a dedicated file

--- 2021-02-23 main.tex
@@
 \label{sec:conclusion}
-
-We have described a system that extracts useful symbol precedences from the graph representations of \gls{cnf} problems.
-Comparison against a conventional symbol precedence heuristic shows that using a \gls{gcn}
-to consider the whole structure of the input problem is beneficial.
-\todo{FB: Should we boast that the reduction of ranking to training of differentiable element scores is innovative?}
-
-An analysis of the trained recommender could reveal new insights into how the symbol precedence influences the proof search,
-and how a symbol precedence should be chosen in the context of a problem so that it is likely to lead to an efficient proof search.
-This might lead to a design of a new precedence heuristic
-that focuses relies on aspects of input problems
-that have been overlooked so far in the context of generating symbol precedences.
-
-While using the \gls{kbo} as our simplification ordering scheme of choice,
-we restricted ourselves to generating the symbol precedences,
-leaving the symbol weights fixed to the constant 1 (the default behavior of \Vampire{}).
-Learning to recommend the symbol weights in addition to the symbol precedences would be interesting.
-\todo{FB: Be more fancy in wording.}
-
-Training both the predicate and the function precedence using a single \gls{gcn} would yield a recommender
-that only needs one pass through a \gls{gcn} to generate both predicate and function precedences for a problem.
-Moreover, the model would have the possibility to exploit the properties of the function precedence
-when generating the predicate precedence, and vice versa.
-Finally, higher training data efficiency could be achieved by considering all pairs of measured executions on a problem
-in one training batch.
-\todo{FB: Confusing?}
-
-\iftoggle{LONG}{
-A more detailed analysis of the training process might yield insights into how the performance generalizes
-from the training set to the validation set
-and from proxy metrics, such as the loss and the accuracy, to the final solver performance.
-Ultimately, this might reveal modifications that make the training more efficient and the final recommender more performant.
-
-The training examples take the form of pairs of precedences,
-where one of the precedences is preferable over the other.
-In this work, the amount by which the quality of the precedences differs is ignored.
-Taking the exact or estimated numbers of saturation loop iterations into account
-might help the recommender to prioritize the more significant gains.
-
-Applying techniques of reinforcement learning to focus the training data on the cases that yield high performance gains
-could further improve the recommender performance.
-
-We restricted our experiments to problems whose graph representation does not exceed \num{100000} nodes.
-Evaluating the recommender on larger problems would be an interesting test of generalization.
-Training on larger problems may be facilitated by employing a lossy graphification.
-
-We performed all experiments with a fixed \gls{atp} \Vampire{} and a fixed configuration
-we consider to be a reasonable baseline.
-Introducing other prover configurations (namely other \glspl{sot})
-or other provers could make the resulting recommender more robust
-and possibly help extract more general knowledge about the structure of good symbol precedences.
-
-Finally, the approach outlined in \cref{sec:architecture}
-could be adjusted to solve tasks on \gls{fol} formulas other than recommending symbol precedences,
-such as premise selection of given clause selection.
-On the other hand, we could try to solve other tasks that involve generating permutations of arbitrary length.
-\todo{FB: TSP? Probably not because it is too combinatorial.}
-}
+\input{conclusion}
 

### 2021-02-23 evaluation.tex
Cut down the length of the non-long version to 15 pages
by conservative, mostly cosmetic changes.

@@
 
-All the experiments were run on a computer with the following specification:
-
-\begin{itemize}
-\item CPU: Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz})
-\item RAM: \SI{383}{GiB}
-\item OS: Ubuntu 20.04
-\item Kernel: 5.4.0-40-generic
-\end{itemize}
+All the experiments were run on a computer with
+the CPU Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz}),
+\SI{383}{GiB} RAM,
+the OS Ubuntu 20.04 and
+the Linux kernel 5.4.0-40-generic.
 
@@
 
-\subsubsection{Input problems}
+\subsection{Dataset preparation}
+
+The training data consists of examples of the form $(P, \PrecBetter, \PrecWorse)$,
+where $P$ is a \gls{cnf} problem and $\PrecBetter, \PrecWorse$ are precedences of symbols of problem $P$
+such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop (see \cref{sec:saturation}).
+\todo{FB: Justify saturation loop iterations as a proxy for success. MS: Ano, ale driv nez zde!}
+
+Since the \gls{tkbo} never compares a predicate symbol with a function symbol,
+\todo{FB: Consider referencing an earlier section that explains KBO or TKBO.}
+two separate precedences can be considered for each problem:
+a predicate precedence and a function precedence.
+We trained a predicate precedence recommender separately from a function precedence recommender
+to simplify the training process and to isolate the effects of the predicate and function precedences.
+This section describes how the training data for training a \emph{predicate} precedence recommender was generated.
+Training data for training a function precedence recommender was generated analogously.
+
+\subsubsection{Base problem set}
 
@@
 \Gls{fof} problems are first converted into equisatisfiable \gls{cnf} problems by \Vampire{}.
-New symbols may be introduced during preprocessing,
-namely due to the Tseitin transformation and Skolemization.
-We denote the preprocessed \gls{cnf} problem as $P = (\Sigma, \mathit{Cl})$,
-where $\Sigma$ denotes the list of all predicate and function symbols of the problem,
-and $\mathit{Cl}$ denotes a set of clauses over $\Sigma$ that constitute the problem.
+%New symbols may be introduced during preprocessing,
+%namely due to the Tseitin transformation and Skolemization.
+%We denote the preprocessed \gls{cnf} problem as $P = (\Sigma, \mathit{Cl})$,
+%where $\Sigma$ denotes the list of all predicate and function symbols of the problem,
+%and $\mathit{Cl}$ denotes a set of clauses over $\Sigma$ that constitute the problem.
+
+The problem library \acrshort{tptp}~v7.4.0 \cite{10.1007/978-3-030-29436-6_29}
+was used as the source of problems for training and evaluation of the recommender,
+offering a total of \num{17053} \gls{fol} problems.
+We denote the set of all the problems available for training and evaluation as $\ProblemsTptp$.
+
+\subsubsection{Node feature extraction}
 
@@
 \todo{FB: Consider simplifying the paragraph by removing overlap with \cref{sec:gcn}.}
-
-\subsection{Training data}
-
-The training data consists of examples of the form $(P, \PrecBetter, \PrecWorse)$,
-where $P$ is a \gls{cnf} problem and $\PrecBetter, \PrecWorse$ are precedences of symbols of problem $P$
-such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop (see \cref{sec:saturation}).
-\todo{FB: Justify saturation loop iterations as a proxy for success. MS: Ano, ale driv nez zde!}
-
-Since the \gls{tkbo} never compares a predicate symbol with a function symbol,
-\todo{FB: Consider referencing an earlier section that explains KBO or TKBO.}
-two separate precedences can be considered for each problem:
-a predicate precedence and a function precedence.
-We trained a predicate precedence recommender separately from a function precedence recommender
-to simplify the training process and to isolate the effects of the predicate and function precedences.
-This section describes how the training data for training a \emph{predicate} precedence recommender was generated.
-Training data for training a function precedence recommender was generated analogously.
-
-\subsubsection{Problem set}
-\todo[inline]{MS: mozna bych dal propagoval cinny rod a minuly cas ...}
-The examples are generated by sampling the \gls{fol} part of the problem library \gls{tptp} v7.4.0 \cite{10.1007/978-3-030-29436-6_29}.
-A total of \num{17053} problems formulated in \gls{fof} and \gls{cnf} are sampled.
-The problems formulated in \gls{fof} are converted to \gls{cnf} by \Vampire{}.
-% vampire --mode clausify
-Let $\ProblemsTptp$ denote the set of all \num{17053} \gls{cnf} problems available for training and evaluation.
 
@@
 In each iteration, the generator samples the problem $P$ that maximizes
-$$
-\frac{s_P}{n_P} + \sqrt{\frac{2 \ln n}{n_P}}
-$$
+$\frac{s_P}{n_P} + \sqrt{\frac{2 \ln n}{n_P}}$,
 \todo{FB: Shrink into text to save space.}
@@
 
-\subsubsection{Sample weighting}
+%\subsubsection{Sample weighting}
 Each of the training examples of problem $P$ contributes to the training with the weight $\frac{1}{s_P}$,
@@
 \iftoggle{LONG}{
-\subsubsection{Metrics}
+%\subsubsection{Metrics}
 To analyze the training process,
@@
 
-\subsubsection{Termination}
+%\subsubsection{Termination}
 We run the training until the validation accuracy stopped increasing for 100 consecutive epochs.

### 2021-02-23 architecture.tex
Clean up the inclusion of layer norm and residual connections
Cut down the length of the non-long version to 15 pages
by conservative, mostly cosmetic changes.
Improve some wording

@@
 
-\todo{FB: Include LayerNorm and Residual if we end up using them.}
 %$$
@@
 We extend the notion of cost from symbols to precedences
-by summing up the symbol costs
+by taking the sum of the symbol costs
 weighted by their positions in the given precedence $\pi$:
@@
 independent of the signature size $n$:
-\begin{align*}
+\begin{multline*}
 \mathbb{E}_\pi [C(\pi)]
-&= \mathbb{E}_\pi \SquareBracket{Z_n \sum_{i=1}^n i \cdot c(\pi(i))} \\
-&= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_{\pi, i} [c(\pi(i))] \\
-&= Z_n \Parentheses{\sum_{i=1}^n i} \mathbb{E}_i [c(i)] \\
-&= \frac{2}{n(n+1)} \frac{n(n+1)}{2} \mathbb{E}_i [c(i)] \\
-&= \mathbb{E}_i [c(i)]
-\end{align*}
+= \mathbb{E}_\pi \SquareBracket{Z_n \sum_{i=1}^n i \cdot c(\pi(i))}
+= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_{\pi, i} [c(\pi(i))] \\
+= Z_n \Parentheses{\sum_{i=1}^n i} \mathbb{E}_i [c(i)]
+= \frac{2}{n(n+1)} \frac{n(n+1)}{2} \mathbb{E}_i [c(i)]
+= \mathbb{E}_i [c(i)]
+\end{multline*}
 

### 2021-02-24 introduction.tex
prelim scanned

@@
 to represent the problem structure. It learns from the ATP performance on selected problems
-and pairs of randomly sampled precedences. This information is then used to train
-a \emph{symbol cost model}, which realizes the recommendation by simply sorting 
+and pairs of randomly sampled precedences. This information is used to train
+a \emph{symbol cost model}, which then realizes the recommendation by simply sorting 
 the problem's symbols according the obtained costs.

### 2021-02-24 preliminaries.tex
Remove a resolved todo
prelim scanned

@@
 % !TEX root = main.tex
-
-% Terminology
-
-\todo[inline,author=FB]{Get inspiration from PAAR paper.}
 
@@
 
+\todo{MS: Celkove hezky! Jen mi tu nejak chybi konec... A taky proc se to vsechno rika.
+V PAAR clanku, pokud si dobre vzpominam, bylo hlavnim cilem zavest znaceni pro
+ ``pocet iteraci nez se najde dukaz''. aby se pak pouzilo dale\dots
+Nicmene ctu ted beginning->end, tak nevim, co chystas dale. }
+
 \todo[inline,author=FB]{Add terminology: $\bot$.}
@@
 \todo{Cite Bachmair Ganzinger or Handbook of AR, chapter 2. For literal selection. Inspiration: Selecting the selection.}
+\todo{MS: the original paper is \cite{DBLP:journals/logcom/BachmairG94}. 
+Stoji za precteni, at se v tom trochu vyznas!
+Mimochodem, mozna ze ``simplification ordering'' neni ten uplne nejpresnejsi nazev. 
+Pripadne na ten clenek mrkni rychle uz ted. V tehle sekci by se hodily nejake citace,
+aby bylo jasne, od koho terminy prejimame.
+(Weidenbachova kapitola v Handbooku taku (Combining superposition, sorts and splitting)
+taky tusim definuje presne vlastnosti toho usporadani a dava jim jmeno.}
 In each clause,
@@
 % Note: The selection function Total does not use the simplification ordering.
+\todo{MS: Ta logika je (pro pripomenuti):
+1) pravidla jsou sound i bez restrikci, (proto selection Total je v pohode)
+2) nicmene se ukazuje, ze cim mene toho selectem a tedy cim mene bude provedeno inferenci, tim lepe typicky pro search (vetsi sance dokazat (i tezke) problemy)
+3) na treti stranu, nemuzem nedelat nic - to by nebylo complete.
+4) Pravidla o selekci literalu, ktera popisujes, vyjadruji
+minimalni selekci, o ktere se podarilo dokazat (BachmairGanzinger), ze zaruci uplnost. 
+}
 Second, the simplification ordering orients some of the equalities
@@
 a permutation of the non-logical symbols of the input problem.
-In this work we focus on finding a symbol precedence achieves a good performance when plugged into the \gls{kbo},
-leaving all the symbol weights at the default value 1 as set by the \gls{atp} \Vampire{}.
+In this work we focus on finding a symbol precedence which 
+leads to a good performance of an ATP
+when plugged into the \gls{kbo},
+leaving all the symbol weights at the default 
+value 1 as set by the \gls{atp} \Vampire{}.
 
@@
 The output of each module is differentiable with respect to the input.
+\todo{MS: mozna bych byl opetrnejsi. Co ReLU a derivace v bode zlomu? ;)}
 
@@
 using each example in the training set exactly once.
+
+\todo{MS: Hezke! Ted uz v arichtekture muzes mavat pojmy o neuronkach a bude to tu uktovne! }

### 2021-02-24 architecture.tex
Add and extend some todos
comments po 3.5

@@
 that solves the input problem in a timely fashion.
+\todo{MS: Ja vim, ze uz je to nuda psat ty dlouhy a presny vety,
+ale ``timely fashion'' uz je mozna moc neformalni a
+a ``precedence does not solve a problem''.}
 
@@
 they order the symbols by a numeric property, such as arity or number of occurrences.
+\todo{MS: super!}
 
@@
 whose values can be trained by gradient descent.
+\todo{MS: tady mi to ted (po neuralnim prelim) uz prijde asi dobry!}
 \todo[inline]{MS: chapu ucel (a vidim, ze dalsi veta navazuje na ``parameters'', ale je to kostrbate.
@@
 that are likely to yield a successful proof in as few iterations of the saturation loop as possible.
+\todo{MS: o dost lespi verze v podstate te samy vety z konce prvniho odstavnce "System overview"}
 
@@
 It is only used in training mode.
+\todo{MS: je to schalne, ze tam mas vsude ``converts''? V nekterych bodech by asi byla k dispozici prilehavejsi slova.
+Treba sorting converts uz zni trochu sroubovane. }
 \end{itemize}
@@
 \item For each relation $r \in \mathcal{R}$, its inverse $\inv{r}$ is also present in the graph,
-typically represented by a different edge type.
+typically\todo{MS: jaka je vyjimka?} represented by a different edge type.
 \todo{MS: tohle jsem nepochopil. Nemuzeme rict, ze (az na nejakou vyjimkou) jsou edges v obou smerech?\\
@@
 This reflects the symmetry of equality.
-\item Perfect sub-expression sharing:
+\item \todo[inline]{MS: (Almost)} Perfect sub-expression sharing:
 \todo[inline]{MS: Predpokladam ze dva ruzne ground literaly p(c) tam budou taky jen jendnou?\\
@@
 \todo{FB: Cite some text about sub-expression sharing. Perhaps Rawson2020?}
-\todo{MS: Ale mezitim se to tu zmenilo a ja prestavam chapat, co je ``Redundant''.}
+\todo{MS: Ale mezitim se to tu zmenilo a ja prestavam chapat, co je ``Redundant''!}
 Note that since each variable is bound by a clause,
@@
 \todo{FB: Reference appendix if we describe the representation in more detail there.}
-\todo[inline]{MS: Filosoficka k ``can be represented''; mozna by se mohlo nekde objevit:
-Snazime se do struktury HIN ``otisknout'' celou strukturu CNF (jak jsem rikal,
-znamena to, ze zobrazeni je proste), abychom siti nevzali moznost ``vedet o problemu
-uplne vsechno'' (az na veci, na kterych nezalezi jako poradi literaly v klauzulich, etc).
-Ta filosoficka poznamka je o tom, ze pro dobre uceni tohle vlastne vubec nemusi byt treba,
-ze nejaky ``hrubsi otisk'' by mohl stacit tez (a byt treba mensi), ale my nevime, jak takovy zvolit.\\
-FB: Zkusim to popsat, kdyz zbyde cas.}
-\todo{FB: Mention other encodings that have been proposed by Mirek and Michael.}
+\todo{FB: Mention other encodings that have been proposed by Mirek and Michael and compare ours to theirs.}
 
@@
 Each symbol node has a feature vector with two bits of data:
-whether the symbol was introduced into the problem during preprocessing,
+whether the symbol was introduced into the problem during preprocessing (most notably clausification),
 and whether the symbol appears in a conjecture clause.
@@
 h_d^{(l+1)} =
-\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (W_r^{(l)} h_s^{(l)} + b_r^{(l)})}
+\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (W_r^{(l)} h_s^{(l)} + b_r^{(l)})}.
 $$
@@
 
-\todo[inline]{MS: neni uplne jiste, ze ``CADE people'' oceni presny zapis 
-strutury site, vcetne prvku jako $\mathrm{LayerNorm}$ ve vzorecku.
-Nerikam, ze bychom to meli uplne zatajit, ale popis, ktery je zde, spis
-patri do appendixu (ML paperu). Na te siti vlastne nic originalniho neni,
-tak neni treba vsechno vysvetlit do detailu. Zajimavejsi tu
-potom je az to, jak se problem $P$ ``otiskne'' v topologii grafu. 
-To uz originalni je (a soutezi to s representacemi jako ta Mirkova)
-a popisujes to pak dal.}
 \todo{Compare our GCN to Michael, Mirek etc.}
@@
 which is an affine transformation with no activation function.
-\todo{FB: Is this clear at this point?}
+\todo{FB: Is this clear at this point? MS: jj, ted uz jo!}
 
@@
 we refer to the predicted cost of $s_i$ simply as $c(i)$
-because the problem $P$ and the parameters $\theta$ are fixed in each respective context.
+because the problem $P$ and the parameters $\theta$ are fixed in each respective context.\todo{MS: I like.}
 
@@
 
-\subsubsection{Precedence cost}
+\todo[inline]{MS: Tady je asi hlavni ``dira'' ve vysvetlovani...
+Na to, abys vzal symbol costy a zavolal sort nepotrebujes definovat
+cost precedenci a neco o nem dokazovat.
+
+Nevim, jestli to nechces rict az pozdeji,
+nebot precedence cost opravdu potrebujem az pro uceni!
+
+Teda vlastne by mi nevadilo o tom mluvit zde, (az na to, ze rozcestnik drive rika
+``Sorting converts the symbol costs into a symbol precedence.
+It is only used in generating mode.'')
+
+ale to vyzneni, kde to vypada, ze to delame kvuli tomu sortu, je matouci.
+
+Predstavuju si odstavec, kde rikame, ze precedence cost je dulezity koncept,
+protoze ma jednak tu vlastnost, ze je minimalizovan sortenim
+ale druhak prirazuje cost i nesetridenym permutacim a tak ho muzem pouzit pri uceni.
+(Coz by splnoval i jiny vzorecek nez \eqref{eq:cost_model}), namely
+jina striktne monotonni funkce na pronasobeni nez to $i$ tam,
+ale berem proste tenhle, protoze neni jasne, proc by jiny mel byt lespi,
+a tenhle je nejjednodussi.)}
+
+\subsubsection{Precedence cost} \todo{MS: subsubsections jsou trochu e-e}
+
 We extend the notion of cost from symbols to precedences
@@
 weighted by their positions in the given precedence $\pi$:
-$$
+\begin{equation} \label{eq:cost_model}
 C(\pi) = Z_n \sum_{i=1}^n i \cdot c(\pi(i))% We call the normalization factor Z_n to follow convention from Foundations of Machine Learning, p. 122.
-$$
+\end{equation}
 $Z_n = \frac{2}{n(n+1)}$ is a normalization factor
@@
 
-\subsubsection{Cost minimization by sorting}
+\subsubsection{Cost minimization by sorting} \todo{MS: subsubsections jsou trochu e-e}
+\todo{MS: tady spis chybi rict, proc to lema vybev potrebujem.}
 \begin{lemma}

### 2021-02-24 architecture.tex
zbytek poznamek k sekci 3

@@
 
-\subsection{System overview}
+\subsection{System overview} \todo{MS: tuhle subsekci by slo zrusit a usetriti misto. Rozcestnik je beztak neco ``meta''.}
 
@@
 = \mathbb{E}_i [c(i)]
-\end{multline*}
+\end{multline*} \todo{MS: jeste jsem zapomnel napsat, ze tenhle vzorecek je hezky!}
 
@@
 it is not feasible to determine the best precedence conclusively on most practical problems.
+\todo{MS: libi se mi, ze tu je tenhle vysvetlujici odstavec!}
 Instead of learning to classify one or more precedences on each problem as the best,
+\todo{MS: To by asi stejne nepomohlo. Protoze jak pak ty dobre hledat pro novy problem?}
+\todo{MS: ale dalo by se znimit, ze v PAAR paperu jsme na to zkusili jit \emph{regresi} (as opposed to classification),
+tj predikovat primo nejakou real-valued kvalitu kazde konkretni precedence.}
 we train the system to decide which of a pair of arbitrary precedences is better.
@@
 \todo{FB: Argue better.}
+\todo[inline]{MS: ta druha myslenka, o ktere jsem mluvil pred obedem, se deje nekde v tomhle odstavci.
+Jasne je, ze chceme vypichnout uceni ze dvojic precedenci jako jeden z klicovych napadu. Trochu min jasne je, proc by teda dvojice mely byt dobre.
+Ja mel pocit, ze kdyz jsme se vloni snazili na tenhle problem napasovat regresi, 
+pusobilo ``neprirozene'' vnucovat modelu konkretni cisla z vampiru. Jasne, nejak to resila normalizace
+(a muselo se davat pozor aby cisla davala smysl nejen napric problemy (jeden resi vsechno rychle, jiny obcas neresi -- penalizace)
+ale i kvuli ruznym velikostem signatury. Coz teda tady mame porad.) ale porad tam bylo to, ze nejak z vnejsku
+modelu narizujeme, na ktere hodnoty ma cilit.
+My tady ale vime, ze nam na konkretnich hodnotach sybol costu nezalezi, 
+a ze ani nemusi byt rozumne porovnavatelne mezi problemy,
+jediny, co je dulezity, je, aby setridena permutace byla ta (to the best of model's knowledge) nejlepsi.
+Takze ja bych shrnul, ze s dvojicema obchazime nutnost stanovovat konkretni target values pro regresi (``problem volby spolecnych jednotek velicin''?)
+a zaroven rafinovane menime ulohu z regresivni na classifikacni. }
 
@@
 We classify the examples, sure, but you did not say it yet.\\
-FB: Is it ok to mention binary classification for the first time here if we cite \cite{Mohri2018} immediately?}
-\todo[inline]{MS: [...] pisem
-``binary'' a ``classification'' a neni tu jasny, co je ``binary''
-a co jsou ``classes''. Z pohledu ctenare, ktery o tom zatim neslysel, se misto ``binary classficiation model'' mohlo
-psat ``housenka'' a vyslo by to pro nej na stejno.}
+FB: Is it ok to mention binary classification for the first time here if we cite \cite{Mohri2018} immediately?
+MS: I think so!}
 \begin{align*}
@@
 Intuitively, by training on the example $(P, \PrecBetter, \PrecWorse)$
-we are pushing $C(\PrecBetter)$ down and $C(\PrecWorse)$ up.
+we are pushing $C(\PrecBetter)$ down and $C(\PrecWorse)$ up.\todo{MS: super, tohle mi takhle nejak nahlas nikdy nedoslo :)}
 
 The loss function is clearly differentiable with respect to the symbol costs,
-\todo{Shall we include the derivative?}
+\todo{Shall we include the derivative? MS: Spis ne.}
 and the symbol cost function $c$ is differentiable with respect to its trainable parameters.

### 2021-02-24 evaluation.tex
Improve some wording
Add and extend some todos
some initial comments to experiments

@@
 % !TEX root = main.tex
+
+\todo[inline]{FB: Scan through this section and make sure we use "we" form and past tense consistently.}
 
@@
 \todo{FB: Add some wrapper scripts and readme for ease of use.}
+\todo{MS: Obycejne schovavan URL do footnote, at tolik netrci!
+Taky se da zkratit, napriklad pomoci \url{git.io}.}
 
@@
 the Linux kernel 5.4.0-40-generic.
+\todo{FB: Add version of Python and notable packages, namely DGL and TensorFlow. 
+MS: Z tohohle bych vetsinu nebo vsechno prenesl do README na adrese vyse.
+Stejne ten paper neobsahuje dost informaci na to, aby si to mohl po nas nekdo naprogramovat a spustit.
+Tak uz muze byt uplne jedno, jakou mame verzi Linuxu...}
 
@@
 The modified version of \Vampire{} is available at the following URL:
-\url{https://github.com/filipbartek/vampire/tree/3bbfa9e6}
-
-\todo[inline,author=MS]{Literal comparison mode is not a standard thing.
-Mentioning the option name is again too low level.
-Explaining the effect (point two) is appropriate, although a bit too vague.
-To kdyztak opravim ja.
-Popsat presne setup je dulezite, kvuli reprodukovatelnosti, ale ne nutne primo v clanku (budem nejspis stejne dodavat odkaz na nejake reproducibility repo).
-Ted zminit AVATAR je nevhodne, pokud nevysvetlis, co to aspon ramcove je.
-A pokud to budes vysvetlovat, je otazka, proc tim ztracet misto, kdyz to neni bezprostredne relevantni pro dalsi vysvetlovani.}
+\url{https://github.com/filipbartek/vampire/tree/3bbfa9e6} \todo{MS: nebo jeste lip. Slo by udelat repo, 
+ve kterym bude textak, co vsechno vysvetli, vcetne linku na ty dve repa co zminujes tady a vyse.}
 
@@
 using the regular \gls{kbo} to break ties between atoms
-and to compare terms.
+and to compare terms (using the \Vampire{} option \texttt{-literal\_comparison\_mode predicate}).\todo{MS: ted s vysvetlenim neni naskodu zminit i option name 
+``Vampire'' se tim chlubi, ze to ma naimplementovane a my tim rikame, ze jsme si to neprogramovali sami.}
 \todo[inline,author=FB]{Describe the detailed configuration in an appendix and reference the appendix here.}
@@
 
-\subsubsection{Sampling}
+\subsubsection{Examples generation}
 
@@
 
-To ensure the efficiency of the sampling, the process is interpreted as an instance of Bernoulli multi-armed bandit problem,
-\todo{Cite? MS: kdyz bude dobra citace, sem by se urcite sikla:) Pri nejhorsim Sutton \& Barto to jisti.}
+To ensure the efficiency of the sampling, the process is interpreted as an instance of Bernoulli multi-armed bandit problem \cite{Sutton1998},
 with the reward of a trial being 1 in case an example is produced, and 0 otherwise.
@@
 The sampling runs until a target number of examples is generated---\num{1000000} predicate precedence examples and \num{800000} function precedence examples.
+\todo{FB: Prevent confusion of dash for minus.}
 % sftp://cluster.ciirc.cvut.cz/home/bartefil/git/vampire-ml/out/20210108-generate-predicate/questions_generated
@@
 
-\subsubsection{Split}
+\subsubsection{Validation split}
 

### 2021-02-24 evaluation.tex
upravy v Experimentech

@@
 % !TEX root = main.tex
+
+% Subsubsekce muzem "odresit" napriklad takto:
+\renewcommand{\subsubsection}{\paragraph}
 
@@
 We tuned the hyperparameters by a small manual grid search.
-\todo[inline]{MS: zase pasivum.
-Tady to urcite bude chtit odkaz na sekci, kde se jasne definuje, co to znamena.
-Jinak recenzenti byvaji dost alergicti na hyperpametry, ktere se jen tak nahodi na nevysvetli.
-Minimalne nejaky komentar typu: treba, zkouseli jsme u ruzne dalsi hodnoty, ale dopadalo to podobne.
-Nebo, pozdeji rekeneme, co se deje, kdyz se tohle meni.
-Nebo: nemeli jsme cas zjistovat, co se deje, kdyz se to meni, tak berem rozumne hodnoty podle blabla.}
+\todo{MS: hezky!}
 
@@
 The results are averaged over 5 runs to reduce the effect of noise due to the wall clock time limit.
-As a baseline, the performance of \Vampire{} with the \texttt{frequency} precedence heuristic was evaluated
-with the same time limit.
+As a baseline, the performance of \Vampire{} with the \texttt{frequency} precedence heuristic\footnote{
+This is \Vampire{}'s analogue of the \texttt{invfreq} scheme in E \cite{E-manual}.}
+was evaluated with the same time limit.
 For comparison, the two trained recommenders are evaluated separately,
@@
 vztahnout k casu klauzifikace? Jako rict, ze to trva x-krat dyl nez jen klauzifikovat?}
+
 \Cref{tab:results} shows the results.
@@
 The \gls{gcn} models are trained according to the description in \cref{sec:architecture,sec:evaluation}.
-The simple model is the final model from \cite{DBLP:conf/cade/Bartek020}.
+The model Simple is the final model from our previous work \cite{DBLP:conf/cade/Bartek020}.
 The models that use machine learning for the predicate precedence only
@@
 \iftoggle{LONG}{
+\todo[inline]{MS: kdyz bude misto, dal bych to driv. Souhlasim, ze kdyz se budu zahazovat, tak spolecne s odstavcem "Metrics" drive.}
 In the process of training,

### 2021-02-24 preliminaries.tex
Improve Preliminaries

@@
 
-The common saturation-based \glspl{atp} structure the proof search
+%The common saturation-based \glspl{atp} structure the proof search
+Since the space of the derivable clauses is typically very large,
+the efficacy of the prover depends on the order in which the inferences are applied.
+The common saturation-based \glspl{atp} order the inferences
 by maintaining two classes of the inferred clauses: processed and unprocessed \cite{10.1007/978-3-030-29436-6_29}.
@@
  ``pocet iteraci nez se najde dukaz''. aby se pak pouzilo dale\dots
-Nicmene ctu ted beginning->end, tak nevim, co chystas dale. }
+Nicmene ctu ted beginning->end, tak nevim, co chystas dale.\\
+FB: Doplnil jsem motivaci do prvni vety odstavce.}
 
@@
 a permutation of the non-logical symbols of the input problem.
-In this work we focus on finding a symbol precedence which 
+In this work we focus on the task of finding a symbol precedence which
 leads to a good performance of an ATP
@@
 Each of the components of the output vector is called a \emph{unit} of the module.
-The output of each module is differentiable with respect to the input.
-\todo{MS: mozna bych byl opetrnejsi. Co ReLU a derivace v bode zlomu? ;)}
+The output of each module is differentiable with respect to the input almost everywhere.
+\todo{FB: Should we explain why "almost everywhere" suffices?}
 
@@
 using each example in the training set exactly once.
-
-\todo{MS: Hezke! Ted uz v arichtekture muzes mavat pojmy o neuronkach a bude to tu uktovne! }

### 2021-02-24 architecture.tex
Improve Architecture
Resolve main points by MS. Reference RankNet.
Move training into a dedicated section (out of Architecture).

@@
 % !TEX root = main.tex
-
-\todo{Advantage of using pairs of precedences: we need to solve classification rather than regression.}
-\todo{Intuice: snazime se nastavit costy tak, aby co nejvic dvojic dopadlo spravne.}
-\todo{Some pairs of precedences are not informative. We hope that the non-systematic examples will cancel each other out.}
-
-\subsection{System overview} \todo{MS: tuhle subsekci by slo zrusit a usetriti misto. Rozcestnik je beztak neco ``meta''.}
 
@@
 For the recommender to be useful, it needs to produce a precedence
-that solves the input problem in a timely fashion.
-\todo{MS: Ja vim, ze uz je to nuda psat ty dlouhy a presny vety,
-ale ``timely fashion'' uz je mozna moc neformalni a
-a ``precedence does not solve a problem''.}
+that, when presented to an \gls{atp} along with the problem $P$,
+yields a proof in few iterations of the saturation loop.
 
@@
 they order the symbols by a numeric property, such as arity or number of occurrences.
-\todo{MS: super!}
 
@@
 whose values can be trained by gradient descent.
-\todo{MS: tady mi to ted (po neuralnim prelim) uz prijde asi dobry!}
-\todo[inline]{MS: chapu ucel (a vidim, ze dalsi veta navazuje na ``parameters'', ale je to kostrbate.
-Recommender = system, chapu jako program. Programy vetsinou neparametrizujeme tenzorama a gradient descent zije na jine urovni,
-nez aby parametrizovane programy primo ucil. Uceni je spis nejaka technologie, kterou recommender pouziva, aby ... ``produces precedences
-that are likely to yield a successful proof''.  }
 The goal of the training is to find parameter values such that the recommender produces precedences
-that are likely to yield a successful proof in as few iterations of the saturation loop as possible.
+that are likely to yield a proof in as few iterations of the saturation loop as possible.
 \todo{MS: o dost lespi verze v podstate te samy vety z konce prvniho odstavnce "System overview"}
@@
 \begin{itemize}
-\item \Cref{sec:graphifier}: A graph constructor converts the input \gls{cnf} problem into a problem graph.
-\item \Cref{sec:gcn}: \Gls{gcn} converts a problem graph into symbol embeddings.
-\item \Cref{sec:output}: An output function converts the symbol embeddings into a vector of symbol costs.
-\item \Cref{sec:ranking}: Sorting converts the symbol costs into a symbol precedence.
-It is only used in generating mode.
-\item \Cref{sec:training}: Loss function converts the symbol costs and a pair of precedences into a loss value.
-It is only used in training mode.
-\todo{MS: je to schalne, ze tam mas vsude ``converts''? V nekterych bodech by asi byla k dispozici prilehavejsi slova.
-Treba sorting converts uz zni trochu sroubovane. }
+\item \Cref{sec:graphifier}: The graph constructor transforms the input \gls{cnf} problem into a problem graph.
+\item \Cref{sec:gcn}: The \gls{gcn} computes symbol embeddings from the problem graph.
+\item \Cref{sec:output}: The output function extracts symbol costs from the symbol embeddings.
+\item \Cref{sec:sorting}: The final symbol precedence is obtained by sorting the symbols by their costs.
 \end{itemize}
@@
 h_d^{(l+1)} =
-\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (W_r^{(l)} h_s^{(l)} + b_r^{(l)})}.
+\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (W_r^{(l)} h_s^{(l)} + b_r^{(l)})}
 $$
@@
 which is an affine transformation with no activation function.
-\todo{FB: Is this clear at this point? MS: jj, ted uz jo!}
 
@@
 we refer to the predicted cost of $s_i$ simply as $c(i)$
-because the problem $P$ and the parameters $\theta$ are fixed in each respective context.\todo{MS: I like.}
+because the problem $P$ and the parameters $\theta$ are fixed in each respective context.
 
 \subsection{Sorting: From symbol costs to precedence}
+\label{sec:sorting}
+
+The symbol precedence heuristics commonly used in the \glspl{atp} sort the symbols by some numeric property
+that is inexpensive to compute,
+such as the number of occurrences in the input problem, or the symbol arity.
+In our precedence recommender,
+we use a \gls{gcn}-based symbol cost model $c$ in place of the simple symbol property,
+and generate a precedence by sorting the symbols by their predicted costs.
+The advantages of this scheme are that
+sorting is a fast operation,
+and that it allows training the underlying symbol costs by gradient descent,
+as \cref{sec:training} explains in detail.
+
+%Note that a precedence that minimizes $C$
+%orders the symbols with the lowest cost as the last, prioritizing them for early inferences.
+
+\section{Training procedure}
+\label{sec:training}
+
+In \cref{sec:architecture} we described the structure of a recommender system that generates a symbol precedence for an arbitrary input problem.
+The efficacy of the recommender depends on the quality of the underlying symbol cost function $c$.
+In theory, the symbol cost function can assign the costs so that
+sorting the symbols by their costs yields an optimum precedence.
+Furthermore, all the information necessary to determine the optimum precedence is present in the graph representation of the input problem
+thanks to the lossless property of the graph encoding.
+\todo{MS: Hlavne tady ale jakoby chybi druha pulky ty vety. Neco jako ``In practice, however, ...'' Nemyslis?} 
+Our approach to defining an appropriate symbol cost function is based on statistical learning
+from executions of an \gls{atp} on a set of problems with random precedences.
+
+To train a useful symbol cost function $c$,
+we define a precedence cost function $C$ on top of $c$
+in a way that ensures that minimizing $C$ corresponds to sorting the symbols by $c$,
+so that finding the precedence that minimizes $C$ can be done efficiently and precisely.
+Then we proceed to train $C$ on the proxy task of ranking the precedences.
+
+% We have:
+% Data allows us to tell whether pi < rho.
+% We need the symbols sorted by c be a good precedence.
+
+\subsection{Precedence cost}
+
+%Sorting a vector $x$ of length $n$ in a non-increasing order corresponds to finding a permutation $\pi$ that minimizes
+%the sum of the components of $x$ weighted by their positions in $\pi$.
+%By defining the cost of a precedence as a measure that is minimized by sorting,
+%we obtain a practical notion that can ultimately be trained by gradient descent.
+
+We extend the notion of cost from symbols to precedences
+by taking the sum of the symbol costs
+weighted by their positions in the given precedence $\pi$:
+\begin{equation*} \label{eq:cost_model}
+C(\pi) = Z_n \sum_{i=1}^n i \cdot c(\pi(i))% We call the normalization factor Z_n to follow convention from Foundations of Machine Learning, p. 122.
+\end{equation*}
+\todo[inline]{FB: Consider accessing elements $\pi$ as vector elements $\pi_i$ instead of $\pi(i)$.
+Keep in mind that $\inv{\pi}$ must be updated as well.
+The motivation for using $\pi(i)$ is that $\inv{\pi}(i)$ looks clearer than $\inv{\pi}_i$.
+How about using $(\inv{\pi})_i$?
+We may also omit the inversion completely.}
+\todo{FB: Consider using the terminology of RankNet: $C(\pi) = o_i$, $S(\pi, \rho) = o_{ij}$, $\loss = C_{ij}$}
+$Z_n = \frac{2}{n(n+1)}$ is a normalization factor
+that ensures the commensurability of precedence costs across signature sizes.
+More precisely, normalizing by $Z_n$ makes the expected value of the precedence cost
+independent of the signature size $n$:
+\begin{multline*}
+\mathbb{E}_\pi [C(\pi)]
+= \mathbb{E}_\pi \SquareBracket{Z_n \sum_{i=1}^n i \cdot c(\pi(i))}
+= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_{\pi, i} [c(\pi(i))] \\
+= Z_n \Parentheses{\sum_{i=1}^n i} \mathbb{E}_i [c(i)]
+= \frac{2}{n(n+1)} \frac{n(n+1)}{2} \mathbb{E}_i [c(i)]
+= \mathbb{E}_i [c(i)]
+\end{multline*}
+
+When $C$ is defined in this way,
+the precedence produced by the recommender (see \cref{sec:sorting}) minimizes $C$.
+
+\begin{lemma}
+Precedence cost $C$ is minimized by any precedence that sorts the symbols by their costs in non-increasing order:
+$$
+\argmin_\rho C(\rho) = \argsort^- (c(1), \ldots, c(n))
+$$
+where $\argsort^-(x)$ is the set of permutations $\pi$
+that sort vector $x$ in non-increasing order ($x_{\pi(1)} \geq x_{\pi(2)} \geq \ldots \geq x_{\pi(n)}$).
+\end{lemma}
+
+\begin{proof}
+We prove direction ``$\argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$'' by contradiction.
+Let $\pi$ minimize $C$ and let $\pi$ not sort the costs in non-increasing order.
+Then there exist $k < l$ such that $c(\pi(k)) < c(\pi(l))$.
+Let $\bar{\pi}$ be a precedence obtained from $\pi$ by swapping the elements $k$ and $l$.
+Then we obtain
+%$\bar{\pi} = (\pi(1), \ldots, \pi(k-1), \pi(l), \pi(k+1), \ldots, \pi(l-1), \pi(k), \pi(l+1), \ldots, \pi(n))$.
+\begin{align*}
+\frac{C(\bar{\pi}) - C(\pi)}{Z_n}
+&= kc(\bar{\pi}(k)) + lc(\bar{\pi}(l)) - kc(\pi(k)) - lc(\pi(l)) \\
+&= kc(\pi(l)) + lc(\pi(k)) - kc(\pi(k)) - lc(\pi(l)) \\
+&= k(c(\pi(l)) - c(\pi(k))) - l(c(\pi(l)) - c(\pi(k))) \\
+&= (k-l) (c(\pi(l)) - c(\pi(k))) \\
+&< 0
+\end{align*}
+\todo{FB: Isn't the inclusion of $Z_n$ too confusing?}
+The final inequality is because $k-l < 0$ and $c(\pi(l)) - c(\pi(k)) > 0$.
+Clearly, $Z_n > 0$ for any $n \geq 0$.
+Thus, $C(\bar{\pi}) < C(\pi)$, which is contradicts the assumption that $\pi$ minimizes $C$.
+
+It is easy to see that all the precedences that sort the symbol costs in a non-increasing order
+have the same precedence cost.
+Since $\emptyset \neq \argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$,
+each of the precedences in $\argsort^- (c(1), \ldots, c(n))$ has the cost $\min_\rho C(\rho)$.
+It follows that $\argsort^- (c(1), \ldots, c(n)) \subseteq \argmin_\rho C(\rho)$.
+\qed
+\end{proof}
+
+\todo[inline]{FB: Discuss that sorting would minimize even if we weighted by a strictly monotonous function other than identity.}
+
+\todo[inline]{FB: Why is the equality predicate always the first in the precedence?
+MS: Andrei Voronokov reasons. It's typically better in practice to postpone equational reasoning,
+so we want equalities to be generally small.}
+
+\subsection{Learning to rank precedences}
 \label{sec:ranking}
+
+Our ultimate goal is to train the precedence cost function $C$ so that it is minimized by the best precedence,
+measuring the quality of a precedence by the number of iterations of the saturation loop taken to solve the problem.
+Approaching this task directly as a regression problem
+runs into the difficulty of establishing sensible target cost values for the precedences in the training dataset,
+especially when a wide variety of input problems is covered.
+Approaching the task as binary classification of precedences offers some promising options,
+such as learning to detect the precedences that yield a successful proof search within the allocated time.
+However, we cast the task as an instance of score-based ranking problem \cite{Mohri2018,Burges2005}
+% Mohri2018: p. 239, chapter 10 Ranking
+by training a classifier to decide which of a pair of precedences is better based on their costs.
+We train the classifier in a way that ensures that better precedences are assigned lower costs.
+The motivation for learning to order pairs of precedences
+is that it allows learning on easy problems,
+and that it may allow the system to generalize to precedences that are better than any of those seen during training.
+\todo{FB: We should test this hypothesis by training on one problem in isolation.}
+\todo[inline]{MS: ta druha myslenka, o ktere jsem mluvil pred obedem, se deje nekde v tomhle odstavci.
+Jasne je, ze chceme vypichnout uceni ze dvojic precedenci jako jeden z klicovych napadu. Trochu min jasne je, proc by teda dvojice mely byt dobre.
+Ja mel pocit, ze kdyz jsme se vloni snazili na tenhle problem napasovat regresi, 
+pusobilo ``neprirozene'' vnucovat modelu konkretni cisla z vampiru. Jasne, nejak to resila normalizace
+(a muselo se davat pozor aby cisla davala smysl nejen napric problemy (jeden resi vsechno rychle, jiny obcas neresi -- penalizace)
+ale i kvuli ruznym velikostem signatury. Coz teda tady mame porad.) ale porad tam bylo to, ze nejak z vnejsku
+modelu narizujeme, na ktere hodnoty ma cilit.
+My tady ale vime, ze nam na konkretnich hodnotach sybol costu nezalezi, 
+a ze ani nemusi byt rozumne porovnavatelne mezi problemy,
+jediny, co je dulezity, je, aby setridena permutace byla ta (to the best of model's knowledge) nejlepsi.
+Takze ja bych shrnul, ze s dvojicema obchazime nutnost stanovovat konkretni target values pro regresi (``problem volby spolecnych jednotek velicin''?)
+a zaroven rafinovane menime ulohu z regresivni na classifikacni.\\
+FB: Regrese $C$ neni jedina alternativa.
+Mohli bychom klasifikovat jednotlive precedence (viz text).
+Mohli bychom relaxovat pozadavek, ze setridena permutace je nejlepsi; stacila by "dost dobra".
+Zkusil jsem nejak vyargumentovat, proc je klasifikace dvojic lepsi nez klasifikace jednotlivych precedenci.}
+
+\todo{Intuice: snazime se nastavit costy tak, aby co nejvic dvojic dopadlo spravne.}
+\todo{Some pairs of precedences are not informative. We hope that the non-systematic examples will cancel each other out.}
 
@@
 
-\subsubsection{Precedence cost} \todo{MS: subsubsections jsou trochu e-e}
-
-We extend the notion of cost from symbols to precedences
-by taking the sum of the symbol costs
-weighted by their positions in the given precedence $\pi$:
-\begin{equation} \label{eq:cost_model}
-C(\pi) = Z_n \sum_{i=1}^n i \cdot c(\pi(i))% We call the normalization factor Z_n to follow convention from Foundations of Machine Learning, p. 122.
-\end{equation}
-$Z_n = \frac{2}{n(n+1)}$ is a normalization factor
-that ensures the commensurability of precedence costs across signature sizes.
-More precisely, normalizing by $Z_n$ makes the expected value of the precedence cost
-independent of the signature size $n$:
-\begin{multline*}
-\mathbb{E}_\pi [C(\pi)]
-= \mathbb{E}_\pi \SquareBracket{Z_n \sum_{i=1}^n i \cdot c(\pi(i))}
-= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_{\pi, i} [c(\pi(i))] \\
-= Z_n \Parentheses{\sum_{i=1}^n i} \mathbb{E}_i [c(i)]
-= \frac{2}{n(n+1)} \frac{n(n+1)}{2} \mathbb{E}_i [c(i)]
-= \mathbb{E}_i [c(i)]
-\end{multline*} \todo{MS: jeste jsem zapomnel napsat, ze tenhle vzorecek je hezky!}
-
-\todo[inline]{FB: Consider accessing elements $\pi$ as vector elements $\pi_i$ instead of $\pi(i)$.
-Keep in mind that $\inv{\pi}$ must be updated as well.
-The motivation for using $\pi(i)$ is that $\inv{\pi}(i)$ looks clearer than $\inv{\pi}_i$.
-How about using $(\inv{\pi})_i$?
-We may also omit the inversion completely.}
-
-\subsubsection{Cost minimization by sorting} \todo{MS: subsubsections jsou trochu e-e}
-\todo{MS: tady spis chybi rict, proc to lema vybev potrebujem.}
-\begin{lemma}
-Precedence cost $C$ is minimized by the precedence that sorts the symbols by their costs in non-increasing order:
-$$
-\argmin_\pi C(\pi) \in \argsort^- (c(1), \ldots, c(n))
-$$
-where $\argsort^-(x)$ is the set of permutations $\rho$ that sort vector $x$ in non-increasing order ($x_{\rho(1)} \geq x_{\rho(2)} \geq \ldots \geq x_{\rho(n)}$).
-\end{lemma}
-
-\begin{proof}
-We prove the lemma by contradiction.
-Let $\pi$ minimize $C$ and let $\pi$ not sort the costs in non-increasing order.
-Then there exist $k < l$ such that $c(\pi(k)) < c(\pi(l))$.
-Let $\bar{\pi}$ be a precedence obtained from $\pi$ by swapping the elements $k$ and $l$.
-Then we obtain
-%$\bar{\pi} = (\pi(1), \ldots, \pi(k-1), \pi(l), \pi(k+1), \ldots, \pi(l-1), \pi(k), \pi(l+1), \ldots, \pi(n))$.
-\begin{align*}
-\frac{C(\bar{\pi}) - C(\pi)}{Z_n}
-&= kc(\bar{\pi}(k)) + lc(\bar{\pi}(l)) - kc(\pi(k)) - lc(\pi(l)) \\
-&= kc(\pi(l)) + lc(\pi(k)) - kc(\pi(k)) - lc(\pi(l)) \\
-&= k(c(\pi(l)) - c(\pi(k))) - l(c(\pi(l)) - c(\pi(k))) \\
-&= (k-l) (c(\pi(l)) - c(\pi(k))) \\
-&< 0
-\end{align*}
-\todo{FB: Isn't the inclusion of $Z_n$ too confusing?}
-The final inequality is because $k-l < 0$ and $c(\pi(l)) - c(\pi(k)) > 0$.
-Clearly, $Z_n > 0$ for any $n \geq 0$.
-Thus, $C(\bar{\pi}) < C(\pi)$, which is contradicts the assumption that $\pi$ minimizes $C$. \qed
-\end{proof}
-
-Once the symbol costs are known,
-producing a precedence that minimizes the precedence cost is cheap
-because sorting is a fast operation.
-
-Note that a precedence that minimizes $C$
-orders the symbols with the lowest cost as the last, prioritizing them for early inferences.
-
-\todo[inline]{FB: Why is the equality predicate always the first in the precedence?
-MS: Andrei Voronokov reasons. It's typically better in practice to postpone equational reasoning,
-so we want equalities to be generally small.}
-\todo[inline]{FB: Mention that the common heuristics fit this scheme.}
-
-\subsection{Training: Classification of pairs of precedences}
-\label{sec:training}
-
-In \cref{sec:graphifier,sec:gcn,sec:output,sec:ranking} we described the structure of a recommender system that generates a precedence for an arbitrary input problem.
-The efficacy of the recommender depends on the quality of the underlying symbol cost function.
-In theory, the symbol cost function can assign the costs so that
-sorting the symbols by their costs yields an optimum precedence.
-Furthermore, all the information necessary to determine the optimum precedence is present in the graph representation of the input problem
-thanks to the lossless property of the graph encoding mentioned before.
-\todo{MS: Hlavne tady ale jakoby chybi druha pulky ty vety. Neco jako ``In practice, however, ...'' Nemyslis?} 
-Our approach to defining an appropriate symbol cost function is based on statistical learning
-from executions of an \gls{atp} on a set of problems with random precedences.
-
-Our ultimate goal is to train the precedence cost function $C$ so that it is minimized by the best precedence,
-measuring the quality of a precedence by the number of iterations of the saturation loop taken to solve the problem.
-Since the number of possible precedences grows with the factorial of the signature size,
-it is not feasible to determine the best precedence conclusively on most practical problems.
-\todo{MS: libi se mi, ze tu je tenhle vysvetlujici odstavec!}
-Instead of learning to classify one or more precedences on each problem as the best,
-\todo{MS: To by asi stejne nepomohlo. Protoze jak pak ty dobre hledat pro novy problem?}
-\todo{MS: ale dalo by se znimit, ze v PAAR paperu jsme na to zkusili jit \emph{regresi} (as opposed to classification),
-tj predikovat primo nejakou real-valued kvalitu kazde konkretni precedence.}
-we train the system to decide which of a pair of arbitrary precedences is better.
-We do this by training $C$ so that better precedences are assigned lower costs.
-The motivation for learning to order pairs of precedences
-is that it may allow the system to generalize to precedences that are better than any of those seen during training.
-\todo{FB: We should test this hypothesis by training on one problem in isolation.}
-\todo{FB: Argue better.}
-\todo[inline]{MS: ta druha myslenka, o ktere jsem mluvil pred obedem, se deje nekde v tomhle odstavci.
-Jasne je, ze chceme vypichnout uceni ze dvojic precedenci jako jeden z klicovych napadu. Trochu min jasne je, proc by teda dvojice mely byt dobre.
-Ja mel pocit, ze kdyz jsme se vloni snazili na tenhle problem napasovat regresi, 
-pusobilo ``neprirozene'' vnucovat modelu konkretni cisla z vampiru. Jasne, nejak to resila normalizace
-(a muselo se davat pozor aby cisla davala smysl nejen napric problemy (jeden resi vsechno rychle, jiny obcas neresi -- penalizace)
-ale i kvuli ruznym velikostem signatury. Coz teda tady mame porad.) ale porad tam bylo to, ze nejak z vnejsku
-modelu narizujeme, na ktere hodnoty ma cilit.
-My tady ale vime, ze nam na konkretnich hodnotach sybol costu nezalezi, 
-a ze ani nemusi byt rozumne porovnavatelne mezi problemy,
-jediny, co je dulezity, je, aby setridena permutace byla ta (to the best of model's knowledge) nejlepsi.
-Takze ja bych shrnul, ze s dvojicema obchazime nutnost stanovovat konkretni target values pro regresi (``problem volby spolecnych jednotek velicin''?)
-a zaroven rafinovane menime ulohu z regresivni na classifikacni. }
-
 \subsubsection{Training data}
@@
 a loss function routinely used in classification tasks in \acrlong{ml}:
-\todo[inline]{MS: First mention of a ``binary classifier''!
-We classify the examples, sure, but you did not say it yet.\\
-FB: Is it ok to mention binary classification for the first time here if we cite \cite{Mohri2018} immediately?
-MS: I think so!}
 \begin{align*}
@@
 % To a skilled NN practitioner, it should now be obvious that the loss is differentiable w.r.t. $c$.
+\todo{FB: Consider exposing the form with inverse precedences to single out the $c$ values and expose the $c$ gradient better.}
 
@@
 Intuitively, by training on the example $(P, \PrecBetter, \PrecWorse)$
-we are pushing $C(\PrecBetter)$ down and $C(\PrecWorse)$ up.\todo{MS: super, tohle mi takhle nejak nahlas nikdy nedoslo :)}
+we are pushing $C(\PrecBetter)$ down and $C(\PrecWorse)$ up.
 
 The loss function is clearly differentiable with respect to the symbol costs,
-\todo{Shall we include the derivative? MS: Spis ne.}
 and the symbol cost function $c$ is differentiable with respect to its trainable parameters.

### 2021-02-24 evaluation.tex
Improve Architecture
Resolve main points by MS. Reference RankNet.
Move training into a dedicated section (out of Architecture).

@@
 
-To demonstrate the capacity of the trainable precedence recommender described in \cref{sec:architecture},
+To demonstrate the capacity of the trainable precedence recommender described in \cref{sec:architecture,sec:training},
 we performed a series of experiments.
@@
 A predicate symbol cost model is trained by gradient descent
-on the precedence pair classification task (described in \cref{sec:training})
+on the precedence pair classification task (described in \cref{sec:ranking})
 using the examples generated from the problems in $\ProblemsTrain$.
@@
 Means and standard deviations over 5 runs are reported.
-The \gls{gcn} models are trained according to the description in \cref{sec:architecture,sec:evaluation}.
+The \gls{gcn} models are trained according to the description in \cref{sec:architecture,sec:training,sec:evaluation}.
 The model Simple is the final model from our previous work \cite{DBLP:conf/cade/Bartek020}.

### 2021-02-24 architecture.tex
Improve wording of a paragraph

@@
 To train a useful symbol cost function $c$,
-we define a precedence cost function $C$ on top of $c$
-in a way that ensures that minimizing $C$ corresponds to sorting the symbols by $c$,
-so that finding the precedence that minimizes $C$ can be done efficiently and precisely.
-Then we proceed to train $C$ on the proxy task of ranking the precedences.
+we define a precedence cost function $C$ using the symbol cost function $c$
+in a manner than ensures that minimizing $C$ corresponds to sorting the symbols by $c$.
+Finding the precedence that minimizes $C$ can then be done efficiently and precisely.
+We proceed to train $C$ on the proxy task of ranking the precedences.
 

### 2021-02-24 evaluation.tex
Remove a resolved todo
Comment out obsolete content

@@
 and \num{1953} problems when training function precedence recommender.
-\todo{FB: Unify the terminology: validation, or train set?
-MS: Co by znamenalo unify? Nebo myslis test set?}
 % /home/filip/projects/vampire-ml/vampire-ml/outputs/2021-02-11/16-27-02/results.csv
@@
 
-\iftoggle{LONG}{
-%\subsubsection{Metrics}
-To analyze the training process,
-we tracked the dynamics of three metrics on $\ProblemsTrain$ and $\ProblemsVal$:
-loss, accuracy and solver performance.
-The solver performance was estimated once per 10 training epochs by running \Vampire{}
-on \num{1000} problems of the respective problem set
-and counting the number of problems successfully solved within the time limit.
-Since the accuracy is a proxy measure of solver performance and the loss is a proxy measure of the accuracy,
-we are interested in generalization from loss to accuracy and from both loss and accuracy to solver performance.
-Similarly, we are interested in generalization from training set to validation set.
-\todo{MS: kdyz se to tady tak pekne pripravi, asi ctenar ceka, ze se to pozdeji 
-nejak zuzitkuje. Pokud se rozhnodnem loss/accuracy/ATP zavislost dal nerozebirat,
-asi je tu navic i tento odstavec, nebo aspon jeho cast.}
-}
+%\iftoggle{LONG}{
+%%\subsubsection{Metrics}
+%To analyze the training process,
+%we tracked the dynamics of three metrics on $\ProblemsTrain$ and $\ProblemsVal$:
+%loss, accuracy and solver performance.
+%The solver performance was estimated once per 10 training epochs by running \Vampire{}
+%on \num{1000} problems of the respective problem set
+%and counting the number of problems successfully solved within the time limit.
+%Since the accuracy is a proxy measure of solver performance and the loss is a proxy measure of the accuracy,
+%we are interested in generalization from loss to accuracy and from both loss and accuracy to solver performance.
+%Similarly, we are interested in generalization from training set to validation set.
+%\todo{MS: kdyz se to tady tak pekne pripravi, asi ctenar ceka, ze se to pozdeji 
+%nejak zuzitkuje. Pokud se rozhnodnem loss/accuracy/ATP zavislost dal nerozebirat,
+%asi je tu navic i tento odstavec, nebo aspon jeho cast.}
+%}
 

### 2021-02-24 abstract.tex
Use \acrlong{ml} consistently

@@
 This paper describes and evaluates a symbol precedence recommender,
-a machine learning system that estimates the best possible precedence
+a \acrlong{ml} system that estimates the best possible precedence
 based on observations of prover performance on a set of problems and random precedences.

### 2021-02-24 evaluation.tex
Use \acrlong{ml} consistently

@@
 The model Simple is the final model from our previous work \cite{DBLP:conf/cade/Bartek020}.
-The models that use machine learning for the predicate precedence only
+The models that use \acrlong{ml} for the predicate precedence only
 use the \texttt{frequency} heuristic for the function precedence, and vice versa.

### 2021-02-24 introduction.tex
Use \acrlong{ml} consistently

@@
 
-In this work, we propose a machine learning system that learns to predict for an ATP
+In this work, we propose a \acrlong{ml} system that learns to predict for an ATP
 whether one precedence is going to lead to a faster proof search on a given problem than another.

### 2021-02-24 main.tex
Disable the SHRINK mode by default
because we currently fit in 15 pages anyway.
Improve Architecture
Resolve main points by MS. Reference RankNet.
Move training into a dedicated section (out of Architecture).
Use \acrlong{ml} consistently

@@
 \newtoggle{SHRINK}
-\toggletrue{LONG}
-%\togglefalse{SHRINK}
+%\toggletrue{SHRINK}
+\togglefalse{SHRINK}
 
@@
 
-Our previous text \cite{DBLP:conf/cade/Bartek020} marked the initial investigation of applying techniques of \gls{ml}
+Our previous text \cite{DBLP:conf/cade/Bartek020} marked the initial investigation of applying techniques of \acrlong{ml}
 to generating good symbol precedences.
@@
 
+\todo[inline]{FB: Mention RankNet.}
 \todo[inline]{Related problem: Ranking. See Mohri etc.}

### 2021-02-24 conclusion.tex
comments po 3.5
Minor corrections

@@
 to consider the whole structure of the input problem is beneficial.
-\todo{FB: Should we boast that the reduction of ranking to training of differentiable element scores is innovative?}
+\todo{FB: Should we boast that the reduction of ranking to training 
+of differentiable element scores is innovative? MS: Yes! Ideally (also) earlier.}
 
@@
 
-\gls{kbo}, that we choose in our experiments, is in addition to a symbol precedences
+\gls{kbo}, that we choose in our experiments, is in addition to a symbol precedence
 also determined by symbol \emph{weights} (we kept these fixed to the default value 1 in this work).
@@
 in one training batch.
+
+\todo{MS: ja bych asi delsi zaver nepsal, ani kdyz bude misto...}
 

### 2021-02-24 evaluation.tex
Minor corrections

@@
 skip connections \cite{Zhou2018}, and layer normalization \cite{Ba2016}.
-We tuned the hyperparameters by a small manual grid search.
-\todo{MS: hezky!}
+We tuned the hyperparameters by a small manual exploration.
 
@@
 use the \texttt{frequency} heuristic for the function precedence, and vice versa.
-The frequency models use the standard \texttt{frequency} heuristic implemented in \Vampire{}.
+The frequency model uses the standard \texttt{frequency} heuristic implemented in \Vampire{}.
 }

### 2021-02-24 introduction.tex
Minor corrections

@@
 
-Modern saturation-based Automatic Theorem Provers (ATPs) such as E \cite{SCV:CADE-2019}, SPASS \cite{DBLP:conf/cade/WeidenbachDFKSW09} 
+Modern saturation-based Automatic Theorem Provers (ATPs) such as E \cite{SCV:CADE-2019}, SPASS \cite{DBLP:conf/cade/WeidenbachDFKSW09},
 or \Vampire{} \cite{DBLP:conf/cav/KovacsV13}
@@
 
-Our recommender uses a graph convolutional neural network \cite{kipf2017semisupervised}
+Our recommender uses a relational graph convolutional neural network \cite{Schlichtkrull2017}
 to represent the problem structure. It learns from the ATP performance on selected problems

### 2021-02-24 architecture.tex
Shorten the introduction in Architecture

@@
 For the recommender to be useful, it needs to produce a precedence
-that, when presented to an \gls{atp} along with the problem $P$,
-yields a proof in few iterations of the saturation loop.
+that is likely to yield a proof in as few iterations of the saturation loop as possible.
 
 The recommender described in this section
-first computes a cost value for each symbol of the input problem,
+first uses a neural network to compute a cost value for each symbol of the input problem,
 and then orders the symbols by their costs in a non-increasing order.
 In this manner, the task of finding good precedences is reduced to the task
-of finding a good symbol cost function.
-Note that the symbol precedence heuristics commonly used in the \glspl{atp}
-conform to this general scheme:
-they order the symbols by a numeric property, such as arity or number of occurrences.
-
-The architecture is designed so that the recommender can be trained
-on the results of \gls{atp} executions on various problems with random precedences.
-Since the recommender contains a neural network,
-it is parameterized by weight tensors
-whose values can be trained by gradient descent.
-The goal of the training is to find parameter values such that the recommender produces precedences
-that are likely to yield a proof in as few iterations of the saturation loop as possible.
-\todo{MS: o dost lespi verze v podstate te samy vety z konce prvniho odstavnce "System overview"}
+of training a good symbol cost function,
+as discussed in \cref{sec:training}.
+%The architecture is designed so that the recommender can be trained
+%on the results of \gls{atp} executions on various problems with random precedences.
+%Since the recommender contains a neural network,
+%it is parameterized by weight tensors
+%whose values can be trained by gradient descent.
 

### 2021-02-24 architecture.tex
Shorten the loss formulas by using multline
Fix a double space due to iftoggle command

@@
 The recommender consists of modules that perform specific subtasks,
-each of which is described in detail in one of the following
-\iftoggle{LONG}{
+each of which is described in detail in one of the following\iftoggle{LONG}{
 sections (see also \cref{fig:architecture}):
@@
 a loss function routinely used in classification tasks in \acrlong{ml}:
-\begin{align*}
+\begin{multline*}
 \loss(P, \PrecBetter, \PrecWorse)
-&= - \log \sigmoid S(\PrecBetter, \PrecWorse) \\
-&= - \log \sigmoid (C(\PrecWorse) - C(\PrecBetter)) \\
-&= - \log \sigmoid Z_n \sum_{i=1}^n i (c(\PrecWorse(i)) - c(\PrecBetter(i)))
-%&= - \log \sigmoid Z_n \sum_{i=1}^n c(i) (\inv{\PrecWorse}(i) - \inv{\PrecBetter}(i))
-\end{align*}
+= - \log \sigmoid S(\PrecBetter, \PrecWorse)
+= - \log \sigmoid (C(\PrecWorse) - C(\PrecBetter)) \\
+= - \log \sigmoid Z_n \sum_{i=1}^n i (c(\PrecWorse(i)) - c(\PrecBetter(i)))
+%= - \log \sigmoid Z_n \sum_{i=1}^n c(i) (\inv{\PrecWorse}(i) - \inv{\PrecBetter}(i))
+\end{multline*}
 % FB: Note: I have included the full expansion to make it visible how the loss depends on $c$.

### 2021-02-24 preliminaries.tex
Add some missing citations

@@
 because it is used in the most successful contemporary \gls{fol} \glspl{atp}.
-The inferences of superposition calculus are constrained by a \emph{\gls{sot}}.
+The inferences of superposition calculus are constrained by a \emph{\gls{sot}} \cite{DBLP:journals/logcom/BachmairG94}.
 
@@
 
-The \emph{\acrfull{kbo}}, a commonly used simplification ordering scheme,
+The \emph{\acrfull{kbo}} \cite{Knuth1983}, a commonly used simplification ordering scheme,
 is parameterized by symbol weights and a \emph{symbol precedence},

### 2021-02-24 architecture.tex
Move todos where they don't influence final typesetting

@@
 This reflects the symmetry of equality.
-\item \todo[inline]{MS: (Almost)} Perfect sub-expression sharing:
+\item Perfect sub-expression sharing:
+\todo[inline]{MS: (Almost)}
 \todo[inline]{MS: Predpokladam ze dva ruzne ground literaly p(c) tam budou taky jen jendnou?\\
@@
 weighted by their positions in the given precedence $\pi$:
-\begin{equation*} \label{eq:cost_model}
-C(\pi) = Z_n \sum_{i=1}^n i \cdot c(\pi(i))% We call the normalization factor Z_n to follow convention from Foundations of Machine Learning, p. 122.
-\end{equation*}
 \todo[inline]{FB: Consider accessing elements $\pi$ as vector elements $\pi_i$ instead of $\pi(i)$.
@@
 \todo{FB: Consider using the terminology of RankNet: $C(\pi) = o_i$, $S(\pi, \rho) = o_{ij}$, $\loss = C_{ij}$}
+\begin{equation*} \label{eq:cost_model}
+C(\pi) = Z_n \sum_{i=1}^n i \cdot c(\pi(i))% We call the normalization factor Z_n to follow convention from Foundations of Machine Learning, p. 122.
+\end{equation*}
 $Z_n = \frac{2}{n(n+1)}$ is a normalization factor
@@
 \end{align*}
-\todo{FB: Isn't the inclusion of $Z_n$ too confusing?}
 The final inequality is because $k-l < 0$ and $c(\pi(l)) - c(\pi(k)) > 0$.
 Clearly, $Z_n > 0$ for any $n \geq 0$.
+\todo{FB: Isn't the inclusion of $Z_n$ too confusing?}
 Thus, $C(\bar{\pi}) < C(\pi)$, which is contradicts the assumption that $\pi$ minimizes $C$.
@@
 a loss function routinely used in classification tasks in \acrlong{ml}:
+\todo{FB: Consider exposing the form with inverse precedences to single out the $c$ values and expose the $c$ gradient better.}
 \begin{multline*}
@@
 % To a skilled NN practitioner, it should now be obvious that the loss is differentiable w.r.t. $c$.
-\todo{FB: Consider exposing the form with inverse precedences to single out the $c$ values and expose the $c$ gradient better.}
 

### 2021-02-24 evaluation.tex
Restore the official subsubsection style
Join a very short paragraph to the previous paragraph
Move todos where they don't influence final typesetting

@@
 % Subsubsekce muzem "odresit" napriklad takto:
-\renewcommand{\subsubsection}{\paragraph}
+%\renewcommand{\subsubsection}{\paragraph}
 
@@
 \end{table*}
-\todo{FB: Add links to Neptune runs?}
 
 The results show that the \gls{gcn}-based model outperforms the \texttt{frequency} heuristic by a significant margin.
+\todo{FB: Add links to Neptune runs?}
 Since the predicate precedence recommender was trained against randomly distributed function precedences,

### 2021-02-24 evaluation.tex
Explain the importance of saturation loop iterations
Remove some useless content
Hide URLs into footnotes

@@
 The scripts that were used to generate the training data and to train and evaluate the recommender
-are available at the following URL:
-\url{https://github.com/filipbartek/vampire-ml/tree/6907ee35}
+are available online.\footnote{\url{https://github.com/filipbartek/vampire-ml/tree/6907ee35}}
 \todo{FB: Tag the version and link to the tag.}
 \todo{FB: Add some wrapper scripts and readme for ease of use.}
-\todo{MS: Obycejne schovavan URL do footnote, at tolik netrci!
-Taky se da zkratit, napriklad pomoci \url{git.io}.}
 
@@
 (normally, the user only picks a precedence generation heuristic).
-The modified version of \Vampire{} is available at the following URL:
-\url{https://github.com/filipbartek/vampire/tree/3bbfa9e6} \todo{MS: nebo jeste lip. Slo by udelat repo, 
+The modified version of \Vampire{} is available online.\footnote{\url{https://github.com/filipbartek/vampire/tree/3bbfa9e6}} \todo{MS: nebo jeste lip. Slo by udelat repo, 
 ve kterym bude textak, co vsechno vysvetli, vcetne linku na ty dve repa co zminujes tady a vyse.}
@@
 such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop (see \cref{sec:saturation}).
-\todo{FB: Justify saturation loop iterations as a proxy for success. MS: Ano, ale driv nez zde!}
 
@@
 % http://www.tptp.org/TPTP/SyntaxBNF.html
-\todo{FB: Consider joining with section Problem set below.}
 \Gls{fof} problems are first converted into equisatisfiable \gls{cnf} problems by \Vampire{}.

### 2021-02-25 evaluation.tex
Fix a citation of TPTP

@@
 
-The problem library \acrshort{tptp}~v7.4.0 \cite{10.1007/978-3-030-29436-6_29}
+The problem library \acrshort{tptp}~v7.4.0 \cite{Sutcliffe2017}
 was used as the source of problems for training and evaluation of the recommender,

### 2021-02-25 introduction.tex
Merge duplicit reference to the E paper

@@
 
-Modern saturation-based Automatic Theorem Provers (ATPs) such as E \cite{SCV:CADE-2019}, SPASS \cite{DBLP:conf/cade/WeidenbachDFKSW09},
+Modern saturation-based Automatic Theorem Provers (ATPs) such as E \cite{Schulz2019}, SPASS \cite{DBLP:conf/cade/WeidenbachDFKSW09},
 or \Vampire{} \cite{DBLP:conf/cav/KovacsV13}
@@
 The state-of-the-art \gls{fol} \glspl{atp},
-such as \Vampire{} \cite{10.1007/978-3-642-39799-8_1} and E \cite{10.1007/978-3-030-29436-6_29},
+such as \Vampire{} \cite{10.1007/978-3-642-39799-8_1} and E \cite{Schulz2019},
 are saturation-based and

### 2021-02-25 preliminaries.tex
Explain the importance of saturation loop iterations
Remove some useless content
Merge duplicit reference to the E paper

@@
 is reduced to proving that the axioms together with the negated conjecture entail a \emph{contradiction}.
-The most popular \gls{fol} \glspl{atp}, such as \Vampire{} \cite{10.1007/978-3-642-39799-8_1}, E \cite{10.1007/978-3-030-29436-6_29}, or SPASS \cite{DBLP:conf/cade/WeidenbachDFKSW09},
+The most popular \gls{fol} \glspl{atp}, such as \Vampire{} \cite{10.1007/978-3-642-39799-8_1}, E \cite{Schulz2019}, or SPASS \cite{DBLP:conf/cade/WeidenbachDFKSW09},
 start the proof search by converting the input \gls{fol} formulas to an equisatisfiable representation in 
@@
 
-%The common saturation-based \glspl{atp} structure the proof search
 Since the space of the derivable clauses is typically very large,
@@
 The common saturation-based \glspl{atp} order the inferences
-by maintaining two classes of the inferred clauses: processed and unprocessed \cite{10.1007/978-3-030-29436-6_29}.
+by maintaining two classes of the inferred clauses: processed and unprocessed \cite{Schulz2019}.
 In each \emph{iteration of the saturation loop}, one clause (so-called \emph{given clause})
@@
 The resulting new clauses are added to the unprocessed set.
+Finishing the proof in as few iterations of the saturation loop as possible is important
+because the number of inferred clauses typically grows exponentially during the proof search.
 

### 2021-02-25 preliminaries.tex
Shorten the paper to 15 pages

@@
 The resulting new clauses are added to the unprocessed set.
-Finishing the proof in as few iterations of the saturation loop as possible is important
+Finishing the proof in few iterations of the saturation loop is important
 because the number of inferred clauses typically grows exponentially during the proof search.

### 2021-02-25 architecture.tex
Fix the architecture diagram

@@
 When recommending a precedence, the input is problem $P$ and the output is precedence $\pi^*$.
-When training on an example, the input is problem $P$ and precedences $\pi$ and $\rho$,
-and the output is the loss value.}
+When training, the input is problem $P$ and precedences $\pi$ and $\rho$,
+and the output is the loss value.
+The edges along which the loss gradient is backpropagated and the trainable modules are shown bold.}
 \label{fig:architecture}
 \centering
-\digraph[scale=0.4]{ArchitectureOverview}{
-graph [splines=ortho,ranksep=0.2];
-node [shape=box, fontsize=20];
-edge [fontsize=20];
+\digraph[scale=0.5]{ArchitectureOverview}{
+graph [splines=ortho, ranksep=0.25];
+node [shape=box, fontsize=14, width=0, height=0];
 
-Problem [label="CNF problem P"];
+{ rank = same;
+Problem [label="Problem P"];
+pi [label=<Precedence &pi;> pos="10,10!"];
+rho [label=<Precedence &rho;>];
+}
+
 Graphifier [style=rounded, label="Graph constructor"];
 g [label="Graph"];
-GCN [style=rounded, label="GCN"];
+GCN [style=<rounded,bold>, label="GCN"];
 SymbolEmbedding [label="Symbol embeddings"];
-SymbolCostModel [style=rounded, label="Projection"];
+SymbolCostModel [style=<rounded,bold>, label="Output unit"];
+
+{ rank = same;
 SymbolCost [label="Symbol costs"];
+LossFunction [style=rounded, label="Loss function"];
+}
+
 Sort [style=rounded, label="Sort"];
-Precedence [label=<Output precedence &pi;*>];
 
-Problem -> Graphifier -> g -> GCN -> SymbolEmbedding -> SymbolCostModel -> SymbolCost -> Sort -> Precedence;
+{ rank = same;
+Precedence [label=<Precedence &pi;*>];
+Loss [label="Loss value"];
+}
 
-pi [label=<Precedence &pi;>];
-rho [label=<Precedence &rho;>];
-LossFunction [style=rounded, label="Loss function"];
-Loss [label="Loss value"];
+Problem -> Graphifier -> g -> GCN;
+GCN -> SymbolEmbedding -> SymbolCostModel -> SymbolCost [style=bold];
+SymbolCost -> Sort -> Precedence;
 
-pi -> LossFunction;
-rho -> LossFunction;
-SymbolCost -> LossFunction;
-LossFunction -> Loss;
+pi -> LossFunction:nw;
+rho -> LossFunction:ne;
+SymbolCost -> LossFunction [style=bold];
+LossFunction -> Loss [style=bold];
 }

### 2021-02-25 architecture.tex
Fix caption of CNF graph schema
Improve diagram of example graph

@@
 \begin{figure}[h]
-\caption{CNF network schema}
+\caption{\gls{cnf} graph schema}
 \label{fig:CnfSchema}
@@
 \centering
-\digraph[scale=0.3]{GcnExample}{
-	node [fontsize=32, shape=record];
-	edge [fontsize=32, dir=both, arrowtail=empty];
+\digraph[scale=0.5]{GcnExample}{
+graph [ranksep=0.3];
+node [fontsize=14, shape=record, height=0, width=0];
+edge [fontsize=14, dir=both, arrowtail=empty];
+
 problem [label=<problem|a=b &and; f(a,b)&ne;f(b,b)>];
+
+{ rank = same;
 c0 [label="clause|a=b"];
 c1 [label=<clause|f(a,b)&ne;f(b,b)>];
+}
+
 problem -> c0;
 problem -> c1;
+
+{ rank = same;
 t0 [label="equality atom|a=b"];
 t1 [label="equality atom|f(a,b)=f(b,b)"];
+}
+
 c0 -> t0 [label=" + "];
 c1 -> t1 [label=" &ndash; "];
+
+{ rank = same;
+tfab [label="term|f(a,b)"];
+tfbb [label="term|f(b,b)"];
+}
+
+{ rank = same;
 ta [label="term|a"];
 tb [label="term|b"];
+}
+
 ff [label="function|f", style=bold];
@@
 fb [label="function|b", style=bold];
-	tfab [label="term|f(a,b)"];
-	tfbb [label="term|f(b,b)"];
 tfab0 [label="argument|1", style=dotted];
@@
 tb -> fb;
+
+% Technical details:
+%ff -> ff [dir=forward];
+%fa -> fa [dir=forward];
+%fb -> fb [dir=forward];
 }

### 2021-02-25 architecture.tex
Remove unused diagram node position specification
Improve architecture diagram

@@
 Problem [label="Problem P"];
-pi [label=<Precedence &pi;> pos="10,10!"];
+pi [label=<Precedence &pi;>];
 rho [label=<Precedence &rho;>];
@@
 SymbolEmbedding [label="Symbol embeddings"];
-SymbolCostModel [style=<rounded,bold>, label="Output unit"];
+SymbolCostModel [style=<rounded,bold>, label="Output layer"];
+SymbolCost [label="Symbol costs"];
 
 { rank = same;
-SymbolCost [label="Symbol costs"];
+Sort [style=rounded, label="Sort"];
 LossFunction [style=rounded, label="Loss function"];
 }
-
-Sort [style=rounded, label="Sort"];
 
@@
 GCN -> SymbolEmbedding -> SymbolCostModel -> SymbolCost [style=bold];
-SymbolCost -> Sort -> Precedence;
+SymbolCost -> Sort;
+Sort -> Precedence;
 

### 2021-02-25 architecture.tex
Unify the style of the diagrams

@@
 \centering
+
+\digraph[scale=0.5]{CnfSchema}{
+graph [ranksep=0.3];
+node [fontsize=14, shape=box, height=0, width=0];
+edge [fontsize=14];
+
+problem;
+clause;
+%{ rank = same;
+predicate;
+atom;
+equality;
+%}
+argument;
+term;
+function;
+variable;
+
+problem -> clause [label=< contains >];
+clause -> atom:nw [label=< pos >];
+clause -> atom:ne [label=< neg >];
+clause -> equality:nw [label=< pos >];
+clause -> equality:ne [label=< neg >];
+clause -> variable [label=< binds >];
+atom -> predicate [label=< atom_applies>];
+atom -> argument [label=< atom_has >];
+equality -> term [label=< equalizes >];
+equality -> variable [label=< equalizes >];
+argument -> argument [label=< precedes >];
+argument -> term [label=< is >];
+argument -> variable [label=< is >];
+term -> argument [label=< term_has >];
+term -> function [label=< term_applies >];
+}
+
+\iffalse
 \tikzstyle{token} = [rectangle, draw]
@@
 \end{tikzpicture}
+\fi
+
 \end{figure}

### 2021-02-25 architecture.tex
Improve some content

@@
 \item \Cref{sec:gcn}: The \gls{gcn} computes symbol embeddings from the problem graph.
-\item \Cref{sec:output}: The output function extracts symbol costs from the symbol embeddings.
+\item \Cref{sec:output}: The output layer extracts symbol costs from the symbol embeddings.
 \item \Cref{sec:sorting}: The final symbol precedence is obtained by sorting the symbols by their costs.
@@
 
-\subsection{From \gls{cnf} to graphs}
+\subsection{Graph consutructor: From \gls{cnf} to graphs}
 \label{sec:graphifier}
@@
 This reflects the symmetry of equality.
-\item Perfect sub-expression sharing:
+\item Sub-expression sharing \cite{Chvalovsky2019,Olsak2019,Rawson2020}:
 \todo[inline]{MS: (Almost)}
@@
 MS: O to my, neslo. Slo o to, jestli se sdily ground termy mezi klauzulemi, ted uz dobry! :)}
-Redundant atoms and terms share a node representation.
+Identical atoms and terms share a node representation.
 \todo{FB: Cite some text about sub-expression sharing. Perhaps Rawson2020?}
@@
 
-\subsection{Sorting: From symbol costs to precedence}
+\subsection{Sort: From symbol costs to precedence}
 \label{sec:sorting}
@@
 that minimize the loss value.
+
+\Cref{fig:architecture} shows how the loss function is linked with the recommender.

### 2021-02-25 architecture.tex
Remove some content to shorten the text

@@
 FB: Chci vyjasnit, ze inverzni edge ma jiny edge type.}
-\item A singleton node of type \ntype{problem} is connected to all the clauses of the problem.
+%\item A singleton node of type \ntype{problem} is connected to all the clauses of the problem.
 \item The polarity of the literals is expressed by the type of the edge (\epos{} or \eneg{})
@@
 \todo{MS: Ale mezitim se to tu zmenilo a ja prestavam chapat, co je ``Redundant''!}
-Note that since each variable is bound by a clause,
-ground terms are shared across clauses,
-but non-ground terms are only shared within the context of a clause.
+%Note that since each variable is bound by a clause,
+%ground terms are shared across clauses,
+%but non-ground terms are only shared within the context of a clause.
 \todo{FB: Remove as of little interest?}

### 2021-02-25 evaluation.tex
Shorten the description of the evaluation machine
Shorten a paragraph to fit into 15 pages

@@
 All the experiments were run on a computer with
-the CPU Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz}),
-\SI{383}{GiB} RAM,
-the OS Ubuntu 20.04 and
-the Linux kernel 5.4.0-40-generic.
+the CPU Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz}) and
+\SI{383}{GiB} RAM.
+%the OS Ubuntu 20.04 and
+%the Linux kernel 5.4.0-40-generic.
 \todo{FB: Add version of Python and notable packages, namely DGL and TensorFlow. 
@@
 
-We have verified that the simple linear predicate precedence heuristic
+We have verified that the linear predicate precedence heuristic
 trained in \cite{DBLP:conf/cade/Bartek020} outperforms the \texttt{frequency} heuristic.
-Moreover, we have confirmed the conjecture that using a \gls{gnn} may yield an even better performance \cite{DBLP:conf/cade/Bartek020}.
+Moreover, we have confirmed the conjecture that using a \gls{gnn} may perform even better \cite{DBLP:conf/cade/Bartek020}.
 

### 2021-02-25 architecture.tex
Improve some wording

@@
 and the output is the loss value.
-The edges along which the loss gradient is backpropagated and the trainable modules are shown bold.}
+The trainable modules and the edges along which the loss gradient is propagated are emphasized by bold lines.}
 \label{fig:architecture}
@@
 
-\Cref{fig:architecture} shows how the loss function is linked with the recommender.
+\Cref{fig:architecture} shows how the loss function is plugged into the recommender for the training.

### 2021-02-25 abstract.tex
Resolve a line overflow

@@
 
-State-of-the-art superposition-based theorem provers for \acrlong{fol}
+The state-of-the-art superposition-based theorem provers for \acrlong{fol}
 rely on \glspl{sot} to constrain the applicability of inference rules,

### 2021-02-25 architecture.tex
Resolve remaining overfull lines

@@
 $$
-where $\argsort^-(x)$ is the set of permutations $\pi$
+where $\argsort^-(x)$ is the set of all permutations $\pi$
 that sort vector $x$ in non-increasing order ($x_{\pi(1)} \geq x_{\pi(2)} \geq \ldots \geq x_{\pi(n)}$).

### 2021-02-25 evaluation.tex
Resolve remaining overfull lines

@@
 
-The sampling runs until a target number of examples is generated---\num{1000000} predicate precedence examples and \num{800000} function precedence examples.
-\todo{FB: Prevent confusion of dash for minus.}
+The sampling runs until \num{1000000} examples are generated when training a predicate precedence recommender,
+or \num{800000} examples in case of function precedence recommender.
 % sftp://cluster.ciirc.cvut.cz/home/bartefil/git/vampire-ml/out/20210108-generate-predicate/questions_generated

### 2021-02-25 architecture.tex
mild tweaks

@@
 and generate a precedence by sorting the symbols by their predicted costs.
-The advantages of this scheme are that
-sorting is a fast operation,
-and that it allows training the underlying symbol costs by gradient descent,
-as \cref{sec:training} explains in detail.
+An advantage of this scheme is that sorting is a fast operation.
+
+Moreover, as we show in \cref{sec:training}, it is possible
+to train the underlying symbol costs by gradient descent.
 
@@
 sorting the symbols by their costs yields an optimum precedence.
-Furthermore, all the information necessary to determine the optimum precedence is present in the graph representation of the input problem
+This is because, at least in principle, all the information necessary 
+to determine the optimum precedence is present in the graph representation of the input problem
 thanks to the lossless property of the graph encoding.
@@
 Finding the precedence that minimizes $C$ can then be done efficiently and precisely.
-We proceed to train $C$ on the proxy task of ranking the precedences.
-
+We proceed to train $C$ on the proxy task of ranking the precedences.\todo{MS: Super!}
 % We have:
@@
 the precedence produced by the recommender (see \cref{sec:sorting}) minimizes $C$.
+\todo{Marting == for the camera ready version ==
+Write here that there could be alternavi formulas to \eqref{eq:cost_model}
+and we pick this one as the arguably simplest, for the lack of a better choice.}
 
@@
 measuring the quality of a precedence by the number of iterations of the saturation loop taken to solve the problem.
-Approaching this task directly as a regression problem
+
+Approaching this task directly, as a regression problem,
 runs into the difficulty of establishing sensible target cost values for the precedences in the training dataset,
@@
 % Mohri2018: p. 239, chapter 10 Ranking
-by training a classifier to decide which of a pair of precedences is better based on their costs.
+by training a classifier to decide which of a \emph{pair} of precedences is better, based on their costs.
 We train the classifier in a way that ensures that better precedences are assigned lower costs.

### 2021-02-25 architecture.tex
a major flip

@@
 especially when a wide variety of input problems is covered.
-Approaching the task as binary classification of precedences offers some promising options,
-such as learning to detect the precedences that yield a successful proof search within the allocated time.
-However, we cast the task as an instance of score-based ranking problem \cite{Mohri2018,Burges2005}
+Approaching the task as binary classification of precedences
+seems possible, but it is not clear which precedences should be a priory
+labeled as positive and which as negative, to give a guarantee
+that a precedence minizing the precedence cost (i.e. the one obtained by sorting)
+would be among the best in any good sense.
+% such as learning to detect the precedences that yield a successful proof search within the allocated time.
+
+We cast the task as an instance of score-based ranking problem \cite{Mohri2018,Burges2005}
 % Mohri2018: p. 239, chapter 10 Ranking

### 2021-02-25 architecture.tex
Correct some small grammar and typos

@@
 in a manner than ensures that minimizing $C$ corresponds to sorting the symbols by $c$.
-Finding the precedence that minimizes $C$ can then be done efficiently and precisely.
+Finding a precedence that minimizes $C$ can then be done efficiently and precisely.
 We proceed to train $C$ on the proxy task of ranking the precedences.\todo{MS: Super!}
@@
 Approaching the task as binary classification of precedences
-seems possible, but it is not clear which precedences should be a priory
+seems possible, but it is not clear which precedences should be a priori
 labeled as positive and which as negative, to give a guarantee
-that a precedence minizing the precedence cost (i.e. the one obtained by sorting)
+that a precedence minimizing the precedence cost (i.e. the one obtained by sorting)
 would be among the best in any good sense.

### 2021-02-25 architecture.tex
Remove a resolved todo
Add a todo

@@
 Finding a precedence that minimizes $C$ can then be done efficiently and precisely.
-We proceed to train $C$ on the proxy task of ranking the precedences.\todo{MS: Super!}
+We proceed to train $C$ on the proxy task of ranking the precedences.
 % We have:
@@
 would be among the best in any good sense.
+\todo{FB: I think we could ensure that the precedence that minimizes $C$ is relatively good, for example the best of the observed.
+I hope that ranking generalizes better to unseen precedences, but I am not sure whether it does and I haven't done an experiment to confirm that.}
 % such as learning to detect the precedences that yield a successful proof search within the allocated time.

### 2021-02-25 evaluation.tex
Clean up Evaluation
Use past tense consistently.
Use "we" form more often.

@@
 In this section, we describe the design and configuration of the experiments,
-and then compare the performance of several trained models to a number of baseline heuristics.
+and then compare the performance of several trained models to a baseline heuristic.
 
@@
 
-\Vampire{} was run with a time limit of 10 seconds.
+We run \Vampire{} with a time limit of 10 seconds.
 To increase the potential impact of predicate precedences,
@@
 to simplify the training process and to isolate the effects of the predicate and function precedences.
-This section describes how the training data for training a \emph{predicate} precedence recommender was generated.
-Training data for training a function precedence recommender was generated analogously.
+This section describes how the training data for the case of training a \emph{predicate} precedence recommender was generated.
+Data for training the function precedence recommender was generated analogously.
 
@@
 
-The input problems are assumed to be specified in the \gls{cnf} or the \gls{fof} fragment
+The input problems were assumed to be specified in the \gls{cnf} or the \gls{fof} fragment
 of the \acrshort{tptp} language \cite{Sutcliffe2017}.
 % http://www.tptp.org/TPTP/SyntaxBNF.html
-\Gls{fof} problems are first converted into equisatisfiable \gls{cnf} problems by \Vampire{}.
+\Gls{fof} problems were first converted into equisatisfiable \gls{cnf} problems by \Vampire{}.
 %New symbols may be introduced during preprocessing,
@@
 
-The problem library \acrshort{tptp}~v7.4.0 \cite{Sutcliffe2017}
-was used as the source of problems for training and evaluation of the recommender,
-offering a total of \num{17053} \gls{fol} problems.
-We denote the set of all the problems available for training and evaluation as $\ProblemsTptp$.
+We used the problem library \acrshort{tptp}~v7.4.0 \cite{Sutcliffe2017}
+as the source of problems for training and evaluation of the recommender.
+We denote the set of all the problems available for training and evaluation as $\ProblemsTptp$ ($\card{\ProblemsTptp} = 17053$).
 
@@
 In addition to the signature and the structure of the problem,
-some metadata is extracted from the input problem to allow training a more efficient recommender.
-First, each clause is annotated with its role in the problem,
-which can be either axiom, assumption, or negated conjecture.
+some metadata was extracted from the input problem to allow training a more efficient recommender.
+First, each clause was annotated with its role in the problem,
+which could be either axiom, assumption, or negated conjecture.
 % This is simplified. There are actually 7 clause roles defined internally in Vampire,
@@
 % so the recommender can actually differentiate between these two forms.
-Second, each symbol is annotated with two bits of data:
-whether it was introduced into the problem during preprocessing,
-and whether the symbol appears in a conjecture clause.
+Second, each symbol was annotated with two bits of data:
+whether the symbol was introduced into the problem during preprocessing,
+and whether the symbol appeared in a conjecture clause.
 % Note that the second bit is redundant, since the clauses are annotated with their roles.
-This metadata is used to construct the initial embeddings of the respective nodes
+This metadata was used to construct the initial embeddings of the respective nodes
 in the graph representation of the problem (see \cref{sec:gcn}).
@@
 
-The examples are generated by iterative sampling of $\ProblemsTptp$.
-In each iteration, a problem $P \in \ProblemsTptp$ is chosen and \Vampire{} is executed twice on $P$
+The examples were generated by iterative sampling of $\ProblemsTptp$.
+In each iteration, a problem $P \in \ProblemsTptp$ was chosen and \Vampire{} was executed twice on $P$
 with two (uniformly) random predicate precedences and a common random function precedence.
-The ``background'' random function precedence serves as additional noise (in addition to the variability 
-contained in \gls{tptp}) and makes sure that the predicate precedence recommender
-will not be able to rely on any specificities that would come from fixing function precedences in the training data.
+The ``background'' random function precedence served as additional noise (in addition to the variability 
+contained in \acrshort{tptp}) and made sure that the predicate precedence recommender
+would not be able to rely on any specificities that would come from fixing function precedences in the training data.
 
-The two executions are compared in terms of performance:
-predicate precedence $\PrecBetter$ is recognized as better than predicate precedence $\PrecWorse$,
+The two executions were compared in terms of performance:
+the predicate precedence $\PrecBetter$ was recognized as better than the predicate precedence $\PrecWorse$,
 denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$,
-if the proof search finishes successfully with $\PrecBetter$ ($\SolverRun{P}{\Prec} = \top$)
-\todo{FB: Alias: We use $S$ for both solver and score of precedence pair.}
-and if the number of iterations of the saturation loop with $\PrecBetter$ is smaller than with $\PrecWorse$.
+if the proof search finished successfully with $\PrecBetter$
+and if the number of iterations of the saturation loop with $\PrecBetter$ was smaller than with $\PrecWorse$.
 \todo{FB: Use notation for saturation loop iterations if the notation was established earlier. 
 If failure is denoted by $\infty$, we can simply use $<$.}
-If one of the two precedences is recognized as better,
-the example $(P, \PrecBetter, \PrecWorse)$ is produced,
-where $\PrecBetter$ is the better precedence,
-and $\PrecWorse$ is the other precedence.
-Otherwise, for example, if \Vampire{} fails on both precedences, we go back to sampling another problem.
+If one of the two precedences was recognized as better,
+the example $(P, \PrecBetter, \PrecWorse)$ would be produced,
+where $\PrecBetter$ was the better precedence,
+and $\PrecWorse$ was the other precedence.
+Otherwise, for example, if the proof search timed out on both precedences, we would go back to sampling another problem.
 \todo{FB: Discuss: How come we mix examples in which both precedences terminate with examples in which only one precedence terminates?}
 
-To ensure the efficiency of the sampling, the process is interpreted as an instance of Bernoulli multi-armed bandit problem \cite{Sutton1998},
+To ensure the efficiency of the sampling, we interpreted the process as an instance of Bernoulli multi-armed bandit problem \cite{Sutton1998},
 with the reward of a trial being 1 in case an example is produced, and 0 otherwise.
-Adaptive sampling balances
+Adaptive sampling balanced
 exploring problems that have been tried relatively scarcely and
@@
 For each problem $P \in \ProblemsTptp$,
-the generator keeps track of the number of times the problem has been tried $n_P$
+the generator kept track of the number of times the problem has been tried $n_P$
 and the number of examples generated from that problem $s_P$.
-The ratio of $s_P$ to $n_P$ corresponds to the average reward of problem $P$ observed so far.
-The problems are sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
-In each iteration, the generator samples the problem $P$ that maximizes
+The ratio $\frac{s_P}{n_P}$ corresponded to the average reward of problem $P$ observed so far.
+The problems were sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
+In each iteration, the generator sampled the problem $P$ that maximized
 $\frac{s_P}{n_P} + \sqrt{\frac{2 \ln n}{n_P}}$,
-\todo{FB: Shrink into text to save space.}
-where $n = \sum_{P \in \ProblemsTptp} n_P$ is the total number of tries on all problems.
-The parallelizing relaxation means that the $s_P$ values are only updated once in \num{1000} iterations,
+where $n = \sum_{P \in \ProblemsTptp} n_P$ was the total number of tries on all problems.
+The parallelizing relaxation means that the $s_P$ values were only updated once in \num{1000} iterations,
 allowing up to \num{2000} parallel solver executions.
@@
 
-The sampling runs until \num{1000000} examples are generated when training a predicate precedence recommender,
-or \num{800000} examples in case of function precedence recommender.
+The sampling continued until \num{1000000} examples were generated when training a predicate precedence recommender,
+or \num{800000} examples in case of a function precedence recommender.
 % sftp://cluster.ciirc.cvut.cz/home/bartefil/git/vampire-ml/out/20210108-generate-predicate/questions_generated
 For example, while generating \num{1000000} examples for the predicate precedence dataset,
-the least explored problem was tried 19 times, and the most exploited problem was tried 504 times.
-\num{5349} out of the \num{17053} problems yielded at least one example.
+\num{5349} out of the \num{17053} problems yielded at least one example,
+while the least explored problem was tried 19 times, and the most exploited problem 504 times.
 
@@
 
-The \num{17053} problems in $\ProblemsTptp$ are first split roughly in half to form the training set and the validation set.
-Next, both training and validation sets are restricted
-to problems whose graph representation consists of at most \num{100000} nodes
+The \num{17053} problems in $\ProblemsTptp$ were first split roughly in half to form the training set and the validation set.
+Next, both training and validation sets were restricted
+to problems whose graph representation consisted of at most \num{100000} nodes
 to limit the memory requirements of the training.
@@
 %a total of \num{15282} out of the \num{17053} (approximately \SI{90}{\percent}) problems satisfy this requirement.
-and there are \num{7648} problems in the resulting validation set $\ProblemsVal$.
-The training set $\ProblemsTrain$ is further restricted to problems that correspond to at least one training example,
-leaving \num{2571} problems when training predicate precedence recommender,
-and \num{1953} problems when training function precedence recommender.
+and there were \num{7648} problems in the resulting validation set $\ProblemsVal$.
+The training set $\ProblemsTrain$ was further restricted to problems that correspond to at least one training example,
+resulting in \num{2571} problems when training a predicate precedence recommender,
+and \num{1953} problems when training a function precedence recommender.
 % /home/filip/projects/vampire-ml/vampire-ml/outputs/2021-02-11/16-27-02/results.csv
@@
 
-A predicate symbol cost model is trained by gradient descent
-on the precedence pair classification task (described in \cref{sec:ranking})
-using the examples generated from the problems in $\ProblemsTrain$.
-To avoid redundant computations, all examples generated from a problem are processed in the same training batch.
-Thus, each training batch contains up to \num{128} problems and all the examples generated from these problems.
-The symbol cost model is trained using the Adam optimizer \cite{Kingma2014}.
-Learning rate starts at \num{1.28e-3}
-and is halved each time the train loss stagnates for 10 consecutive epochs.
+A symbol cost model was trained by gradient descent
+on the precedence ranking task (see \cref{sec:ranking})
+using the examples generated from $\ProblemsTrain$.
+To avoid redundant computations, all examples generated from a problem were processed in the same training batch.
+Thus, each training batch contained up to \num{128} problems and all the examples generated from these problems.
+The symbol cost model was trained using the Adam optimizer \cite{Kingma2014}.
+Learning rate started at \num{1.28e-3}
+and was halved each time the loss on $\ProblemsTrain$ stagnated for 10 consecutive epochs.
 % tf.keras.callbacks.ReduceLROnPlateau(monitor='loss', factor=0.5, patience=10)
@@
 %\subsubsection{Sample weighting}
-Each of the training examples of problem $P$ contributes to the training with the weight $\frac{1}{s_P}$,
-where $s_P$ is the number of examples of problem $P$ in the training set,
-so that each problem contributes to the training to the same degree irrespective of the relative numbers of examples.
+The examples were weighted.
+Each of the examples of problem $P$ contributed to the training with the weight $\frac{1}{s_P}$,
+where $s_P$ was the number of examples of problem $P$ in the training set.
+This ensured that each problem contributed to the training to the same degree irrespective of the relative numbers of examples.
 
@@
 %\subsubsection{Termination}
-We run the training until the validation accuracy stopped increasing for 100 consecutive epochs.
+We continued the training until the validation accuracy stopped increasing for 100 consecutive epochs.
 
@@
 The model that manifested the best estimated solver performance on a sample of \num{1000} validation problems
-was chosen as the most promising.
+was taken as the most promising.
 \todo[inline]{FB: Watch out: This way we may overfit on the 1000 problems used for sample solver performance evaluation. We should leave out these 1000 problems from the final evaluation.}
@@
 was evaluated with the same time limit.
-For comparison, the two trained recommenders are evaluated separately,
+For comparison, the two trained recommenders were evaluated separately,
 with the predicate precedence recommender using the \texttt{frequency} heuristic to generate the function precedences, and vice versa.
@@
 and finally orders the symbols by their costs to produce the precedence.
-To simplify the experiment, the time limit of 10 seconds is only imposed on the \Vampire{} run
-and excludes the time taken by the recommender to generate the precedence.
+To simplify the experiment, the time limit of 10 seconds was only imposed on the \Vampire{} run
+and excluded the time taken by the recommender to generate the precedence.
 When run with 2 threads,
@@
 vztahnout k casu klauzifikace? Jako rict, ze to trva x-krat dyl nez jen klauzifikovat?}
-\Cref{tab:results} shows the results.
+\Cref{tab:results} shows the results of the final evaluation.
 
@@
 Means and standard deviations over 5 runs are reported.
-The \gls{gcn} models are trained according to the description in \cref{sec:architecture,sec:training,sec:evaluation}.
-The model Simple is the final model from our previous work \cite{DBLP:conf/cade/Bartek020}.
-The models that use \acrlong{ml} for the predicate precedence only
-use the \texttt{frequency} heuristic for the function precedence, and vice versa.
-The frequency model uses the standard \texttt{frequency} heuristic implemented in \Vampire{}.
+The \gls{gcn} models were trained according to the description in \cref{sec:architecture,sec:training,sec:evaluation}.
+The model Simple is the final linear model from our previous work \cite{DBLP:conf/cade/Bartek020}.
+The models that used \acrlong{ml} only for the predicate precedence
+used the \texttt{frequency} heuristic for the function precedence, and vice versa.
+The frequency model uses the standard \texttt{frequency} heuristic for both predicate and function precedence.
 }
@@
 
-Frequency &
+Frequency (baseline) &
 %\texttt{vampire -lcm predicate} &
@@
 
-The results show that the \gls{gcn}-based model outperforms the \texttt{frequency} heuristic by a significant margin.
+The results show that the \gls{gcn}-based model outperformed the \texttt{frequency} heuristic by a significant margin.
 \todo{FB: Add links to Neptune runs?}
@@
 it is expected to perform well irrespective of the function precedence heuristic it is combined with.
-Combining the trained recommenders for predicate and function precedences manifests better performance
+Combining the trained recommenders for predicate and function precedences manifested better performance
 than any of the two in combination with the standard \texttt{frequency} heuristic,
@@
 
-We have verified that the linear predicate precedence heuristic
+We verified that the linear predicate precedence heuristic
 trained in \cite{DBLP:conf/cade/Bartek020} outperforms the \texttt{frequency} heuristic.
-Moreover, we have confirmed the conjecture that using a \gls{gnn} may perform even better \cite{DBLP:conf/cade/Bartek020}.
+Moreover, we confirmed the conjecture that using a \gls{gnn} may perform even better \cite{DBLP:conf/cade/Bartek020}.
 

### 2021-02-25 evaluation.tex
Fix links to source code repos
Use tags so that we can update the content later if necessary.

@@
 The scripts that were used to generate the training data and to train and evaluate the recommender
-are available online.\footnote{\url{https://github.com/filipbartek/vampire-ml/tree/6907ee35}}
-\todo{FB: Tag the version and link to the tag.}
+are available online.\footnote{\url{https://github.com/filipbartek/vampire-ml/tree/cade28}}
 \todo{FB: Add some wrapper scripts and readme for ease of use.}
@@
 (normally, the user only picks a precedence generation heuristic).
-The modified version of \Vampire{} is available online.\footnote{\url{https://github.com/filipbartek/vampire/tree/3bbfa9e6}} \todo{MS: nebo jeste lip. Slo by udelat repo, 
+The modified version of \Vampire{} is available online.\footnote{\url{https://github.com/filipbartek/vampire/tree/cade28}} \todo{MS: nebo jeste lip. Slo by udelat repo, 
 ve kterym bude textak, co vsechno vysvetli, vcetne linku na ty dve repa co zminujes tady a vyse.}

### 2021-02-26 evaluation.tex
Add comments with hard URLs to the scripts
Update the referenced code repo commit in a comment

@@
 are available online.\footnote{\url{https://github.com/filipbartek/vampire-ml/tree/cade28}}
-\todo{FB: Add some wrapper scripts and readme for ease of use.}
+% https://github.com/filipbartek/vampire-ml/tree/10ee2d730f96ea264dc829b8aabd2d95cc083e50
 
@@
 (normally, the user only picks a precedence generation heuristic).
-The modified version of \Vampire{} is available online.\footnote{\url{https://github.com/filipbartek/vampire/tree/cade28}} \todo{MS: nebo jeste lip. Slo by udelat repo, 
+The modified version of \Vampire{} is available online.\footnote{\url{https://github.com/filipbartek/vampire/tree/cade28}}
+% https://github.com/filipbartek/vampire/tree/3bbfa9e6cd009f501f74d26eabc7e7811b5bb00e
+\todo{MS: nebo jeste lip. Slo by udelat repo,
 ve kterym bude textak, co vsechno vysvetli, vcetne linku na ty dve repa co zminujes tady a vyse.}

### 2021-03-05 introduction.tex
Add a missing reference to sec Training in Introduction
one more typo

@@
 a \emph{symbol cost model}, which then realizes the recommendation by simply sorting 
-the problem's symbols according the obtained costs.
+the problem's symbols according to the obtained costs.
 
@@
 \Cref{sec:preliminaries} exposes the basic terminology used throughout the remaining sections.
-\Cref{sec:architecture} proposes a structure of the precedence recommender that can be trained on pairs of symbol precedences.
+\Cref{sec:architecture} proposes a structure of the precedence recommender that can be trained on pairs of symbol precedences,
+as described in \cref{sec:training}.
 \Cref{sec:evaluation} summarizes and discusses experiments performed

### 2021-03-30 rebuttal.txt
Add a draft of the rebuttal
Reviews can be viewed here:
https://easychair.org/conferences/submission?a=25958734;submission=5327793

We are grateful for the attention and care the reviewers took when considering our paper.

Response to Review 1
--------------------

- An obvious question is how is this work related to the work and methods used for Enigma?

[FB: I'll try to read the Enigma papers and compare our architecture etc. to theirs.]

- Despite the clear improvement over baseline, the percentage gained does not appear
to be too big. It is possible, that the potential effect of better orderings is not
too high, regardless of the optimizations. Can you give some insights for this
line of thought?

The impact of symbol precedence on the proof search is limited,
especially in case it is only used as a tie-breaker in the regular KBO.
[FB: Explain in more detail.]

Response to Review 2
--------------------

- How does your tool behave in the presence of theories (assuming AVATAR is used)?

Both in the training and in the evaluation, AVATAR was disabled.
To avoid confusion, we intend to extend the final version of the paper with an appendix including a detailed description of the Vampire configuration.

- Now Vampire can also handle higher-order problems. Can your technique also improve Vampire's performance in this context?

[FB: Martin, are the precedences compatible with the HOL reasoning in Vampire?]

- How long did it take to do all the training?

In total, the generation of the training data and the training of the model took approximately 8 days.
More precisely, it took approximately 2 and 4 days to generate the training data for the predicate and function precedence recommender, respectively,
and it took approximately 45 and 20 hours to train the predicate and function precedence recommender, respectively.

- What kind of new problems were solved in terms of the rating of the problems?

A total of 234 new problems were solved by the trained recommender when compared to the baseline heuristic.
Among these 234 problems, the maximum rating is 0.88,
the mean rating is approximately 0.36 and the median rating is 0.36.

- How independent are the training and test sets, given that the problems in TPTP are grouped by families that may include extremely similar problems?

In this experiment, we have not attempted to control nor analyze the similarity between the problems in the training and test sets.
Splitting the problem set by the domain or the source of the problems is, however, an interesting idea.

Response to Review 3
--------------------

- Why do you use the number or iterations of the main loop?

The idea behind using the number of iterations of the main loop is that it ensures that the orientation of each pair of precedences is unique –
once we observe that precedence pi is better than precedence rho, we are certain that we will never observe the opposite orientation.
While this approach reduces the amount of noise in the training data,
it is not necessary for the training to succeed.
The point raised by the reviewer is valid and suggests that using wall clock time as the decisive metric, if implemented well, may increase the performance of the trained system.

- You don't describe how many "incomplete" precedence pairs you
have, e.g. pair where one precedence leads to a proof, the other
to a timeout.

[FB: I'll try to extract this from the data. Most likely this information is not available.]

- If I understand you correctly, the graph representation of a problem is fixed. So why don't you filter before generating training examples?

We agree that filtering the problems first by the graph representation size would make the procedure clearer.
The procedure described in the paper was used mainly because it allowed cheaper tuning of the hyperparameters that control the conversion to graphs --
in most of the experiments, we only need to convert a small part of the training and test problems,
and determining whether a graph representation of a problem has at most 100 000 nodes requires performing the conversion to graph.
Filtering by the graph size before splitting into training and test set, once the hyperparameters are tuned, seems to be a reasonable improvement.

### 2021-03-30 architecture.tex
a typo
Add todos based on reviews 1 and 2 (excluding Minor comments)

@@
 \todo{FB: Improve the diagram. Consider using tikz. See the disabled tikz figure in the source file.}
+\todo[author=R2]{The small bold arrows are quite difficult to distinguish from the small non-bold arrows.}
 
-\subsection{Graph consutructor: From \gls{cnf} to graphs}
+\subsection{Graph constructor: From \gls{cnf} to graphs}
 \label{sec:graphifier}
@@
 \end{figure}
+\todo[author=R2]{There are unneeded differences in the notations used in the two figures; for example, pos/neg vs +/-, equality vs equality atom, the various (and non-specified) types of boxes around the nodes in fig.
+3...}
 
@@
 Each layer consists of a collection of differentiable modules---one module per edge type.
+\todo[author=R1]{Are there just so many nodes in the layer as the types of graph edges in Figure 2, or is each edge in the whole graph (a large set) represented by a collection of modules?}
 The computation of the \gls{gcn} starts with assigning each node an initial embedding
@@
 we use a \gls{gcn}-based symbol cost model $c$ in place of the simple symbol property,
+\todo[author=R1]{What exactly is the GCN-bases symbol cost? Is it the cost calculated by
+the model for each symbol, or are different copies of symbols in different occurrences given
+different costs?}
 and generate a precedence by sorting the symbols by their predicted costs.
@@
 \end{multline*}
+\todo[inline,author=R2]{In the equations showing that the expected value of the precedence cost is independent of the size of the signature, there is a (minor) problem in the second line: the i occurring in $E_i[c(i)]$ is not defined and probably unneeded if, as hinted by the equations, the expected value of each symbol is the same (which should also be stated somewhere).}
 
@@
 that minimize the loss value.
+\todo[author=R2]{I expect that you mean "to *locally* minimize the loss value". If you do, the fix is simple (just add "locally"); if not, more explanations are needed.}
 

### 2021-03-30 evaluation.tex
Add todos based on reviews 1 and 2 (excluding Minor comments)

@@
 The empirical evaluation was performed using a modified version of the \gls{atp} \Vampire{} 4.3.0 \cite{10.1007/978-3-642-39799-8_1}.
+\todo[author=R2]{the reference for Vampire ([20]) describes version 2.6 of Vampire and you are using version 4.3.
+If available, something more recent would give a better idea of the current capacities of Vampire.}
 The prover was used to generate the training data and to evaluate the trained precedence recommender.
@@
 \todo[inline,author=FB]{Describe the detailed configuration in an appendix and reference the appendix here.}
+\todo[inline,author=R2]{Did you fix the strategy and heuristics used by Vampire throughout the training and experiments or was it run in portfolio mode? What about AVATAR, was it activated?}
 
@@
 $\frac{s_P}{n_P} + \sqrt{\frac{2 \ln n}{n_P}}$,
+\todo[author=R2]{Regarding the sampling of problems, what happens when $n_P = 0$, i.e., a problem has not yet been sampled?
+Or do you start with trying each problem at least once before implementing UCB1?}
 where $n = \sum_{P \in \ProblemsTptp} n_P$ was the total number of tries on all problems.
@@
 \todo{Explain in detail?}
+\todo[inline,author=FB]{We bootstrap with a per-problem lower bound on the final number of questions. The lower bound is a solution to the equation for $n_B$:
+
+$$
+\frac{s_B}{n_B} + \sqrt{\frac{h \log n}{2 n_B}} < \frac{s_G}{n_G} + \sqrt{\frac{h \log n}{2 n_G}}
+$$
+
+By taking $s_B = 0$, $s_G = n_G = \frac{n}{|\ProblemsTptp|}$, we get:
+
+$$
+\sqrt{\frac{h \log n}{2 x}} < 1 + \sqrt{\frac{h \log n}{2 \frac{n}{|\ProblemsTptp|}}}
+$$
+
+The standard way is to bootstrap with only one sample per problem.
+By enlarging the bootstrap set, we get better estimates early on.
+The expected outcome is the same but the variance is lower (?).
+}
+\todo[inline,author=R2]{To clarify the last paragraph of the page, that introduces concepts with which people outside of ML wouldn't be familiar with, I suggest to use columns to show that some sentences are definitions for the terms introduced in the previous sentences, in particular, "...
+and 0 otherwise.
+Adaptive sampling..." -> "...
+and 0 otherwise: Adaptive sampling..." and "...
+with a parallelizing relaxation.
+In each iteration..." -> "with a parallelizing relaxation: In each iteration..."}
 
@@
 % tf.keras.callbacks.ReduceLROnPlateau(monitor='loss', factor=0.5, patience=10)
+\todo[author=R2]{Same comment as just above: "... Adam optimizer [15]. Learning rate..." -> "... Adam optimizer [15]: Learning rate..."}
 
@@
 by extrapolation from a sample of \num{1000} problems.
+\todo[author=R2]{What about the remaining 20\% that do not take at most 1.26 seconds? Do they all timeout?}
 % Analysis: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit?usp=sharing
@@
 
+\todo[inline,author=R2]{In your PAAR paper [7], the experimental results show that your linear model is not as good as the baseline but it is no longer the case here.
+How do you explain this?
+If it was further improved after PAAR, it should be mentioned.}
+
 The results show that the \gls{gcn}-based model outperformed the \texttt{frequency} heuristic by a significant margin.
@@
 outperforming the \texttt{frequency} heuristic by approximately \SI{4.8}{\percent}.
+
+\todo[inline,author=R1]{Despite the clear improvement over baseline, the percentage gained does not appear
+to be too big. It is possible, that the potential effect of better orderings is not
+too high, regardless of the optimizations. Can you give some insights for this
+line of thought?
+}
 

### 2021-03-30 main.tex
Add RankNet to related work
Enable the final version mode
Move a todo
a mild flip
Add todos based on reviews 1 and 2 (excluding Minor comments)

@@
 \newtoggle{LONG}
-\toggletrue{LONG}
-%\togglefalse{LONG}
+%\toggletrue{LONG}
+\togglefalse{LONG}
 
@@
 
-\todo[inline]{FB: Mention RankNet.}
-\todo[inline]{Related problem: Ranking. See Mohri etc.}
+The problem of learning to rank objects represented by scores trainable by gradient descent was explored in \cite{Burges2005}.
+Our work can be seen to apply the approach of \cite{Burges2005} to rank permutations represented by weighted sums of symbol costs.
+\todo{Related problem: Ranking. See Mohri etc.}
+
+\todo[inline,author=R1]{An obvious question is how is this work related to the work and methods
+used for Enigma?
+
+Although the paper related to the Enigma system by Jakubuv has been
+cited, it appears to not be referred to in the text. It should be referred and
+the reference list should be checked.
+}
+
+% Fast differentiable ranking (and probably other texts): They use the permutation scoring by weighted sum.
 

### 2021-03-30 preliminaries.tex
back-propagation > chain rule
Add todos based on reviews 1 and 2 (excluding Minor comments)

@@
 A \emph{\acrfull{fol} problem} consists of a set of axiom formulas and a conjecture formula.
+\todo{FB: Clarify that we use FOL with equality.}
 In a \emph{refutation-based} \emph{\acrfull{atp}},
@@
 We denote a problem in \gls{cnf} as $P = (\Sigma, \mathit{Cl})$,
+% Handbook of AR, Chapter 3: signature $\Sigma = (P_\Sigma, F_\Sigma)$
+\todo{FB: What about the variables? Handbook of AR (chapter 3) defines the set Var.}
 where $\Sigma$ is a list of all non-logical (predicate and function)
@@
 \todo{FB: Is this terminology correct?}
-can be computed using the chain rule \cite{DBLP:books/daglib/0040158}.
+can be computed using the \emph{back-propagation} algorithm \cite{DBLP:books/daglib/0040158}.
 The trainable parameters are then updated by taking a small step
@@
 using each example in the training set exactly once.
+
+\todo[inline,author=R2]{Why present only the feedforward NN in sect.
+2.3 when you are using a GCN?
+You could at least include a paragraph about the main differences between these two models at the end of 2.3.
+Then 3.2 could focus on the aspects of GCN that are specific to this particular problem.}

### 2021-03-30 rebuttal.txt
Compare our recommender with ENIGMA in detail

@@
 
-[FB: I'll try to read the Enigma papers and compare our architecture etc. to theirs.]
+ENIGMA-NG [9] differs from our neural precedence recommender (NPR) significantly in that it deals with a different task (given clause selection),
+it assumes a common signature across the problems
+and it uses a recursive neural network (a more restrictive NN architecture).
+ENIGMA Anonymous [Jakubuv 2020] uses the graph neural network (GNN) architecture proposed in [25], and the relation of our work to this architecture is outlined in section 6.
+In more detail, NPR deals with the task of proposing good symbol precedences, while ENIGMA solves given clause selection (an instance of clause classification).
+NPR is trained on a proxy task of precedence pair classification,
+while ENIGMA is trained directly on the task of clause classification.
+ENIGMA uses a lossy hypergraph encoding,
+while we use a lossless graph encoding with only binary edges,
+which allows our architecture to match the standard R-GCN as proposed in [31] more closely.
 

### 2021-03-30 rebuttal.txt
Expand the explanation of limited impact of precedences

@@
 especially in case it is only used as a tie-breaker in the regular KBO.
-[FB: Explain in more detail.]
+While using the TKBO for literal ordering observably increases the impact of the predicate precedence on the proof search,
+the impact remains indirect and thus it is expected to be relatively limited compared to,
+e.g., given clause selection.
+[FB: Try to estimate how much learning precedences can help by summarizing the results on random precedences.]
 

### 2021-03-30 rebuttal.txt
Minor improvements

@@
-We are grateful for the attention and care the reviewers took when considering our paper.
+We are very grateful for the attention and care the reviewers took when considering our paper.
 
@@
 We agree that filtering the problems first by the graph representation size would make the procedure clearer.
-The procedure described in the paper was used mainly because it allowed cheaper tuning of the hyperparameters that control the conversion to graphs --
+The procedure described in the paper was used mainly because it allowed cheaper tuning of the hyperparameters that control the conversion to graphs –
 in most of the experiments, we only need to convert a small part of the training and test problems,

### 2021-03-31 rebuttal.txt
Reformat section titles in rebuttal

@@
 
-Response to Review 1
---------------------
+----------- Response to Review 1 -----------
 
@@
 
-The impact of symbol precedence on the proof search is limited,
-especially in case it is only used as a tie-breaker in the regular KBO.
-While using the TKBO for literal ordering observably increases the impact of the predicate precedence on the proof search,
-the impact remains indirect and thus it is expected to be relatively limited compared to,
-e.g., given clause selection.
-[FB: Try to estimate how much learning precedences can help by summarizing the results on random precedences.]
+It is incredibly difficult to estimate in absolute terms, how large an improvement
+one could in our setting on TPTP achieve using some form of "perfect orderings".
+However, experiments with random precedences [7] showed that the prover perceptibly responds 
+to changes of this parameter and that work on a recommender is worthwhile.
 
-Response to Review 2
---------------------
+----------- Response to Review 2 -----------
 
@@
 
-Both in the training and in the evaluation, AVATAR was disabled.
-To avoid confusion, we intend to extend the final version of the paper with an appendix including a detailed description of the Vampire configuration.
+Both in the training and in the evaluation, AVATAR was disabled and we didn't consider problems with theories.
+Although, in principle, theory symbols could be subject to our recommender, Vampire treats them differently than the rest  
+when constructing a precedence and we did not want to be sidetracked by these specificities.
 
@@
 
-[FB: Martin, are the precedences compatible with the HOL reasoning in Vampire?]
+Again, this seems in principle possible, as long as the ordering used by the HO vampire still relies on a precedence,
+but we did not investigate the details yet.
 
@@
 
-Response to Review 3
---------------------
+----------- Response to Review 3 -----------
 
@@
 
-The idea behind using the number of iterations of the main loop is that it ensures that the orientation of each pair of precedences is unique –
-once we observe that precedence pi is better than precedence rho, we are certain that we will never observe the opposite orientation.
-While this approach reduces the amount of noise in the training data,
-it is not necessary for the training to succeed.
-The point raised by the reviewer is valid and suggests that using wall clock time as the decisive metric, if implemented well, may increase the performance of the trained system.
-
-- You don't describe how many "incomplete" precedence pairs you
-have, e.g. pair where one precedence leads to a proof, the other
-to a timeout.
-
-[FB: I'll try to extract this from the data. Most likely this information is not available.]
+We mainly selected this metric because it is deterministic
+and can be measured while other processes are making the computer busy.
+Wall-clock time is more sensitive to the compute environment 
+and more care needs to be taken to obtain meaningful commeasureable across multiple runs.
+However, the point raised by the reviewer is valid and suggests that using wall clock time as the decisive metric,
+if implemented well, may increase the performance of the trained system.
 

### 2021-03-31 rebuttal.txt
Improve answer to question 2 from R3

@@
 
-- If I understand you correctly, the graph representation of a problem is fixed. So why don't you filter before generating training examples?
+- If I understand you correctly, the graph representation of a problem is fixed. So why don't you filter before generating training examples? CPU time must be cheap! ;-)
 
-We agree that filtering the problems first by the graph representation size would make the procedure clearer.
-The procedure described in the paper was used mainly because it allowed cheaper tuning of the hyperparameters that control the conversion to graphs –
-in most of the experiments, we only need to convert a small part of the training and test problems,
-and determining whether a graph representation of a problem has at most 100 000 nodes requires performing the conversion to graph.
-Filtering by the graph size before splitting into training and test set, once the hyperparameters are tuned, seems to be a reasonable improvement.
+We chose to generate the training and validation examples (in the form of oriented pairs of precedences) independently from the graph representation of the problems.
+This allowed us to adjust the hyperparameters of the two processes (example generation and graph representation) independently,
+keeping the computation cost of the graph representation hyperparameter tuning relatively low.

### 2021-03-31 rebuttal.txt
Improve answer to question 1 from R1 (ENIGMA)

@@
 
-ENIGMA-NG [9] differs from our neural precedence recommender (NPR) significantly in that it deals with a different task (given clause selection),
-it assumes a common signature across the problems
-and it uses a recursive neural network (a more restrictive NN architecture).
-ENIGMA Anonymous [Jakubuv 2020] uses the graph neural network (GNN) architecture proposed in [25], and the relation of our work to this architecture is outlined in section 6.
-In more detail, NPR deals with the task of proposing good symbol precedences, while ENIGMA solves given clause selection (an instance of clause classification).
-NPR is trained on a proxy task of precedence pair classification,
-while ENIGMA is trained directly on the task of clause classification.
-ENIGMA uses a lossy hypergraph encoding,
-while we use a lossless graph encoding with only binary edges,
-which allows our architecture to match the standard R-GCN as proposed in [31] more closely.
+ENIGMA [9, Jakubův 2020] differs from our neural precedence recommender especially in the task it deals with:
+ENIGMA identifies promising clauses for given clause selection,
+while our recommender proposes promising symbol precedences.
+The most recent version of ENIGMA, named ENIGMA Anonymous [Jakubův 2020], uses the graph neural network (GNN) architecture proposed in [25], and the relation of our work to this architecture is outlined in section 6 of our paper.
+While both ours and ENIGMA GNNs process the input problems in a signature-agnostic manner,
+the two GNNs are developed independently and have different architectures.
 
@@
 to changes of this parameter and that work on a recommender is worthwhile.
+
+[Jakubův 2020]: Jakubův, J., Chvalovský, K., Olšák, M., Piotrowski, B., Suda, M., Urban, J.: ENIGMA Anonymous: Symbol-Independent Inference Guiding Machine (System Description).
+In: LNCS.
+vol.
+12167 LNAI, pp.
+448–463.
+Springer (2020).
+https://doi.org/10.1007/978-3-030-51054-1_29
 

### 2021-03-31 rebuttal.txt
MS upravy rebuttalu
did not > didn't
Add a missing word: "[meaningful] results [commeasurable]"

@@
 
-Both in the training and in the evaluation, AVATAR was disabled and we didn't consider problems with theories.
+Both in the training and in the evaluation, AVATAR was disabled and we did not consider problems with theories.
 Although, in principle, theory symbols could be subject to our recommender, Vampire treats them differently than the rest  
@@
 Wall-clock time is more sensitive to the compute environment 
-and more care needs to be taken to obtain meaningful commeasureable across multiple runs.
+and more care needs to be taken to obtain meaningful results commeasureable across multiple runs.
 However, the point raised by the reviewer is valid and suggests that using wall clock time as the decisive metric,

### 2021-03-31 rebuttal.txt
Improve "Engima" answer

@@
 ENIGMA identifies promising clauses for given clause selection,
-while our recommender proposes promising symbol precedences.
+while our recommender proposes promising symbol precedences for the proof search.
 The most recent version of ENIGMA, named ENIGMA Anonymous [Jakubův 2020], uses the graph neural network (GNN) architecture proposed in [25], and the relation of our work to this architecture is outlined in section 6 of our paper.
-While both ours and ENIGMA GNNs process the input problems in a signature-agnostic manner,
+While both our recommender and ENIGMA use a GNN to process the input problems in a signature-agnostic manner,
 the two GNNs are developed independently and have different architectures.

### 2021-03-31 rebuttal.txt
minimalni upravky

--- 2021-03-31 rebuttal.txt
@@
 ENIGMA identifies promising clauses for given clause selection,
-while our recommender proposes promising symbol precedences.
-The most recent version of ENIGMA, named ENIGMA Anonymous [Jakubův 2020], uses the graph neural network (GNN) architecture proposed in [25], and the relation of our work to this architecture is outlined in section 6 of our paper.
-While both ours and ENIGMA GNNs process the input problems in a signature-agnostic manner,
-the two GNNs are developed independently and have different architectures.
+while our recommender proposes a promising symbol precedence for the proof search.
+The most recent version of ENIGMA, named ENIGMA Anonymous [Jakubův 2020],
+uses the graph neural network (GNN) architecture proposed in [25],
+and the relation of our work to this architecture is outlined in section 6 of our paper.
+While both our recommender and ENIGMA use a GNN to process the input problems in a signature-agnostic manner,
+the two GNNs are developed independently and their architectures are different.
 
@@
 
-It is incredibly difficult to estimate in absolute terms, how large an improvement
+It is incredibly difficult to estimate, in absolute terms, how large an improvement
 one could in our setting on TPTP achieve using some form of "perfect orderings".
@@
 However, the point raised by the reviewer is valid and suggests that using wall clock time as the decisive metric,
-if implemented well, may increase the performance of the trained system.
+if implemented well, could increase the performance of the trained system.
 

### 2021-03-31 rebuttal.txt
Reformat to uniform line length
with `fmt`.
Small corrections
aided by Grammarly

@@
-We are very grateful for the attention and care the reviewers took when considering our paper.
+We are very grateful for the attention and care the reviewers took when
+considering our paper.
 
@@
 
-- An obvious question is how is this work related to the work and methods used for Enigma?
+- An obvious question is how is this work related to the work and methods
+used for Enigma?
 
-ENIGMA [9, Jakubův 2020] differs from our neural precedence recommender especially in the task it deals with:
-ENIGMA identifies promising clauses for given clause selection,
-while our recommender proposes a promising symbol precedence for the proof search.
-The most recent version of ENIGMA, named ENIGMA Anonymous [Jakubův 2020],
-uses the graph neural network (GNN) architecture proposed in [25],
-and the relation of our work to this architecture is outlined in section 6 of our paper.
-While both our recommender and ENIGMA use a GNN to process the input problems in a signature-agnostic manner,
-the two GNNs are developed independently and their architectures are different.
+ENIGMA [9, Jakubův 2020] differs from our neural precedence recommender
+especially in the task it deals with: ENIGMA identifies promising clauses
+for given clause selection, while our recommender proposes a promising
+symbol precedence for the proof search.  The most recent version of
+ENIGMA, named ENIGMA Anonymous [Jakubův 2020], uses the graph neural
+network (GNN) architecture proposed in [25], and the relation of our work
+to this architecture is outlined in section 6 of our paper.  While both
+our recommender and ENIGMA use a GNN to process the input problems in
+a signature-agnostic manner, the two GNNs are developed independently
+and their architectures are different.
 
-- Despite the clear improvement over baseline, the percentage gained does not appear
-to be too big. It is possible, that the potential effect of better orderings is not
-too high, regardless of the optimizations. Can you give some insights for this
-line of thought?
+- Despite the clear improvement over baseline, the percentage gained does
+not appear to be too big. It is possible, that the potential effect of
+better orderings is not too high, regardless of the optimizations. Can
+you give some insights for this line of thought?
 
-It is incredibly difficult to estimate, in absolute terms, how large an improvement
-one could in our setting on TPTP achieve using some form of "perfect orderings".
-However, experiments with random precedences [7] showed that the prover perceptibly responds 
-to changes of this parameter and that work on a recommender is worthwhile.
+It is incredibly difficult to estimate, in absolute terms, how large an
+improvement one could in our setting on TPTP achieve using some form of
+"perfect orderings".  However, experiments with random precedences [7]
+showed that the prover perceptibly responds to changes of this parameter
+and that work on a recommender is worthwhile.
 
-[Jakubův 2020]: Jakubův, J., Chvalovský, K., Olšák, M., Piotrowski, B., Suda, M., Urban, J.: ENIGMA Anonymous: Symbol-Independent Inference Guiding Machine (System Description).
-In: LNCS.
-vol.
-12167 LNAI, pp.
-448–463.
-Springer (2020).
-https://doi.org/10.1007/978-3-030-51054-1_29
+[Jakubův 2020]: Jakubův, J., Chvalovský, K., Olšák,
+M., Piotrowski, B., Suda, M., Urban, J.: ENIGMA Anonymous:
+Symbol-Independent Inference Guiding Machine (System
+Description). In: LNCS. vol. 12167 LNAI, pp. 448–463. Springer
+(2020). https://doi.org/10.1007/978-3-030-51054-1_29
 
@@
 
-- How does your tool behave in the presence of theories (assuming AVATAR is used)?
+- How does your tool behave in the presence of theories (assuming AVATAR
+is used)?
 
-Both in the training and in the evaluation, AVATAR was disabled and we did not consider problems with theories.
-Although, in principle, theory symbols could be subject to our recommender, Vampire treats them differently than the rest  
-when constructing a precedence and we did not want to be sidetracked by these specificities.
+Both in the training and in the evaluation, AVATAR was disabled and
+we did not consider problems with theories.  Although, in principle,
+theory symbols could be subject to our recommender, Vampire treats them
+differently than the rest when constructing a precedence and we did not
+want to be sidetracked by these specificities.
 
-- Now Vampire can also handle higher-order problems. Can your technique also improve Vampire's performance in this context?
+- Now Vampire can also handle higher-order problems. Can your technique
+also improve Vampire's performance in this context?
 
-Again, this seems in principle possible, as long as the ordering used by the HO vampire still relies on a precedence,
-but we did not investigate the details yet.
+Again, this seems in principle possible, as long as the ordering used by
+the HO vampire still relies on a precedence, but we did not investigate
+the details yet.
 
@@
 
-In total, the generation of the training data and the training of the model took approximately 8 days.
-More precisely, it took approximately 2 and 4 days to generate the training data for the predicate and function precedence recommender, respectively,
-and it took approximately 45 and 20 hours to train the predicate and function precedence recommender, respectively.
+In total, the generation of the training data and the training of the
+model took approximately 8 days.  More precisely, it took approximately 2
+and 4 days to generate the training data for the predicate and function
+precedence recommender, respectively, and it took approximately 45 and
+20 hours to train the predicate and function precedence recommender,
+respectively.
 
-- What kind of new problems were solved in terms of the rating of the problems?
+- What kind of new problems were solved in terms of the rating of the
+problems?
 
-A total of 234 new problems were solved by the trained recommender when compared to the baseline heuristic.
-Among these 234 problems, the maximum rating is 0.88,
-the mean rating is approximately 0.36 and the median rating is 0.36.
+A total of 234 new problems were solved by the trained recommender
+when compared to the baseline heuristic.  Among these 234 problems,
+the maximum rating is 0.88, the mean rating is approximately 0.36 and
+the median rating is 0.36.
 
-- How independent are the training and test sets, given that the problems in TPTP are grouped by families that may include extremely similar problems?
+- How independent are the training and test sets, given that the
+problems in TPTP are grouped by families that may include extremely
+similar problems?
 
-In this experiment, we have not attempted to control nor analyze the similarity between the problems in the training and test sets.
-Splitting the problem set by the domain or the source of the problems is, however, an interesting idea.
+In this experiment, we have not attempted to control nor analyze
+the similarity between the problems in the training and test sets.
+Splitting the problem set by the domain or the source of the problems is,
+however, an interesting idea.
 
@@
 
-We mainly selected this metric because it is deterministic
-and can be measured while other processes are making the computer busy.
-Wall-clock time is more sensitive to the compute environment 
-and more care needs to be taken to obtain meaningful results commeasureable across multiple runs.
-However, the point raised by the reviewer is valid and suggests that using wall clock time as the decisive metric,
-if implemented well, could increase the performance of the trained system.
+We mainly selected this metric because it is deterministic and can be
+measured while other processes are making the computer busy.  Wall-clock
+time is more sensitive to the computing environment and more care needs to
+be taken to obtain meaningful results commeasureable across multiple runs.
+However, the point raised by the reviewer is valid and suggests that
+using wall-clock time as the decisive metric, if implemented well,
+could increase the performance of the trained system.
 
-- If I understand you correctly, the graph representation of a problem is fixed. So why don't you filter before generating training examples? CPU time must be cheap! ;-)
+- If I understand you correctly, the graph representation of a problem is
+fixed. So why don't you filter before generating training examples? CPU
+time must be cheap! ;-)
 
-We chose to generate the training and validation examples (in the form of oriented pairs of precedences) independently from the graph representation of the problems.
-This allowed us to adjust the hyperparameters of the two processes (example generation and graph representation) independently,
-keeping the computation cost of the graph representation hyperparameter tuning relatively low.
+We chose to generate the training and validation examples (in the form of
+oriented pairs of precedences) independently from the graph representation
+of the problems.  This allowed us to adjust the hyperparameters of the two
+processes (example generation and graph representation) independently,
+keeping the computation cost of the graph representation hyperparameter
+tuning relatively low.

### 2021-04-13 architecture.tex
Remove a superfluous expectation index
Clarify how the expected precedence cost is computed

@@
 that ensures the commensurability of precedence costs across signature sizes.
-More precisely, normalizing by $Z_n$ makes the expected value of the precedence cost
-independent of the signature size $n$:
+More precisely, normalizing by $Z_n$ makes the expected value of the precedence cost on a given problem
+independent of the problem's signature size $n$,
+provided the expected symbol cost $\mathbb{E}_i [c(i)]$ does not depend on $n$:
 \begin{multline*}
@@
 = \mathbb{E}_\pi \SquareBracket{Z_n \sum_{i=1}^n i \cdot c(\pi(i))}
-= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_{\pi, i} [c(\pi(i))] \\
+= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_\pi [c(\pi(i))] \\
 = Z_n \Parentheses{\sum_{i=1}^n i} \mathbb{E}_i [c(i)]

### 2021-04-14 architecture.tex
Indent a paragraph following an equation
Add todos with some ideas regarding precedence cost

@@
 \end{equation*}
+\todo[inline,author=FB]{
+To center the precedence cost at 0:
+
+Indexing from 0:
+$C(\pi) = \frac{1}{n} \sum_{i=0}^{n-1} c(\pi(i)) \cdot (\frac{2i}{n-1} - 1)$
+
+Indexing from 1:
+$C(\pi) = \frac{1}{n} \sum_{i=1}^{n} c(\pi(i)) \cdot (\frac{2(i-1)}{n-1} - 1)$
+}
+
 $Z_n = \frac{2}{n(n+1)}$ is a normalization factor
@@
 \end{multline*}
+\todo[author=FB]{Discuss variance of the precedence cost in addition to the expected value.}
 \todo[inline,author=R2]{In the equations showing that the expected value of the precedence cost is independent of the size of the signature, there is a (minor) problem in the second line: the i occurring in $E_i[c(i)]$ is not defined and probably unneeded if, as hinted by the equations, the expected value of each symbol is the same (which should also be stated somewhere).}

### 2021-04-14 main.tex
Clean up the acknowledgements
Follow the recommendation from Hanka's email from 2021-04-14.

@@
 
-\todo{MS: zvazit, jestli nerozepsat zvlast Martin, zvlast Filip.
-Pripadne se zeptat Hanky, jestli bychom nemeli nejak vypichnout
-jen GACR.}
-
 This work was supported by
-the Czech Science Foundation project 20-06390Y,
+the Czech Science Foundation project no.~20-06390Y (JUNIOR grant),
 the project RICAIP no. 857306 under the EU-H2020 programme,
 and
-the Grant Agency of the Czech Technical University in Prague, grant\\
+the Grant Agency of the Czech Technical University in Prague, grant
 no.~SGS20/215/OHK3/3T/37.

### 2021-04-14 main.tex
Use a non-breaking space after "no."

@@
 the Czech Science Foundation project no.~20-06390Y (JUNIOR grant),
-the project RICAIP no. 857306 under the EU-H2020 programme,
+the project RICAIP no.~857306 under the EU-H2020 programme,
 and

### 2021-04-19 architecture.tex
Remove a superfluous empty line
Move figure captions under the figures
> Figures are [...] to have a caption which should always be positioned
under the figures
ftp://ftp.springernature.com/cs-proceeding/svproc/guidelines/Springer_Instructions_for_Authors_of_Proceedings_CS.pdf
Remove a superfluous period at the end of a figure caption
> Captions that do not constitute a full sentence, do not have a period.
ftp://ftp.springernature.com/cs-proceeding/svproc/guidelines/Springer_Instructions_for_Authors_of_Proceedings_CS.pdf
Resolve most of the minor comments from review 2

@@
 \begin{figure}[h]
-\caption{Recommender architecture overview.
-When recommending a precedence, the input is problem $P$ and the output is precedence $\pi^*$.
-When training, the input is problem $P$ and precedences $\pi$ and $\rho$,
-and the output is the loss value.
-The trainable modules and the edges along which the loss gradient is propagated are emphasized by bold lines.}
-\label{fig:architecture}
 \centering
@@
 
+\caption{Recommender architecture overview.
+When recommending a precedence, the input is problem $P$ and the output is precedence $\pi^*$.
+When training, the input is problem $P$ and precedences $\pi$ and $\rho$,
+and the output is the loss value.
+The trainable modules and the edges along which the loss gradient is propagated are emphasized by bold lines.}
+\label{fig:architecture}
 \end{figure}
@@
 \begin{figure}[h]
-\caption{\gls{cnf} graph schema}
-\label{fig:CnfSchema}
 \centering
-
 \digraph[scale=0.5]{CnfSchema}{
@@
 
+\caption{\gls{cnf} graph schema}
+\label{fig:CnfSchema}
 \end{figure}
@@
 \begin{figure}[h]
-\caption{Graph representation of the \gls{cnf} formula $a=b \wedge f(a,b) \neq f(b,b)$.}
-\label{fig:GcnExample}
 \centering
@@
 }
+\caption{Graph representation of the \gls{cnf} formula $a=b \wedge f(a,b) \neq f(b,b)$}
+\label{fig:GcnExample}
 \end{figure}
@@
 Each symbol node has a feature vector with two bits of data:
-whether the symbol was introduced into the problem during preprocessing (most notably clausification),
+whether the symbol was introduced into the problem during preprocessing (most notably during clausification),
 and whether the symbol appears in a conjecture clause.
@@
 \begin{lemma}
-Precedence cost $C$ is minimized by any precedence that sorts the symbols by their costs in non-increasing order:
+The precedence cost $C$ is minimized by any precedence that sorts the symbols by their costs in non-increasing order:
 $$
@@
 $$
-where $\argsort^-(x)$ is the set of all permutations $\pi$
+where
+$\argmin_\rho C(\rho)$ is the set of all precedences that minimize precedence cost $C$ for a given symbol cost $c$, and
+%$\argmin_\rho C(\rho) = \{\rho \in Prec(n) | \forall \pi \in Prec(n) . C(\rho) \leq C(\pi)\}$, and
+$\argsort^-(x)$ is the set of all permutations $\pi$
 that sort vector $x$ in non-increasing order ($x_{\pi(1)} \geq x_{\pi(2)} \geq \ldots \geq x_{\pi(n)}$).

### 2021-04-19 evaluation.tex
Add a comment with some data about the duration of the training
Resolve most of the minor comments from review 2

@@
 
-To ensure the efficiency of the sampling, we interpreted the process as an instance of Bernoulli multi-armed bandit problem \cite{Sutton1998},
+To ensure the efficiency of the sampling, we interpreted the process as an instance of the Bernoulli multi-armed bandit problem \cite{Sutton1998},
 with the reward of a trial being 1 in case an example is produced, and 0 otherwise.
@@
 The symbol cost model was trained using the Adam optimizer \cite{Kingma2014}.
-Learning rate started at \num{1.28e-3}
+The learning rate started at \num{1.28e-3}
 and was halved each time the loss on $\ProblemsTrain$ stagnated for 10 consecutive epochs.
@@
 For each problem $P \in \ProblemsVal$,
-a predicate and a function precedence
-was generated by the respective trained recommender,
+a predicate and a function precedences
+were generated by the respective trained recommender,
 and \Vampire{} was run using these precedences
@@
 the preprocessing of a single problem
-takes at most at most \num[round-mode=places,round-precision=2]{1.262744486} seconds
+takes at most \num[round-mode=places,round-precision=2]{1.262744486} seconds
 for \SI{80}{\percent} of the problems
@@
 Since the predicate precedence recommender was trained against randomly distributed function precedences,
-it is expected to perform well irrespective of the function precedence heuristic it is combined with.
+it is expected to perform well irrespective of the function precedence heuristic it is combined with, and conversely.
 Combining the trained recommenders for predicate and function precedences manifested better performance
@@
 Moreover, we confirmed the conjecture that using a \gls{gnn} may perform even better \cite{DBLP:conf/cade/Bartek020}.
+
+% The following figures probably exclude the graphification because it is cached.
+
+% Generating questions for predicate precedence recommender:
+% - Data: sftp://cluster.ciirc.cvut.cz/home/bartefil/git/vampire-ml/logs/train/20210108-161206
+% - Time to generate 1M questions: 1d 18h (1318k attempts)
+
+% Predicate recommender training: VML-540:
+% - Best epoch: 79
+% - Last epoch: 673
+% - Total time: 1d 21h
+% - Time to reach epoch 79: 3h 15m
+
+% Generating questions for function precedence recommender: VML-555:
+% - Time to generate 800k questions: 3d 16h (1 227 553 attempts)
+
+% Training of function precedence recommender: VML-672:
+% - Best epoch: 289
+% - Last epoch: 489
+% - Total time: 19h 32m
+% - Time to reach epoch 289: 11h 37m
 

### 2021-04-19 main.tex
Resolve R1 comment: Relate your work to ENIGMA

@@
 
-In \cite{Olsak2019} and \cite{Rawson2020}, the authors propose similar \gls{gnn} architectures to solve tasks on \gls{fol} problems.
+In \cite{Olsak2019}, \cite{Jakubuv2020} and \cite{Rawson2020}, the authors propose similar \gls{gnn} architectures to solve tasks on \gls{fol} problems.
 They use the \glspl{gnn} to solve classification tasks such as premise selection.
@@
 the main task it is evaluated on is the generation of useful precedences.
+% Jakubuv2020 uses the same architecture as Olsak2019.
+% Our GNN uses a different particular architecture than Olsak2019.
 
@@
 \todo{Related problem: Ranking. See Mohri etc.}
-
-\todo[inline,author=R1]{An obvious question is how is this work related to the work and methods
-used for Enigma?
-
-Although the paper related to the Enigma system by Jakubuv has been
-cited, it appears to not be referred to in the text. It should be referred and
-the reference list should be checked.
-}
 

### 2021-04-19 architecture.tex
Resolve a comment from R1: Symbol costs

@@
 In our precedence recommender,
-we use a \gls{gcn}-based symbol cost model $c$ in place of the simple symbol property,
-\todo[author=R1]{What exactly is the GCN-bases symbol cost? Is it the cost calculated by
-the model for each symbol, or are different copies of symbols in different occurrences given
-different costs?}
-and generate a precedence by sorting the symbols by their predicted costs.
+we sort the symbols by their costs $c$ produced by the \acrlong{nn} described in \cref{sec:gcn,sec:output}.
 An advantage of this scheme is that sorting is a fast operation.

### 2021-04-19 architecture.tex
Architecture overview diagram: Make the bold arrows thicker
to make them easily distinguishable.

Resolves a comment from R2.

@@
 Problem -> Graphifier -> g -> GCN;
-GCN -> SymbolEmbedding -> SymbolCostModel -> SymbolCost [style=bold];
+GCN -> SymbolEmbedding -> SymbolCostModel -> SymbolCost [penwidth=3];
 SymbolCost -> Sort;
@@
 rho -> LossFunction:ne;
-SymbolCost -> LossFunction [style=bold];
-LossFunction -> Loss [style=bold];
+SymbolCost -> LossFunction [penwidth=3];
+LossFunction -> Loss [penwidth=3];
 }
@@
 \todo{FB: Improve the diagram. Consider using tikz. See the disabled tikz figure in the source file.}
-\todo[author=R2]{The small bold arrows are quite difficult to distinguish from the small non-bold arrows.}
 

### 2021-04-19 architecture.tex
Make the problem graph and metagraph diagrams consistent and clear
Resolves a comment from R2.

@@
 predicate;
-atom;
-equality;
+atom [label="non-equality atom"];
+equality [label="equality atom"];
 %}
@@
 
-c0 -> t0 [label=" + "];
-c1 -> t1 [label=" &ndash; "];
+c0 -> t0 [label=" pos "];
+c1 -> t1 [label=" neg "];
 
@@
 
-ff [label="function|f", style=bold];
-fa [label="function|a", style=bold];
-fb [label="function|b", style=bold];
-tfab0 [label="argument|1", style=dotted];
-tfab1 [label="argument|2", style=dotted];
-tfbb0 [label="argument|1", style=dotted];
-tfbb1 [label="argument|2", style=dotted];
+ff [label="function|f"];
+fa [label="function|a"];
+fb [label="function|b"];
+tfab0 [label="argument|1"];
+tfab1 [label="argument|2"];
+tfbb0 [label="argument|1"];
+tfbb1 [label="argument|2"];
 t0 -> ta;
@@
 \end{figure}
-\todo[author=R2]{There are unneeded differences in the notations used in the two figures; for example, pos/neg vs +/-, equality vs equality atom, the various (and non-specified) types of boxes around the nodes in fig.
-3...}
 

### 2021-04-19 architecture.tex
Remove a resolved comment from R2: Expected symbol cost

@@
 \todo[author=FB]{Discuss variance of the precedence cost in addition to the expected value.}
-\todo[inline,author=R2]{In the equations showing that the expected value of the precedence cost is independent of the size of the signature, there is a (minor) problem in the second line: the i occurring in $E_i[c(i)]$ is not defined and probably unneeded if, as hinted by the equations, the expected value of each symbol is the same (which should also be stated somewhere).}
 

### 2021-04-19 architecture.tex
Resolve a R2 comment: "locally minimize"

@@
 This enables the use of gradient descent to find the values of the parameters of $c$
-that minimize the loss value.
-\todo[author=R2]{I expect that you mean "to *locally* minimize the loss value". If you do, the fix is simple (just add "locally"); if not, more explanations are needed.}
+that locally minimize the loss value.
 

### 2021-04-19 architecture.tex
Add a todo comment

@@
 \todo[author=R1]{Are there just so many nodes in the layer as the types of graph edges in Figure 2, or is each edge in the whole graph (a large set) represented by a collection of modules?}
+\todo[author=FB]{I propose we ignore this comment because I don't understand its point and I can't think of a straightforward way to improve the clarity of the relevant part of the paper.}
 The computation of the \gls{gcn} starts with assigning each node an initial embedding

### 2021-04-19 architecture.tex
Qualify properties used in common precedence heuristics as "syntactic"

@@
 
-The symbol precedence heuristics commonly used in the \glspl{atp} sort the symbols by some numeric property
+The symbol precedence heuristics commonly used in the \glspl{atp} sort the symbols by some numeric syntactic property
 that is inexpensive to compute,

### 2021-04-19 evaluation.tex
Add a comment with a note about parallelizing relaxation of UCB1
Describe bootstrapping of UCB1
Resolves a comment from R2.

@@
 The problems were sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
-In each iteration, the generator sampled the problem $P$ that maximized
+% FB: The parallelizing relaxation is not described in Auer2002. We have designed it ourselves.
+First, each problem was sampled once.
+In each subsequent iteration, the generator sampled the problem $P$ that maximized
 $\frac{s_P}{n_P} + \sqrt{\frac{2 \ln n}{n_P}}$,
-\todo[author=R2]{Regarding the sampling of problems, what happens when $n_P = 0$, i.e., a problem has not yet been sampled?
-Or do you start with trying each problem at least once before implementing UCB1?}
 where $n = \sum_{P \in \ProblemsTptp} n_P$ was the total number of tries on all problems.

### 2021-04-19 evaluation.tex
Explain UCB1 bootstrapping precisely

@@
 % FB: The parallelizing relaxation is not described in Auer2002. We have designed it ourselves.
-First, each problem was sampled once.
-In each subsequent iteration, the generator sampled the problem $P$ that maximized
-$\frac{s_P}{n_P} + \sqrt{\frac{2 \ln n}{n_P}}$,
-where $n = \sum_{P \in \ProblemsTptp} n_P$ was the total number of tries on all problems.
-The parallelizing relaxation means that the $s_P$ values were only updated once in \num{1000} iterations,
-allowing up to \num{2000} parallel solver executions.
-\todo{Explain in detail?}
-\todo[inline,author=FB]{We bootstrap with a per-problem lower bound on the final number of questions. The lower bound is a solution to the equation for $n_B$:
+First, the values of $n_P$ and $s_P$ for each problem $P$ were bootstrapped by sampling the problem a number of times equal to a lower bound on the final value of $n_P$ (at least 1).\footnote{The number of tries each problem was boostrapped with is
+$n_0 = \ceil{\frac{2 \log{N}}{\Parentheses{1 + \sqrt{\frac{2 \log{N} \card{\ProblemsTptp}}{N}}}^2}}$,
+where $N$ is the final number of examples to be generated.
+For example, if $N=1000000$ and $\card{\ProblemsTptp}=17053$, then $n_0 = 10$.}
+% FB: Note that the original UCB1 initially samples each object exactly once.
+% FB: More precisely, N can be any lower bound on the number of tries to be performed.
+\todo[inline,author=FB,disable]{We bootstrap with a per-problem lower bound on the final number of questions. The lower bound is a solution to the equation for $n_B$:
 
@@
 $$
-\sqrt{\frac{h \log n}{2 x}} < 1 + \sqrt{\frac{h \log n}{2 \frac{n}{|\ProblemsTptp|}}}
+\sqrt{\frac{h \log n}{2 n_B}} < 1 + \sqrt{\frac{h \log n}{2 \frac{n}{|\ProblemsTptp|}}}
+$$
+
+This leads to the following number of bootstrap samples:
+$$
+\ceil*{\frac{c}{2 \Parentheses*{1 + \sqrt{\frac{c |\ProblemsTptp|}{2 N}}}^2}}
+$$
+where $c = h \log{N}$, $N$ is the desired final number of samples (acting as a lower bound on the total number of tries), and $h$ is the Hoeffding exponent (UCB1 default: 4).
+
+Nicely written for $h=4$:
+$$
+\ceil*{\frac{2 \log{N}}{\Parentheses*{1 + \sqrt{\frac{4 \log{N} |\ProblemsTptp|}{2 N}}}^2}}
 $$
@@
 }
+In each subsequent iteration, the generator sampled the problem $P$ that maximized
+$\frac{s_P}{n_P} + \sqrt{\frac{2 \ln n}{n_P}}$,
+where $n = \sum_{P \in \ProblemsTptp} n_P$ was the total number of tries on all problems.
+The parallelizing relaxation means that the $s_P$ values were only updated once in \num{1000} iterations,
+allowing up to \num{2000} parallel solver executions.
+\todo{Explain in detail?}
 \todo[inline,author=R2]{To clarify the last paragraph of the page, that introduces concepts with which people outside of ML wouldn't be familiar with, I suggest to use columns to show that some sentences are definitions for the terms introduced in the previous sentences, in particular, "...

### 2021-04-19 evaluation.tex
Fix a typo: "boostrapped"

@@
 % FB: The parallelizing relaxation is not described in Auer2002. We have designed it ourselves.
-First, the values of $n_P$ and $s_P$ for each problem $P$ were bootstrapped by sampling the problem a number of times equal to a lower bound on the final value of $n_P$ (at least 1).\footnote{The number of tries each problem was boostrapped with is
+First, the values of $n_P$ and $s_P$ for each problem $P$ were bootstrapped by sampling the problem a number of times equal to a lower bound on the final value of $n_P$ (at least 1).\footnote{The number of tries each problem was bootstrapped with is
 $n_0 = \ceil{\frac{2 \log{N}}{\Parentheses{1 + \sqrt{\frac{2 \log{N} \card{\ProblemsTptp}}{N}}}^2}}$,

### 2021-04-19 evaluation.tex
Add some Oxford commas

@@
 Adaptive sampling balanced
-exploring problems that have been tried relatively scarcely and
+exploring problems that have been tried relatively scarcely, and
 exploiting problems that have yielded examples relatively often.
 For each problem $P \in \ProblemsTptp$,
-the generator kept track of the number of times the problem has been tried $n_P$
+the generator kept track of the number of times the problem has been tried $n_P$,
 and the number of examples generated from that problem $s_P$.

### 2021-04-19 evaluation.tex
Document the 20 % problems that did not preprocess in 1.26 s
Resolves a comment from R2.

@@
 for \SI{80}{\percent} of the problems
-by extrapolation from a sample of \num{1000} problems.
-\todo[author=R2]{What about the remaining 20\% that do not take at most 1.26 seconds? Do they all timeout?}
+by extrapolation from a sample of \num{1000} problems.\footnote{The remaining \SI{20}{\percent} of the problems either finished preprocessing within 5 seconds, or were omitted from preprocessing due to exceeding the node count limit.}
+% \num[round-mode=places,round-precision=2]{4.745481158}
+\todo[author=FB]{Is the footnote with maximum observed time worth the space?}
 % Analysis: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit?usp=sharing

### 2021-04-19 evaluation.tex
Correct the 80th percentile of preprocessing time
Does not influence the typeset version.

@@
 the preprocessing of a single problem
-takes at most \num[round-mode=places,round-precision=2]{1.262744486} seconds
+takes at most \num[round-mode=places,round-precision=2]{1.263048204} seconds
 for \SI{80}{\percent} of the problems

### 2021-04-19 evaluation.tex
Use past tense with preprocessing time experiment

@@
 the preprocessing of a single problem
-takes at most \num[round-mode=places,round-precision=2]{1.263048204} seconds
+took at most \num[round-mode=places,round-precision=2]{1.263048204} seconds
 for \SI{80}{\percent} of the problems

### 2021-04-19 conclusion.tex
Add todos based on reviews 1 and 2 (excluding Minor comments)
Improve the paragraph discussing KBO weights
Resolves a comment from R2.

@@
 The challenge is to extract these pattern to a human-understandable form.
+\todo[inline,author=R2]{[...] the analysis of the key patterns used by the trained recommender (only hinted at as a future work in the conclusion) would have been much more interesting in my opinion.}
 
-\gls{kbo}, that we choose in our experiments, is in addition to a symbol precedence
-also determined by symbol \emph{weights} (we kept these fixed to the default value 1 in this work).
-Learning to recommend also the symbol weights in addition to the precedences
+In addition to the symbol precedence,
+\gls{kbo} is determined by symbol \emph{weights}.
+In this work, we kept the symbol weights fixed to the value 1.
+Learning to recommend symbol weights in addition to the precedences
 represents an interesting avenue for future research.

### 2021-04-19 introduction.tex
Resolve parts of comments from R2

@@
 the unfailing completion \cite{Bachmair89completionwithout}, superposition is a powerful calculus with 
-a native support for equational reasoning. The calculus is parameterized by a simplification ordering on terms % and literals,
+native support for equational reasoning. The calculus is parameterized by a simplification ordering on terms % and literals,
 and uses it to constrain the applicability of inferences, with a significant impact on performance.

### 2021-04-19 preliminaries.tex
Resolve most of the minor comments from review 2
Resolve parts of comments from R2

@@
 As soon as the empty clause, denoted by $\square$, is inferred,
-the prover concludes that the premises entail the conjecture,
-the sequence of inferences taken constituting a proof.
+the prover concludes that the premises entail the conjecture.
+The sequence of inferences taken in the proof search constitutes a proof.
 In case the premises do not entail the conjecture,
@@
 because it is used in the most successful contemporary \gls{fol} \glspl{atp}.
-The inferences of superposition calculus are constrained by a \emph{\gls{sot}} \cite{DBLP:journals/logcom/BachmairG94}.
+The inferences of the superposition calculus are constrained by a \emph{\gls{sot}} \cite{DBLP:journals/logcom/BachmairG94}.
 

### 2021-04-19 evaluation.tex
Add some todo discussion to comparison with PAAR results

@@
 
-\todo[inline,author=R2]{In your PAAR paper [7], the experimental results show that your linear model is not as good as the baseline but it is no longer the case here.
+\todo[inline]{R2: In your PAAR paper [7], the experimental results show that your linear model is not as good as the baseline but it is no longer the case here.
 How do you explain this?
-If it was further improved after PAAR, it should be mentioned.}
+If it was further improved after PAAR, it should be mentioned.
+
+FB: I think this is because here we evaluate on a different distribution of problems, one that is possibly more similar to the training set.
+In the PAAR paper, the test problems were sampled from problems with at most 1024 predicates in TPTP v7.2.0 ($\frac{15751}{16748}$ = \SI{94.05}{\percent}).
+Here, the test problems are sampled from problems with at most 100k nodes ($\frac{7658}{8526}$ = \SI{89.82}{\percent}) in TPTP v7.4.0.
+Should I discuss this in this paper?
+It seems of relatively little interest.}
 

### 2021-04-19 preliminaries.tex
Unify two bib entries for the same Vampire paper
Resolves a comment from R2.

@@
 is reduced to proving that the axioms together with the negated conjecture entail a \emph{contradiction}.
-The most popular \gls{fol} \glspl{atp}, such as \Vampire{} \cite{10.1007/978-3-642-39799-8_1}, E \cite{Schulz2019}, or SPASS \cite{DBLP:conf/cade/WeidenbachDFKSW09},
+The most popular \gls{fol} \glspl{atp}, such as \Vampire{} \cite{DBLP:conf/cav/KovacsV13}, E \cite{Schulz2019}, or SPASS \cite{DBLP:conf/cade/WeidenbachDFKSW09},
 start the proof search by converting the input \gls{fol} formulas to an equisatisfiable representation in 

### 2021-04-20 conclusion.tex
conclusion typos

@@
+% !TEX root = main.tex
+
 We have described a system that extracts useful symbol precedences from the graph representations of \gls{cnf} problems.
@@
 despite their seemingly chaotic behaviour as perceived by a human observer.
-The challenge is to extract these pattern to a human-understandable form.
+The challenge is to extract these patterns to a human-understandable form.
 \todo[inline,author=R2]{[...] the analysis of the key patterns used by the trained recommender (only hinted at as a future work in the conclusion) would have been much more interesting in my opinion.}
@@
 while the current setup implicitly assumes that the effects are independent.
-Finally, higher training data efficiency could be achieved by considering all pairs of measured executions on a problem
+Finally, a higher training data efficiency could be achieved by considering all pairs of measured executions on a problem
 in one training batch.

### 2021-04-20 introduction.tex
minor

@@
 
-It is well known that giving the highest precedence to the predicate symbols introduced as names 
-during the Tseitin transformation % of the input formula 
-\cite{Tseitin1983} can immediately make saturation produce the exponential 
+It is well known that giving the highest precedence to the predicate symbols introduced as sub-formula names 
+during clausification \cite{DBLP:books/el/RV01/NonnengartW01}
+% during the Tseitin transformation % of the input formula \cite{Tseitin1983} 
+can immediately make saturation produce the exponential 
 set of clauses that the transformation is designed to avoid \cite{Reger2016}.
@@
 \Cref{sec:architecture} proposes a structure of the precedence recommender that can be trained on pairs of symbol precedences,
-as described in \cref{sec:training}.
+as described in \Cref{sec:training}.
 \Cref{sec:evaluation} summarizes and discusses experiments performed

### 2021-04-20 preliminaries.tex
what is a proof?
KBO and a precedence as a permutation

@@
 the prover concludes that the premises entail the conjecture.
-The sequence of inferences taken in the proof search constitutes a proof.
+The sequence of those inferences leading up from the input clauses $\mathit{Cl}$ to the discovered $\square$ constitutes a proof.
 In case the premises do not entail the conjecture,
@@
 is parameterized by symbol weights and a \emph{symbol precedence},
-a permutation of the non-logical symbols of the input problem.
+a permutation\footnote{
+The definition of KBO does not require the precedence to be total. 
+However, for the use in ATPs, the more symbols and thus also terms 
+we can compare, the better. % That is why we define a precedence as a permutation.
+} of the non-logical symbols of the input problem.
 In this work we focus on the task of finding a symbol precedence which

### 2021-04-20 architecture.tex
Use DeclarePairedDelimiter to declare paired delimiters
why number of iterations?

@@
 and produces a precedence $\pi^*$ over the symbols $\Sigma$ as the output.
-For the recommender to be useful, it needs to produce a precedence
-that is likely to yield a proof in as few iterations of the saturation loop as possible.
+For the recommender to be useful, it should produce a precedence
+that likely leads to a quick search for a proof. In this work,
+we use the number of iterations of the saturation loop as a % (reproducible)
+metric describing the effort required to find a proof.
 
@@
 h_d^{(l+1)} =
-\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (W_r^{(l)} h_s^{(l)} + b_r^{(l)})}
+\sum_{r \in \mathcal{R}} \sigma \Parentheses*{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (W_r^{(l)} h_s^{(l)} + b_r^{(l)})}
 $$
@@
 %h_i^{(l+1)} =
-%\mathrm{LayerNorm} \Parentheses{h_i^{(l)} + \sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in %\mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}}
+%\mathrm{LayerNorm} \Parentheses*{h_i^{(l)} + \sum_{r \in \mathcal{R}} \sigma \Parentheses*{\sum_{j \in %\mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}}
 %$$
@@
 \mathbb{E}_\pi [C(\pi)]
-= \mathbb{E}_\pi \SquareBracket{Z_n \sum_{i=1}^n i \cdot c(\pi(i))}
+= \mathbb{E}_\pi \SquareBracket*{Z_n \sum_{i=1}^n i \cdot c(\pi(i))}
 = Z_n \sum_{i=1}^n i \cdot \mathbb{E}_\pi [c(\pi(i))] \\
-= Z_n \Parentheses{\sum_{i=1}^n i} \mathbb{E}_i [c(i)]
+= Z_n \Parentheses*{\sum_{i=1}^n i} \mathbb{E}_i [c(i)]
 = \frac{2}{n(n+1)} \frac{n(n+1)}{2} \mathbb{E}_i [c(i)]

### 2021-04-21 introduction.tex
Correct a cref: do not capitalize in the middle of sentence
Partially reverts bb630515e3633ec4c7df6a5e6d67c6ac853876da

@@
 \Cref{sec:architecture} proposes a structure of the precedence recommender that can be trained on pairs of symbol precedences,
-as described in \Cref{sec:training}.
+as described in \cref{sec:training}.
 \Cref{sec:evaluation} summarizes and discusses experiments performed

### 2021-04-21 evaluation.tex
Specify figure placement with [ht] > [h]
Justification: https://tex.stackexchange.com/a/1527/202639
Correct an invalid reference: Vampire
Remove a todo we have decided to pass

@@
 
-The empirical evaluation was performed using a modified version of the \gls{atp} \Vampire{} 4.3.0 \cite{10.1007/978-3-642-39799-8_1}.
+The empirical evaluation was performed using a modified version of the \gls{atp} \Vampire{} 4.3.0 \cite{DBLP:conf/cav/KovacsV13}.
 \todo[author=R2]{the reference for Vampire ([20]) describes version 2.6 of Vampire and you are using version 4.3.
@@
 
-\begin{table*}[h]
+\begin{table*}[ht]
 \caption{
@@
 
-\todo[inline,author=R1]{Despite the clear improvement over baseline, the percentage gained does not appear
-to be too big. It is possible, that the potential effect of better orderings is not
-too high, regardless of the optimizations. Can you give some insights for this
-line of thought?
-}
-
 We verified that the linear predicate precedence heuristic

### 2021-04-21 evaluation.tex
Remove a resolved R2 comment: Fresh Vampire reference

@@
 The empirical evaluation was performed using a modified version of the \gls{atp} \Vampire{} 4.3.0 \cite{DBLP:conf/cav/KovacsV13}.
-\todo[author=R2]{the reference for Vampire ([20]) describes version 2.6 of Vampire and you are using version 4.3.
-If available, something more recent would give a better idea of the current capacities of Vampire.}
 The prover was used to generate the training data and to evaluate the trained precedence recommender.

### 2021-04-21 preliminaries.tex
Briefly document GCN in Preliminaries
Resolves a comment from R2

@@
 
-\todo[inline,author=R2]{Why present only the feedforward NN in sect.
-2.3 when you are using a GCN?
-You could at least include a paragraph about the main differences between these two models at the end of 2.3.
-Then 3.2 could focus on the aspects of GCN that are specific to this particular problem.}
+A \emph{\gls{gcn}} is a special case of feedforward \acrlong{nn}.
+The modules of a \gls{gcn} transform messages that are passed along the edges of a graph encoded in the input example.
+A particular architecture of a \gls{gcn} used prominently in this work is discussed in detail in \cref{sec:gcn}.

### 2021-04-21 evaluation.tex
Correct the verbatim Vampire option: use double hyphen

@@
 using the regular \gls{kbo} to break ties between atoms
-and to compare terms (using the \Vampire{} option \texttt{-literal\_comparison\_mode predicate}).\todo{MS: ted s vysvetlenim neni naskodu zminit i option name 
+and to compare terms (using the \Vampire{} option \texttt{-{}-literal\_comparison\_mode predicate}).\todo{MS: ted s vysvetlenim neni naskodu zminit i option name 
 ``Vampire'' se tim chlubi, ze to ma naimplementovane a my tim rikame, ze jsme si to neprogramovali sami.}

### 2021-04-21 evaluation.tex
Describe Vampire strategy configuration
Resolves a R2 comment

@@
 
-We run \Vampire{} with a time limit of 10 seconds.
+We run \Vampire{} with a fixed strategy\footnote{
+Saturation algorithm: discount,
+age-weight ratio: 1:10,
+AVATAR \cite{Voronkov2014}: disabled,
+literal comparison mode: predicate
+}
+and a time limit of 10 seconds.
 To increase the potential impact of predicate precedences,
@@
 ``Vampire'' se tim chlubi, ze to ma naimplementovane a my tim rikame, ze jsme si to neprogramovali sami.}
-\todo[inline,author=FB]{Describe the detailed configuration in an appendix and reference the appendix here.}
-\todo[inline,author=R2]{Did you fix the strategy and heuristics used by Vampire throughout the training and experiments or was it run in portfolio mode? What about AVATAR, was it activated?}
 

### 2021-04-21 architecture.tex
Specify figure placement with [ht] > [h]
Justification: https://tex.stackexchange.com/a/1527/202639
Small stylistic improvements

@@
 
-The precedence recommender is a system that takes
+A \emph{symbol precedence recommender} is a system that takes
 a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$ as the input,
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering
@@
 
-The graph representation has the following properties:
+The graph representation exhibits namely the following properties:
 \begin{itemize}
@@
 
-The symbol embeddings are output by a \gls{rgcn} \cite{Schlichtkrull2017},
+The symbol embeddings are output by a \emph{\gls{rgcn}} \cite{Schlichtkrull2017},
 which is a stack of \emph{graph convolutional layers}.

### 2021-04-21 preliminaries.tex
Small stylistic improvements

@@
 Since each of the modules is differentiable with respect to its inputs and trainable parameters,
-the gradient of the loss in the trainable parameters
-\todo{FB: Is this terminology correct?}
+the gradient of the loss with respect to all the trainable parameters of the neural network
 can be computed using the \emph{back-propagation} algorithm \cite{DBLP:books/daglib/0040158}.
 The trainable parameters are then updated by taking a small step
-against the gradient---in the direction that is expected to make the loss value smaller.
+against the gradient---in the direction that is expected to reduce the loss.
 An \emph{epoch} is a sequence of iterations that updates the trainable parameters

### 2021-04-21 introduction.tex
Update on Overleaf.

@@
 employ the superposition calculus \cite{DBLP:journals/logcom/BachmairG94,DBLP:books/el/RV01/NieuwenhuisR01} as their underlying inference system.
-Integrating flavors of resolution \cite{DBLP:books/el/RV01/BachmairG01}, paramodulation \cite{Robinson1983}, and 
+Integrating the flavors of resolution \cite{DBLP:books/el/RV01/BachmairG01}, paramodulation \cite{Robinson1983}, and 
 the unfailing completion \cite{Bachmair89completionwithout}, superposition is a powerful calculus with 
@@
 
-Both of the two main classes of simplification orderings used in practice,
+Both main classes of simplification orderings used in practice,
 the \acrlong*{kbo} \cite{Knuth1983}
@@
 % during the Tseitin transformation % of the input formula \cite{Tseitin1983} 
-can immediately make saturation produce the exponential 
+can immediately make the saturation produce the exponential 
 set of clauses that the transformation is designed to avoid \cite{Reger2016}.
-Also, certain orderings help to make superposition a decision procedure on certain fragments of first-order logic 
+Also, certain orderings help to make the superposition a decision procedure on certain fragments of first-order logic 
 (see, e.g., \cite{DBLP:conf/lics/GanzingerN99,DBLP:conf/cade/HustadtKS05}).
@@
 \todo[inline,author=FB]{Try to use the first page for something more flashy than exposure of saturation-based automated proving.
-Ideas: catchy puzzle-like example, abstract description of the crucial challenge etc.}
+Ideas: catchy puzzle-like example, abstract description of the crucial challenge, etc.}
 

### 2021-04-21 preliminaries.tex
Update on Overleaf.

@@
 \emph{\acrfull{cnf}} \cite{DBLP:books/el/RV01/NonnengartW01,Harrison2009}.
-We denote a problem in \gls{cnf} as $P = (\Sigma, \mathit{Cl})$,
+We denote the problem in \gls{cnf} as $P = (\Sigma, \mathit{Cl})$,
 % Handbook of AR, Chapter 3: signature $\Sigma = (P_\Sigma, F_\Sigma)$
@@
 \emph{symbols} in the problem called the \emph{signature},
-and $\mathit{Cl}$ is the set of the clauses of the problem (including the negated conjecture).
+and $\mathit{Cl}$ is the set of clauses of the problem (including the negated conjecture).
 
@@
 the proof search continues until
-the set of the inferred clauses is saturated with respect to the inference rules.
+the set of inferred clauses is saturated with respect to the inference rules.
 In the common setting of time-restricted proof search, a time limit may end the process prematurely.
 
-Since the space of the derivable clauses is typically very large,
+Since the space of derivable clauses is typically very large,
 the efficacy of the prover depends on the order in which the inferences are applied.
 The common saturation-based \glspl{atp} order the inferences
-by maintaining two classes of the inferred clauses: processed and unprocessed \cite{Schulz2019}.
+by maintaining two classes of inferred clauses: processed and unprocessed \cite{Schulz2019}.
 In each \emph{iteration of the saturation loop}, one clause (so-called \emph{given clause})
@@
 In each clause,
-either a negative literal or all the maximal literals are selected.
+either a negative literal or all maximal literals are selected.
 The maximality is evaluated
@@
 The definition of KBO does not require the precedence to be total. 
-However, for the use in ATPs, the more symbols and thus also terms 
+However, for use in ATPs, the more symbols and thus also terms 
 we can compare, the better. % That is why we define a precedence as a permutation.
 } of the non-logical symbols of the input problem.
-In this work we focus on the task of finding a symbol precedence which
+In this work, we focus on the task of finding a symbol precedence which
 leads to a good performance of an ATP
@@
 
-In a typical use case, the \acrlong{nn} is trained by \emph{gradient descent} on a \emph{training set} of \emph{examples}.
+In a typical scenario, the \acrlong{nn} is trained by \emph{gradient descent} on a \emph{training set} of \emph{examples}.
 % Note: In case of GCN, the example is actually a set of edge matrices.
@@
 The loss of a batch is typically computed as a weighted sum of the losses of the individual examples.
-Since each of the modules is differentiable with respect to its inputs and trainable parameters,
-the gradient of the loss with respect to all the trainable parameters of the neural network
+Since each of the modules is differentiable with respect to its input and trainable parameters,
+the gradient of the loss with respect to all trainable parameters of the neural network
 can be computed using the \emph{back-propagation} algorithm \cite{DBLP:books/daglib/0040158}.

### 2021-04-21 architecture.tex
Update on Overleaf.

@@
 
-The recommender consists of modules that perform specific subtasks,
+The recommender consists of modules that perform specific sub-tasks,
 each of which is described in detail in one of the following\iftoggle{LONG}{
@@
 Each node corresponds to one of the elements that constitute the \gls{cnf} formula,
-such as a clause, an atom or a predicate symbol.
+such as a clause, an atom, or a predicate symbol.
 Each such category of elements corresponds to one node type.
@@
 
-The graph representation exhibits namely the following properties:
+The graph representation exhibits, namely, the following properties:
 \begin{itemize}
@@
 \todo[author=R1]{Are there just so many nodes in the layer as the types of graph edges in Figure 2, or is each edge in the whole graph (a large set) represented by a collection of modules?}
-\todo[author=FB]{I propose we ignore this comment because I don't understand its point and I can't think of a straightforward way to improve the clarity of the relevant part of the paper.}
+\todo[author=FB]{I propose we ignore this comment because I do not understand its point and I cannot think of a straightforward way to improve the clarity of the relevant part of the paper.}
 The computation of the \gls{gcn} starts with assigning each node an initial embedding
@@
 
-Once all the messages are computed,
-they are aggregated at the destination nodes to form the new node embeddings.
+Once all messages are computed,
+they are aggregated at the destination nodes to form new node embeddings.
 Each node $d$ aggregates all the incoming messages of a given edge type $r$ by summation,
@@
 
-The following formula captures the complete update of embedding of node $d$ by layer $l$:
+The following formula captures the complete update of the embedding of node $d$ by layer $l$:
 $$
@@
 
-Let $\theta$ denote the vector of all the parameters of the whole \acrlong{nn} consisting of the \gls{gcn} and the output unit.
+Let $\theta$ denote the vector of all parameters of the whole \acrlong{nn} consisting of the \gls{gcn} and the output unit.
 Given an input problem $P$ with signature $\Sigma = (s_1, \ldots, s_n)$,
@@
 \end{multline*}
-\todo[author=FB]{Discuss variance of the precedence cost in addition to the expected value.}
+\todo[author=FB]{Discuss the variance of the precedence cost in addition to the expected value.}
 
@@
 
-It is easy to see that all the precedences that sort the symbol costs in a non-increasing order
+It is easy to see that all precedences that sort the symbol costs in a non-increasing order
 have the same precedence cost.
@@
 especially when a wide variety of input problems is covered.
-Approaching the task as binary classification of precedences
+Approaching the task as a binary classification of precedences
 seems possible, but it is not clear which precedences should be a priori
@@
 % Mohri2018: p. 239, chapter 10 Ranking
-by training a classifier to decide which of a \emph{pair} of precedences is better, based on their costs.
+by training a classifier to decide which of a \emph{pair} of precedences is better based on their costs.
 We train the classifier in a way that ensures that better precedences are assigned lower costs.
@@
 
-\Cref{fig:architecture} shows how the loss function is plugged into the recommender for the training.
+\Cref{fig:architecture} shows how the loss function is plugged into the recommender for training.

### 2021-04-21 conclusion.tex
Update on Overleaf.

@@
 We have described a system that extracts useful symbol precedences from the graph representations of \gls{cnf} problems.
-Comparison against a conventional symbol precedence heuristic shows that using a \gls{gcn}
+Comparison with a conventional symbol precedence heuristic shows that using a \gls{gcn}
 to consider the whole structure of the input problem is beneficial.
@@
 A manual analysis of the trained recommender could produce new insights into how the choice of the symbol precedence influences the proof search,
-which could in turn help designing new efficient precedence generating schemes.
-Indeed, a trained cost model summarizes the observed behaviours of the ATP on the random precedences
+which could in turn help design new efficient precedence generating schemes.
+Indeed, a trained cost model summarizes the observed behaviours of an ATP with random precedences
 and is able to discover patterns in them (as we know implicitly from its accuracy) 
 despite their seemingly chaotic behaviour as perceived by a human observer.
-The challenge is to extract these patterns to a human-understandable form.
+The challenge is to extract these patterns in a human-understandable form.
 \todo[inline,author=R2]{[...] the analysis of the key patterns used by the trained recommender (only hinted at as a future work in the conclusion) would have been much more interesting in my opinion.}
@@
 \gls{kbo} is determined by symbol \emph{weights}.
-In this work, we kept the symbol weights fixed to the value 1.
+In this work, we keep the symbol weights fixed to the value 1.
 Learning to recommend symbol weights in addition to the precedences
@@
 The same applies to the idea of learning to recommend 
-both the predicate and the function precedences using a single \gls{gcn}.
+both the predicate and function precedences using a single \gls{gcn}.
 The joint learning, although more complex to design, could 
 additionally discover interdependencies
-between the effects of the function precedence and predicate precedence on the proof search,
+between the effects of function precedence and predicate precedence on the proof search,
 while the current setup implicitly assumes that the effects are independent.

### 2021-04-21 evaluation.tex
Update on Overleaf.

@@
 
-All the experiments were run on a computer with
+All experiments were run on a computer with
 the CPU Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz}) and
@@
 %the Linux kernel 5.4.0-40-generic.
-\todo{FB: Add version of Python and notable packages, namely DGL and TensorFlow. 
+\todo{FB: Add the version of Python and notable packages, namely, DGL and TensorFlow.
 MS: Z tohohle bych vetsinu nebo vsechno prenesl do README na adrese vyse.
@@
 as the source of problems for training and evaluation of the recommender.
-We denote the set of all the problems available for training and evaluation as $\ProblemsTptp$ ($\card{\ProblemsTptp} = 17053$).
+We denote the set of all problems available for training and evaluation as $\ProblemsTptp$ ($\card{\ProblemsTptp} = 17053$).
 
@@
 contained in \acrshort{tptp}) and made sure that the predicate precedence recommender
-would not be able to rely on any specificities that would come from fixing function precedences in the training data.
+would not be able to rely on any specificity that would come from fixing function precedences in the training data.
 
@@
 and if the number of iterations of the saturation loop with $\PrecBetter$ was smaller than with $\PrecWorse$.
-\todo{FB: Use notation for saturation loop iterations if the notation was established earlier. 
+\todo{FB: Use the notation for saturation loop iterations if the notation was established earlier. 
 If failure is denoted by $\infty$, we can simply use $<$.}
@@
 The sampling continued until \num{1000000} examples were generated when training a predicate precedence recommender,
-or \num{800000} examples in case of a function precedence recommender.
+or \num{800000} examples in the case of a function precedence recommender.
 % sftp://cluster.ciirc.cvut.cz/home/bartefil/git/vampire-ml/out/20210108-generate-predicate/questions_generated
@@
 using the examples generated from $\ProblemsTrain$.
-To avoid redundant computations, all examples generated from a problem were processed in the same training batch.
-Thus, each training batch contained up to \num{128} problems and all the examples generated from these problems.
+To avoid redundant computations, all examples generated from any given problem were processed in the same training batch.
+Thus, each training batch contained up to \num{128} problems and all examples generated from these problems.
 The symbol cost model was trained using the Adam optimizer \cite{Kingma2014}.
@@
 where $s_P$ was the number of examples of problem $P$ in the training set.
-This ensured that each problem contributed to the training to the same degree irrespective of the relative numbers of examples.
+This ensured that each problem contributed to the training to the same degree irrespective of the relative number of examples.
 
@@
 \todo{FB: Add links to Neptune runs?}
-Since the predicate precedence recommender was trained against randomly distributed function precedences,
-it is expected to perform well irrespective of the function precedence heuristic it is combined with, and conversely.
+Since the predicate precedence recommender was trained with randomly distributed function precedences,
+it was expected to perform well irrespective of the function precedence heuristic it is combined with, and conversely.
 Combining the trained recommenders for predicate and function precedences manifested better performance

### 2021-04-22 architecture.tex
Remove some review comments we have decided to ignore

@@
 Each layer consists of a collection of differentiable modules---one module per edge type.
-\todo[author=R1]{Are there just so many nodes in the layer as the types of graph edges in Figure 2, or is each edge in the whole graph (a large set) represented by a collection of modules?}
-\todo[author=FB]{I propose we ignore this comment because I do not understand its point and I cannot think of a straightforward way to improve the clarity of the relevant part of the paper.}
 The computation of the \gls{gcn} starts with assigning each node an initial embedding

### 2021-04-22 architecture.tex
Modify a diagram to make it shorter

@@
 { rank = same;
-Problem [label="Problem P"];
 pi [label=<Precedence &pi;>];
@@
 
+Problem [label="Problem P"];
+
+{ rank = same;
 Graphifier [style=rounded, label="Graph constructor"];
@@
 SymbolCostModel [style=<rounded,bold>, label="Output layer"];
+}
+
 SymbolCost [label="Symbol costs"];
 
-{ rank = same;
 Sort [style=rounded, label="Sort"];
 LossFunction [style=rounded, label="Loss function"];
-}
 

### 2021-04-26 evaluation.tex
Explain the difference between PAAR and CADE measurements
Resolves a comment from R2

@@
 
-We verified that the linear predicate precedence heuristic
-trained in \cite{DBLP:conf/cade/Bartek020} outperforms the \texttt{frequency} heuristic.
-Moreover, we confirmed the conjecture that using a \gls{gnn} may perform even better \cite{DBLP:conf/cade/Bartek020}.
+We confirmed our earlier conjecture \cite{DBLP:conf/cade/Bartek020} that using a \gls{gnn}
+may outperform the ``simple'' linear predicate precedence heuristic
+trained in \cite{DBLP:conf/cade/Bartek020}.\footnote{The measurements presented in \cref{tab:results}
+are not directly comparable with those reported in \cite{DBLP:conf/cade/Bartek020}
+due to differences in the validation problem sets and the computation environments.}
 

### 2021-04-26 evaluation.tex
Split a long paragraph explaining UCB1
Resolves a comment from R2

@@
 with the reward of a trial being 1 in case an example is produced, and 0 otherwise.
+
 Adaptive sampling balanced
@@
 % FB: The parallelizing relaxation is not described in Auer2002. We have designed it ourselves.
+
 First, the values of $n_P$ and $s_P$ for each problem $P$ were bootstrapped by sampling the problem a number of times equal to a lower bound on the final value of $n_P$ (at least 1).\footnote{The number of tries each problem was bootstrapped with is
@@
 \todo{Explain in detail?}
-\todo[inline,author=R2]{To clarify the last paragraph of the page, that introduces concepts with which people outside of ML wouldn't be familiar with, I suggest to use columns to show that some sentences are definitions for the terms introduced in the previous sentences, in particular, "...
-and 0 otherwise.
-Adaptive sampling..." -> "...
-and 0 otherwise: Adaptive sampling..." and "...
-with a parallelizing relaxation.
-In each iteration..." -> "with a parallelizing relaxation: In each iteration..."}
 

### 2021-04-27 architecture.tex
Grammarly: Make small corrections (replacing words etc.)

@@
 The edges represent the (oriented) relations between the elements,
-for example the incidence relation between a clause and one of its (literals') atoms,
+for example, the incidence relation between a clause and one of its (literals') atoms,
 or the relation between an atom and its predicate symbol.
@@
 we define a precedence cost function $C$ using the symbol cost function $c$
-in a manner than ensures that minimizing $C$ corresponds to sorting the symbols by $c$.
+in a manner that ensures that minimizing $C$ corresponds to sorting the symbols by $c$.
 Finding a precedence that minimizes $C$ can then be done efficiently and precisely.
@@
 \todo{FB: Isn't the inclusion of $Z_n$ too confusing?}
-Thus, $C(\bar{\pi}) < C(\pi)$, which is contradicts the assumption that $\pi$ minimizes $C$.
+Thus, $C(\bar{\pi}) < C(\pi)$, which contradicts the assumption that $\pi$ minimizes $C$.
 

### 2021-04-27 evaluation.tex
Remove a R2 comment me and Martin agreed to ignore
Add comments with some missing data references into the result table
Grammarly: Make small corrections (replacing words etc.)

@@
 
-The examples were generated by iterative sampling of $\ProblemsTptp$.
+The examples were generated by an iterative sampling of $\ProblemsTptp$.
 In each iteration, a problem $P \in \ProblemsTptp$ was chosen and \Vampire{} was executed twice on $P$
-with two (uniformly) random predicate precedences and a common random function precedence.
+with two (uniformly) random predicate precedences and one common random function precedence.
 The ``background'' random function precedence served as additional noise (in addition to the variability 
@@
 Adaptive sampling balanced
-exploring problems that have been tried relatively scarcely, and
+exploring problems that have been tried relatively scarcely and
 exploiting problems that have yielded examples relatively often.
@@
 % tf.keras.callbacks.ReduceLROnPlateau(monitor='loss', factor=0.5, patience=10)
-\todo[author=R2]{Same comment as just above: "... Adam optimizer [15]. Learning rate..." -> "... Adam optimizer [15]: Learning rate..."}
 
@@
 we performed a final evaluation of the most promising intermediate trained model on the whole $\ProblemsVal$.
-The model that manifested the best estimated solver performance on a sample of \num{1000} validation problems
+The model that manifested the best solver performance on a sample of \num{1000} validation problems
 was taken as the most promising.
@@
 and finally orders the symbols by their costs to produce the precedence.
-To simplify the experiment, the time limit of 10 seconds was only imposed on the \Vampire{} run
-and excluded the time taken by the recommender to generate the precedence.
+To simplify the experiment, the time limit of 10 seconds was only imposed on the \Vampire{} run,
+excluding the time taken by the recommender to generate the precedence.
 When run with 2 threads,
@@
 Simple (predicate only) &
+% https://ui.neptune.ai/filipbartek/vampire-ml/e/VML-737
 \num{3827.2} &
@@
 % https://ui.neptune.ai/filipbartek/vampire-ml/e/VML-490
+% sftp://cluster.ciirc.cvut.cz/home/bartefil/git/vampire-ml/outputs/2021-02-04/17-17-38
 % /home/filip/projects/vampire-ml/vampire-ml/outputs/2021-02-09/12-13-43

### 2021-04-27 introduction.tex
Grammarly: Make small corrections (replacing words etc.)

@@
 set of clauses that the transformation is designed to avoid \cite{Reger2016}.
-Also, certain orderings help to make the superposition a decision procedure on certain fragments of first-order logic 
+Also, certain orderings help to make the superposition a decision procedure on specific fragments of first-order logic 
 (see, e.g., \cite{DBLP:conf/lics/GanzingerN99,DBLP:conf/cade/HustadtKS05}).
@@
 In this work, we propose a \acrlong{ml} system that learns to predict for an ATP
-whether one precedence is going to lead to a faster proof search on a given problem than another.
+whether one precedence will lead to a faster proof search on a given problem than another.
 Given a previously unseen problem, it can then be asked to recommend the best possible precedence for an ATP to run with.

### 2021-04-27 preliminaries.tex
Grammarly: Make small corrections (replacing words etc.)

@@
 The sequence of those inferences leading up from the input clauses $\mathit{Cl}$ to the discovered $\square$ constitutes a proof.
-In case the premises do not entail the conjecture,
+If the premises do not entail the conjecture,
 the proof search continues until
 the set of inferred clauses is saturated with respect to the inference rules.
-In the common setting of time-restricted proof search, a time limit may end the process prematurely.
+In the standard setting of time-restricted proof search, a time limit may end the process prematurely.
 
@@
 the efficacy of the prover depends on the order in which the inferences are applied.
-The common saturation-based \glspl{atp} order the inferences
+The standard saturation-based \glspl{atp} order the inferences
 by maintaining two classes of inferred clauses: processed and unprocessed \cite{Schulz2019}.
@@
 
-The \emph{superposition calculus} is of special interest
+The \emph{superposition calculus} is of particular interest
 because it is used in the most successful contemporary \gls{fol} \glspl{atp}.
@@
 
-The common modules include
+The standard modules include
 the \emph{fully connected layer}, which performs an affine transformation,
@@
 % Note: In case of GCN, the example is actually a set of edge matrices.
-In such setting, the network outputs a single numeric value called \emph{loss} when evaluated on a \emph{batch} of examples.
+In such a setting, the network outputs a single numeric value called \emph{loss} when evaluated on a \emph{batch} of examples.
 The loss of a batch is typically computed as a weighted sum of the losses of the individual examples.
@@
 The modules of a \gls{gcn} transform messages that are passed along the edges of a graph encoded in the input example.
-A particular architecture of a \gls{gcn} used prominently in this work is discussed in detail in \cref{sec:gcn}.
+A particular architecture of a \gls{gcn} used prominently in this work is discussed in \cref{sec:gcn}.

### 2021-04-27 conclusion.tex
behavior > behaviour
Use American English consistently.
As suggested by Grammarly.

@@
 which could in turn help design new efficient precedence generating schemes.
-Indeed, a trained cost model summarizes the observed behaviours of an ATP with random precedences
+Indeed, a trained cost model summarizes the observed behaviors of an ATP with random precedences
 and is able to discover patterns in them (as we know implicitly from its accuracy) 
-despite their seemingly chaotic behaviour as perceived by a human observer.
+despite their seemingly chaotic behavior as perceived by a human observer.
 The challenge is to extract these patterns in a human-understandable form.

### 2021-04-27 preliminaries.tex
Reword two paragraphs
following suggestions from Grammarly.

@@
 In each \emph{iteration of the saturation loop}, one clause (so-called \emph{given clause})
-is selected from the unprocessed set
-and all the inferences between the given clause and the processed clauses are performed.
-The resulting new clauses are added to the unprocessed set.
+is combined with all the processed clauses for inferences.
+The resulting new clauses and the given clause are added to the unprocessed set and the processed set, respectively.
 Finishing the proof in few iterations of the saturation loop is important
@@
 because it is used in the most successful contemporary \gls{fol} \glspl{atp}.
-The inferences of the superposition calculus are constrained by a \emph{\gls{sot}} \cite{DBLP:journals/logcom/BachmairG94}.
+A \emph{\gls{sot}} \cite{DBLP:journals/logcom/BachmairG94} constrains the inferences of the superposition calculus.
 

### 2021-04-27 evaluation.tex
Remove some resolved todos

@@
 
-\todo[inline]{R2: In your PAAR paper [7], the experimental results show that your linear model is not as good as the baseline but it is no longer the case here.
-How do you explain this?
-If it was further improved after PAAR, it should be mentioned.
-
-FB: I think this is because here we evaluate on a different distribution of problems, one that is possibly more similar to the training set.
-In the PAAR paper, the test problems were sampled from problems with at most 1024 predicates in TPTP v7.2.0 ($\frac{15751}{16748}$ = \SI{94.05}{\percent}).
-Here, the test problems are sampled from problems with at most 100k nodes ($\frac{7658}{8526}$ = \SI{89.82}{\percent}) in TPTP v7.4.0.
-Should I discuss this in this paper?
-It seems of relatively little interest.}
-
 The results show that the \gls{gcn}-based model outperformed the \texttt{frequency} heuristic by a significant margin.

### 2021-04-27 introduction.tex
Break some long lines in source
Remove long disabled text in Introduction

@@
 Integrating the flavors of resolution \cite{DBLP:books/el/RV01/BachmairG01}, paramodulation \cite{Robinson1983}, and 
-the unfailing completion \cite{Bachmair89completionwithout}, superposition is a powerful calculus with 
-native support for equational reasoning. The calculus is parameterized by a simplification ordering on terms % and literals,
+the unfailing completion \cite{Bachmair89completionwithout},
+superposition is a powerful calculus with
+native support for equational reasoning.
+The calculus is parameterized by a simplification ordering on terms % and literals,
 and uses it to constrain the applicability of inferences, with a significant impact on performance.
@@
 % -rewriting from \emph{large to small}
-
-\iffalse
-
-Choosing the next inference to apply is arguably the most important decision point in the state-of-the-art
-\todo{FB: Add "saturation-based"?}
-\glspl{atp} for \gls{fol}.
-Since the most popular \glspl{atp} use the superposition calculus with literal selection \cite{DBLP:journals/logcom/BachmairG94},
-the \gls{sot}, such as the \gls{kbo} \cite{Knuth1983},
-plays an important role in restricting the inferences and thus guiding the proof search.
-The \gls{kbo} is typically specified by a symbol precedence,
-that is a permutation of non-logical symbols of the input problem.
-Each of the commonly used precedence heuristics orders the symbols
-lexicographically according to a small number of simple
-\todo{FB: Is using the "simple" terminology from PAAR paper better than trying to find a better term?}
-symbol properties,
-such as the number of occurrences in the input problem,
-% vampire --symbol_precedence frequency
-the arity of the symbol, or
-% vampire --symbol_precedence arity
-%occurrence in the conjecture,
-% vampire --symbol_precedence_boost goal
-%number of occurrences in unit clauses, or
-% vampire --symbol_precedence_boost units
-whether or not the symbol was introduced in the process of Tseitin transformation \cite{Tseitin1983} or Skolemization \cite{Harrison2009}.
-\todo{FB: Is citing Harrison better than nothing?}
-% vampire --introduced_symbol_precedence top
-Given that each of the heuristics used in practice, up to our knowledge, fails on some problems,
-\todo{Mention that we tried already to find a good simple heuristic by ML.}
-the general task of
-finding a symbol precedence that guides the proof search efficiently on an arbitrary problem
-remains to be intriguing.
-This paper explores the possibility of tackling this task by training a neural network
-on the results of running the \gls{atp} \Vampire{} \cite{10.1007/978-3-642-39799-8_1} with randomly sampled precedences.
-\todo{Ensure that the first paragraph fits on the first page.}
-
-\todo[author=Filip,inline]{Consider an alternative approach: Start with an example problem, rewrite in two ways, describe how do state-of-the-art provers differentiate between these two ways (by symbol precedence), ...}
-
-\todo[inline,author=FB]{Try to use the first page for something more flashy than exposure of saturation-based automated proving.
-Ideas: catchy puzzle-like example, abstract description of the crucial challenge, etc.}
-
-Modern \gls{fol} \glspl{atp}, such as \Vampire{}, E or SPASS,
-solve \gls{fol} problems by iteratively applying the inference rules of superposition calculus.
-Literal selection and equation orienting are employed to limit the ... while preserving the refutation completeness.
-Both literal selection and equation orienting are determined by \gls{sot}.
-
-A \gls{fol} problem consists of \gls{fol} formulas divided into two categories:
-one or more premises and one conjecture.
-% We assume that \gls{fol} is expanded to FOL.
-% For this reason the article is "an".
-When presented with a \gls{fol} problem,
-a \definiendum{saturation-based} \gls{atp} negates the conjecture (as a first step of proof by contradiction)
-and converts all the formulas into an equisatisfiable set of clauses in \gls{cnf}.
-\todo[author=Filip]{Are there any saturation-based ATPs that don't use CNF?}
-The prover proceeds to iteratively infer new provable clauses
-until a contradiction, represented by the empty clause, is inferred,
-or until no new clauses can be inferred.
-A proof of the fact that the premises and the negated conjecture entail a contradiction
-constitutes a proof that the premises entail the conjecture.
-\todo[author=Filip]{Cite some source that explains refutation-based automated theorem proving. Perhaps Harris?}
-\todo[author=Martin]{prvni odstavec uvodu bych pro CADE publikum vynechal a zacal rovnou s druhym}
-
-The state-of-the-art \gls{fol} \glspl{atp},
-such as \Vampire{} \cite{10.1007/978-3-642-39799-8_1} and E \cite{Schulz2019},
-are saturation-based and
-infer new provable clauses by applying the rules of the \definiendum{superposition calculus}.
-\todo[author=Filip]{Cite some source that explains superposition calculus.}
-The inferences under superposition calculus are constrained by a \definiendum{simplification ordering on the terms}.
-\todo[author=Filip]{Do we mean terms in sensu stricto (applications of functions), or generalized terms (applications of functions and predicates)?}
-The two classes of simplification orderings commonly used in practice are
-\gls{lpo} \cite{Kamin1980} and \gls{kbo} \cite{Knuth1983}.
-In both classes the ordering is specified by a \definiendum{symbol precedence},
-\todo[author=Filip]{This may be an oversimplification: KBO is further parameterized by symbol weights.}
-which is a permutation of predicate and function symbols of the input problem.
-
-The typical approach to constructing a symbol precedence orders the symbols by a property
-that is relatively cheap and straightforward to compute,
-such as the frequency (the number of occurrences in the input problem) \cite{E-manual} or the arity.
-\todo[author=Filip]{Cite the original source of the arity heuristic.}
-The structure of the problem contains much information that is relevant for the choice of symbol precedence,
-but is completely ignored by the symbol properties that inform the symbol precedences.
-\todo[author=Filip]{Why do we believe this?}
-\todo[author=Martin]{Klicovou vetu ...
-by asi chtelo rozvest treba do celeho odstavce.
-Takhle vyzni dost krypticky a neni moc jasne, co se snazi vyjadrit: "The structure of the problem" neni predem vysvetleno.
-"completely ignored" - "ignored" trosku zavani nejakym agentem, pritom je zde predmetem neziva vec / abstraktum}
-
-This paper describes the architecture (\cref{sec:architecture}) and an empirical evaluation (\cref{sec:evaluation})
-of a symbol precedence heuristic based on a \gls{gcn} \cite{kipf2017semisupervised}
-and trained on proof attempts with random symbol precedences.
-The experiments presented in \cref{sec:evaluation} demonstrate an improvement of success rate by 20 \%
-compared to the state-of-the-art heuristic.
-\todo[author=Martin]{Poslednimyu ostaveci by taky asi jeste mohlo neco predhazet, aby to mohl shrnout: "the architecture" ma urcity clen, ale predtim zadna "architecture" jeste neni.
-"graph convolution network" taky vlastne zminujes poprve}
-
-% Filip: I decided not to follow the AWR structure in favor of Martin and CADE.
-
-Our contributions:
-\begin{itemize}
-\item Up to our knowledge, \cref{sec:architecture} constitutes the first attempt
-to propose good symbol precedences automatically using a non-linear transformation of the input problem structure.
-Specifically, we explore the possibility of using a \gls{gnn} to learn symbol representations conducive for creating good precedences.
-\item The experimental evaluation in \cref{sec:evaluation} proves practical feasibility of the proposed approach.
-\item Besides tackling the particular task of generating symbol precedences,
-the approach described in \cref{sec:architecture} may be of a more general interest
-for a researcher trying to apply statistical learning to produce arbitrarily long permutations
-that optimize a quantitative criterion.
-\todo{FB: Give examples of such tasks. How about constructive TSP?}
-\end{itemize}
-
-% \iffalse % AWR draft
-
-The performance of the state-of-the-art \acrfullpl{atp} is severely limited by some of the design decisions that constitute the provers' architecture.
-For example, the \frequency{} symbol precedence heuristic of the \acrfull{fol} \acrshort{atp} \Vampire{} is easily outperformed by the best of 10 random precedences.\cite{}
-The gap in performance suggests that a more elaborate precedence heuristic with a superior performance exists.
-% what is precedence heuristic?
-% Thesis statement
-Training a model from proof attempts with random precedences yields a heuristic that significantly outperforms the state-of-the-art heuristic.
-
-\fi

### 2021-04-27 abstract.tex
Resolve overfull lines
by small changes.

--- 2021-02-24 abstract.tex
@@
 
-State-of-the-art superposition-based theorem provers for \acrlong{fol}
+The state-of-the-art superposition-based theorem provers for first order logic
 rely on \glspl{sot} to constrain the applicability of inference rules,
@@
 The popular Knuth-Bendix simplification ordering is parameterized by 
-a \emph{symbol precedence}---a permutation of the predicate and function symbols
+\emph{symbol precedence}---a permutation of the predicate and function symbols
 of the input problem's signature.
-Thus, the choice of a precedence has an indirect yet often substantial impact
-on the amount of work required to successfully complete a proof search.
+Thus, the choice of precedence has an indirect yet often substantial impact
+on the amount of work required to complete a proof search successfully.
 

### 2021-04-27 evaluation.tex
Resolve overfull lines
by small changes.

@@
 
-Adaptive sampling balanced
+We employed adaptive sampling to balance
 exploring problems that have been tried relatively scarcely and

### 2021-04-27 main.tex
Correct formatting of clever references
Always capitalize.
Use "Sect." and "Sects." unless beginning a sentence.
Use package 'times' to shrink the text to less than 15 pages
Use a more parsimonous font.
Resolve overfull lines
by small changes.

@@
 
-\usepackage{cleveref}
+\usepackage[capitalise]{cleveref}
+\crefname{section}{Sect.}{Sects.}
+\Crefname{section}{Section}{Sections}
 
@@
 \setlength{\intextsep}{0.7\baselineskip plus 0.2\baselineskip minus 0.2\baselineskip} % between a float in text and text
+
+\usepackage{times}
 
@@
 
-This work was supported by
+This work was generously supported by
 the Czech Science Foundation project no.~20-06390Y (JUNIOR grant),

### 2021-04-27 main.tex
Remove appendix.tex (unused)
Move the content of section Related to a dedicated file

@@
 \label{sec:related}
-
-Our previous text \cite{DBLP:conf/cade/Bartek020} marked the initial investigation of applying techniques of \acrlong{ml}
-to generating good symbol precedences.
-The neural recommender presented here uses a \gls{gnn} to model symbol costs,
-while \cite{DBLP:conf/cade/Bartek020} used a linear combination of symbol features readily available in the \gls{atp} \Vampire{}.
-The \gls{gnn}-based approach yields more performant precedences at the cost of longer training and preprocessing time.
-
-In \cite{Olsak2019}, \cite{Jakubuv2020} and \cite{Rawson2020}, the authors propose similar \gls{gnn} architectures to solve tasks on \gls{fol} problems.
-They use the \glspl{gnn} to solve classification tasks such as premise selection.
-While our system is trained on a proxy classification task,
-the main task it is evaluated on is the generation of useful precedences.
-% Jakubuv2020 uses the same architecture as Olsak2019.
-% Our GNN uses a different particular architecture than Olsak2019.
-
-The problem of learning to rank objects represented by scores trainable by gradient descent was explored in \cite{Burges2005}.
-Our work can be seen to apply the approach of \cite{Burges2005} to rank permutations represented by weighted sums of symbol costs.
-\todo{Related problem: Ranking. See Mohri etc.}
-
-% Fast differentiable ranking (and probably other texts): They use the permutation scoring by weighted sum.
+\input{related}
 
@@
 
-%\appendix
-%\input{appendix}
-
 \end{document}

### 2021-04-27 related.tex
Move the content of section Related to a dedicated file

Our previous text \cite{DBLP:conf/cade/Bartek020} marked the initial investigation of applying techniques of \acrlong{ml}
to generating good symbol precedences.
The neural recommender presented here uses a \gls{gnn} to model symbol costs,
while \cite{DBLP:conf/cade/Bartek020} used a linear combination of symbol features readily available in the \gls{atp} \Vampire{}.
The \gls{gnn}-based approach yields more performant precedences at the cost of longer training and preprocessing time.

In \cite{Olsak2019}, \cite{Jakubuv2020} and \cite{Rawson2020}, the authors propose similar \gls{gnn} architectures to solve tasks on \gls{fol} problems.
They use the \glspl{gnn} to solve classification tasks such as premise selection.
While our system is trained on a proxy classification task,
the main task it is evaluated on is the generation of useful precedences.
% Jakubuv2020 uses the same architecture as Olsak2019.
% Our GNN uses a different particular architecture than Olsak2019.

The problem of learning to rank objects represented by scores trainable by gradient descent was explored in \cite{Burges2005}.
Our work can be seen to apply the approach of \cite{Burges2005} to rank permutations represented by weighted sums of symbol costs.
\todo{Related problem: Ranking. See Mohri etc.}

% Fast differentiable ranking (and probably other texts): They use the permutation scoring by weighted sum.

### 2021-04-28 abstract.tex
dash, but breakable or\-der

@@
 
-The state-of-the-art superposition-based theorem provers for first order logic
+The state-of-the-art superposition-based theorem provers for {first-or\-der} logic
 rely on \glspl{sot} to constrain the applicability of inference rules,

### 2021-04-28 architecture.tex
consistent cref

@@
 \begin{itemize}
-\item \Cref{sec:graphifier}: The graph constructor transforms the input \gls{cnf} problem into a problem graph.
-\item \Cref{sec:gcn}: The \gls{gcn} computes symbol embeddings from the problem graph.
-\item \Cref{sec:output}: The output layer extracts symbol costs from the symbol embeddings.
-\item \Cref{sec:sorting}: The final symbol precedence is obtained by sorting the symbols by their costs.
+\item \cref{sec:graphifier}: The graph constructor transforms the input \gls{cnf} problem into a problem graph.
+\item \cref{sec:gcn}: The \gls{gcn} computes symbol embeddings from the problem graph.
+\item \cref{sec:output}: The output layer extracts symbol costs from the symbol embeddings.
+\item \cref{sec:sorting}: The final symbol precedence is obtained by sorting the symbols by their costs.
 \end{itemize}
@@
 $\mathcal{R}$ denotes the set of all relations in the graph.
-\Cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.
-\Cref{fig:GcnExample} shows an example of a graph representation of a simple problem.
+\cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.
+\cref{fig:GcnExample} shows an example of a graph representation of a simple problem.
 
@@
 Given an input problem $P$ with signature $\Sigma = (s_1, \ldots, s_n)$,
-we denote the cost of symbol $s_i$ predicted by the \acrlong{nn} as $c(i, P; \theta)$.
+we denote the cost of symbol $s_i$ predicted by the network as $c(i, P; \theta)$.
 In the rest of this text,
@@
 \end{align*}
-The final inequality is because $k-l < 0$ and $c(\pi(l)) - c(\pi(k)) > 0$.
+The final inequality is due to $k-l < 0$ and $c(\pi(l)) - c(\pi(k)) > 0$.
 Clearly, $Z_n > 0$ for any $n \geq 0$.
@@
 have the same precedence cost.
-Since $\emptyset \neq \argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$,
+Since $\argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$,
 each of the precedences in $\argsort^- (c(1), \ldots, c(n))$ has the cost $\min_\rho C(\rho)$.
@@
 
-\Cref{fig:architecture} shows how the loss function is plugged into the recommender for training.
+\cref{fig:architecture} shows how the loss function is plugged into the recommender for training.

### 2021-04-28 introduction.tex
consistent cref

@@
 The rest of this paper is organized as follows.
-\Cref{sec:preliminaries} exposes the basic terminology used throughout the remaining sections.
-\Cref{sec:architecture} proposes a structure of the precedence recommender that can be trained on pairs of symbol precedences,
+\cref{sec:preliminaries} exposes the basic terminology used throughout the remaining sections.
+\cref{sec:architecture} proposes a structure of the precedence recommender that can be trained on pairs of symbol precedences,
 as described in \cref{sec:training}.
-\Cref{sec:evaluation} summarizes and discusses experiments performed
+\cref{sec:evaluation} summarizes and discusses experiments performed
 using an implementation of the precedence recommender.
-\Cref{sec:related} compares the system proposed in this work with notable related works.
-\Cref{sec:conclusion} concludes the investigation and outlines possible directions for future research.
+\cref{sec:related} compares the system proposed in this work with notable related works.
+\cref{sec:conclusion} concludes the investigation and outlines possible directions for future research.
 

### 2021-04-28 evaluation.tex
Add a todo comment
consistent cref
trochu lepsi popis strategies

@@
 We run \Vampire{} with a fixed strategy\footnote{
-Saturation algorithm: discount,
-age-weight ratio: 1:10,
+Saturation algorithm: DISCOUNT,
+age to weight ratio: 1:10,
 AVATAR \cite{Voronkov2014}: disabled,
-literal comparison mode: predicate
+literal comparison mode: predicate; all other options left at their default values.
 }
@@
 % FB: The parallelizing relaxation is not described in Auer2002. We have designed it ourselves.
+\todo[author=FB]{Use some standard batching scheme instead of custom "parallelizing relaxation".}
 
@@
 vztahnout k casu klauzifikace? Jako rict, ze to trva x-krat dyl nez jen klauzifikovat?}
-\Cref{tab:results} shows the results of the final evaluation.
+\cref{tab:results} shows the results of the final evaluation.
 

### 2021-04-28 abstract.tex
Use \acrlong{fol} in abstract and hyphenate the acronym definition

--- 2021-04-27 abstract.tex
@@
 
-The state-of-the-art superposition-based theorem provers for first order logic
+The state-of-the-art superposition-based theorem provers for \acrlong{fol}
 rely on \glspl{sot} to constrain the applicability of inference rules,

### 2021-04-28 architecture.tex
Avoid an overfull line in non-compressed version
at minimization of precedence cost.

@@
 have the same precedence cost.
-Since $\argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$,
+Since
+\iftoggle{COMPRESS}{$\argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$}{$\emptyset \neq \argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$},
 each of the precedences in $\argsort^- (c(1), \ldots, c(n))$ has the cost $\min_\rho C(\rho)$.

### 2021-04-28 evaluation.tex
Revert "consistent cref"
This reverts commit 4a035ede5ffc8e31b4d41461b8d1a5eee540508e.
Avoid an overfull line in non-compressed version

@@
 vztahnout k casu klauzifikace? Jako rict, ze to trva x-krat dyl nez jen klauzifikovat?}
-\cref{tab:results} shows the results of the final evaluation.
+\Cref{tab:results} shows the results of the final evaluation.
 
@@
 
-We confirmed our earlier conjecture \cite{DBLP:conf/cade/Bartek020} that using a \gls{gnn}
+We have confirmed our earlier conjecture \cite{DBLP:conf/cade/Bartek020} that using a \gls{gnn}
 may outperform the ``simple'' linear predicate precedence heuristic

### 2021-04-28 architecture.tex
Make the proof of Lemma 1 typeset well irrespective of font
The typesetting no longer depends on the toggle COMPRESS,
so that restoring the default font will not mess up the formatting.

--- 2021-04-28 architecture.tex
@@
 
-It is easy to see that all precedences that sort the symbol costs in a non-increasing order
-have the same precedence cost.
-Since $\argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$,
+To prove the other direction of the equality,
+first observe that all precedences $\pi$ that sort the symbol costs in a non-increasing order
+necessarily have the same precedence cost $C(\pi)$.
+Since
+$\emptyset \neq \argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$,
 each of the precedences in $\argsort^- (c(1), \ldots, c(n))$ has the cost $\min_\rho C(\rho)$.

### 2021-05-03 architecture.tex
Use only expandable glossary commands in section titles
as recommended by glossaries user manual.
Restore the LLNCS formatting of subsubsections

@@
 
-\subsection{Graph constructor: From \gls{cnf} to graphs}
+\subsection{\titlecap{Graph constructor: From \glsentryshort{cnf} to graphs}}
 \label{sec:graphifier}
@@
 
-\subsection{\Gls{gcn}: From graphs to symbol embeddings}
+\subsection{\titlecap{\glsentryshort{gcn}: From graphs to symbol embeddings}}
 \label{sec:gcn}
@@
 
-\subsection{Output layer: From symbol embeddings to symbol costs}
+\subsection{\titlecap{Output layer: From symbol embeddings to symbol costs}}
 \label{sec:output}
@@
 
-\subsection{Sort: From symbol costs to precedence}
+\subsection{\titlecap{Sort: From symbol costs to precedence}}
 \label{sec:sorting}
@@
 
-\section{Training procedure}
+\section{\titlecap{Training procedure}}
 \label{sec:training}
@@
 
-\subsection{Precedence cost}
+\subsection{\titlecap{Precedence cost}}
 
@@
 
-\subsection{Learning to rank precedences}
+\subsection{\titlecap{Learning to rank precedences}}
 \label{sec:ranking}
@@
 
-\subsubsection{Training data}
+\subsubsection{\titlecap{Training data}.}
 
@@
 
-\subsubsection{Loss function}
+\subsubsection{\titlecap{Loss function}.}
 

### 2021-05-14 architecture.tex
Paper: Move section Training to a dedicated source file

@@
 %orders the symbols with the lowest cost as the last, prioritizing them for early inferences.
-
-\section{\titlecap{Training procedure}}
-\label{sec:training}
-
-In \cref{sec:architecture} we described the structure of a recommender system that generates a symbol precedence for an arbitrary input problem.
-The efficacy of the recommender depends on the quality of the underlying symbol cost function $c$.
-In theory, the symbol cost function can assign the costs so that
-sorting the symbols by their costs yields an optimum precedence.
-This is because, at least in principle, all the information necessary 
-to determine the optimum precedence is present in the graph representation of the input problem
-thanks to the lossless property of the graph encoding.
-\todo{MS: Hlavne tady ale jakoby chybi druha pulky ty vety. Neco jako ``In practice, however, ...'' Nemyslis?} 
-Our approach to defining an appropriate symbol cost function is based on statistical learning
-from executions of an \gls{atp} on a set of problems with random precedences.
-
-To train a useful symbol cost function $c$,
-we define a precedence cost function $C$ using the symbol cost function $c$
-in a manner that ensures that minimizing $C$ corresponds to sorting the symbols by $c$.
-Finding a precedence that minimizes $C$ can then be done efficiently and precisely.
-We proceed to train $C$ on the proxy task of ranking the precedences.
-% We have:
-% Data allows us to tell whether pi < rho.
-% We need the symbols sorted by c be a good precedence.
-
-\subsection{\titlecap{Precedence cost}}
-
-%Sorting a vector $x$ of length $n$ in a non-increasing order corresponds to finding a permutation $\pi$ that minimizes
-%the sum of the components of $x$ weighted by their positions in $\pi$.
-%By defining the cost of a precedence as a measure that is minimized by sorting,
-%we obtain a practical notion that can ultimately be trained by gradient descent.
-
-We extend the notion of cost from symbols to precedences
-by taking the sum of the symbol costs
-weighted by their positions in the given precedence $\pi$:
-\todo[inline]{FB: Consider accessing elements $\pi$ as vector elements $\pi_i$ instead of $\pi(i)$.
-Keep in mind that $\inv{\pi}$ must be updated as well.
-The motivation for using $\pi(i)$ is that $\inv{\pi}(i)$ looks clearer than $\inv{\pi}_i$.
-How about using $(\inv{\pi})_i$?
-We may also omit the inversion completely.}
-\todo{FB: Consider using the terminology of RankNet: $C(\pi) = o_i$, $S(\pi, \rho) = o_{ij}$, $\loss = C_{ij}$}
-\begin{equation*} \label{eq:cost_model}
-C(\pi) = Z_n \sum_{i=1}^n i \cdot c(\pi(i))% We call the normalization factor Z_n to follow convention from Foundations of Machine Learning, p. 122.
-\end{equation*}
-\todo[inline,author=FB]{
-To center the precedence cost at 0:
-
-Indexing from 0:
-$C(\pi) = \frac{1}{n} \sum_{i=0}^{n-1} c(\pi(i)) \cdot (\frac{2i}{n-1} - 1)$
-
-Indexing from 1:
-$C(\pi) = \frac{1}{n} \sum_{i=1}^{n} c(\pi(i)) \cdot (\frac{2(i-1)}{n-1} - 1)$
-}
-
-$Z_n = \frac{2}{n(n+1)}$ is a normalization factor
-that ensures the commensurability of precedence costs across signature sizes.
-More precisely, normalizing by $Z_n$ makes the expected value of the precedence cost on a given problem
-independent of the problem's signature size $n$,
-provided the expected symbol cost $\mathbb{E}_i [c(i)]$ does not depend on $n$:
-\begin{multline*}
-\mathbb{E}_\pi [C(\pi)]
-= \mathbb{E}_\pi \SquareBracket*{Z_n \sum_{i=1}^n i \cdot c(\pi(i))}
-= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_\pi [c(\pi(i))] \\
-= Z_n \Parentheses*{\sum_{i=1}^n i} \mathbb{E}_i [c(i)]
-= \frac{2}{n(n+1)} \frac{n(n+1)}{2} \mathbb{E}_i [c(i)]
-= \mathbb{E}_i [c(i)]
-\end{multline*}
-\todo[author=FB]{Discuss the variance of the precedence cost in addition to the expected value.}
-
-When $C$ is defined in this way,
-the precedence produced by the recommender (see \cref{sec:sorting}) minimizes $C$.
-\todo{Marting == for the camera ready version ==
-Write here that there could be alternavi formulas to \eqref{eq:cost_model}
-and we pick this one as the arguably simplest, for the lack of a better choice.}
-
-\begin{lemma}
-The precedence cost $C$ is minimized by any precedence that sorts the symbols by their costs in non-increasing order:
-$$
-\argmin_\rho C(\rho) = \argsort^- (c(1), \ldots, c(n))
-$$
-where
-$\argmin_\rho C(\rho)$ is the set of all precedences that minimize precedence cost $C$ for a given symbol cost $c$, and
-%$\argmin_\rho C(\rho) = \{\rho \in Prec(n) | \forall \pi \in Prec(n) . C(\rho) \leq C(\pi)\}$, and
-$\argsort^-(x)$ is the set of all permutations $\pi$
-that sort vector $x$ in non-increasing order ($x_{\pi(1)} \geq x_{\pi(2)} \geq \ldots \geq x_{\pi(n)}$).
-\end{lemma}
-
-\begin{proof}
-We prove direction ``$\argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$'' by contradiction.
-Let $\pi$ minimize $C$ and let $\pi$ not sort the costs in non-increasing order.
-Then there exist $k < l$ such that $c(\pi(k)) < c(\pi(l))$.
-Let $\bar{\pi}$ be a precedence obtained from $\pi$ by swapping the elements $k$ and $l$.
-Then we obtain
-%$\bar{\pi} = (\pi(1), \ldots, \pi(k-1), \pi(l), \pi(k+1), \ldots, \pi(l-1), \pi(k), \pi(l+1), \ldots, \pi(n))$.
-\begin{align*}
-\frac{C(\bar{\pi}) - C(\pi)}{Z_n}
-&= kc(\bar{\pi}(k)) + lc(\bar{\pi}(l)) - kc(\pi(k)) - lc(\pi(l)) \\
-&= kc(\pi(l)) + lc(\pi(k)) - kc(\pi(k)) - lc(\pi(l)) \\
-&= k(c(\pi(l)) - c(\pi(k))) - l(c(\pi(l)) - c(\pi(k))) \\
-&= (k-l) (c(\pi(l)) - c(\pi(k))) \\
-&< 0
-\end{align*}
-The final inequality is due to $k-l < 0$ and $c(\pi(l)) - c(\pi(k)) > 0$.
-Clearly, $Z_n > 0$ for any $n \geq 0$.
-\todo{FB: Isn't the inclusion of $Z_n$ too confusing?}
-Thus, $C(\bar{\pi}) < C(\pi)$, which contradicts the assumption that $\pi$ minimizes $C$.
-
-To prove the other direction of the equality,
-first observe that all precedences $\pi$ that sort the symbol costs in a non-increasing order
-necessarily have the same precedence cost $C(\pi)$.
-Since
-$\emptyset \neq \argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$,
-each of the precedences in $\argsort^- (c(1), \ldots, c(n))$ has the cost $\min_\rho C(\rho)$.
-It follows that $\argsort^- (c(1), \ldots, c(n)) \subseteq \argmin_\rho C(\rho)$.
-\qed
-\end{proof}
-
-\todo[inline]{FB: Discuss that sorting would minimize even if we weighted by a strictly monotonous function other than identity.}
-
-\todo[inline]{FB: Why is the equality predicate always the first in the precedence?
-MS: Andrei Voronokov reasons. It's typically better in practice to postpone equational reasoning,
-so we want equalities to be generally small.}
-
-\subsection{\titlecap{Learning to rank precedences}}
-\label{sec:ranking}
-
-Our ultimate goal is to train the precedence cost function $C$ so that it is minimized by the best precedence,
-measuring the quality of a precedence by the number of iterations of the saturation loop taken to solve the problem.
-
-Approaching this task directly, as a regression problem,
-runs into the difficulty of establishing sensible target cost values for the precedences in the training dataset,
-especially when a wide variety of input problems is covered.
-Approaching the task as a binary classification of precedences
-seems possible, but it is not clear which precedences should be a priori
-labeled as positive and which as negative, to give a guarantee
-that a precedence minimizing the precedence cost (i.e. the one obtained by sorting)
-would be among the best in any good sense.
-\todo{FB: I think we could ensure that the precedence that minimizes $C$ is relatively good, for example the best of the observed.
-I hope that ranking generalizes better to unseen precedences, but I am not sure whether it does and I haven't done an experiment to confirm that.}
-% such as learning to detect the precedences that yield a successful proof search within the allocated time.
-
-We cast the task as an instance of score-based ranking problem \cite{Mohri2018,Burges2005}
-% Mohri2018: p. 239, chapter 10 Ranking
-by training a classifier to decide which of a \emph{pair} of precedences is better based on their costs.
-We train the classifier in a way that ensures that better precedences are assigned lower costs.
-The motivation for learning to order pairs of precedences
-is that it allows learning on easy problems,
-and that it may allow the system to generalize to precedences that are better than any of those seen during training.
-\todo{FB: We should test this hypothesis by training on one problem in isolation.}
-\todo[inline]{MS: ta druha myslenka, o ktere jsem mluvil pred obedem, se deje nekde v tomhle odstavci.
-Jasne je, ze chceme vypichnout uceni ze dvojic precedenci jako jeden z klicovych napadu. Trochu min jasne je, proc by teda dvojice mely byt dobre.
-Ja mel pocit, ze kdyz jsme se vloni snazili na tenhle problem napasovat regresi, 
-pusobilo ``neprirozene'' vnucovat modelu konkretni cisla z vampiru. Jasne, nejak to resila normalizace
-(a muselo se davat pozor aby cisla davala smysl nejen napric problemy (jeden resi vsechno rychle, jiny obcas neresi -- penalizace)
-ale i kvuli ruznym velikostem signatury. Coz teda tady mame porad.) ale porad tam bylo to, ze nejak z vnejsku
-modelu narizujeme, na ktere hodnoty ma cilit.
-My tady ale vime, ze nam na konkretnich hodnotach sybol costu nezalezi, 
-a ze ani nemusi byt rozumne porovnavatelne mezi problemy,
-jediny, co je dulezity, je, aby setridena permutace byla ta (to the best of model's knowledge) nejlepsi.
-Takze ja bych shrnul, ze s dvojicema obchazime nutnost stanovovat konkretni target values pro regresi (``problem volby spolecnych jednotek velicin''?)
-a zaroven rafinovane menime ulohu z regresivni na classifikacni.\\
-FB: Regrese $C$ neni jedina alternativa.
-Mohli bychom klasifikovat jednotlive precedence (viz text).
-Mohli bychom relaxovat pozadavek, ze setridena permutace je nejlepsi; stacila by "dost dobra".
-Zkusil jsem nejak vyargumentovat, proc je klasifikace dvojic lepsi nez klasifikace jednotlivych precedenci.}
-
-\todo{Intuice: snazime se nastavit costy tak, aby co nejvic dvojic dopadlo spravne.}
-\todo{Some pairs of precedences are not informative. We hope that the non-systematic examples will cancel each other out.}
-
-\todo[inline]{MS: Tady je asi hlavni ``dira'' ve vysvetlovani...
-Na to, abys vzal symbol costy a zavolal sort nepotrebujes definovat
-cost precedenci a neco o nem dokazovat.
-
-Nevim, jestli to nechces rict az pozdeji,
-nebot precedence cost opravdu potrebujem az pro uceni!
-
-Teda vlastne by mi nevadilo o tom mluvit zde, (az na to, ze rozcestnik drive rika
-``Sorting converts the symbol costs into a symbol precedence.
-It is only used in generating mode.'')
-
-ale to vyzneni, kde to vypada, ze to delame kvuli tomu sortu, je matouci.
-
-Predstavuju si odstavec, kde rikame, ze precedence cost je dulezity koncept,
-protoze ma jednak tu vlastnost, ze je minimalizovan sortenim
-ale druhak prirazuje cost i nesetridenym permutacim a tak ho muzem pouzit pri uceni.
-(Coz by splnoval i jiny vzorecek nez \eqref{eq:cost_model}), namely
-jina striktne monotonni funkce na pronasobeni nez to $i$ tam,
-ale berem proste tenhle, protoze neni jasne, proc by jiny mel byt lespi,
-a tenhle je nejjednodussi.)}
-
-\subsubsection{\titlecap{Training data}.}
-
-Each training example has the form $(P, \PrecBetter, \PrecWorse)$,
-where $P = (\Sigma, \mathit{Cl})$ is a problem
-and $\PrecBetter, \PrecWorse$ are precedences over $\Sigma$
-such that the prover using $\PrecBetter$ solves $P$ in fewer iterations of the saturation loop than with $\PrecWorse$,
-denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$.
-\todo{FB: Is this sufficient?}
-\todo{FB: Describe the distribution of problems and precedences.}
-
-\subsubsection{\titlecap{Loss function}.}
-
-Let $(P, \PrecBetter, \PrecWorse)$ be a training example ($\Better{\PrecBetter}{\PrecWorse}{P}$).
-The precedence cost classifies this example correctly if $C(\PrecBetter) < C(\PrecWorse)$,
-or alternatively $S(\PrecBetter, \PrecWorse) = C(\PrecWorse) - C(\PrecBetter) > 0$.
-% We have positive S score for correctly predicted examples.
-% The loss function transorms that into a loss value close to 0.
-We approach this problem as an instance of binary classification with the logistic loss \cite{Mohri2018},
-% p. 128
-a loss function routinely used in classification tasks in \acrlong{ml}:
-\todo{FB: Consider exposing the form with inverse precedences to single out the $c$ values and expose the $c$ gradient better.}
-\begin{multline*}
-\loss(P, \PrecBetter, \PrecWorse)
-= - \log \sigmoid S(\PrecBetter, \PrecWorse)
-= - \log \sigmoid (C(\PrecWorse) - C(\PrecBetter)) \\
-= - \log \sigmoid Z_n \sum_{i=1}^n i (c(\PrecWorse(i)) - c(\PrecBetter(i)))
-%= - \log \sigmoid Z_n \sum_{i=1}^n c(i) (\inv{\PrecWorse}(i) - \inv{\PrecBetter}(i))
-\end{multline*}
-% FB: Note: I have included the full expansion to make it visible how the loss depends on $c$.
-% To a skilled NN practitioner, it should now be obvious that the loss is differentiable w.r.t. $c$.
-
-Note that the classifier cannot simply train $S$ to output a positive number on all pairs of precedences
-because $S$ is defined as a difference of two precedence costs.
-Intuitively, by training on the example $(P, \PrecBetter, \PrecWorse)$
-we are pushing $C(\PrecBetter)$ down and $C(\PrecWorse)$ up.
-
-The loss function is clearly differentiable with respect to the symbol costs,
-and the symbol cost function $c$ is differentiable with respect to its trainable parameters.
-This enables the use of gradient descent to find the values of the parameters of $c$
-that locally minimize the loss value.
-
-\Cref{fig:architecture} shows how the loss function is plugged into the recommender for training.

### 2021-05-14 training.tex
Paper: Move section Training to a dedicated source file

In \cref{sec:architecture} we described the structure of a recommender system that generates a symbol precedence for an arbitrary input problem.
The efficacy of the recommender depends on the quality of the underlying symbol cost function $c$.
In theory, the symbol cost function can assign the costs so that
sorting the symbols by their costs yields an optimum precedence.
This is because, at least in principle, all the information necessary 
to determine the optimum precedence is present in the graph representation of the input problem
thanks to the lossless property of the graph encoding.
\todo{MS: Hlavne tady ale jakoby chybi druha pulky ty vety. Neco jako ``In practice, however, ...'' Nemyslis?} 
Our approach to defining an appropriate symbol cost function is based on statistical learning
from executions of an \gls{atp} on a set of problems with random precedences.

To train a useful symbol cost function $c$,
we define a precedence cost function $C$ using the symbol cost function $c$
in a manner that ensures that minimizing $C$ corresponds to sorting the symbols by $c$.
Finding a precedence that minimizes $C$ can then be done efficiently and precisely.
We proceed to train $C$ on the proxy task of ranking the precedences.
% We have:
% Data allows us to tell whether pi < rho.
% We need the symbols sorted by c be a good precedence.

\subsection{\titlecap{Precedence cost}}

%Sorting a vector $x$ of length $n$ in a non-increasing order corresponds to finding a permutation $\pi$ that minimizes
%the sum of the components of $x$ weighted by their positions in $\pi$.
%By defining the cost of a precedence as a measure that is minimized by sorting,
%we obtain a practical notion that can ultimately be trained by gradient descent.

We extend the notion of cost from symbols to precedences
by taking the sum of the symbol costs
weighted by their positions in the given precedence $\pi$:
\todo[inline]{FB: Consider accessing elements $\pi$ as vector elements $\pi_i$ instead of $\pi(i)$. Keep in mind that $\inv{\pi}$ must be updated as well. The motivation for using $\pi(i)$ is that $\inv{\pi}(i)$ looks clearer than $\inv{\pi}_i$. How about using $(\inv{\pi})_i$? We may also omit the inversion completely.}
\todo{FB: Consider using the terminology of RankNet: $C(\pi) = o_i$, $S(\pi, \rho) = o_{ij}$, $\loss = C_{ij}$}
\begin{equation*} \label{eq:cost_model}
C(\pi) = Z_n \sum_{i=1}^n i \cdot c(\pi(i))% We call the normalization factor Z_n to follow convention from Foundations of Machine Learning, p. 122.
\end{equation*}
\todo[inline,author=FB]{
To center the precedence cost at 0:

Indexing from 0:
$C(\pi) = \frac{1}{n} \sum_{i=0}^{n-1} c(\pi(i)) \cdot (\frac{2i}{n-1} - 1)$

Indexing from 1:
$C(\pi) = \frac{1}{n} \sum_{i=1}^{n} c(\pi(i)) \cdot (\frac{2(i-1)}{n-1} - 1)$
}

$Z_n = \frac{2}{n(n+1)}$ is a normalization factor
that ensures the commensurability of precedence costs across signature sizes.
More precisely, normalizing by $Z_n$ makes the expected value of the precedence cost on a given problem
independent of the problem's signature size $n$,
provided the expected symbol cost $\mathbb{E}_i [c(i)]$ does not depend on $n$:
\begin{multline*}
\mathbb{E}_\pi [C(\pi)]
= \mathbb{E}_\pi \SquareBracket*{Z_n \sum_{i=1}^n i \cdot c(\pi(i))}
= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_\pi [c(\pi(i))] \\
= Z_n \Parentheses*{\sum_{i=1}^n i} \mathbb{E}_i [c(i)]
= \frac{2}{n(n+1)} \frac{n(n+1)}{2} \mathbb{E}_i [c(i)]
= \mathbb{E}_i [c(i)]
\end{multline*}
\todo[author=FB]{Discuss the variance of the precedence cost in addition to the expected value.}

When $C$ is defined in this way,
the precedence produced by the recommender (see \cref{sec:sorting}) minimizes $C$.
\todo{Marting == for the camera ready version ==
Write here that there could be alternavi formulas to \eqref{eq:cost_model}
and we pick this one as the arguably simplest, for the lack of a better choice.}

\begin{lemma}
The precedence cost $C$ is minimized by any precedence that sorts the symbols by their costs in non-increasing order:
$$
\argmin_\rho C(\rho) = \argsort^- (c(1), \ldots, c(n))
$$
where
$\argmin_\rho C(\rho)$ is the set of all precedences that minimize precedence cost $C$ for a given symbol cost $c$, and
%$\argmin_\rho C(\rho) = \{\rho \in Prec(n) | \forall \pi \in Prec(n) . C(\rho) \leq C(\pi)\}$, and
$\argsort^-(x)$ is the set of all permutations $\pi$
that sort vector $x$ in non-increasing order ($x_{\pi(1)} \geq x_{\pi(2)} \geq \ldots \geq x_{\pi(n)}$).
\end{lemma}

\begin{proof}
We prove direction ``$\argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$'' by contradiction.
Let $\pi$ minimize $C$ and let $\pi$ not sort the costs in non-increasing order.
Then there exist $k < l$ such that $c(\pi(k)) < c(\pi(l))$.
Let $\bar{\pi}$ be a precedence obtained from $\pi$ by swapping the elements $k$ and $l$.
Then we obtain
%$\bar{\pi} = (\pi(1), \ldots, \pi(k-1), \pi(l), \pi(k+1), \ldots, \pi(l-1), \pi(k), \pi(l+1), \ldots, \pi(n))$.
\begin{align*}
\frac{C(\bar{\pi}) - C(\pi)}{Z_n}
&= kc(\bar{\pi}(k)) + lc(\bar{\pi}(l)) - kc(\pi(k)) - lc(\pi(l)) \\
&= kc(\pi(l)) + lc(\pi(k)) - kc(\pi(k)) - lc(\pi(l)) \\
&= k(c(\pi(l)) - c(\pi(k))) - l(c(\pi(l)) - c(\pi(k))) \\
&= (k-l) (c(\pi(l)) - c(\pi(k))) \\
&< 0
\end{align*}
The final inequality is due to $k-l < 0$ and $c(\pi(l)) - c(\pi(k)) > 0$.
Clearly, $Z_n > 0$ for any $n \geq 0$.
\todo{FB: Isn't the inclusion of $Z_n$ too confusing?}
Thus, $C(\bar{\pi}) < C(\pi)$, which contradicts the assumption that $\pi$ minimizes $C$.

To prove the other direction of the equality,
first observe that all precedences $\pi$ that sort the symbol costs in a non-increasing order
necessarily have the same precedence cost $C(\pi)$.
Since
$\emptyset \neq \argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$,
each of the precedences in $\argsort^- (c(1), \ldots, c(n))$ has the cost $\min_\rho C(\rho)$.
It follows that $\argsort^- (c(1), \ldots, c(n)) \subseteq \argmin_\rho C(\rho)$.
\qed
\end{proof}

\todo[inline]{FB: Discuss that sorting would minimize even if we weighted by a strictly monotonous function other than identity.}

\todo[inline]{FB: Why is the equality predicate always the first in the precedence?
MS: Andrei Voronokov reasons. It's typically better in practice to postpone equational reasoning,
so we want equalities to be generally small.}

\subsection{\titlecap{Learning to rank precedences}}
\label{sec:ranking}

Our ultimate goal is to train the precedence cost function $C$ so that it is minimized by the best precedence,
measuring the quality of a precedence by the number of iterations of the saturation loop taken to solve the problem.

Approaching this task directly, as a regression problem,
runs into the difficulty of establishing sensible target cost values for the precedences in the training dataset,
especially when a wide variety of input problems is covered.
Approaching the task as a binary classification of precedences
seems possible, but it is not clear which precedences should be a priori
labeled as positive and which as negative, to give a guarantee
that a precedence minimizing the precedence cost (i.e. the one obtained by sorting)
would be among the best in any good sense.
\todo{FB: I think we could ensure that the precedence that minimizes $C$ is relatively good, for example the best of the observed. I hope that ranking generalizes better to unseen precedences, but I am not sure whether it does and I haven't done an experiment to confirm that.}
% such as learning to detect the precedences that yield a successful proof search within the allocated time.

We cast the task as an instance of score-based ranking problem \cite{Mohri2018,Burges2005}
% Mohri2018: p. 239, chapter 10 Ranking
by training a classifier to decide which of a \emph{pair} of precedences is better based on their costs.
We train the classifier in a way that ensures that better precedences are assigned lower costs.
The motivation for learning to order pairs of precedences
is that it allows learning on easy problems,
and that it may allow the system to generalize to precedences that are better than any of those seen during training.
\todo{FB: We should test this hypothesis by training on one problem in isolation.}
\todo[inline]{MS: ta druha myslenka, o ktere jsem mluvil pred obedem, se deje nekde v tomhle odstavci.
Jasne je, ze chceme vypichnout uceni ze dvojic precedenci jako jeden z klicovych napadu. Trochu min jasne je, proc by teda dvojice mely byt dobre.
Ja mel pocit, ze kdyz jsme se vloni snazili na tenhle problem napasovat regresi, 
pusobilo ``neprirozene'' vnucovat modelu konkretni cisla z vampiru. Jasne, nejak to resila normalizace
(a muselo se davat pozor aby cisla davala smysl nejen napric problemy (jeden resi vsechno rychle, jiny obcas neresi -- penalizace)
ale i kvuli ruznym velikostem signatury. Coz teda tady mame porad.) ale porad tam bylo to, ze nejak z vnejsku
modelu narizujeme, na ktere hodnoty ma cilit.
My tady ale vime, ze nam na konkretnich hodnotach sybol costu nezalezi, 
a ze ani nemusi byt rozumne porovnavatelne mezi problemy,
jediny, co je dulezity, je, aby setridena permutace byla ta (to the best of model's knowledge) nejlepsi.
Takze ja bych shrnul, ze s dvojicema obchazime nutnost stanovovat konkretni target values pro regresi (``problem volby spolecnych jednotek velicin''?)
a zaroven rafinovane menime ulohu z regresivni na classifikacni.\\
FB: Regrese $C$ neni jedina alternativa. Mohli bychom klasifikovat jednotlive precedence (viz text). Mohli bychom relaxovat pozadavek, ze setridena permutace je nejlepsi; stacila by "dost dobra". Zkusil jsem nejak vyargumentovat, proc je klasifikace dvojic lepsi nez klasifikace jednotlivych precedenci.}

\todo{Intuice: snazime se nastavit costy tak, aby co nejvic dvojic dopadlo spravne.}
\todo{Some pairs of precedences are not informative. We hope that the non-systematic examples will cancel each other out.}

\todo[inline]{MS: Tady je asi hlavni ``dira'' ve vysvetlovani...
Na to, abys vzal symbol costy a zavolal sort nepotrebujes definovat
cost precedenci a neco o nem dokazovat.

Nevim, jestli to nechces rict az pozdeji,
nebot precedence cost opravdu potrebujem az pro uceni!

Teda vlastne by mi nevadilo o tom mluvit zde, (az na to, ze rozcestnik drive rika
``Sorting converts the symbol costs into a symbol precedence.
It is only used in generating mode.'')

ale to vyzneni, kde to vypada, ze to delame kvuli tomu sortu, je matouci.

Predstavuju si odstavec, kde rikame, ze precedence cost je dulezity koncept,
protoze ma jednak tu vlastnost, ze je minimalizovan sortenim
ale druhak prirazuje cost i nesetridenym permutacim a tak ho muzem pouzit pri uceni.
(Coz by splnoval i jiny vzorecek nez \eqref{eq:cost_model}), namely
jina striktne monotonni funkce na pronasobeni nez to $i$ tam,
ale berem proste tenhle, protoze neni jasne, proc by jiny mel byt lespi,
a tenhle je nejjednodussi.)}

\subsubsection{\titlecap{Training data}.}

Each training example has the form $(P, \PrecBetter, \PrecWorse)$,
where $P = (\Sigma, \mathit{Cl})$ is a problem
and $\PrecBetter, \PrecWorse$ are precedences over $\Sigma$
such that the prover using $\PrecBetter$ solves $P$ in fewer iterations of the saturation loop than with $\PrecWorse$,
denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$.
\todo{FB: Is this sufficient?}
\todo{FB: Describe the distribution of problems and precedences.}

\subsubsection{\titlecap{Loss function}.}

Let $(P, \PrecBetter, \PrecWorse)$ be a training example ($\Better{\PrecBetter}{\PrecWorse}{P}$).
The precedence cost classifies this example correctly if $C(\PrecBetter) < C(\PrecWorse)$,
or alternatively $S(\PrecBetter, \PrecWorse) = C(\PrecWorse) - C(\PrecBetter) > 0$.
% We have positive S score for correctly predicted examples.
% The loss function transorms that into a loss value close to 0.
We approach this problem as an instance of binary classification with the logistic loss \cite{Mohri2018},
% p. 128
a loss function routinely used in classification tasks in \acrlong{ml}:
\todo{FB: Consider exposing the form with inverse precedences to single out the $c$ values and expose the $c$ gradient better.}
\begin{multline*}
\loss(P, \PrecBetter, \PrecWorse)
= - \log \sigmoid S(\PrecBetter, \PrecWorse)
= - \log \sigmoid (C(\PrecWorse) - C(\PrecBetter)) \\
= - \log \sigmoid Z_n \sum_{i=1}^n i (c(\PrecWorse(i)) - c(\PrecBetter(i)))
%= - \log \sigmoid Z_n \sum_{i=1}^n c(i) (\inv{\PrecWorse}(i) - \inv{\PrecBetter}(i))
\end{multline*}
% FB: Note: I have included the full expansion to make it visible how the loss depends on $c$.
% To a skilled NN practitioner, it should now be obvious that the loss is differentiable w.r.t. $c$.

Note that the classifier cannot simply train $S$ to output a positive number on all pairs of precedences
because $S$ is defined as a difference of two precedence costs.
Intuitively, by training on the example $(P, \PrecBetter, \PrecWorse)$
we are pushing $C(\PrecBetter)$ down and $C(\PrecWorse)$ up.

The loss function is clearly differentiable with respect to the symbol costs,
and the symbol cost function $c$ is differentiable with respect to its trainable parameters.
This enables the use of gradient descent to find the values of the parameters of $c$
that locally minimize the loss value.

\Cref{fig:architecture} shows how the loss function is plugged into the recommender for training.
